### 2016-03-18 submission/manuscript.Rmd
Revise methods [summary statistics study 1]

---
title: "Ecological validity of detecting data fabrication in experimental studies."
author: "Chris HJ Hartgerink"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: word_document
csl: ../bibliography/apa.csl
bibliography: ../bibliography/library.bib
---
<!---

# Abstract
--placeholder--

# Introduction

Data fabrication is malicious to scientific knowledge, hence it is imperative to be able to detect it. An estimated 2% of all researchers admit to having fabricated data at least once, and 14% have said to have witnessed someone fabricate data [@fanelli2009]. In stark contrast to plagiarism, which has a similar admittance rate but double the witness rate [@pupovac2015], no systems are implemented during the editorial process to detect problematic data, although at least one journal is considering such a system (Miller 2015). Editors and reviewers hardly pay attention to potential problems with the data during the editor process either (Bornmann et al. 2008), which highlights the potential of automated detection systems.

Similar to how plagiarism scanners are implemented to detect plagiarism, statistical methods can be applied to detect potentially fabricated data. By extracting information from research papers, called content mining (Smith-Unna and Murray-Rust 2014), statistical analyses of the presented research results can be facilitated. Previous statistical content mining methods, extracting for example reported test results across 30,000 papers (Nuijten et al. 2015), indicate the feasibility of extracting statistical information from research papers in large quantities.

However helpful these technological advances are, the statistical methods applied to extracted data in order to detect potential data fabrication require thorough validation. More specifically, the statistical methods need to have a well-balanced trade-off between the false positive rate and the false negative rate. Considering the, presumably, low prevalence rate of data fabrication, false positive rates can have tremendous effects when applied at a large scale. For example, if we assume that 2% of the research papers is fabricated and we can detect it perfectly if it occurs, we would detect approximately 2.5 times more false positives than true positives. And this is if we assume the false positive rate is 5% and no higher.

How data is fabricated by researchers is not well-known and simulating the properties of statistical methods to detect data fabrication is therefore invalid. When the process is unknown, it is hardly feasible to properly approximate reality and draw valid conclusions. Moreover, it seems reasonable to state that there are many different ways to fabricate data and that these different data fabrication ‘styles’ can be combined. Even if certain fabrication processes were known, simulating ecologically valid processes would still be quite difficult.

Nonetheless, statistical methods to detect data fabrication have been developed based on theoretical principles, which help detect data fabrication in experiments. These methods are based on the tenet that humans are bad at fabricating results that originate from probabilistic processes. Outcome variables that are inspected in experiments are based on a sample which results in observations that are the result of a random variable, hence subject to probabilistic (i.e., stochastic) processes. The inadequacy of humans in generating such sequences is the consequence of mental heuristics. For example, most humans succumb to the gambler’s fallacy, estimating the probability of heads as more likely when we have thrown tails several times (Tversky and Kahneman 1974). Other fallacious heuristics include the local-representativeness heuristic (), .

Statistical methods to detect data fabrication have been successfully applied in ad hoc investigations, but their value in screening processes remains opaque. For example, Simonsohn’s variance of variances method (Simonsohn 2013) has been applied to the Smeesters and Sanna cases, but only after suspicions had already arisen. The value of applying such a method as a screening measure is hard to assess regardless of its previous successes in ad hoc investigations.

In this paper, we experimentally test the validity of a set of statistical methods to detect data fabrication, based on summary results (Study 1) or raw data (Study 2), and assess the optimal balance between decision criterion and detection accuracy. We apply the statistical methods to detect data fabrication to both (assumed) genuine data from the Many Labs experiments and fabricated datasets, which we collected in an experimental setting where researchers were invited to fabricate data according to a controlled set of hypotheses. Both experiments were approved by the Tilburg Ethics committee (EC-2015.50).
--->
# Study 1

To test the validity of statistical methods to detect data fabrication in summary results, we investigated summary results for four anchoring studies [@jacowitz1995]. We selected the anchoring effect because it is a well-known psychological phenomenon and data from the Many Labs were available for inclusion in our study. The unit of analysis for this study is the set of summary statistics for the four anchoring studies from one respondent. Respondent is defined as either one of the Many Labs locations, or a researcher who participated in fabricating results.

## Methods

The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States. Each of the four studies provided summary results for a two-factorial design, including a high- and low anchor condition and gender. These four anchoring studies were selected because quality data were available from the Many Labs project [@klein2014].

### Data collection.

Thirty-six genuine datasets were collected from the publicly available Many Labs project [@klein2014, osf.io/pqf9r]. The Many Labs (ML) project replicated several effects, including the anchoring effect, across thirty-six locations. ML replicated the anchoring effect with the four studies mentioned previously. Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine. For each of the thirty-six locations, means and standard deviations were collected for each of the four conditions in the four anchoring studies. In total, this yielded both `r 4*4` means per location and `r 4*4` variances per location. The raw data were cleaned according to the original analysis script from the ML project.

<!---
```{r}
# Insert the data collection from Many Labs in here (directly!)
```
--->

<!---
Replace thirty-six with actual number
--->

Thirty-six fabricated sets of summary results were collected for all four anchoring studies. We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS). Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995], for which summary results were fabricated. U.S. researchers were sampled to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies. WoS was searched on October 13, 2015. In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).

The full sample frame was digitally approached to participate in this study on March XX, 2016 (invitation: osf.io/XXXX). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-address saved at all). The researchers were fully informed that the study would require them to fabricate data and that we conducted this study to test the validity of statistical methods to detect data fabrication. Participants were also informed they could stop at any time without providing a reason. If they wanted, participants received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address. These email addresses were unlinked from email addresses upon completion of the study and sending out the gift cards.

Each respondent was instructed to fabricate summary statistics that fulfilled three hypotheses. That is, 4 (studies) × 2 (conditions) × 2 (sex) × 2 (mean or sd) = 32 statistics were fabricated. We instructed participants to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex. The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data that is used to test the detection of data fabrication.

In order to standardize the fabrication process to a minimal extent, we provided participants with a spreadsheet where the fabricated data had to be filled in. The fabricated data are checked against the provided hypotheses and the statistical test are provided instantaneously, given the fabricated means and standard deviations. Figure `r fig <- 1; fig` depicts an example of this spreadsheet. Respondents were required to copy-paste the yellow cells into Qualtrics, to provide a standardized way of reporting the means and standard deviations.

![spreadsheet](../figures/spreadsheet.png)

**Figure `r fig`.** Example of a filled in spreadsheet used in the fabrication process.

Upon completing the fabrication of the data, participants were debriefed. Several questions were asked about their statistical knowledge and approach to data fabrication, and they were reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike. The full set of questions from the study are available at osf.io/XXXX.

Participation was rewarded with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card. If the participant wanted to receive a compensation and contend for the bonus $50, he/she had to enter an email to receive the reward. These email addresses were unlinked from individual responses upon sending the gift cards. Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum).

### Data analysis.

We included two methods to test for data fabrication and we combined the results of these two tests. These statistical tests compute the probability that, given sampling theory, the current data or an even more unlikely set would be observed. As a result, this probability can be seen as a *p*-value for the null hypothesis that the data is genuine (i.e., P[data|genuine]).

First we apply the "variance of variances" method [@simonsohn2013]. This method tests whether the observed variances contain a reasonable amount of variation expected based on stochastic sampling processes. For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent. More technically, the method first estimates the observed variation of the standardized standard deviations. Second, the method simulates how much variation in the standardized standard deviations can be expected given the sample sizes, means and variances. This yields an estimate of the probability that the observed lack of variation in the variances would be observed, or even less. This is in fact a *p*-value that tests the hypothesis that the observed variances are genuine and originate from a stochastic sampling distribution, under a set of distributional assumptions.

Second, we apply the reversed Fisher method, which tests whether there is an excessive amount of high *p*-values. The default Fisher method [@fisher1925] tests whether a set of *p*-values deviates from uniformity, where smaller *p*-values occur more frequently than larger *p*-values (i.e., whether there is evidence for an effect). However, the reversed Fisher method tests whether a set of *p*-values deviates from uniformity in such a way that there are more large *p*-values than small ones. As such, it tests whether a theoretically infeasible distribution of *p*-values is presented in a study, which is overly consistent with the null hypothesis. The reversed Fisher method is computed as

$\chi^2_{2k}=-2\sum\ln(1-\frac{p_i-t}{1-t})$

where *t* is the lowerbound (i.e., threshold) of the *k* number of *p*-values taken into account. The resulting *p*-value indicates the probability that the observed nonsignificant *p*-values are actually from a genuine null distribution.

<!---
Something about reporting tendencies?
--->

Third, we combine the results of the "variance of variances" test and reversed Fisher method by testing for evidential value. To this end, we apply the default Fisher method. The Fisher method tests whether there is sufficient evidence for deviation from genuine data in the two separate tests and is computed as

$\chi^2_{2k}=-2\sum\ln(p_i)$

Given that this is a combination test, we expect this to be a more powerful test than the "variance of variances" method or the reversed Fisher method alone. The three respondents with the highest *p*-value contained the least evidential value for deviating from genuine data and received an additional $50 Amazon gift card. 
<!---
### Results.

# Study 2

To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment (Stroop 1935).

## Methods

### Data collection.

Twenty genuine datasets were collected from the Many Labs 3 project (Ebersole et al. ).

Twenty faked datasets were collected experimentally. We sampled 20 of 84 Dutch or Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015, which was indexed in Thomson Reuters’ Web of Science database. Dutch and Flemish researchers were selected to allow for potential follow-up on the way data was fabricated in a face-to-face interview. The period 2005-2015 was chosen to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email. Researchers who published on the Stroop task were selected to ensure their familiarity with the type of task for which data had to be fabricated. The database was searched on October 13, 2015 and 84 unique e-mails were extracted from 86 articles.

## Results

# Discussion

- Open data for further testing (see osf.io/xxxx)
- Ecological validity
--->

# References

### 2016-03-19 data/study_01_anchoring/compute_summary_stats.R
Update some summary stats computing

@@ -104,3 +104,40 @@ par(mfrow = c(2,1)); hist(gender_p_2, breaks = 10); hist(inter_p_2, breaks = 10)
 par(mfrow = c(2,1)); hist(gender_p_3, breaks = 10); hist(inter_p_3, breaks = 10)
 par(mfrow = c(2,1)); hist(gender_p_4, breaks = 10); hist(inter_p_4, breaks = 10)
 dev.off()
+
+chi2 <- -2*sum(log(inter_p_1))
+degr_f <- 2*length(inter_p_1)
+pval <- 1 - pchisq(-2*sum(log(inter_p_1)), df = 2*length(inter_p_1))
+sprintf('chi2(%s)=%s, p=%s', degr_f, chi2, pval)
+
+chi2 <- -2*sum(log(inter_p_2))
+degr_f <- 2*length(inter_p_2)
+pval <- 1 - pchisq(-2*sum(log(inter_p_2)), df = 2*length(inter_p_2))
+sprintf('chi2(%s)=%s, p=%s', degr_f, chi2, pval)
+
+chi2 <- -2*sum(log(inter_p_3))
+degr_f <- 2*length(inter_p_3)
+pval <- 1 - pchisq(-2*sum(log(inter_p_3)), df = 2*length(inter_p_3))
+sprintf('chi2(%s)=%s, p=%s', degr_f, chi2, pval)
+
+chi2 <- -2*sum(log(inter_p_4))
+degr_f <- 2*length(inter_p_4)
+pval <- 1 - pchisq(-2*sum(log(inter_p_4)), df = 2*length(inter_p_4))
+sprintf('chi2(%s)=%s, p=%s', degr_f, chi2, pval)
+
+chi2 <- -2*sum(log(c(inter_p_1,
+                     inter_p_2,
+                     inter_p_3,
+                     inter_p_4)))
+degr_f <- 2*length(c(inter_p_1,
+                     inter_p_2,
+                     inter_p_3,
+                     inter_p_4))
+pval <- 1 - pchisq(-2*sum(log(c(inter_p_1,
+                        inter_p_2,
+                        inter_p_3,
+                        inter_p_4))), df = 2*(length(inter_p_1) +
+                                                   length(inter_p_2) +
+                                                   length(inter_p_3) +
+                                                   length(inter_p_4)))
+sprintf('chi2(%s)=%s, p=%s', degr_f, chi2, pval)

### 2016-04-18 submission/manuscript.Rmd
Update files

@@
 
-To test the validity of statistical methods to detect data fabrication in summary results, we investigated summary results for four anchoring studies [@jacowitz1995].
-We selected the anchoring effect because it is a well-known psychological phenomenon and data from the Many Labs were available for inclusion in our study.
-The unit of analysis for this study is the set of summary statistics for the four anchoring studies from one respondent.
-Respondent is defined as either one of the Many Labs locations, or a researcher who participated in fabricating results.
+To test the validity of statistical methods to detect data fabrication in summary results, we investigated summary results of four anchoring studies [@tversky1974;@jacowitz1995].
+We selected the anchoring effect because it is a well-known psychological phenomenon and many genuine data sets on the effect are available from the Many Labs project [@klein2014].
+The unit of analysis for this study is the set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
+Respondent is defined here as either one of the Many Labs locations, or a researcher who fabricated the four anchoring studies' summary statistics.
 
@@
 The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States.
-Each of the four studies provided summary results for a two-factorial design, including a high- and low anchor condition and gender.
-These four anchoring studies were selected because quality data were available from the Many Labs project [@klein2014].
+Each of the four studies provided summary results for a 2 (low/high anchoring) × 2 (male/female) factorial design.
 
@@
 Thirty-six genuine datasets were collected from the publicly available Many Labs project [@klein2014, osf.io/pqf9r].
-The Many Labs (ML) project replicated several effects, including the anchoring effect, across thirty-six locations.
-ML replicated the anchoring effect with the four studies mentioned previously.
+The Many Labs (ML) project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
 Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, means and standard deviations were collected for each of the four conditions in the four anchoring studies.
-In total, this yielded both `r 4*4` means per location and `r 4*4` variances per location.
-The raw data were cleaned according to the original analysis script from the ML project.
+For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were collected for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., 48 × 36).
+These summary statistics were collected from the raw ML data, which were cleaned using the original analyses scripts from the ML project to ensure that the data did not contain improper responses.
 
@@
 
-Thirty-six fabricated sets of summary results were collected for all four anchoring studies.
+Thirty-six fabricated sets of summary results were also collected for all four anchoring studies.
 We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS).
@@
 
-Each respondent was instructed to fabricate summary statistics that fulfilled three hypotheses.
-That is, 4 (studies) × 2 (conditions) × 2 (sex) × 2 (mean or sd) = 32 statistics were fabricated.
+Each respondent was instructed to fabricate 32 summary statistics (4 studies × 2 conditions × 2 sexes × 2 statistics [mean and sd]) that fulfilled three hypotheses.
+Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
 We instructed participants to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
-The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data that is used to test the detection of data fabrication.
+The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
 
-In order to standardize the fabrication process to a minimal extent, we provided participants with a spreadsheet where the fabricated data had to be filled in.
-The fabricated data are checked against the provided hypotheses and the statistical test are provided instantaneously, given the fabricated means and standard deviations.
+In order to standardize the fabrication process to a minimal extent, we provided participants with a spreadsheet where the fabricated data had to be filled out.
 Figure `r fig <- 1; fig` depicts an example of this spreadsheet.
-Respondents were required to copy-paste the yellow cells into Qualtrics, to provide a standardized way of reporting the means and standard deviations.
+The yellow cells are those that the respondent is requested to fabricate and include both the means and the standard deviations.
+Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
+When these results corroborate the given expectations, a checkmark appears as in the green cells in Figure `r fig`.
+We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format.
 
@@
 
-We included two methods to test for data fabrication and we combined the results of these two tests.
-These statistical tests compute the probability that, given sampling theory, the current data or an even more unlikely set would be observed.
-As a result, this probability can be seen as a *p*-value for the null hypothesis that the data is genuine (i.e., P[data|genuine]).
+To detect data fabrication in a set of summary results, we first apply the "variance of variances" method [@simonsohn2013] on the fabricated standard deviations across the four anchoring studies.
+This method tests whether the observed variances contain a reasonable amount of variation expected based on stochastic sampling processes.
+For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000.
 
-First we apply the "variance of variances" method [@simonsohn2013].
-This method tests whether the observed variances contain a reasonable amount of variation expected based on stochastic sampling processes.
-For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent.
-More technically, the method first estimates the observed variation of the standardized standard deviations.
-Second, the method simulates how much variation in the standardized standard deviations can be expected given the sample sizes, means and variances.
-This yields an estimate of the probability that the observed lack of variation in the variances would be observed, or even less.
-This is in fact a *p*-value that tests the hypothesis that the observed variances are genuine and originate from a stochastic sampling distribution, under a set of distributional assumptions.
+To compute the "variance of variances" method we use the following procedure. First, we compute the standardized variation in the observed variances for each of the four studies. 
+Second, we compute the mean of these standardized variations, which results in one summary statistic that captures the variation in the variances across all four anchoring studies.
+Third, in order
 
-Second, we apply the reversed Fisher method, which tests whether there is an excessive amount of high *p*-values.
-The default Fisher method [@fisher1925] tests whether a set of *p*-values deviates from uniformity, where smaller *p*-values occur more frequently than larger *p*-values (i.e., whether there is evidence for an effect).
-However, the reversed Fisher method tests whether a set of *p*-values deviates from uniformity in such a way that there are more large *p*-values than small ones.
-As such, it tests whether a theoretically infeasible distribution of *p*-values is presented in a study, which is overly consistent with the null hypothesis.
-The reversed Fisher method is computed as
+Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, one for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
+The Fisher method [@fisher1925] tests for evidence of an effect in a set of *p*-values and has previously been used as a meta-analytic method [@hong2008], but we adjust it here to test for results that are overly consistent with the null hypothesis.
+The original Fisher method is computed as
+
+$\chi^2_{2k}=-2\sum\ln(p_i)$
+
+and tests for right-skew in a set of *p*-values, but we adjust it to the following
 
@@
 
-where *t* is the lowerbound (i.e., threshold) of the *k* number of *p*-values taken into account.
-The resulting *p*-value indicates the probability that the observed nonsignificant *p*-values are actually from a genuine null distribution.
+where it now tests for left-skew (i.e., more larger *p*-values than smaller *p*-values) across the *k* number of *p*-values that falls above the threshold *t*.
+We set this threshold to .05 in order to include only nonsignificant test results.
+
+Finally, we combined the results of these three individual tests for data fabrication using the Fisher method.
+We expect this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests.
+Based on the results of the combined test results, the three 'best' data fabricators are selected.
+The three respondents with the highest *p*-values contain the least evidential value for deviating from genuine data and receive an additional $50 Amazon gift card.
+
+For each of these three tests to detect data fabrication we carry out sensitivity and specificity analyses using ROC-curves in order to determine optimal alpha levels.
+This analysis helps determine the classification performance of these three tests.
+In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1 and assessed the classification performance of these methods to detect data fabrication.
+The optimal alpha level is determined by finding that alpha level for which both the true positive classification rate and the true negative classification rate are highest.
+For example,
 
@@
 
-Third, we combine the results of the "variance of variances" test and reversed Fisher method by testing for evidential value.
-To this end, we apply the default Fisher method.
-The Fisher method tests whether there is sufficient evidence for deviation from genuine data in the two separate tests and is computed as
-
-$\chi^2_{2k}=-2\sum\ln(p_i)$
-
-Given that this is a combination test, we expect this to be a more powerful test than the "variance of variances" method or the reversed Fisher method alone.
-The three respondents with the highest *p*-value contained the least evidential value for deviating from genuine data and received an additional $50 Amazon gift card.
 <!---

### 2016-04-25 submission/manuscript.Rmd
Redo the spreadsheets for study 1, update manuscript, add qualtrics questions

@@
 We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS).
-Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995], for which summary results were fabricated.
+Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995;@tversky1974], for which summary results were fabricated.
 U.S.
@@
 
-The full sample frame was digitally approached to participate in this study on March XX, 2016 (invitation: osf.io/XXXX).
+The full sample frame was digitally approached to participate in this study on April XX, 2016 (invitation: osf.io/s4w8r).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-address saved at all).
@@
 
-To detect data fabrication in a set of summary results, we first apply the "variance of variances" method [@simonsohn2013] on the fabricated standard deviations across the four anchoring studies.
-This method tests whether the observed variances contain a reasonable amount of variation expected based on stochastic sampling processes.
-For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000.
+To detect data fabrication in a set of summary results, we first test the variance of fabricated standard deviations [SDs; @simonsohn2013] across the four anchoring studies.
+This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on stochastic sampling processes.
+For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000 (this is simply an example).
+To compute this test, we first standardize the SDs for each of the four studies by computing
 
-To compute the "variance of variances" method we use the following procedure. First, we compute the standardized variation in the observed variances for each of the four studies. 
-Second, we compute the mean of these standardized variations, which results in one summary statistic that captures the variation in the variances across all four anchoring studies.
-Third, in order
+$\tilde{s}_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
+<!--- \limits^k_{j=1} --->
 
-Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, one for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
+where $\tilde{s}_j$ denotes the standardized SD in group *j*.
+Note that $MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells.
+We test several different measures to detect data fabrication that utilize these standardized SDs (i.e., $\tilde{s}_j$), including the max-min distance (denoted $\tilde{\sigma}_{max-min}$) and the variance of the standardized SDs [i.e.,  $\tilde{\sigma}_{sd}$; @simonsohn2013].
+We compare the observed value for each $\tilde{\sigma}$ measure with the expected distribution of outcomes when the data would be the result of random sampling processes.
+To this end, we simulate the expected distribution of standardized SDs and compute the expected distribution of each $\tilde{\sigma}$.
+This expected distribution is used to determine the *p*-value of the observed $\tilde{\sigma}$ value.
+We simulate the standardized SD for each of the *j* groups as
+
+$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}s^2_j}{N_j-1}\Bigg]/MS_w$
+
+These simulated values are used to compute the expected distribution of all $\tilde{\sigma}$ measures.
+
+Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
 The Fisher method [@fisher1925] tests for evidence of an effect in a set of *p*-values and has previously been used as a meta-analytic method [@hong2008], but we adjust it here to test for results that are overly consistent with the null hypothesis.
@@
 $\chi^2_{2k}=-2\sum\ln(p_i)$
+<!--- \limits^k_{i=1} --->
 

### 2016-04-25 submission/manuscript.Rmd
Add osf link to qualtrics questions
Add separate sets of sampling frames study 1 (for qualtrics batch mailing)

@@
 date: '`r format(Sys.time(), "%d %B, %Y")`'
-output: word_document
+output: pdf_document
 csl: ../bibliography/apa.csl
@@
 Several questions were asked about their statistical knowledge and approach to data fabrication, and they were reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
-The full set of questions from the study are available at osf.io/XXXX.
+The full set of questions from the study are available at osf.io/w984b.
 

### 2016-05-10 data/study_01_anchoring/compute_summary_stats.R
Move files around

@@ -1,173 +1,0 @@
-library(foreign)
-library(car)
-library(plyr)
-
-ml_dat <- read.spss('data/study_01_anchoring/chjh ml1_anchoring cleaned.sav',
-                    to.data.frame = TRUE,
-                    use.value.labels = FALSE)
-
-# Correct the gender variable to see 1 as NA
-# partgender = 1 described as no response in ML syntax
-ml_dat$partgender <- ifelse(ml_dat$partgender == 1, NA,
-                            ifelse(ml_dat$partgender == 3, 0, 1))
-# 0 = male
-# 1 = female
-
-# listwise deletion of participants without gender
-ml_dat <- ml_dat[!is.na(ml_dat$partgender), ]
-
-summary_stat_1 <- ddply(ml_dat, .(referrer, partgender, anch1group), function(x){
-  anch1_n <- length(x$anchoring1[!is.na(x$anchoring1)])
-  anch1_m <- mean(x$anchoring1, na.rm = TRUE)
-  anch1_sd <- sd(x$anchoring1, na.rm = TRUE)
-  
-  return(cbind(anch1_n,
-               anch1_m,
-               anch1_sd))
-})
-names(summary_stat_1)[3:6] <- c('anchoring',
-                                'anch_n',
-                                'anch_m',
-                                'anch_sd')
-
-summary_stat_2 <- ddply(ml_dat, .(referrer, partgender, anch2group), function(x){
-  anch2_n <- length(x$anchoring2[!is.na(x$anchoring2)])
-  anch2_m <- mean(x$anchoring2, na.rm = TRUE)
-  anch2_sd <- sd(x$anchoring2, na.rm = TRUE)
-  
-  return(cbind(anch2_n,
-               anch2_m,
-               anch2_sd))
-})
-names(summary_stat_2)[3:6] <- c('anchoring',
-                                'anch_n',
-                                'anch_m',
-                                'anch_sd')
-
-summary_stat_3 <- ddply(ml_dat, .(referrer, partgender, anch3group), function(x){
-  anch3_n <- length(x$anchoring3[!is.na(x$anchoring3)])
-  anch3_m <- mean(x$anchoring3, na.rm = TRUE)
-  anch3_sd <- sd(x$anchoring3, na.rm = TRUE)
-  
-  return(cbind(anch3_n,
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Availability Heuristic.R

@@ -1,757 +1,0 @@
-#############MANY LABS 3 AVAILABILITY HEURISTIC##################
-#######Charlie Ebersole, Begin January 21, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-require(compute.es)
-
-###Calculating whether individual selected first or third position more
-
-head(ML3)
-str(ML3$vposition)  #1=more often in first position, 2=more often in third position
-sum(ML3$vposition==1,na.rm=TRUE)
-sum(ML3$vposition==2,na.rm=TRUE)
-list(ML3$vposition)
-
-###Tallying number of times 1st position was judged to be more common
-K1stTotal<-sum(ML3$kposition==1,na.rm=TRUE)
-L1stTotal<-sum(ML3$Lposition==1,na.rm=TRUE)
-N1stTotal<-sum(ML3$nposition==1,na.rm=TRUE)
-R1stTotal<-sum(ML3$rposition==1,na.rm=TRUE)
-V1stTotal<-sum(ML3$vposition==1,na.rm=TRUE)
-
-###Tallying number of times 3rd position was judged to be more common
-K3rdTotal<-sum(ML3$kposition==2,na.rm=TRUE)
-L3rdTotal<-sum(ML3$Lposition==2,na.rm=TRUE)
-N3rdTotal<-sum(ML3$nposition==2,na.rm=TRUE)
-R3rdTotal<-sum(ML3$rposition==2,na.rm=TRUE)
-V3rdTotal<-sum(ML3$vposition==2,na.rm=TRUE)
-
-###Calculating total times 1st postion was judged to be more common
-FirstSelected<-K1stTotal+L1stTotal+N1stTotal+R1stTotal+V1stTotal
-
-###Calculating total responses
-TotalResponses<-K1stTotal+L1stTotal+N1stTotal+R1stTotal+V1stTotal+K3rdTotal+L3rdTotal+N3rdTotal+R3rdTotal+V3rdTotal
-
-###Assigning Sign 
-str(ML3$FirstSelected)
-ML3$K1st[ML3$kposition==1]<-1
-ML3$L1st[ML3$lposition==1]<-1
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Conscientiousness Persistence Script.R

@@ -1,347 +1,0 @@
-#############MANY LABS 3 CONSCIENTIOUSNESS AND PERSISTENCE#################
-#######Charlie Ebersole, Begin January 21, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-
-str(ML3$Conscientiousness)
-str(ML3$Persistence)
-
-#Checking number of participants who answered both measures
-Consc<-subset(ML3,ML3$Conscientiousness!="NA")
-length(Consc$session_id)
-Persist<-subset(ML3,ML3$Persistence!="NA")
-length(Persist$session_id)
-Persist2<-subset(Persist,Persist$Conscientiousness!="NA")
-length(unique(Persist2$session_id))
-
-#checking mTurk
-mTurk<-subset(Persist2,Persist2$Site=="mTurk")
-length(mTurk$session_id)
-list(mTurk$Conscientiousness)
-list(mTurk$Persistence)
-
-
-###Replicating Previous Effect###
-#Persistence will be measured as the amount of time spent on the anagrams page before pressing the continue button.  The relationship between persistence and conscientiousness will be assessed as a pearson’s correlation.
-
-cor(ML3$Conscientiousness,ML3$Persistence,use="complete.obs",method="pearson")
-plot(ML3$Conscientiousness,ML3$Persistence)
-cor.test(ML3$Conscientiousness,ML3$Persistence,alternative="two.sided",method="pearson",conf.level=0.95)
-res(0.02655341,var.r=NULL,3193)
-res(0.02655341,var.r=NULL,3193,level=99)
-
-###Calculating effect size from previous work
-res(.46,var.r=NULL,130)
-
-###DESCRIPTIVES###
-summary(ML3$Conscientiousness)
-sd(ML3$Conscientiousness,na.rm=TRUE)
-hist(ML3$Conscientiousness)
-
-summary(ML3$Persistence)
-sd(ML3$Persistence,na.rm=TRUE)
-hist(ML3$Persistence)
-
-##############################Exploratory Analyses#######################################
-str(ML3$DaysInComp)
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Elaboration Likelihood Script.R

@@ -1,449 +1,0 @@
-#############MANY LABS 3 ELABORATION LIKELIHOOD MODEL##################
-#######Charlie Ebersole, Begin January 21, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-require(MBESS)
-
-str(ML3$NFCcenter)
-str(ML3$ArgumentQuality)
-str(ML3$ELMCond)
-ML3$ELMCond<-as.factor(ML3$ELMCond)
-Cond<-subset(ML3,ML3$ELMCond!="NA")
-NFC<-subset(Cond,Cond$NFCcenter!="NA")
-DV<-length(unlist(NFC$ArgumentQuality!="NA"))
-
-###Replicating Previous Effect###
-#The five items will be averaged as an index of argument quality.  In the original study, participants who scored in the upper or lower third of need for cognition were recruited from the available sample for the study and were labeled as being high or low on the trait for analysis.  We will use all participants and treat need for cognition as a continuous measure.  As such the key analysis will be a general linear model with condition (strong = 1 vs. weak = -1), need for cognition (mean centered), and their interaction predicting argument quality.  The key test is the interaction term to show that the effect of the manipulation is moderated by need for cognition.
-
-ELM.lm<-lm(ArgumentQuality~NFCcenter*ELMCond,data=ML3)
-Anova(ELM.lm,type="II")
-summary(ELM.lm)
-plot(allEffects(ELM.lm))
-ci.pvaf(F.value= 79.9251,df.1=1,df.2=2361,N=2365,conf.level=.95)
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Graphing Script.R

@@ -1,70 +1,0 @@
-############ML3 Aggregate Graphs#############
-#######Charlie Ebersole######
-
-
-require(ggplot2)
-require(reshape2)
-
-###Effects with Cohen's d
-
-setwd("/Users/Charlie/Desktop/ML3 Graph Data")
-dstats<-read.csv(file="dplot.csv",header=TRUE)
-dstats
-
-dflip<-t(dstats)
-dflip
-write.csv(dflip,file="dflip.csv",row.names=FALSE)
-
-flipped<-read.csv(file="dflip.csv",header=TRUE)
-flipped
-
-dlong<-melt(flipped,id.vars="Effect")
-head(dlong)
-write.csv(dlong,file="dlong.csv",row.names=FALSE)
-
-dlong<-read.csv(file="dlong.csv",header=TRUE)
-str(dlong$Effect)
-list(levels(dlong$Effect))
-dlong$Effect<-factor(dlong$Effect,levels=c("Warmth Perceptions","Weight Embodiment","Power and Perspective","Persistence","Availability Heuristic","Metaphoric Restructuring","Stroop Effect"))
-
-Aggregate<-subset(dlong,SiteorAgg=="Aggregate")
-Sites<-subset(dlong,SiteorAgg=="Single Site")
-Original<-subset(dlong,SiteorAgg=="Original")
-dlong$SiteorAgg<-factor(dlong$SiteorAgg,levels=c("Single Site","Aggregate","Original"))
-
-d<-ggplot(Aggregate,aes(x=Effect,y=value,ymin=lwr,ymax=upr))+geom_point(data=Sites,aes(x=Effect,y=value,ymin=lwr,ymax=upr),shape=4,size=4)+geom_point(data=Aggregate,aes(x=Effect,y=value,ymin=lwr,ymax=upr),shape=16,size=6,color="blue",fill="blue")+geom_point(data=Original,aes(x=Effect,y=value,ymin=lwr,ymax=upr),shape=24,fill="green",size=4)+geom_errorbar(colour='Blue',size=1,width=.35)+coord_flip()+ylab("Cohen's d")+theme_bw()+theme(panel.grid.major=element_blank())+geom_hline(yintercept=0,color="black")+theme(text=element_text(size=15))
-d
-
-
-#Effects with partial eta squared
-
-etastats<-read.csv(file="etaplot.csv",header=TRUE)
-etastats
-
-etaflip<-t(etastats)
-etaflip
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/ML3 Individual Differences and Data Quality by Time of Semester.R

@@ -1,428 +1,0 @@
-#############MANY LABS 3 INDIVIDUAL DIFFERENCES BY TIME##################
-#######Charlie Ebersole, Begin January 31, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-require(lme4)
-require(compute.es)
-
-length(unique(ML3$session_id))
-
-Pool<-subset(ML3,ML3$Site!="mTurk")
-length(unique(Pool$session_id))
-
-#######################Exploratory Examination of Individual Differences####################
-
-
-
-
-head(Pool)
-range(Pool$DaysInComp,na.rm=TRUE)
-
-###Attention###
-table(Pool$AttentionCheck)
-Fail<-subset(Pool,Pool$AttentionCheck=="Fail")
-Pass<-subset(Pool,Pool$AttentionCheck=="Pass")
-hist(Fail$DaysInComp)
-plot(density(Fail$DaysInComp))
-hist(Pass$DaysInComp)
-plot(density(Pass$DaysInComp))
-
-#############BIG FIVE###############
-###Openness
-summary(Pool$Openness)
-sd(Pool$Openness,na.rm=TRUE)
-hist(Pool$Openness)
-cor(Pool$DaysInComp,Pool$Openness,use="complete.obs",method="pearson")
-
-###Conscientiousness
-summary(Pool$Conscientiousness)
-sd(Pool$Conscientiousness,na.rm=TRUE)
-hist(Pool$Conscientiousness)
-cor(Pool$DaysInComp,Pool$Conscientiousness,use="complete.obs",method="pearson")
-
-###Extraversion
-summary(Pool$Extraversion)
-sd(Pool$Extraversion,na.rm=TRUE)
-hist(Pool$Extraversion)
-cor(Pool$DaysInComp,Pool$Extraversion,use="complete.obs",method="pearson")
-
-###Agreeableness
-summary(Pool$Agreeableness)
-sd(Pool$Agreeableness,na.rm=TRUE)
-hist(Pool$Agreeableness)
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Reformatting Order Script.R

@@ -1,97 +1,0 @@
-########ML3 Reformatting Order Script########
-###March 4 2015###
-
-setwd("/Users/Charlie/Desktop/ML3 Data Analysis")
-ML3Order<-read.csv(file="ML3Order.csv",header=TRUE)
-head(ML3Order)
-
-BestGrade<-subset(ML3Order,bestgrade_order!="NA")
-WorstGrade<-subset(ML3Order,worstgrade_order!="NA")
-BestGrade$grade_order<-BestGrade$bestgrade_order
-WorstGrade$grade_order<-WorstGrade$worstgrade_order
-Grades<-rbind(BestGrade,WorstGrade)
-head(Grades)
-GradeOrder<-Grades[,c("session_id","grade_order")]
-ML3Order<-merge(ML3Order,GradeOrder,by="session_id",all=TRUE)
-head(ML3Order)
-
-JustStart<-ML3Order[,c("session_id",
-"elmques_order",
-"galinskyvignette_order",
-"moninvignette_order",
-"grade_order",
-"stroop_order",
-"anagrams_order",
-"availinstruct_order",
-"tempfollowup_order",
-"inlab_order")]
-
-head(JustStart)
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE)
-head(ML3)
-str(ML3$OrderofTasks)
-
-
-ML3IdLab<-ML3[,c("session_id","OrderofTasks")]
-head(ML3IdLab)
-
-
-ML3OrderNew<-merge(JustStart,ML3IdLab,by="session_id",all=TRUE)
-head(ML3OrderNew)
-tail(ML3OrderNew)
-
-IIFirst<-subset(ML3OrderNew,OrderofTasks=="II-SR")
-SRFirst<-subset(ML3OrderNew,OrderofTasks=="SR-II")
-head(IIFirst)
-head(SRFirst)
-list(IIFirst$OrderofTasks)
-list(SRFirst$OrderofTasks)
-
-IIFirst$II_order<-IIFirst$inlab_order+.2
-IIFirst$SR_order<-IIFirst$inlab_order+.5
-head(IIFirst)
-
-SRFirst$II_order<-SRFirst$inlab_order+.5
-SRFirst$SR_order<-SRFirst$inlab_order+.2
-head(SRFirst)
-
-InLab<-rbind(SRFirst,IIFirst)
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Self-Esteem Subjective Distance Script.R

@@ -1,507 +1,0 @@
-#############MANY LABS 3 SELF-ESTEEM AND SUBJECTIVE DISTANCE##################
-#######Charlie Ebersole, Begin January 21, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-require(MBESS)
-
-str(ML3$bestgrade2)
-str(ML3$worstgrade2)
-
-ML3$SubDistCond[ML3$bestgrade2!="NA"]<-"BestGrade"
-ML3$SubDistCond[ML3$worstgrade2!="NA"]<-"WorstGrade"
-list(ML3$SubDistCond)
-
-###worst/bestgrade3 is DV
-BestGrade<-subset(ML3,ML3$SubDistCond=="BestGrade")
-WorstGrade<-subset(ML3,ML3$SubDistCond=="WorstGrade")
-head(BestGrade)
-head(WorstGrade)
-tail(WorstGrade)
-
-BestGrade$SubDist<-BestGrade$bestgrade3
-WorstGrade$SubDist<-WorstGrade$worstgrade3
-BestGrade$TimeSince<-BestGrade$bestgrade1
-WorstGrade$TimeSince<-WorstGrade$worstgrade1
-BestGrade$SESDOrder<-BestGrade$bestgrade_order
-WorstGrade$SESDOrder<-WorstGrade$worstgrade_order
-SESDdata<-rbind(BestGrade,WorstGrade)
-head(SESDdata)
-tail(SESDdata)
-list(SESDdata$SubDistCond)
-
-###Adding Months Since data
-setwd("/Users/Charlie/Desktop/ML3 Data Analysis")
-Months<-read.csv(file="ML3 SESD Open Response.csv",header=TRUE,stringsAsFactors=FALSE)
-head(Months)
-tail(Months)
-str(Months$Year)
-str(Months$TermsBack)
-Months$YearMonths<-(2014-Months$Year)*12
-Months$TermMonths[Months$TermsBack==0]<-0
-Months$TermMonths[Months$TermsBack==1]<-1
-Months$TermMonths[Months$TermsBack==2]<-4
-Months$TermMonths[Months$TermsBack==3]<-8
[…]

### 2016-05-10 data/study_02 ml3_stroop/ML3 Data Analysis Scripts/ML3 Data Analysis Scripts/Warmer Hearts Rooms Script.R

@@ -1,458 +1,0 @@
-#############MANY LABS 3 WARMER HEARTS WARMER ROOMS SCRIPT#################
-#######Charlie Ebersole, Begin January 21, 2014###########
-
-setwd("/Users/Charlie/Desktop/ML3 Final Data")
-ML3<-read.csv(file="ML3AllSitesandmTurk.csv",header=TRUE,na.strings=c("","NA"),stringsAsFactors=FALSE)
-head(ML3)
-
-#Required Packages
-require(car)
-require(doBy)
-require(ggplot2)
-require(effects)
-require(stringr)
-require(compute.es)
-require(dplyr)
-
-#Reformatting temperature estimate
-str(ML3$tempest1)
-list(ML3$tempest1)
-regexp<-"[[:digit:]]+"
-ML3$tempestclean<-str_extract(ML3$tempest1,regexp)
-list(ML3$tempestclean)
-str(ML3$tempestclean)
-ML3$tempestclean<-as.numeric(ML3$tempestclean)
-
-#Checking other variables
-str(ML3$TempCond)
-ML3$TempCond<-as.factor(ML3$TempCond)
-list(levels(ML3$TempCond))
-str(ML3$TargetGender)
-ML3$TargetGender<-as.factor(ML3$TargetGender)
-str(ML3$Genderfactor)
-ML3$Genderfactor<-as.factor(ML3$Genderfactor)
-str(ML3$Temperatureinlab)
-ML3$Temperatureinlab<-as.numeric(ML3$Temperatureinlab)
-
-###Eliminating estimates higher than 95, lower than 50
-tempclean1<-subset(ML3,ML3$tempestclean<95)
-TempClean<-subset(tempclean1,tempclean1$tempestclean>50)
-head(TempClean)
-range(TempClean$tempestclean)
-str(TempClean$tempestclean)
-length(TempClean$tempestclean)
-list(TempClean$tempestclean)
-
-Communal<-subset(TempClean,TempClean$TempCond=="Communal")
-length(Communal$session_id)
-Agentic<-subset(TempClean,TempClean$TempCond=="Agentic")
-length(Agentic$session_id)
-
-###Replicating Previous Effect###
[…]

### 2016-05-10 functions/compute_summary_anch_ml.R
Update ML summary stats extraction

@@ -1,0 +1,186 @@
+if(!require(foreign)){install.packages('foreign')}
+if(!require(car)){install.packages('car')}
+if(!require(plyr)){install.packages('plyr')}
+library(foreign)
+library(car)
+library(plyr)
+
+ml_dat <- read.spss('../data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav',
+                    to.data.frame = TRUE,
+                    use.value.labels = FALSE)
+
+# Correct the gender variable to see 1 as NA
+# partgender = 1 described as no response in ML syntax
+ml_dat$partgender <- ifelse(ml_dat$partgender == 1, NA,
+                            ifelse(ml_dat$partgender == 3, 0, 1))
+# 0 = male
+# 1 = female
+
+# listwise deletion of participants without gender
+ml_dat <- ml_dat[!is.na(ml_dat$partgender), ]
+
+summary_stat_1 <- ddply(ml_dat, .(referrer, partgender, anch1group), function(x){
+  anch1_n <- length(x$anchoring1[!is.na(x$anchoring1)])
+  anch1_m <- mean(x$anchoring1, na.rm = TRUE)
+  anch1_sd <- sd(x$anchoring1, na.rm = TRUE)
+  study <- 1
+  
+  return(cbind(anch1_n,
+               anch1_m,
+               anch1_sd,
+               study))
+})
+names(summary_stat_1)[3:6] <- c('anchoring',
+                                'anch_n',
+                                'anch_m',
+                                'anch_sd')
+
+summary_stat_2 <- ddply(ml_dat, .(referrer, partgender, anch2group), function(x){
+  anch2_n <- length(x$anchoring2[!is.na(x$anchoring2)])
+  anch2_m <- mean(x$anchoring2, na.rm = TRUE)
+  anch2_sd <- sd(x$anchoring2, na.rm = TRUE)
+  study <- 2
+  
+  return(cbind(anch2_n,
+               anch2_m,
+               anch2_sd,
+               study))
+})
+names(summary_stat_2)[3:6] <- c('anchoring',
+                                'anch_n',
+                                'anch_m',
+                                'anch_sd')
+
[…]

### 2016-05-10 functions/process_qualtrics_anch_01.R
Clean qualtrics data, project 1

@@ -1,0 +1,328 @@
+if(!require(stringr)) install.packages('stringr')
+library(stringr)
+
+# file <- '../data/study_01/raw_summary_results_fabrication.csv'
+file <- 'data/study_01/raw_summary_results_fabrication_qualtrics.csv'
+dat_qualtrics <- read.csv(file, stringsAsFactors = FALSE, na.strings = '')
+
+# Remove the description of the question
+dat_qualtrics <- dat_qualtrics[-1,]
+
+# Remove the redundant variables
+dat <- data.frame(id = dat_qualtrics$V1,
+                  anch_1 = dat_qualtrics$res_01,
+                  anch_2 = dat_qualtrics$res_02,
+                  anch_3 = dat_qualtrics$res_03,
+                  anch_4 = dat_qualtrics$res_04,
+                  stat_know = dat_qualtrics$deb_02,
+                  spss = dat_qualtrics$deb_03_1,
+                  rcran = dat_qualtrics$deb_03_2,
+                  stata = dat_qualtrics$deb_03_3,
+                  sas = dat_qualtrics$deb_03_4,
+                  matlab = dat_qualtrics$deb_03_5,
+                  python = dat_qualtrics$deb_03_6,
+                  other = dat_qualtrics$deb_03_7,
+                  nopro = dat_qualtrics$deb_03_8,
+                  noanch = ifelse(dat_qualtrics$deb_01 == 2,
+                                  0,
+                                  ifelse(dat_qualtrics$deb_01 == 1,
+                                         1,
+                                         NA)),
+                  rng = ifelse(dat_qualtrics$deb_04 == 2,
+                               0,
+                               ifelse(dat_qualtrics$deb_04 == 1,
+                                      1,
+                                      NA)),
+                  full = ifelse(dat_qualtrics$deb_05 == 2,
+                                0,
[…]

### 2016-05-13 functions/process_qualtrics_anch_01.R
Minor fix for processing qualtrics data

@@ -114,8 +114,10 @@ bonus <- NULL
 for (i in 1:dim(dat)[1])
 {
   referrer <- c(referrer, rep(dat$id[i], 16))
-  partgender <- c(partgender, rep(c(rep(0, 2), rep(1, 2)), 4))
-  anchoring <- c(anchoring, rep(rep(c(0, 1), 2), 4))
+  partgender <- c(partgender, rep(c(1, 0, 1, 0), 4))
+  # 0 = male
+  # 1 = female
+  anchoring <- c(anchoring, rep(rep(c(0, 0, 1, 1), 4)))
   anch_n <- c(anch_n, rep(25, 16))
   study <- c(study, sort(rep(1:4, 4)))
   

### 2016-05-14 submission/manuscript.Rmd
Forgot a square, also in the prereg... :-( Did not forget it in the formula after though!
First run at data analysis

@@
 
-$\tilde{s}_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
+$\tilde{s}^2_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
 <!--- \limits^k_{j=1} --->
@@
 
+### Results.
+```{r prep data study 1, echo = FALSE}
+options(digits = 20)
+# Compute the summary statistics for Many Labs
+source('../functions/compute_summary_anch_ml.R')
+# Process the collected, fabricated data
+source('../functions/process_qualtrics_anch_01.R')
+
+# Read the data
+ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
+qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
+ml$stat_know <- NA
+ml$spss <- NA
+ml$rcran <- NA
+ml$stata <- NA
+ml$sas <- NA
+ml$matlab <- NA
+ml$python <- NA
+ml$other <- NA
+ml$nopro <- NA
+ml$noanch <- NA
+ml$rng <- NA
+ml$full <- NA
+ml$tries <- NA
+ml$descr <- NA
+ml$bonus <- NA
+ml$type <- 'ml'
+qualtrics$type <- 'qualtrics'
+
+dat <- rbind(qualtrics, ml)
+```
+
+```{r compile results for detecting data fabrication, echo = FALSE}
+# conduct the analyses iteratively
+for (pp in unique(dat$referrer))
+{
+  # Loop through each study to compute the ANOVA results
+  for (j in 1:4)
+  {
+    study_nr <- j    
+    indexor <- dat$referrer == pp & dat$study == study_nr
+
+    harm_mean <- 4^2/(sum(1/dat$anch_n[indexor]))
+    male_mean <- mean(dat$anch_m[indexor & dat$partgender == 0])
+    female_mean <- mean(dat$anch_m[indexor & dat$partgender == 1])
+    control_mean <- mean(dat$anch_m[indexor & dat$anchoring == 0])
+    exp_mean <- mean(dat$anch_m[indexor & dat$anchoring == 1])
+
+    ss_error <- sum((dat$anch_n[indexor] - 1) * dat$anch_sd[indexor]^2)
+    ss_gender <- (harm_mean * var(c(male_mean, female_mean))) / 2
+    ss_condition <- (harm_mean * var(c(control_mean, exp_mean))) / 2
+    ss_interaction <- harm_mean * var(dat$anch_m[indexor]) * 3/4 - ss_gender - ss_condition
+    ss_total <- ss_error + ss_gender + ss_condition + ss_interaction
+
+    ms_error <- ss_error / (sum(dat$anch_n[indexor]) - 4)
+    ms_gender <- ss_gender / (2 - 1)
+    ms_condition <- ss_condition / (2 - 1)
+    ms_interaction <- ss_interaction / 1
+
+    dat$f_gender[indexor] <- ms_gender / ms_error
+    dat$df1_gender[indexor] <- 2 - 1
+    dat$df2_gender[indexor] <- sum(dat$anch_n[indexor]) - 4
+    dat$p_gender[indexor] <- pf(q = ms_gender / ms_error,
+                                df1 = 2 - 1,
+                                df2 = sum(dat$anch_n[indexor]) - 4,
+                                lower.tail = FALSE)
+
+    dat$f_condition[indexor] <- ms_condition / ms_error
+    dat$df1_condition[indexor] <- 2 - 1
+    dat$df2_condition[indexor] <- sum(dat$anch_n[indexor]) - 4
+    dat$p_condition[indexor] <- pf(q = ms_condition / ms_error,
+                                   df1 = 2 - 1,
+                                   df2 = sum(dat$anch_n[indexor]) - 4,
+                                   lower.tail = FALSE)
+
+    dat$f_interaction[indexor] <- ms_interaction / ms_error
+    dat$df1_interaction[indexor] <- 1
+    dat$df2_interaction[indexor] <- sum(dat$anch_n[indexor]) - 4
+    dat$p_interaction[indexor] <- pf(q = ms_interaction / ms_error,
+                                     df1 = 1,
+                                     df2 = sum(dat$anch_n[indexor]) - 4,
+                                     lower.tail = FALSE)
+  }
+
+  sel <- dat$referrer == pp
+
+  # Variance analysis
+  # Standardizing the sds
+
+  # Study 1
+  sel1 <- dat$referrer == pp & dat$study == 1
+  ms_w_1 <- sum((dat$anch_n[sel1] - 1) * dat$anch_sd[sel1]^2) / sum((dat$anch_n[sel1] - 1))
+  tilde_s2_1 <- dat$anch_sd[sel1]^2 / ms_w_1
+  # Study 2
+  sel2 <- dat$referrer == pp & dat$study == 2
+  ms_w_2 <- sum((dat$anch_n[sel2] - 1) * dat$anch_sd[sel2]^2) / sum((dat$anch_n[sel2] - 1))
+  tilde_s2_2 <- dat$anch_sd[sel2]^2 / ms_w_2
+  # Study 3
+  sel3 <- dat$referrer == pp & dat$study == 3
+  ms_w_3 <- sum((dat$anch_n[sel3] - 1) * dat$anch_sd[sel3]^2) / sum((dat$anch_n[sel3] - 1))
+  tilde_s2_3 <- dat$anch_sd[sel3]^2 / ms_w_3
+  # Study 4
+  sel4 <- dat$referrer == pp & dat$study == 4
+  ms_w_4 <- sum((dat$anch_n[sel4] - 1) * dat$anch_sd[sel4]^2) / sum((dat$anch_n[sel4] - 1))
+  tilde_s2_4 <- dat$anch_sd[sel4]^2 / ms_w_4
+
+  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
+
+  iter <- 100000
+  s2 <- dat$anch_sd[dat$referrer == pp]^2
+  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
+  ms_w <- c(rep(ms_w_1, 4), rep(ms_w_2, 4),
+            rep(ms_w_3, 4), rep(ms_w_4, 4))
+  sim_sigma <- NULL
+
+  for (z in 1:16)
+  {
+    sim_sigma <- cbind(sim_sigma, ((rchisq(n = iter, df = n_min_1[z]) *  s2[z]) / n_min_1[z]) / ms_w[z])
+  }
+
+  sim_sigma_sd <- apply(sim_sigma, 1, sd)
+
+  dat$variance_sd_p[sel] <- sum(sim_sigma_sd < obs_sigma_sd) / iter
+
+  # Compute the Fisher method p-values 
+  # for gender and interaction
+
+  # Safety check to make sure there are 4 unique values
+  # Iteratively made exceptions for the cases that do not
+  if (length(unique(dat$p_gender[sel])) < 4 | 
+      # length(unique(dat$p_condition[sel])) < 4 |
+      length(unique(dat$p_interaction[sel])) < 4)
+  {
+    if (pp == 'R_6opw4qQURhqxT3D')
+    {
+      p_gender <- rep(1, 4)
+    } else
+    {
+      stop(sprintf('Something wrong with the number of p-values available for %s',
+                   pp))
+    }
+  } else 
+  {
+    p_gender <- unique(dat$p_gender[sel])  
+  }
+
+  dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
+  dat$gender_fish_df[sel] <- 2 * length(p_gender)
+  dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
+                                   df = 2 * length(p_gender),
+                                   lower.tail = FALSE)
+
+  p_interaction <- unique(dat$p_interaction[sel])
+  dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
+  dat$interaction_fish_df[sel] <- 2 * length(p_interaction)
+  dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
+                                        df = 2 * length(p_interaction),
+                                        lower.tail = FALSE)
+}
+
+dat_summary <- dat[ , -which(names(dat) %in% c("study",
+                                               "partgender",
+                                               "anchoring",
+                                               "anch_n",
+                                               "anch_m",
+                                               "anch_sd",
+                                               "f_gender",
+                                               "df1_gender",
+                                               "df2_gender",
+                                               "p_gender",
+                                               "f_condition",
+                                               "df1_condition",
+                                               "df2_condition",
+                                               "p_condition",
+                                               "f_interaction",
+                                               "df1_interaction",
+                                               "df2_interaction",
+                                               "p_interaction"))]
+dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
+dat_summary$fish_combine <- -2 * (log(dat_summary$variance_sd_p) + log(dat_summary$gender_fish_p) + 
+        log(dat_summary$interaction_fish_p))
+dat_summary$fish_combine_p <- pchisq(q = dat_summary$fish_combine,
+                                     df = 2 * 3, lower.tail = FALSE)
+
+write.csv(dat_summary,
+          'test.csv', row.names = FALSE)
+```
+
+```{r inspect results to detect data fabrication, echo = FALSE}
+
+```
+
 <!---
-### Results.
+
+library(ROCR)
+data(ROCR.simple)
+pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
+perf <- performance(pred,"tpr","fpr")
+plot(perf)
 

### 2016-05-23 functions/compute_summary_anch_ml.R
Update processing script

@@ -5,7 +5,13 @@ library(foreign)
 library(car)
 library(plyr)
 
-ml_dat <- read.spss('../data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav',
+# Make it easy to switch to rmarkdown files (add ../)
+ml_dat_file <- 'data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
+summary_stat_file <- 'data/study_01/ml_summary_stats.csv'
+pdf_file <- 'archive/gender_interaction.pdf'
+
+# GO
+ml_dat <- read.spss(ml_dat_file,
                     to.data.frame = TRUE,
                     use.value.labels = FALSE)
 
@@ -89,7 +95,7 @@ summary_stat <- rbind(summary_stat_1,
                       summary_stat_4)
 
 write.csv(summary_stat,
-          'data/study_01/ml_summary_stats.csv',
+          summary_stat_file,
           row.names = FALSE)
 
 refer <- unique(ml_dat$referrer)
@@ -141,7 +147,7 @@ for (i in 1:length(refer)){
   inter_p_4 <-c(inter_p_4, anova_mod$`Pr(>F)`[3])
 }
 
-pdf(file = '../archive/gender_interaction.pdf', onefile = TRUE)
+pdf(file = pdf_file, onefile = TRUE)
 par(mfrow = c(2,1)); hist(gender_p_1, breaks = 10); hist(inter_p_1, breaks = 10)
 par(mfrow = c(2,1)); hist(gender_p_2, breaks = 10); hist(inter_p_2, breaks = 10)
 par(mfrow = c(2,1)); hist(gender_p_3, breaks = 10); hist(inter_p_3, breaks = 10)

### 2016-05-23 functions/process_qualtrics_anch_01.R

@@ -1,8 +1,10 @@
 if(!require(stringr)) install.packages('stringr')
 library(stringr)
 
-# file <- '../data/study_01/raw_summary_results_fabrication.csv'
+# Add ../ before running rmarkdown, or vice versa when not running there
 file <- 'data/study_01/raw_summary_results_fabrication_qualtrics.csv'
+res_file <- 'data/study_01/qualtrics_processed.csv'
+
 dat_qualtrics <- read.csv(file, stringsAsFactors = FALSE, na.strings = '')
 
 # Remove the description of the question
@@ -327,4 +329,4 @@ res <- data.frame(referrer,
                   descr,
                   bonus)
 
-write.csv(res, 'data/study_01/qualtrics_processed.csv', row.names = FALSE)
+write.csv(res, res_file, row.names = FALSE)

### 2016-05-23 submission/manuscript.Rmd
Correct an error from the preregistration.
Update filepaths

@@
 
-$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}s^2_j}{N_j-1}\Bigg]/MS_w$
+$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}}{N_j-1}\Bigg]/MS_w$
 
@@
 # Compute the summary statistics for Many Labs
-source('../functions/compute_summary_anch_ml.R')
+# source('../functions/compute_summary_anch_ml.R')
+source('functions/compute_summary_anch_ml.R')
 # Process the collected, fabricated data
-source('../functions/process_qualtrics_anch_01.R')
+# source('../functions/process_qualtrics_anch_01.R')
+source('functions/process_qualtrics_anch_01.R')
 
 # Read the data
-ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
-qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
+# ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
+# qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
+ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
+qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
 ml$stat_know <- NA
@@
 ```{r compile results for detecting data fabrication, echo = FALSE}
+dat_summary_file <- 'data/study1_res.csv'
+
 # conduct the analyses iteratively
@@
   {
-    study_nr <- j    
-    indexor <- dat$referrer == pp & dat$study == study_nr
+    indexor <- dat$referrer == pp & dat$study == j
 

### 2016-05-23 submission/manuscript.Rmd
Add variance analyses per study, in addition to the one over all studies.

@@
   obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
+  # Add the sigma sd observed per study (NOT PREREGISTERED)
+  # Nog wijzigen adhv mva opmerkingen
+  obs_sigma_sd_study1 <- sd(tilde_s2_1)
+  obs_sigma_sd_study2 <- sd(tilde_s2_2)
+  obs_sigma_sd_study3 <- sd(tilde_s2_3)
+  obs_sigma_sd_study4 <- sd(tilde_s2_4)
 
@@
   n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
-  ms_w <- c(rep(ms_w_1, 4), rep(ms_w_2, 4),
-            rep(ms_w_3, 4), rep(ms_w_4, 4))
   sim_sigma <- NULL
@@
   {
-    sim_sigma <- cbind(sim_sigma, ((rchisq(n = iter, df = n_min_1[z]) *  s2[z]) / n_min_1[z]) / ms_w[z])
+    # Made a small error in the preregistration, so this now deviates.
+    sim_sigma <- cbind(sim_sigma, rchisq(n = iter, df = n_min_1[z]) / n_min_1[z])
   }
 
-  sim_sigma_sd <- apply(sim_sigma, 1, sd)
+  # Standardize the generated SDs based on the msW from the simulated values
+  # Per study
+  ms_w_1 <- apply(sim_sigma[,1:4], 1, function(x) sum(n_min_1[1:4] * x) / sum(n_min_1[1:4]))
+  ms_w_2 <- apply(sim_sigma[,5:8], 1, function(x) sum(n_min_1[5:8] * x) / sum(n_min_1[5:8]))
+  ms_w_3 <- apply(sim_sigma[,9:12], 1, function(x) sum(n_min_1[9:12] * x) / sum(n_min_1[9:12]))
+  ms_w_4 <- apply(sim_sigma[,13:16], 1, function(x) sum(n_min_1[13:16] * x) / sum(n_min_1[13:16]))
 
-  dat$variance_sd_p[sel] <- sum(sim_sigma_sd < obs_sigma_sd) / iter
+  sim_sigma[,1:4] <- sim_sigma[,1:4] / ms_w_1
+  sim_sigma[,5:8] <- sim_sigma[,5:8] / ms_w_2
+  sim_sigma[,9:12] <- sim_sigma[,9:12] / ms_w_3
+  sim_sigma[,13:16] <- sim_sigma[,13:16] / ms_w_4
+
+  # Calculate the variance of the simulated sds
+  sim_sigma_sd_overall <- apply(sim_sigma, 1, sd)
+  sim_sigma_sd_study1 <- apply(sim_sigma[,1:4], 1, sd)
+  sim_sigma_sd_study2 <- apply(sim_sigma[,5:8], 1, sd)
+  sim_sigma_sd_study3 <- apply(sim_sigma[,9:12], 1, sd)
+  sim_sigma_sd_study4 <- apply(sim_sigma[,13:16], 1, sd)
+
+  # Calculate the p-value overall and per study
+  dat$variance_sd_p_overall[sel] <- sum(sim_sigma_sd_overall < obs_sigma_sd) / iter
+  dat$variance_sd_p_study1[sel] <- sum(sim_sigma_sd_study1 < obs_sigma_sd_study1) / iter
+  dat$variance_sd_p_study2[sel] <- sum(sim_sigma_sd_study2 < obs_sigma_sd_study2) / iter
+  dat$variance_sd_p_study3[sel] <- sum(sim_sigma_sd_study3 < obs_sigma_sd_study3) / iter
+  dat$variance_sd_p_study4[sel] <- sum(sim_sigma_sd_study4 < obs_sigma_sd_study4) / iter
 
@@
   dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
-  dat$gender_fish_df[sel] <- 2 * length(p_gender)
+  dat$gender_fish_df[sel] <- 2 * length(p_gender[p_gender > .05])
   dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
-                                   df = 2 * length(p_gender),
+                                   df = 2 * length(p_gender[p_gender > .05]),
                                    lower.tail = FALSE)
@@
   dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
-  dat$interaction_fish_df[sel] <- 2 * length(p_interaction)
+  dat$interaction_fish_df[sel] <- 2 * length(p_interaction[p_interaction > .05])
   dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
-                                        df = 2 * length(p_interaction),
+                                        df = 2 * length(p_interaction[p_interaction > .05]),
                                         lower.tail = FALSE)
+
+  # correct outcomes for those participants 
+  # who fabricated significant gender effects
+  if (pp == 'R_9XhjfXDjcchvSiF' | pp == 'R_3JEilrqcgWYTOkd')
+  {
+    dat$gender_fish[sel] <- NA
+    dat$gender_fish_df[sel] <- NA
+    dat$gender_fish_p[sel] <- NA
+
+    dat$interaction_fish[sel] <- NA
+    dat$interaction_fish_df[sel] <- NA
+    dat$interaction_fish_p[sel] <- NA
+
+  } 
 }
@@
 dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
-dat_summary$fish_combine <- -2 * (log(dat_summary$variance_sd_p) + log(dat_summary$gender_fish_p) + 
+dat_summary$fish_combine_3 <- -2 * (log(dat_summary$variance_sd_p_overall) + log(dat_summary$gender_fish_p) + 
                                       log(dat_summary$interaction_fish_p))
-dat_summary$fish_combine_p <- pchisq(q = dat_summary$fish_combine,
+dat_summary$fish_combine_3_p <- pchisq(q = dat_summary$fish_combine_3,
                                        df = 2 * 3, lower.tail = FALSE)
+dat_summary$fish_combine_6 <- -2 * (log(dat_summary$variance_sd_p_study1) +
+                                      log(dat_summary$variance_sd_p_study2) + 
+                                      log(dat_summary$variance_sd_p_study3) + 
+                                      log(dat_summary$variance_sd_p_study4) +
+                                      log(dat_summary$gender_fish_p) + 
+                                      log(dat_summary$interaction_fish_p))
+dat_summary$fish_combine_6_p <- pchisq(q = dat_summary$fish_combine_6,
+                                       df = 2 * 6, lower.tail = FALSE)
 
 write.csv(dat_summary,
-          'test.csv', row.names = FALSE)
+          dat_summary_file, row.names = FALSE)
 ```

### 2016-05-24 functions/compute_summary_anch_ml.R
Minor path updates

@@ -6,9 +6,9 @@ library(car)
 library(plyr)
 
 # Make it easy to switch to rmarkdown files (add ../)
-ml_dat_file <- 'data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
-summary_stat_file <- 'data/study_01/ml_summary_stats.csv'
-pdf_file <- 'archive/gender_interaction.pdf'
+ml_dat_file <- '../data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
+summary_stat_file <- '../data/study_01/ml_summary_stats.csv'
+pdf_file <- '../archive/gender_interaction.pdf'
 
 # GO
 ml_dat <- read.spss(ml_dat_file,

### 2016-05-24 functions/process_qualtrics_anch_01.R

@@ -2,8 +2,8 @@ if(!require(stringr)) install.packages('stringr')
 library(stringr)
 
 # Add ../ before running rmarkdown, or vice versa when not running there
-file <- 'data/study_01/raw_summary_results_fabrication_qualtrics.csv'
-res_file <- 'data/study_01/qualtrics_processed.csv'
+file <- '../data/study_01/raw_summary_results_fabrication_qualtrics.csv'
+res_file <- '../data/study_01/qualtrics_processed.csv'
 
 dat_qualtrics <- read.csv(file, stringsAsFactors = FALSE, na.strings = '')
 

### 2016-05-24 submission/manuscript.Rmd
Small update analysis script

@@
 ---
+
+```{r prepwork, echo = FALSE}
+if(!require(pROC)){install.packages('pROC')}
+library(pROC)
+if(!require(foreign)){install.packages('foreign')}
+library(foreign)
+
+# Compute the summary statistics for Many Labs
+source('../functions/compute_summary_anch_ml.R')
+# source('functions/compute_summary_anch_ml.R')
+# Process the collected, fabricated data
+source('../functions/process_qualtrics_anch_01.R')
+# source('functions/process_qualtrics_anch_01.R')
+
+# Read the data
+ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
+qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
+# ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
+# qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
+
+dat_summary_file <- '../data/study1_res.csv'
+```
+
 <!---
@@
 options(digits = 20)
-# Compute the summary statistics for Many Labs
-# source('../functions/compute_summary_anch_ml.R')
-source('functions/compute_summary_anch_ml.R')
-# Process the collected, fabricated data
-# source('../functions/process_qualtrics_anch_01.R')
-source('functions/process_qualtrics_anch_01.R')
-
-# Read the data
-# ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
-# qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
-ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
-qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
 ml$stat_know <- NA
@@
 ```{r compile results for detecting data fabrication, echo = FALSE}
-dat_summary_file <- 'data/study1_res.csv'
-
 # conduct the analyses iteratively
@@
   obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
-  # Add the sigma sd observed per study (NOT PREREGISTERED)
-  # Nog wijzigen adhv mva opmerkingen
+
   obs_sigma_sd_study1 <- sd(tilde_s2_1)
@@
 
-  iter <- 100000
+  iter <- 10
   s2 <- dat$anch_sd[dat$referrer == pp]^2
@@
 
+dat_summary <- read.csv(dat_summary_file)
+
+tp <- NULL
+fp <- NULL
+fn <- NULL
+tn <- NULL
+
+i <- 1
+
+for (threshold in seq(0, .1, .01))
+{
+  tp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+  fp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'ml', na.rm = TRUE)
+  fn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+  tn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'ml', na.rm = TRUE)
+
+  i <- i + 1
+}
+
+fpr <- fp / (fp + tn)
+tpr <- tp / (tp + fp)
+fnr <- fn / (fn + tp)
+tnr <- tn / (tn + fn)
 ```
-
-<!---
 
@@
 plot(perf)
-
+--->
 # Study 2

### 2016-05-24 functions/compute_summary_anch_ml.R
Make the ordering of qualtrics data and ml data equivalent (sort first on anchor, then partgender)

@@ -6,9 +6,9 @@ library(car)
 library(plyr)
 
 # Make it easy to switch to rmarkdown files (add ../)
-ml_dat_file <- '../data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
-summary_stat_file <- '../data/study_01/ml_summary_stats.csv'
-pdf_file <- '../archive/gender_interaction.pdf'
+ml_dat_file <- 'data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
+summary_stat_file <- 'data/study_01/ml_summary_stats.csv'
+pdf_file <- 'archive/gender_interaction.pdf'
 
 # GO
 ml_dat <- read.spss(ml_dat_file,
@@ -25,7 +25,7 @@ ml_dat$partgender <- ifelse(ml_dat$partgender == 1, NA,
 # listwise deletion of participants without gender
 ml_dat <- ml_dat[!is.na(ml_dat$partgender), ]
 
-summary_stat_1 <- ddply(ml_dat, .(referrer, partgender, anch1group), function(x){
+summary_stat_1 <- ddply(ml_dat, .(referrer, anch1group, partgender), function(x){
   anch1_n <- length(x$anchoring1[!is.na(x$anchoring1)])
   anch1_m <- mean(x$anchoring1, na.rm = TRUE)
   anch1_sd <- sd(x$anchoring1, na.rm = TRUE)
@@ -36,12 +36,12 @@ summary_stat_1 <- ddply(ml_dat, .(referrer, partgender, anch1group), function(x)
                anch1_sd,
                study))
 })
-names(summary_stat_1)[3:6] <- c('anchoring',
+names(summary_stat_1)[c(2,4:6)] <- c('anchoring',
                                 'anch_n',
                                 'anch_m',
                                 'anch_sd')
 
-summary_stat_2 <- ddply(ml_dat, .(referrer, partgender, anch2group), function(x){
+summary_stat_2 <- ddply(ml_dat, .(referrer, anch2group, partgender), function(x){
   anch2_n <- length(x$anchoring2[!is.na(x$anchoring2)])
   anch2_m <- mean(x$anchoring2, na.rm = TRUE)
   anch2_sd <- sd(x$anchoring2, na.rm = TRUE)
@@ -52,12 +52,12 @@ summary_stat_2 <- ddply(ml_dat, .(referrer, partgender, anch2group), function(x)
                anch2_sd,
[…]

### 2016-05-24 functions/concatenate_analyze_01.R
Move code to function file for oversight.

@@ -1,0 +1,341 @@
+options(digits = 20)
+
+# Read the data
+ml <- read.csv(ml_file, stringsAsFactors = FALSE)
+qualtrics <- read.csv(qualtrics_file, stringsAsFactors = FALSE)
+
+
+ml$stat_know <- NA
+ml$spss <- NA
+ml$rcran <- NA
+ml$stata <- NA
+ml$sas <- NA
+ml$matlab <- NA
+ml$python <- NA
+ml$other <- NA
+ml$nopro <- NA
+ml$noanch <- NA
+ml$rng <- NA
+ml$full <- NA
+ml$tries <- NA
+ml$descr <- NA
+ml$bonus <- NA
+ml$type <- 'ml'
+qualtrics$type <- 'qualtrics'
+
+dat <- rbind(qualtrics, ml)
+
+# conduct the analyses iteratively
+for (pp in unique(dat$referrer))
+{
+  # Loop through each study to compute the ANOVA results
+  for (j in 1:4)
+  {
+    indexor <- dat$referrer == pp & dat$study == j
+    
+    harm_mean <- 4^2/(sum(1/dat$anch_n[indexor]))
+    male_mean <- mean(dat$anch_m[indexor & dat$partgender == 0])
+    female_mean <- mean(dat$anch_m[indexor & dat$partgender == 1])
+    control_mean <- mean(dat$anch_m[indexor & dat$anchoring == 0])
+    exp_mean <- mean(dat$anch_m[indexor & dat$anchoring == 1])
+    
+    ss_error <- sum((dat$anch_n[indexor] - 1) * dat$anch_sd[indexor]^2)
+    ss_gender <- (harm_mean * var(c(male_mean, female_mean))) / 2
+    ss_condition <- (harm_mean * var(c(control_mean, exp_mean))) / 2
+    ss_interaction <- harm_mean * var(dat$anch_m[indexor]) * 3/4 - ss_gender - ss_condition
+    ss_total <- ss_error + ss_gender + ss_condition + ss_interaction
+    
+    ms_error <- ss_error / (sum(dat$anch_n[indexor]) - 4)
+    ms_gender <- ss_gender / (2 - 1)
+    ms_condition <- ss_condition / (2 - 1)
+    ms_interaction <- ss_interaction / 1
+    
[…]

### 2016-05-24 submission/manuscript.Rmd
Some minor code shifting and updating.

--- 2016-05-23 submission/manuscript.Rmd
@@
 ---
+
+```{r prepwork, echo = FALSE}
+VsuppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
+suppressPackageStartupMessages(library(pROC))
+suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
+suppressPackageStartupMessages(library(foreign))
+
+# Add ../ before running rmarkdown, or vice versa when not running there
+x12 <- '../'
+x12 <- ''
+ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
+dat_summary_file <- sprintf('%sdata/study1_res.csv', x12)
+file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
+res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
+ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
+summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
+
+# Set the number of iterations to use in calculations
+iter <- 100000
+
+# Compute the summary statistics for Many Labs
+source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
+# Process the collected, fabricated data
+source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
+# Concatenate, analyze, and write out all ML and qualtrics data
+# Uncomment this line to rerun
+set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
+
+```
+
 <!---
@@
 ### Results.
-```{r prep data study 1, echo = FALSE}
-options(digits = 20)
-# Compute the summary statistics for Many Labs
-# source('../functions/compute_summary_anch_ml.R')
-source('functions/compute_summary_anch_ml.R')
-# Process the collected, fabricated data
-# source('../functions/process_qualtrics_anch_01.R')
-source('functions/process_qualtrics_anch_01.R')
+```{r inspect results to detect data fabrication, echo = FALSE}
 
-# Read the data
-# ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
-# qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
-ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
-qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
-ml$stat_know <- NA
-ml$spss <- NA
-ml$rcran <- NA
-ml$stata <- NA
-ml$sas <- NA
-ml$matlab <- NA
-ml$python <- NA
-ml$other <- NA
-ml$nopro <- NA
-ml$noanch <- NA
-ml$rng <- NA
-ml$full <- NA
-ml$tries <- NA
-ml$descr <- NA
-ml$bonus <- NA
-ml$type <- 'ml'
-qualtrics$type <- 'qualtrics'
+dat_summary <- read.csv(dat_summary_file)
 
-dat <- rbind(qualtrics, ml)
-```
+tp <- NULL
+fp <- NULL
+fn <- NULL
+tn <- NULL
 
-```{r compile results for detecting data fabrication, echo = FALSE}
-dat_summary_file <- 'data/study1_res.csv'
+i <- 1
 
-# conduct the analyses iteratively
-for (pp in unique(dat$referrer))
+for (threshold in seq(0, .1, .01))
 {
-  # Loop through each study to compute the ANOVA results
-  for (j in 1:4)
-  {
-    indexor <- dat$referrer == pp & dat$study == j
+  tp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+  fp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'ml', na.rm = TRUE)
+  fn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+  tn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'ml', na.rm = TRUE)
 
-    harm_mean <- 4^2/(sum(1/dat$anch_n[indexor]))
-    male_mean <- mean(dat$anch_m[indexor & dat$partgender == 0])
-    female_mean <- mean(dat$anch_m[indexor & dat$partgender == 1])
-    control_mean <- mean(dat$anch_m[indexor & dat$anchoring == 0])
-    exp_mean <- mean(dat$anch_m[indexor & dat$anchoring == 1])
-
-    ss_error <- sum((dat$anch_n[indexor] - 1) * dat$anch_sd[indexor]^2)
-    ss_gender <- (harm_mean * var(c(male_mean, female_mean))) / 2
-    ss_condition <- (harm_mean * var(c(control_mean, exp_mean))) / 2
-    ss_interaction <- harm_mean * var(dat$anch_m[indexor]) * 3/4 - ss_gender - ss_condition
-    ss_total <- ss_error + ss_gender + ss_condition + ss_interaction
-
-    ms_error <- ss_error / (sum(dat$anch_n[indexor]) - 4)
-    ms_gender <- ss_gender / (2 - 1)
-    ms_condition <- ss_condition / (2 - 1)
-    ms_interaction <- ss_interaction / 1
-
-    dat$f_gender[indexor] <- ms_gender / ms_error
-    dat$df1_gender[indexor] <- 2 - 1
-    dat$df2_gender[indexor] <- sum(dat$anch_n[indexor]) - 4
-    dat$p_gender[indexor] <- pf(q = ms_gender / ms_error,
-                                df1 = 2 - 1,
-                                df2 = sum(dat$anch_n[indexor]) - 4,
-                                lower.tail = FALSE)
-
-    dat$f_condition[indexor] <- ms_condition / ms_error
-    dat$df1_condition[indexor] <- 2 - 1
-    dat$df2_condition[indexor] <- sum(dat$anch_n[indexor]) - 4
-    dat$p_condition[indexor] <- pf(q = ms_condition / ms_error,
-                                   df1 = 2 - 1,
-                                   df2 = sum(dat$anch_n[indexor]) - 4,
-                                   lower.tail = FALSE)
-
-    dat$f_interaction[indexor] <- ms_interaction / ms_error
-    dat$df1_interaction[indexor] <- 1
-    dat$df2_interaction[indexor] <- sum(dat$anch_n[indexor]) - 4
-    dat$p_interaction[indexor] <- pf(q = ms_interaction / ms_error,
-                                     df1 = 1,
-                                     df2 = sum(dat$anch_n[indexor]) - 4,
-                                     lower.tail = FALSE)
+  i <- i + 1
 }
 
-  sel <- dat$referrer == pp
-
-  # Variance analysis
-  # Standardizing the sds
-
-  # Study 1
-  sel1 <- dat$referrer == pp & dat$study == 1
-  ms_w_1 <- sum((dat$anch_n[sel1] - 1) * dat$anch_sd[sel1]^2) / sum((dat$anch_n[sel1] - 1))
-  tilde_s2_1 <- dat$anch_sd[sel1]^2 / ms_w_1
-  # Study 2
-  sel2 <- dat$referrer == pp & dat$study == 2
-  ms_w_2 <- sum((dat$anch_n[sel2] - 1) * dat$anch_sd[sel2]^2) / sum((dat$anch_n[sel2] - 1))
-  tilde_s2_2 <- dat$anch_sd[sel2]^2 / ms_w_2
-  # Study 3
-  sel3 <- dat$referrer == pp & dat$study == 3
-  ms_w_3 <- sum((dat$anch_n[sel3] - 1) * dat$anch_sd[sel3]^2) / sum((dat$anch_n[sel3] - 1))
-  tilde_s2_3 <- dat$anch_sd[sel3]^2 / ms_w_3
-  # Study 4
-  sel4 <- dat$referrer == pp & dat$study == 4
-  ms_w_4 <- sum((dat$anch_n[sel4] - 1) * dat$anch_sd[sel4]^2) / sum((dat$anch_n[sel4] - 1))
-  tilde_s2_4 <- dat$anch_sd[sel4]^2 / ms_w_4
-
-  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
-
-  iter <- 100000
-  s2 <- dat$anch_sd[dat$referrer == pp]^2
-  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
-  ms_w <- c(rep(ms_w_1, 4), rep(ms_w_2, 4),
-            rep(ms_w_3, 4), rep(ms_w_4, 4))
-  sim_sigma <- NULL
-
-  for (z in 1:16)
-  {
-    sim_sigma <- cbind(sim_sigma, ((rchisq(n = iter, df = n_min_1[z]) *  s2[z]) / n_min_1[z]) / ms_w[z])
-  }
-
-  sim_sigma_sd <- apply(sim_sigma, 1, sd)
-
-  dat$variance_sd_p[sel] <- sum(sim_sigma_sd < obs_sigma_sd) / iter
-
-  # Compute the Fisher method p-values 
-  # for gender and interaction
-
-  # Safety check to make sure there are 4 unique values
-  # Iteratively made exceptions for the cases that do not
-  if (length(unique(dat$p_gender[sel])) < 4 | 
-      # length(unique(dat$p_condition[sel])) < 4 |
-      length(unique(dat$p_interaction[sel])) < 4)
-  {
-    if (pp == 'R_6opw4qQURhqxT3D')
-    {
-      p_gender <- rep(1, 4)
-    } else
-    {
-      stop(sprintf('Something wrong with the number of p-values available for %s',
-                   pp))
-    }
-  } else 
-  {
-    p_gender <- unique(dat$p_gender[sel])  
-  }
-
-  dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
-  dat$gender_fish_df[sel] <- 2 * length(p_gender)
-  dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
-                                   df = 2 * length(p_gender),
-                                   lower.tail = FALSE)
-
-  p_interaction <- unique(dat$p_interaction[sel])
-  dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
-  dat$interaction_fish_df[sel] <- 2 * length(p_interaction)
-  dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
-                                        df = 2 * length(p_interaction),
-                                        lower.tail = FALSE)
-}
-
-dat_summary <- dat[ , -which(names(dat) %in% c("study",
-                                               "partgender",
-                                               "anchoring",
-                                               "anch_n",
-                                               "anch_m",
-                                               "anch_sd",
-                                               "f_gender",
-                                               "df1_gender",
-                                               "df2_gender",
-                                               "p_gender",
-                                               "f_condition",
-                                               "df1_condition",
-                                               "df2_condition",
-                                               "p_condition",
-                                               "f_interaction",
-                                               "df1_interaction",
-                                               "df2_interaction",
-                                               "p_interaction"))]
-dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
-dat_summary$fish_combine <- -2 * (log(dat_summary$variance_sd_p) + log(dat_summary$gender_fish_p) + 
-        log(dat_summary$interaction_fish_p))
-dat_summary$fish_combine_p <- pchisq(q = dat_summary$fish_combine,
-                                     df = 2 * 3, lower.tail = FALSE)
-
-write.csv(dat_summary,
-          'test.csv', row.names = FALSE)
+fpr <- fp / (fp + tn)
+tpr <- tp / (tp + fp)
+fnr <- fn / (fn + tp)
+tnr <- tn / (tn + fn)
 ```
-
-```{r inspect results to detect data fabrication, echo = FALSE}
-
-```
-
-<!---
 

### 2016-05-24 functions/compute_summary_anch_ml.R

@@ -5,11 +5,6 @@ library(foreign)
 library(car)
 library(plyr)
 
-# Make it easy to switch to rmarkdown files (add ../)
-ml_dat_file <- 'data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
-summary_stat_file <- 'data/study_01/ml_summary_stats.csv'
-pdf_file <- 'archive/gender_interaction.pdf'
-
 # GO
 ml_dat <- read.spss(ml_dat_file,
                     to.data.frame = TRUE,

### 2016-05-24 functions/process_qualtrics_anch_01.R

@@ -1,10 +1,6 @@
 if(!require(stringr)) install.packages('stringr')
 library(stringr)
 
-# Add ../ before running rmarkdown, or vice versa when not running there
-file <- '../data/study_01/raw_summary_results_fabrication_qualtrics.csv'
-res_file <- '../data/study_01/qualtrics_processed.csv'
-
 dat_qualtrics <- read.csv(file, stringsAsFactors = FALSE, na.strings = '')
 
 # Remove the description of the question

### 2016-05-24 submission/manuscript.Rmd
Rerun analysis etc.

@@
 qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
-dat_summary_file <- sprintf('%sdata/study1_res.csv', x12)
+dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
 file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)

### 2016-05-30 submission/manuscript.Rmd
APS2016 talk commit

@@
 ```{r prepwork, echo = FALSE}
-VsuppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
+suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
 suppressPackageStartupMessages(library(pROC))
@@
 # Uncomment this line to rerun
-set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
+# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
 
@@
 ```{r inspect results to detect data fabrication, echo = FALSE}
+# Read in datafile, just in case the computations were not re-run.
+dat_summary <- read.csv(dat_summary_file)
+dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
+# Select only those from qualtrics who did for bonus
 
-dat_summary <- read.csv(dat_summary_file)
+type_index <- which(names(dat_summary) == 'type')
 
-tp <- NULL
-fp <- NULL
-fn <- NULL
-tn <- NULL
+temp <- dat_summary[, c(type_index, 18:45)]
 
+# ggplot(temp) +
+#   facet_grid ()
+# geom_density(aes(Result, group = type, col = type)) + 
+#   xlab(title_name)
+# 
+# p <- ggplot(temp)
+# for (i in 18:45)
+# {
+#   temp <- dat_summary[, c(type_index, i)]  
+#   title_name <- names(temp)[2]
+#   names(temp)[2] <- 'Result'
+#   
+#   ggplot(temp) +
+#     geom_density(aes(Result, group = type, col = type)) + 
+#     xlab(title_name)
+# }
+# dev.off()
+
+tp <- matrix(NA, ncol = 20, nrow = 101)
+fp <- matrix(NA,ncol = 20, nrow = 101)
+fn <- matrix(NA,ncol = 20, nrow = 101)
+tn <- matrix(NA,ncol = 20, nrow = 101)
+
+temp <- names(dat_summary)[c(18:31, 34, 37, 39, 41, 43, 45)]
+
+j <- 1
+
+for (variables in c(18:31, 34, 37, 39, 41, 43, 45))
+{
   i <- 1
 
-for (threshold in seq(0, .1, .01))
+  for (threshold in seq(0, 1, .01))
   {
-  tp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
-  fp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'ml', na.rm = TRUE)
-  fn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
-  tn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'ml', na.rm = TRUE)
+    tp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    fp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'ml', na.rm = TRUE)
+    fn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    tn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'ml', na.rm = TRUE)
 
@@
 
-fpr <- fp / (fp + tn)
-tpr <- tp / (tp + fp)
-fnr <- fn / (fn + tp)
-tnr <- tn / (tn + fn)
+  j <- j + 1
+}
+
+# loop through matrix for proper comps
+
+for (i in 1:20)
+{
+  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
+  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
+  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
+  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])
+
+  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
+  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
+  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
+  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
+}
+fpr <- as.data.frame(fpr)
+tpr <- as.data.frame(tpr)
+fnr <- as.data.frame(fnr)
+tnr <- as.data.frame(tnr)
+
+ppv <- as.data.frame(ppv)
+fdr <- as.data.frame(fdr)
+npv <- as.data.frame(npv)
+false_or <- as.data.frame(false_or)
+
+names(fpr) <- temp
+names(tpr) <- temp
+names(fnr) <- temp
+names(tnr) <- temp
+
+names(ppv) <- temp
+names(fdr) <- temp
+names(npv) <- temp
+names(false_or) <- temp
+
+for(i in 1:20)
+{
+  plot(fpr[, i], tpr[, i],
+       type = 's', xlim = c(0,1), ylim = c(0,1), main = names(fpr)[i],
+       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
+  abline(a = 0, b = 1)
+}
+
+tp[6,which(temp == 'fish_combine_3_hetero_p')]
+fp[6,which(temp == 'fish_combine_3_hetero_p')]
+fn[6,which(temp == 'fish_combine_3_hetero_p')]
+tn[6,which(temp == 'fish_combine_3_hetero_p')]
+
+plot(fpr$fish_combine_3_hetero_p, tpr$fish_combine_3_hetero_p,
+     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Fisher combined',
+     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
+abline(a = 0, b = 1)
+roc(response = dat_summary$type, predictor = dat_summary$fish_combine_3_hetero_p)
+
+height = (tpr$fish_combine_3_hetero_p[-1]+tpr$fish_combine_3_hetero_p[-length(tpr$fish_combine_3_hetero_p)])/2
+width = diff(fpr$fish_combine_3_hetero_p) # = diff(rev(omspec))
+sum(height*width)
+
+plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
+     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
+     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
+abline(a = 0, b = 1)
+roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_homo)
+
+height = (tpr$variance_sd_p_overall_homo[-1]+tpr$variance_sd_p_overall_homo[-length(tpr$variance_sd_p_overall_homo)])/2
+width = diff(fpr$variance_sd_p_overall_homo) # = diff(rev(omspec))
+sum(height*width)
+
+plot(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
+     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
+     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
+abline(a = 0, b = 1)
+roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_hetero)
+
+height = (tpr$variance_sd_p_overall_hetero[-1]+tpr$variance_sd_p_overall_hetero[-length(tpr$variance_sd_p_overall_hetero)])/2
+width = diff(fpr$variance_sd_p_overall_hetero) # = diff(rev(omspec))
+sum(height*width)
+
+plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
+     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
+     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
+abline(a = 0, b = 1)
+lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
+     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
+     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)
+
+legend(x = 0, y = 1, bty = 'n', lty = c(1, 2), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
+
+plot(x = roc(response = dat_summary$type,
+             predictor = dat_summary$fish_combine_3_hetero_p,
+             percent = TRUE,
+             ci = TRUE,
+             of = 'se',
+             sp = seq(0, 100, 5)), ci.type="shape")
+
+plot(x = roc(response = dat_summary$type,
+             predictor = dat_summary$variance_sd_p_overall_homo,
+             percent = TRUE,
+             ci = TRUE,
+             of = 'se',
+             sp = seq(0, 100, 5)), ci.type="shape")
+
+for (i in c(18,23))
+{
+  plot(x = roc(response = dat_summary$type,
+               predictor = dat_summary[, i],
+               percent = TRUE,
+               ci = TRUE,
+               of = 'se',
+               sp = seq(0, 100, 5)), ci.type="shape", main = names(dat_summary)[i])
+}
+
+plot(fpr[,1], tpr[,1], type = 's')
+lines(fpr[,6], tpr[,6], type = 's')
+
+plot(x = roc(response = dat_summary$type,
+             predictor = dat_summary$variance_sd_p_overall_homo,
+             percent = TRUE,
+             ci = TRUE,
+             of = 'se',
+             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
+plot(x = fpr$variance_sd_p_overall_homo, y = tpr$variance_sd_p_overall_homo, type = 's')
+
+plot(x = roc(response = dat_summary$type,
+             predictor = dat_summary$variance_sd_p_overall_hetero,
+             percent = TRUE,
+             ci = TRUE,
+             of = 'se',
+             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
+plot(x = fpr$variance_sd_p_overall_hetero, y = tpr$variance_sd_p_overall_hetero, type = 's')
 ```
 
-library(ROCR)
-data(ROCR.simple)
-pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
-perf <- performance(pred,"tpr","fpr")
-plot(perf)
---->
+<!---
+
 # Study 2

### 2016-08-02 submission/manuscript.Rmd
Update manuscript files; start port to Sweave

@@
 title: "Ecological validity of detecting data fabrication in experimental studies."
-author: "Chris HJ Hartgerink"
+author: "Chris HJ Hartgerink, Jelte M Wicherts, Marcel ALM van Assen"
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 x12 <- '../'
-x12 <- ''
-ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
-qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
-dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
-file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
-res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
-ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
-summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
-pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
-
-# Set the number of iterations to use in calculations
-iter <- 100000
-
-# Compute the summary statistics for Many Labs
-source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
-# Process the collected, fabricated data
-source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
-# Concatenate, analyze, and write out all ML and qualtrics data
-# Uncomment this line to rerun
-# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
-
+# x12 <- ''
 ```
@@
 An estimated 2% of all researchers admit to having fabricated data at least once, and 14% have said to have witnessed someone fabricate data [@fanelli2009].
-In stark contrast to plagiarism, which has a similar admittance rate but double the witness rate [@pupovac2015], no systems are implemented during the editorial process to detect problematic data, although at least one journal is considering such a system (Miller 2015).
+In stark contrast to plagiarism, which has a similar admittance rate but double the witness rate [@pupovac2015], hardly any systems are implemented during the editorial process to detect problematic data.
+Recently, one journal has explicitly stated they are considering such a system (Miller 2015), another is looking BMC SCIENCEMATTERS.
 Editors and reviewers hardly pay attention to potential problems with the data during the editor process either (Bornmann et al.
@@
 
-To test the validity of statistical methods to detect data fabrication in summary results, we investigated summary results of four anchoring studies [@tversky1974;@jacowitz1995].
-We selected the anchoring effect because it is a well-known psychological phenomenon and many genuine data sets on the effect are available from the Many Labs project [@klein2014].
-The unit of analysis for this study is the set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
-Respondent is defined here as either one of the Many Labs locations, or a researcher who fabricated the four anchoring studies' summary statistics.
+```{r, echo = FALSE}
+# Dynamically generate path names
+ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
+dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
+file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
+res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
+ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
+summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
+
+# Set the number of iterations to use in calculations
+iter <- 100000
+
+# Compute the summary statistics for Many Labs
+source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
+# Process the collected, fabricated data
+source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
+# Concatenate, analyze, and write out all ML and qualtrics data
+# Uncomment this line to rerun
+# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
+```
+
+We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies [@tversky1974;@jacowitz1995].
+The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
+For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'.
+These questions yield mean responses of 25\% and 45\%, respectively [@tversky1974], despite essentially posing the same factual question.
+A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
 
@@
 Each of the four studies provided summary results for a 2 (low/high anchoring) × 2 (male/female) factorial design.
+Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
+Respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
+All materials, data, and analyses scripts are freely available on the OSF ([osf.io/b24pq](osf.io/b24pq)) and were preregistered ([osf.io/ejf5x](osf.io/ejf5x); deviations are explicated in this report).
 
@@
 
-Thirty-six genuine datasets were collected from the publicly available Many Labs project [@klein2014, osf.io/pqf9r].
-The Many Labs (ML) project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
+We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project [@klein2014, [osf.io/pqf9r](osf.io/pqf9r)].
+The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
 Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were collected for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., 48 × 36).
-These summary statistics were collected from the raw ML data, which were cleaned using the original analyses scripts from the ML project to ensure that the data did not contain improper responses.
+For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed, for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
+We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
 
-<!---
-```{r}
-# Insert the data collection from Many Labs in here (directly!)
-```
---->
-
-<!---
-Replace thirty-six with actual number
---->
-
-Thirty-six fabricated sets of summary results were also collected for all four anchoring studies.
-We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS).
-Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995;@tversky1974], for which summary results were fabricated.
-U.S.
-researchers were sampled to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies.
+Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
+The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
+We sampled psychology researchers to improve familiarity with the anchoring effect [@jacowitz1995;@tversky1974], for which summary results were fabricated.
+We filtered for U.S.
+researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
+researchers were included because this filter also retained papers with co-authors from the U.S.).
 WoS was searched on October 13, 2015.
@@
 
-The full sample frame was digitally approached to participate in this study on April XX, 2016 (invitation: osf.io/s4w8r).
-The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-address saved at all).
-The researchers were fully informed that the study would require them to fabricate data and that we conducted this study to test the validity of statistical methods to detect data fabrication.
-Participants were also informed they could stop at any time without providing a reason.
-If they wanted, participants received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address.
-These email addresses were unlinked from email addresses upon completion of the study and sending out the gift cards.
+A random sample of 1,000 researchers were digitally approached to participate in this study on April 25, 2016 (invitation: [osf.io/s4w8r](osf.io/s4w8r)).
+The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
+We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication.
+We also clarified to the  respondents that they could stop at any time without providing a reason.
+If they wanted, respondents received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address, after which they could win an additional $50 Amazon gift card if they were one of three top fabricators.
+The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
+The text of the Qualtrics survey is available at [osf.io/w984b](osf.io/w984b).
 
-Each respondent was instructed to fabricate 32 summary statistics (4 studies × 2 conditions × 2 sexes × 2 statistics [mean and sd]) that fulfilled three hypotheses.
+Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
+We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
 Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
-We instructed participants to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
 The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
 
-In order to standardize the fabrication process to a minimal extent, we provided participants with a spreadsheet where the fabricated data had to be filled out.
-Figure `r fig <- 1; fig` depicts an example of this spreadsheet.
-The yellow cells are those that the respondent is requested to fabricate and include both the means and the standard deviations.
+We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they choose to fabricate data.
+Figure `r fig <- 1; fig` depicts an example of this spreadsheet (original:  [osf.io/w6v4u](osf.io/w6v4u)).
+We requested the respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
 Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
-When these results corroborate the given expectations, a checkmark appears as in the green cells in Figure `r fig`.
-We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format.
+When these results confirm the hypotheses, a checkmark appears as depicted in the green cells.
+We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
 
@@
 
-**Figure `r fig`.** Example of a filled in spreadsheet used in the fabrication process.
+**Figure `r fig`.** Example of a filled in template spreadsheet used in the fabrication process.
+Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
+If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell.
 
-Upon completing the fabrication of the data, participants were debriefed.
-Several questions were asked about their statistical knowledge and approach to data fabrication, and they were reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
-The full set of questions from the study are available at osf.io/w984b.
+Upon completing the fabrication of the data, respondents were debriefed.
+Several questions were asked about their statistical knowledge and approach to data fabrication.
+They were also reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
 
-Participation was rewarded with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card.
+We rewarded participation with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card.
 If the participant wanted to receive a compensation and contend for the bonus $50, he/she had to enter an email to receive the reward.
 These email addresses were unlinked from individual responses upon sending the gift cards.
-Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum).
+Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
 
@@
 
+tpr <- matrix(NA, ncol = 20, nrow = 101)
+fpr <- matrix(NA,ncol = 20, nrow = 101)
+fnr <- matrix(NA,ncol = 20, nrow = 101)
+tnr <- matrix(NA,ncol = 20, nrow = 101)
+
+ppv <- matrix(NA, ncol = 20, nrow = 101)
+fdr <- matrix(NA,ncol = 20, nrow = 101)
+npv <- matrix(NA,ncol = 20, nrow = 101)
+false_or <- matrix(NA,ncol = 20, nrow = 101)
+
 for (i in 1:20)
@@
 legend(x = 0, y = 1, bty = 'n', lty = c(1, 2), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
-
-plot(x = roc(response = dat_summary$type,
-             predictor = dat_summary$fish_combine_3_hetero_p,
-             percent = TRUE,
-             ci = TRUE,
-             of = 'se',
-             sp = seq(0, 100, 5)), ci.type="shape")
-
-plot(x = roc(response = dat_summary$type,
-             predictor = dat_summary$variance_sd_p_overall_homo,
-             percent = TRUE,
-             ci = TRUE,
-             of = 'se',
-             sp = seq(0, 100, 5)), ci.type="shape")
-
-for (i in c(18,23))
-{
-  plot(x = roc(response = dat_summary$type,
-               predictor = dat_summary[, i],
-               percent = TRUE,
-               ci = TRUE,
-               of = 'se',
-               sp = seq(0, 100, 5)), ci.type="shape", main = names(dat_summary)[i])
-}
-
-plot(fpr[,1], tpr[,1], type = 's')
-lines(fpr[,6], tpr[,6], type = 's')
-
-plot(x = roc(response = dat_summary$type,
-             predictor = dat_summary$variance_sd_p_overall_homo,
-             percent = TRUE,
-             ci = TRUE,
-             of = 'se',
-             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
-plot(x = fpr$variance_sd_p_overall_homo, y = tpr$variance_sd_p_overall_homo, type = 's')
-
-plot(x = roc(response = dat_summary$type,
-             predictor = dat_summary$variance_sd_p_overall_hetero,
-             percent = TRUE,
-             ci = TRUE,
-             of = 'se',
-             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
-plot(x = fpr$variance_sd_p_overall_hetero, y = tpr$variance_sd_p_overall_hetero, type = 's')
 ```

### 2016-08-02 submission/manuscript.Rnw
Update manuscript files; start port to Sweave

\documentclass{article}

\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{hyperref}
\bibliographystyle{apalike}

\title{Ecological validity of detecting data fabrication in experimental studies.}
\author{Chris HJ Hartgerink, Jelte M Wicherts, Marcel ALM van Assen}

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle

<<prepwork, echo=FALSE,results=hide>>=
suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
suppressPackageStartupMessages(library(latex2exp))

# Add ../ before running rmarkdown, or vice versa when not running there
x12 <- '../'
# x12 <- ''
@

\section*{Study 1}

<<data prepper, echo=FALSE,results=hide>>=
# Dynamically generate path names
ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)

# Set the number of iterations to use in calculations
iter <- 100000

# Compute the summary statistics for Many Labs
source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
# Process the collected, fabricated data
source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
# Concatenate, analyze, and write out all ML and qualtrics data
# Uncomment this line to rerun
# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
@

We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies \citep{tversky1974,jacowitz1995}. The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity. For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'. These questions yield mean responses of 25\% and 45\%, respectively \citep{tversky1974}, despite essentially posing the same factual question. A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.

\subsection*{Methods}

The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States. Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. Respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. All materials, data, and analyses scripts are freely available on the OSF (\url{osf.io/b24pq}) and were preregistered (\url{osf.io/ejf5x}; deviations are explicated in this report).

\subsubsection*{Data collection}

We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{osf.io/pqf9r};][]{klein2014}. The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously. Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine. For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed, for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$). We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.

Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies. The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S. We sampled psychology researchers to improve familiarity with the anchoring effect \citep{jacowitz1995,tversky1974}, for which summary results were fabricated. We filtered for U.S. researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S. researchers were included because this filter also retained papers with co-authors from the U.S.). WoS was searched on October 13, 2015. In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).

A random sample of 1,000 researchers were digitally approached to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved). We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication. We also clarified to the  respondents that they could stop at any time without providing a reason. If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation for which they had to provide their email address, after which they could win an additional \$50 Amazon gift card if they were one of three top fabricators. The provided email addresses were unlinked from individual responses upon sending the bonus gift cards. The full text of the Qualtrics survey is available at \url{osf.io/w984b}.

Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses. We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex. Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori. The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.

We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they choose to fabricate data. Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{osf.io/w6v4u}). We requested the respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions. Using these values, statistical tests are computed and shown in the "Current result" column instantaneously. When these results confirm the hypotheses, a checkmark appears as depicted in the green cells. We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet.png}
\caption{Example of a filled in template spreadsheet used in the fabrication process. Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests. If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell.}
\label{fig1}
\end{center}
\end{figure}

Upon completing the fabrication of the data, respondents were debriefed. Several questions were asked about their statistical knowledge and approach to data fabrication. They were also reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.

We rewarded participation with a \$30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus \$50 Amazon gift card. If the participant wanted to receive a compensation and contend for the bonus \$50, he/she had to enter an email to receive the reward. These email addresses were unlinked from individual responses upon sending the gift cards. Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).

\subsubsection*{Data analysis}

To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies. Such methods test whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes. For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples. To compute this test, we first standardized the SDs for each of the four studies by computing
\begin{equation}
z_j=\sqrt{\frac{s^2_j}{MS_w}}=\sqrt{\frac{s^2_j}{\left(\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}\right)}}
\label{s2_j}
\end{equation}
where $z_j$ denotes the standardized SD in group $j$ ($MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells, which is the case for the fabricated datasets). We tested different measures to detect data fabrication that utilize these standardized SDs (i.e., $z_j$). We included the variance of the standardized SDs \citep[i.e.,  $SD_{z}$;][]{simonsohn2013} and tried out the max-min distance of the standardized SDs (denoted $max-min_{z}$) as an alternative measure. We compared the observed value for each measure with the expected distribution when the summary results are used to generate random samples. To this end, we simulated the expected distribution of standardized SDs and computed the expected distribution of each measure. This expected distribution was used to determine the $p$-value of the observed $SD_z$ and $max-min_z$. We simulated the standardized variance for each of the $j$ groups as
\begin{equation}
z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
\label{simvar}
\end{equation}
These simulated values are used to compute the expected distribution of the $SD_z$ and $max-min_z$  measures.

Second, we applied the reversed Fisher method to the nonsignificant $p$-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication. The Fisher method \citep{fisher1925} tests for evidence of an effect in a set of $p$-values by testing for a right-skew $p$-value distribution, but we adjusted it here to test for results that are overly consistent with the null hypothesis and result in a left-skew distribution (see Figure \ref{leftskew}). The original Fisher method is computed as
\begin{equation}
\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
\label{fishertest}
\end{equation}
and tests for right-skew in a set of $p$-values, but we adjust it to the following
\begin{equation}
\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
\label{fisheradjusted}
\end{equation}
where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$. We set this threshold to .05 in order to include only nonsignificant test results.

<<figure, echo = FALSE, results = hide>>=
if(!file.exists(sprintf('%sfigures/fisherfig.pdf', x12)))
{
  pdf(sprintf('%sfigures/fisherfig.pdf', x12), width = 14, height = 7)
  par(mar = c(5, 5, 3, 1), mfrow = c(1, 2))

  plot(dbeta(seq(0, 1, .001), .05, 1),
       x = seq(0, 1, .001), type = 'l',
       bty = 'n', xlab = 'P-value', ylab = 'Density',
       main = '(A) Right-skew')
  lines(dunif(seq(0, 1, .001)),
        x = seq(0, 1, .001), lty = 2)
  plot(dbeta(seq(0, 1, .001), 1, .05),
       x = seq(0, 1, .001), type = 'l',
       bty = 'n', xlab = 'P-value', ylab = 'Density',
       main = '(B) Left-skew')
  lines(dunif(seq(0, 1, .001)),
        x = seq(0, 1, .001), lty = 2)

  dev.off()
}
@

% add plot of left and right skew
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/fisherfig.pdf}
\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and our adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B). Both panels test whether there is sufficient evidence that the solid line deviates from the dashed line, except that the type of deviation that the test is sensitive to is the exact opposite.}
\label{leftskew}
\end{center}
\end{figure}

Finally, we combined the three methods to detect data fabrication into an overall detection method (i.e., combination method). This included the $SD_z$ measure and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.  We expected this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications. Based on the results of the combined test results, the three least detectable data fabricators were selected. The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional $50 Amazon gift card.

For each of these four tests to detect data fabrication ($SD_z$, Fisher test per hypothesis, combination method) we carried out sensitivity and specificity analyses using ROC-curves. With these ROC-curves, more informed decisions about optimal alpha levels can be made. In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1. The optimal alpha level was determined by finding that alpha level for which the combination of true positive rate (TPR) and the true negative rate (TNR) were highest. For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.

\subsection*{Results}

\bibliography{../bibliography/library}
\end{document}

### 2016-08-02 submission/manuscript.tex
Update manuscript files; start port to Sweave

--- 2016-08-02 submission/manuscript.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+\input{manuscript-concordance}
 \maketitle
 
-<<prepwork, echo=FALSE,results=hide>>=
-suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
-suppressPackageStartupMessages(library(pROC))
-suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
-suppressPackageStartupMessages(library(foreign))
-suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
-suppressPackageStartupMessages(library(latex2exp))
-
-# Add ../ before running rmarkdown, or vice versa when not running there
-x12 <- '../'
-# x12 <- ''
-@
-
 \section*{Study 1}
-
-<<data prepper, echo=FALSE,results=hide>>=
-# Dynamically generate path names
-ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
-qualtrics_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
-dat_summary_file <- sprintf('%sdata/study_01/study1_res.csv', x12)
-file <- sprintf('%sdata/study_01/raw_summary_results_fabrication_qualtrics.csv', x12)
-res_file <- sprintf('%sdata/study_01/qualtrics_processed.csv', x12)
-ml_dat_file <- sprintf('%sdata/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav', x12)
-summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
-pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
-
-# Set the number of iterations to use in calculations
-iter <- 100000
-
-# Compute the summary statistics for Many Labs
-source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
-# Process the collected, fabricated data
-source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
-# Concatenate, analyze, and write out all ML and qualtrics data
-# Uncomment this line to rerun
-# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
-@
 
@@
 \chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
-\label{fishertest}
+\label{fisher}
 \end{equation}
@@
 We set this threshold to .05 in order to include only nonsignificant test results.
-
-<<figure, echo = FALSE, results = hide>>=
-if(!file.exists(sprintf('%sfigures/fisherfig.pdf', x12)))
-{
-  pdf(sprintf('%sfigures/fisherfig.pdf', x12), width = 14, height = 7)
-  par(mar = c(5, 5, 3, 1), mfrow = c(1, 2))
-
-  plot(dbeta(seq(0, 1, .001), .05, 1),
-       x = seq(0, 1, .001), type = 'l',
-       bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(A) Right-skew')
-  lines(dunif(seq(0, 1, .001)),
-        x = seq(0, 1, .001), lty = 2)
-  plot(dbeta(seq(0, 1, .001), 1, .05),
-       x = seq(0, 1, .001), type = 'l',
-       bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(B) Left-skew')
-  lines(dunif(seq(0, 1, .001)),
-        x = seq(0, 1, .001), lty = 2)
-
-  dev.off()
-}
-@
 
@@
 
-Finally, we combined the three methods to detect data fabrication into an overall detection method (i.e., combination method).
-This included the $SD_z$ measure and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
-We expected this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications.
-Based on the results of the combined test results, the three least detectable data fabricators were selected.
-The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional $50 Amazon gift card.
-
-For each of these four tests to detect data fabrication ($SD_z$, Fisher test per hypothesis, combination method) we carried out sensitivity and specificity analyses using ROC-curves.
-With these ROC-curves, more informed decisions about optimal alpha levels can be made.
-In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1.
-The optimal alpha level was determined by finding that alpha level for which the combination of true positive rate (TPR) and the true negative rate (TNR) were highest.
-For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.
+% Finally, we combined the results of these three individual tests for data fabrication using the Fisher method.
+We expect this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests.
+Based on the results of the combined test results, the three 'best' data fabricators are selected.
+The three respondents with the highest *p*-values contain the least evidential value for deviating from genuine data and receive an additional $50 Amazon gift card.
+% 
+% For each of these three tests to detect data fabrication we carry out sensitivity and specificity analyses using ROC-curves in order to determine optimal alpha levels.
+This analysis helps determine the classification performance of these three tests.
+In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1 and assessed the classification performance of these methods to detect data fabrication.
+The optimal alpha level is determined by finding that alpha level for which both the true positive classification rate and the true negative classification rate are highest.
+For example,
 

### 2016-09-01 functions/concatenate_analyze_01.R
Retain p-values in final dataset

@@ -417,15 +417,14 @@ dat_summary <- dat[ , -which(names(dat) %in% c("study",
                                                "f_gender",
                                                "df1_gender",
                                                "df2_gender",
-                                               "p_gender",
+                                               # "p_gender",
                                                "f_condition",
                                                "df1_condition",
                                                "df2_condition",
-                                               "p_condition",
+                                               # "p_condition",
                                                "f_interaction",
                                                "df1_interaction",
-                                               "df2_interaction",
-                                               "p_interaction"))]
+                                               "df2_interaction"))]
 dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
 dat_summary$fish_combine_3_homo <- -2 * (log(dat_summary$variance_sd_p_overall_homo) +
                                            log(dat_summary$gender_fish_p) + 

### 2016-09-01 submission/manuscript.Rnw
Update manuscript files

@@
 \usepackage{hyperref}
+\usepackage{adjustbox}
 \bibliographystyle{apalike}
 
-\title{Ecological validity of detecting data fabrication in experimental studies.}
+\title{Ecological performance of detecting data fabrication with summary statistics}
 \author{Chris HJ Hartgerink, Jelte M Wicherts, Marcel ALM van Assen}
@@
 suppressPackageStartupMessages(library(latex2exp))
+suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2')})
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra')})
+suppressPackageStartupMessages(library(gridExtra))
+suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable')})
+suppressPackageStartupMessages(library(xtable))
+suppressPackageStartupMessages(if(!require(httr)){install.packages('httr')})
+suppressPackageStartupMessages(library(httr))
 
@@
 # Concatenate, analyze, and write out all ML and qualtrics data
-# Uncomment this line to rerun
-# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
+# Uncomment this line to rerun, but take care: might take a while
+if(!file.exists(sprintf('%sdata/study_01/study1_res.csv', x12)))
+{
+  set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))  
+}
 @
@@
 Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
-Respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
+For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
 All materials, data, and analyses scripts are freely available on the OSF (\url{osf.io/b24pq}) and were preregistered (\url{osf.io/ejf5x}; deviations are explicated in this report).
@@
 Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed, for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
+For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
 We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
@@
 Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
+Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
 The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
@@
 
-A random sample of 1,000 researchers were digitally approached to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}).
+A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 We also clarified to the  respondents that they could stop at any time without providing a reason.
-If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation for which they had to provide their email address, after which they could win an additional \$50 Amazon gift card if they were one of three top fabricators.
+If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation if they were willing to enter their email address.
+They could win an additional \$50 Amazon gift card if they were one of three top fabricators.
 The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
@@
 
-We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they choose to fabricate data.
+We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data.
 Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{osf.io/w6v4u}).
-We requested the respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
+We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
 Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
-When these results confirm the hypotheses, a checkmark appears as depicted in the green cells.
+If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure \ref{fig1}.
 We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
@@
 Upon completing the fabrication of the data, respondents were debriefed.
-Several questions were asked about their statistical knowledge and approach to data fabrication.
-They were also reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
-
+Respondents answered several questions about their statistical knowledge and approach to data fabrication and finally we reminded them that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
 We rewarded participation with a \$30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus \$50 Amazon gift card.
-If the participant wanted to receive a compensation and contend for the bonus \$50, he/she had to enter an email to receive the reward.
-These email addresses were unlinked from individual responses upon sending the gift cards.
-Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
 
@@
 To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies.
-Such methods test whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
+This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
 For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
-To compute this test, we first standardized the SDs for each of the four studies by computing
+To compute this probability, we first standardized the SDs for each of the four studies with
 \begin{equation}
@@
 
-Second, we applied the reversed Fisher method to the nonsignificant $p$-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
+Testing the standardized SDs for potential data fabrication can be done either for each study separately or all studies combined; the test can also be done under different assumptions of population variances across conditions.
+The assumptions of population variance can either by that all SDs originate from the same distribution \citep[as in][]{simonsohn2013}, the SDs within a factor are from the same distribution, or each group comes from its own distribution.
+We preregistered the method that assumes the SDs are drawn from the same distribution for the various conditions (i.e., homogeneous SDs) and are tested across all studies.
+However, upon conducting the analyses, we decided homogenous SDs are not unequivocal and included computations where the SDs for the low anchor and high anchor are from different distributions (i.e., heterogeneous SDs).
+Additionally, the signal for data fabrication across the four anchoring studies might result in different studies cancelling each other out, so we also included analyses where each study was analyzed separately.
+
+Second, we applied the reversed Fisher method to detect data fabrication to the nonsignificant $p$-values twice: once for the results of gender effects hypothesis in each study and once for the results of the interaction effect hypothesis for each study.
 The Fisher method \citep{fisher1925} tests for evidence of an effect in a set of $p$-values by testing for a right-skew $p$-value distribution, but we adjusted it here to test for results that are overly consistent with the null hypothesis and result in a left-skew distribution (see Figure \ref{leftskew}).
@@
        bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(A) Right-skew')
+       main = '(A) Right-skew (normal)')
   lines(dunif(seq(0, 1, .001)),
@@
        bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(B) Left-skew')
+       main = '(B) Left-skew (potentially anomalous)')
   lines(dunif(seq(0, 1, .001)),
         x = seq(0, 1, .001), lty = 2)
-
+  abline(v = .05, lty = 3)
+  text(x = .15, y = 33, labels = "<- Threshold")
   dev.off()
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/fisherfig.pdf}
-\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and our adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B).
+\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and what the adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B).
 Both panels test whether there is sufficient evidence that the solid line deviates from the dashed line, except that the type of deviation that the test is sensitive to is the exact opposite.}
@@
 Finally, we combined the three methods to detect data fabrication into an overall detection method (i.e., combination method).
-This included the $SD_z$ measure and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
-We expected this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications.
+This included the $SD_z$ measure across all studies and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
+We expected this combination test of the three individual tests for data fabrication to be more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications.
 Based on the results of the combined test results, the three least detectable data fabricators were selected.
-The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional $50 Amazon gift card.
+The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional \$50 Amazon gift card.
 
-For each of these four tests to detect data fabrication ($SD_z$, Fisher test per hypothesis, combination method) we carried out sensitivity and specificity analyses using ROC-curves.
+For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combination method) we carried out sensitivity and specificity analyses using ROC-curves.
 With these ROC-curves, more informed decisions about optimal alpha levels can be made.
@@
 The optimal alpha level was determined by finding that alpha level for which the combination of true positive rate (TPR) and the true negative rate (TNR) were highest.
-For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.
+For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.
 
@@
 
+<<read in data, echo = FALSE, results = hide>>=
+# Read in datafile, just in case the computations were not re-run.
+dat_summary <- read.csv(dat_summary_file)
+# Select only those from qualtrics who did for bonus
+# removed <- sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))
+# dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
+
+type_index <- which(names(dat_summary) == 'type')
+temp <- dat_summary[, c(type_index, 18:length(names(dat_summary)))]  
+dat_summary$es_gender <- sqrt(dat_summary$es2_gender)
+dat_summary$es_condition <- sqrt(dat_summary$es2_condition)
+dat_summary$es_interaction <- sqrt(dat_summary$es2_interaction)
+
+# naming just for ease of use later
+dat_summary$es_p <- 1 - dat_summary$es_condition
+
+if(!file.exists(sprintf('%sfigures/ddfab_density.pdf', x12)))
+{
+  pdf(sprintf('%sfigures/ddfab_density.pdf', x12), width = 10, height = 7)
+  # Gender
+  plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    ylim(0, 1.5) + 
+    scale_fill_discrete(guide=FALSE) + 
+    ggtitle('Gender')
+
+  plot_es_gender <- ggplot(dat_summary, aes(x = es_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Condition
+  plot_p_condition <- ggplot(dat_summary, aes(x = p_condition, fill = type)) +
+    geom_density(alpha = .3) +
+    xlim(0, 1) +
+    xlab(TeX("$P$-value")) +
+    ylab("Density") +
+    scale_fill_discrete(labels = c("Genuine","Fabricated")) + 
+    theme(legend.position="top") + 
+    ggtitle('Condition')
+
+  plot_p_condition$labels$fill <- ""
+
+  plot_es_condition <- ggplot(dat_summary, aes(x = es_condition, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlim(0, 1) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Interaction
+  plot_p_interaction <- ggplot(dat_summary, aes(x = p_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE) +
+    ylim(0, 1.5) +
+    ggtitle('Interaction')
+
+  plot_es_interaction <- ggplot(dat_summary, aes(x = es_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Plot
+  grid.arrange(plot_p_gender,
+               plot_p_condition,
+               plot_p_interaction,
+               plot_es_gender,
+               plot_es_condition,
+               plot_es_interaction,
+               ncol = 3)
+  dev.off()
+}
+@
+
+The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{osf.io/e6zys}).
+\Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus.
+Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
+Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+
+% add plot of left and right skew
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/ddfab_density.pdf}
+\caption{Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.}
+\label{densities}
+\end{center}
+\end{figure}
+
+The distributions in Figure \ref{densities} indicate little difference between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large differences when subjects were required to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have raised initial suspicions previously.
+These data confirm that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, nonetheless).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+
+<<generate results p/method, echo = FALSE, results = hide>>=
+tp <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fp <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
+
+j <- 1
+
+for (variables in which(grepl(names(dat_summary), pattern = "_p")))
+{
+  i <- 1
+
+  for (threshold in seq(0, 1, .01))
+  {
+    tp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    fp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'ml', na.rm = TRUE)
+    fn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    tn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'ml', na.rm = TRUE)
+
+    i <- i + 1
+  }
+
+  j <- j + 1
+}
+
+# loop through matrix for proper comps
+
+tpr <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fpr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+ppv <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fdr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+npv <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+false_or <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+for (i in 1:sum(grepl(names(dat_summary), pattern = "_p")))
+{
+  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
+  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
+  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
+  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])
+
+  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
+  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
+  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
+  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
+}
+fpr <- as.data.frame(fpr)
+tpr <- as.data.frame(tpr)
+fnr <- as.data.frame(fnr)
+tnr <- as.data.frame(tnr)
+
+ppv <- as.data.frame(ppv)
+fdr <- as.data.frame(fdr)
+npv <- as.data.frame(npv)
+false_or <- as.data.frame(false_or)
+
+names(fpr) <- temp
+names(tpr) <- temp
+names(fnr) <- temp
+names(tnr) <- temp
+
+names(ppv) <- temp
+names(fdr) <- temp
+names(npv) <- temp
+names(false_or) <- temp
+
+height = (tpr[-1, ] + tpr[-dim(tpr)[1], ])/2
+width = apply(fpr, 2, diff) # = diff(rev(omspec))
+AUC_res <- apply(height * width, 2, sum)
+
+Method <- c("$SD_z$ homogeneous all",
+                    "$SD_z$ study 1",
+                    "$SD_z$ study 2",
+                    "$SD_z$ study 3",
+                    "$SD_z$ study 4",
+                    "$maxmin_z$ homogeneous all",
+                    "$maxmin_z$ study 1",
+                    "$maxmin_z$ study 2",
+                    "$maxmin_z$ study 3",
+                    "$maxmin_z$ study 4",
+                    "$SD_z$ heterogeneous all",
+                    "$SD_z$ study 1 low condition",
+                    "$SD_z$ study 1 high condition",
+                    "$SD_z$ study 2 low condition",
+                    "$SD_z$ study 2 high condition",
+                    "$SD_z$ study 3 low condition",
+                    "$SD_z$ study 3 high condition",
+                    "$SD_z$ study 4 low condition",
+                    "$SD_z$ study 4 high condition",
+                    "$maxmin_z$ heterogeneous all",
+                    "$maxmin_z$ study 1 low condition",
+                    "$maxmin_z$ study 1 high condition",
+                    "$maxmin_z$ study 2 low condition",
+                    "$maxmin_z$ study 2 high condition",
+                    "$maxmin_z$ study 3 low condition",
+                    "$maxmin_z$ study 3 high condition",
+                    "$maxmin_z$ study 4 low condition",
+                    "$maxmin_z$ study 4 high condition",
+                    "Fisher test gender hypothesis",
+                    "Fisher test interaction hypothesis",
+                    "Combined Fisher test (3 results, $SD_z$ homogeneous)",
+                    "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
+                    "Combined Fisher test (6 results, $SD_z$ homogeneous)",
+                    "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
+                    "Effect sizes (1-r)")
+AUC <- as.numeric(AUC_res)
+# print(xtable(data.frame(Method, AUC),
+#              caption = "Area Under the Curve (AUC) for the various statistical methods used to detect data fabrication.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.",
+#              label = "auc", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+
+@
+
+\subsubsection*{Performance of using SDs to detect data fabrication}
+
+<<AUC for variance methods, echo=FALSE, results=tex>>=
+selmaxmin <- grepl(Method, pattern = '^.maxmin_')
+selsd <- grepl(x = Method, pattern = '^.SD_z')
+row_table <- c("Homogeneous combined",
+                    "Homogeneous study 1",
+                    "Homogeneous study 2",
+                    "Homogeneous study 3",
+                    "Homogeneous study 4",
+                    "Heterogeneous combined",
+                    "Study 1 low condition",
+                    "Study 1 high condition",
+                    "Study 2 low condition",
+                    "Study 2 high condition",
+                    "Study 3 low condition",
+                    "Study 3 high condition",
+                    "Study 4 low condition",
+                    "Study 4 high condition")
+variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
+names(variances_table) <- c("Method", "$SD_z$", "$maxmin_z$")
+print(xtable(variances_table,
+             caption = "Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.",
+             label = "auc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+<<generate variance ROC, echo=FALSE, results=hide>>=
+if(!file.exists(sprintf('%sfigures/varianceplot.pdf', x12)))
+{
+  pdf(sprintf('%sfigures/varianceplot.pdf', x12), width = 8, height = 6)
+  plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
+       type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance analysis',
+       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)
+  abline(a = 0, b = 1)
+  lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
+        type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
+        xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 1)
+  legend(x = 0, y = 1, bty = 'n', lty = c(2, 1), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
+  dev.off()
+}
+@
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/varianceplot.pdf}
+\caption{PLACEHOLDER}
+\label{varianceplot}
+\end{center}
+\end{figure}
+
+\subsubsection*{Performance of using $p$-values to detect data fabrication}
+
+We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
+Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
+).
+However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance.
+In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
+
+<<AUC for single fisher methods, echo=FALSE, results=tex>>=
+sel <- grepl(Method, pattern = '^(Fisher test)')
+row_table <- Method[sel]
+tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+print(xtable(tabl,
+             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
+             label = "auc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+\subsubsection*{Performance of combining SDs and $p$-value methods to detect data fabrication}
+
+<<AUC for combined fisher methods, echo=FALSE, results=tex>>=
+sel <- grepl(Method, pattern = 'Combined Fisher test')
+row_table <- Method[sel]
+tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+print(xtable(tabl,
+             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
+             label = "auc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+\subsubsection*{Performance of large effect sizes to detect data fabrication}
+
+<<get massive statcheck data for checks, echo=FALSE, results=hide>>=
+if(!file.exists(sprintf('%sdata/statcheck_dataset.csv', x12)))
+{
+  url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
+  # If link is broken, more persistent version availabl at
+  # http://dx.doi.org/10.17026/dans-2cm-v9j9
+
+  GET(url,
+      write_disk(sprintf('%sdata/statcheck_dataset.csv', x12),
+                 overwrite = TRUE))
+}
+
+statcheck_data <- read.csv(sprintf('%sdata/statcheck_dataset.csv', x12))
+# Compute the effect sizes
+sel <- statcheck_data$Statistic == 'F'
+statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel] *
+                                  (statcheck_data$df1[sel] /
+                                     statcheck_data$df2[sel])) /
+                                 (((statcheck_data$Value[sel] *
+                                      statcheck_data$df1[sel]) /
+                                     statcheck_data$df2[sel]) + 1))
+
+sel <- statcheck_data$Statistic == 't'
+statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel]^2 *
+                                  (1 / statcheck_data$df2[sel])) /
+                                 (((statcheck_data$Value[sel]^2 * 1) /
+                                     statcheck_data$df2[sel]) + 1))
+
+sel <- statcheck_data$Statistic == 'r' &
+  statcheck_data$Value <= 1 &
+  statcheck_data$Value > 0
+statcheck_data$es[sel] <- statcheck_data$Value[sel]
+@
+
+%The \Sexpr{sum(dat_summary$es_condition > max(dat_summary$es_condition[dat_summary$type == 'ml']))} largest significant effects were fabricated, with \Sexpr{sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9)} (\Sexpr{round(sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9) / sum(dat_summary$type == 'qualtrics'), 3)}\%) larger than $r=.9$.
+Based on descriptive data throughout psychology \citep{Hartgerink2016-lg}, effect sizes $\geq.9$ belong to the \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .9) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile of effects throughout the psychology literature and effect sizes $\geq.95$ \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .95) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile.
+
+\subsection*{Discussion}
+
+% variance analysis and effect size best ways to inspect
+% but severely correlated: smaller variances = larger effects
+% easiest way is too look for massive effects in the effects
+
+% Simonsohn method not invalid under homogeneous, just somethign to take into account
+% easily adjusted
+
+% Discuss how the PPV is likely to be overestimated because prevalence is 50% in this study
+% How we don't know the prevalence, in fact.
+
 \bibliography{../bibliography/library}
+\newpage
+%------------------------------------
+%handy to include this at the end
+%------------------------------------
+\section*{SessionInfo}
+%-------------------------------------
+
+<<sessionInfo>>=
+
+sessionInfo()
+
+@
+
 \end{document}

### 2016-09-01 submission/manuscript.tex
Update manuscript files

@@
 \chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
-\label{fisher}
+\label{fishertest}
 \end{equation}
@@
 
-% Finally, we combined the results of these three individual tests for data fabrication using the Fisher method.
-We expect this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests.
-Based on the results of the combined test results, the three 'best' data fabricators are selected.
-The three respondents with the highest *p*-values contain the least evidential value for deviating from genuine data and receive an additional $50 Amazon gift card.
-% 
-% For each of these three tests to detect data fabrication we carry out sensitivity and specificity analyses using ROC-curves in order to determine optimal alpha levels.
-This analysis helps determine the classification performance of these three tests.
-In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1 and assessed the classification performance of these methods to detect data fabrication.
-The optimal alpha level is determined by finding that alpha level for which both the true positive classification rate and the true negative classification rate are highest.
-For example,
+Finally, we combined the three methods to detect data fabrication into an overall detection method (i.e., combination method).
+This included the $SD_z$ measure across all studies and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
+We expected this combination test of the three individual tests for data fabrication to be more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications.
+Based on the results of the combined test results, the three least detectable data fabricators were selected.
+The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional \$50 Amazon gift card.
+
+For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combination method) we carried out sensitivity and specificity analyses using ROC-curves.
+With these ROC-curves, more informed decisions about optimal alpha levels can be made.
+In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1.
+The optimal alpha level was determined by finding that alpha level for which the combination of true positive rate (TPR) and the true negative rate (TNR) were highest.
+For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.
 
@@
 
+The collected data included 36 genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and 39 fabricated datasets(\url{osf.io/e6zys}).
+3 participants did not participate for a bonus.
+Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
+Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+
+% add plot of left and right skew
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/ddfab_density.pdf}
+\caption{Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.}
+\label{densities}
+\end{center}
+\end{figure}
+
+The distributions in Figure \ref{densities} indicate little difference between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large differences when subjects were required to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have raised initial suspicions previously.
+These data confirm that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, nonetheless).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+
+\subsubsection*{Performance of using SDs to detect data fabrication}
+
+% latex table generated in R 3.3.1 by xtable 1.8-2 package
+% Thu Sep  1 17:46:56 2016
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrr}
+  \hline
+Method & $SD_z$ & $maxmin_z$ \\ 
+  \hline
+Homogeneous combined & 0.423 & 0.303 \\ 
+  Homogeneous study 1 & 0.368 & 0.374 \\ 
+  Homogeneous study 2 & 0.421 & 0.446 \\ 
+  Homogeneous study 3 & 0.510 & 0.521 \\ 
+  Homogeneous study 4 & 0.540 & 0.542 \\ 
+  Heterogeneous combined & 0.770 & 0.756 \\ 
+  Study 1 low condition & 0.643 & 0.643 \\ 
+  Study 1 high condition & 0.438 & 0.438 \\ 
+  Study 2 low condition & 0.751 & 0.751 \\ 
+  Study 2 high condition & 0.612 & 0.612 \\ 
+  Study 3 low condition & 0.668 & 0.668 \\ 
+  Study 3 high condition & 0.651 & 0.651 \\ 
+  Study 4 low condition & 0.796 & 0.796 \\ 
+  Study 4 high condition & 0.555 & 0.555 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.}
+\label{auc_variances}
+\end{table}
+
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/varianceplot.pdf}
+\caption{PLACEHOLDER}
+\label{varianceplot}
+\end{center}
+\end{figure}
+
+\subsubsection*{Performance of using $p$-values to detect data fabrication}
+
+We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
+Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
+).
+However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance.
+In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
+
+% latex table generated in R 3.3.1 by xtable 1.8-2 package
+% Thu Sep  1 17:46:56 2016
+\begin{table}[ht]
+\centering
+\begin{tabular}{lr}
+  \hline
+Method & AUC \\ 
+  \hline
+Fisher test gender hypothesis & 0.521 \\ 
+  Fisher test interaction hypothesis & 0.535 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Curve (AUC) for PLACEHOLDER} 
+\label{auc_fisher}
+\end{table}
+\subsubsection*{Performance of combining SDs and $p$-value methods to detect data fabrication}
+
+% latex table generated in R 3.3.1 by xtable 1.8-2 package
+% Thu Sep  1 17:46:56 2016
+\begin{table}[ht]
+\centering
+\begin{tabular}{lr}
+  \hline
+Method & AUC \\ 
+  \hline
+Combined Fisher test (3 results, $SD_z$ homogeneous) & 0.602 \\ 
+  Combined Fisher test (3 results, $SD_z$ heterogeneous) & 0.736 \\ 
+  Combined Fisher test (6 results, $SD_z$ homogeneous) & 0.643 \\ 
+  Combined Fisher test (6 results, $SD_z$ heterogeneous) & 0.643 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Curve (AUC) for PLACEHOLDER} 
+\label{auc_combined}
+\end{table}
+
+\subsubsection*{Performance of large effect sizes to detect data fabrication}
+
+%The 23 largest significant effects were fabricated, with 13 (0.333\%) larger than $r=.9$.
+Based on descriptive data throughout psychology \citep{Hartgerink2016-lg}, effect sizes $\geq.9$ belong to the 96th percentile of effects throughout the psychology literature and effect sizes $\geq.95$ 98th percentile.
+
+\subsection*{Discussion}
+
+% variance analysis and effect size best ways to inspect
+% but severely correlated: smaller variances = larger effects
+% easiest way is too look for massive effects in the effects
+
+% Simonsohn method not invalid under homogeneous, just somethign to take into account
+% easily adjusted
+
+% Discuss how the PPV is likely to be overestimated because prevalence is 50% in this study
+% How we don't know the prevalence, in fact.
+
 \bibliography{../bibliography/library}
+\newpage
+%------------------------------------
+%handy to include this at the end
+%------------------------------------
+\section*{SessionInfo}
+%-------------------------------------
+
+\begin{Schunk}
+\begin{Sinput}
+> sessionInfo()
+\end{Sinput}
+\begin{Soutput}
+R version 3.3.1 (2016-06-21)
+Platform: x86_64-redhat-linux-gnu (64-bit)
+Running under: Fedora 23 (Workstation Edition)
+
+locale:
+ [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
+ [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
+ [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
+ [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
+ [9] LC_ADDRESS=C               LC_TELEPHONE=C            
+[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C
+
+attached base packages:
+[1] stats     graphics  grDevices utils     datasets  methods   base
+
+other attached packages:
+ [1] stringr_1.0.0   plyr_1.8.4      car_2.0-19      httr_1.2.0     
+ [5] xtable_1.8-2    gridExtra_2.2.1 ggplot2_2.1.0   latex2exp_0.4.0
+ [9] foreign_0.8-66  pROC_1.8
+
+loaded via a namespace (and not attached):
+ [1] Rcpp_0.12.6      MASS_7.3-45      R6_2.1.2         grid_3.3.1      
+ [5] gtable_0.2.0     magrittr_1.5     scales_0.4.0     stringi_1.1.1   
+ [9] tools_3.3.1      munsell_0.4.3    colorspace_1.2-6 nnet_7.3-12     
+\end{Soutput}
+\begin{Sinput}
+> 
+\end{Sinput}
+\end{Schunk}
+
 \end{document}

### 2016-09-05 submission/manuscript.Rnw
Update methods

@@
 We set this threshold to .05 in order to include only nonsignificant test results.
+The theoretical idea behind this method is that researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution, given the frequent misinterpretation of $p$-values \citep[e.g., as the probability of an effect,][]{Goodman2008135,Altman_1995}.
+% I can add more refs but it is just a rabbit hole to start with more.
 
@@
 
-Finally, we combined the three methods to detect data fabrication into an overall detection method (i.e., combination method).
+Finally, we combined the aforementioned methods to detect data fabrication with the Fisher method.
 This included the $SD_z$ measure across all studies and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
@@
 
-For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combination method) we carried out sensitivity and specificity analyses using ROC-curves.
-With these ROC-curves, more informed decisions about optimal alpha levels can be made.
-In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1.
-The optimal alpha level was determined by finding that alpha level for which the combination of true positive rate (TPR) and the true negative rate (TNR) were highest.
-For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.7$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, then .05 was chosen as an optimal decision criterion based on the sample.
+For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combined methods) we carried out sensitivity and specificity analyses using ROC-curves.
+ROC-curves indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
+With these ROC-curves, informed decisions about optimal alpha levels can be made based on various criteria.
+In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest.
+For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.
 

### 2016-09-05 submission/manuscript.Rnw
Update results

@@
 
-The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{osf.io/e6zys}).
-\Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus.
+The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{osf.io/e6zys}; \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus).
+
 Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
-Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
+These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
 
@@
 \end{figure}
-
-The distributions in Figure \ref{densities} indicate little difference between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large differences when subjects were required to fabricate significant data (i.e., condition hypothesis).
-From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have raised initial suspicions previously.
-These data confirm that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, nonetheless).
-Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
 
@@
 width = apply(fpr, 2, diff) # = diff(rev(omspec))
-AUC_res <- apply(height * width, 2, sum)
+auroc_res <- apply(height * width, 2, sum)
 
@@
                     "Effect sizes (1-r)")
-AUC <- as.numeric(AUC_res)
-# print(xtable(data.frame(Method, AUC),
-#              caption = "Area Under the Curve (AUC) for the various statistical methods used to detect data fabrication.
+auroc <- as.numeric(auroc_res)
+# print(xtable(data.frame(Method, auroc),
+#              caption = "Area Under the Receiver Operating Curve (AUROC) for the various statistical methods used to detect data fabrication.
 Homogeneous: assumes one population variance underlying all groups.
 Heterogeneous: assumes separate population variance per anchoring condition.",
-#              label = "auc", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+#              label = "auroc", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 
@@
 
-<<AUC for variance methods, echo=FALSE, results=tex>>=
+We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
+The $SD_z$ method \citep{simonsohn2013} inspects whether there the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs.
+Table \ref{auroc_variances} indicates that both methods have similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC).
+
+The AUROC value indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
+In other words, if $AUROC=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+Considering this, we will regard any AUROC$<.6$ as plainly insufficient for detecting data fabrication, $.6\leq AUROC<.7$ as failed, $.7\leq AUROC<.8$ as sufficient, $.8\leq AUROC<.9$ as good, and $.9\leq AUROC\leq 1$ as excellent.
+
+<<auroc for variance methods, echo=FALSE, results=tex>>=
 selmaxmin <- grepl(Method, pattern = '^.maxmin_')
 selsd <- grepl(x = Method, pattern = '^.SD_z')
-row_table <- c("Homogeneous combined",
-                    "Homogeneous study 1",
-                    "Homogeneous study 2",
-                    "Homogeneous study 3",
-                    "Homogeneous study 4",
-                    "Heterogeneous combined",
-                    "Study 1 low condition",
-                    "Study 1 high condition",
-                    "Study 2 low condition",
-                    "Study 2 high condition",
-                    "Study 3 low condition",
-                    "Study 3 high condition",
-                    "Study 4 low condition",
-                    "Study 4 high condition")
-variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
-names(variances_table) <- c("Method", "$SD_z$", "$maxmin_z$")
+row_table <- c("Homogeneous, combined",
+                    "Homogeneous, study 1",
+                    "Homogeneous, study 2",
+                    "Homogeneous, study 3",
+                    "Homogeneous, study 4",
+                    "Heterogeneous, combined",
+                    "Heterogeneous study 1, low anchor condition",
+                    "Heterogeneous study 1, high anchor condition",
+                    "Heterogeneous study 2, low anchor condition",
+                    "Heterogeneous study 2, high anchor condition",
+                    "Heterogeneous study 3, low anchor condition",
+                    "Heterogeneous study 3, high anchor condition",
+                    "Heterogeneous study 4, low anchor condition",
+                    "Heterogeneous study 4, high anchor condition")
+variances_table <- data.frame(Method = row_table, SDz = auroc[selsd], maxminz = auroc[selmaxmin])
+names(variances_table) <- c("Method", "auroc $SD_z$", "auroc $maxmin_z$")
 print(xtable(variances_table,
-             caption = "Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances.
+             caption = "Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
 Homogeneous: assumes one population variance underlying all groups.
 Heterogeneous: assumes separate population variance per anchoring condition.",
-             label = "auc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             label = "auroc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
@@
 We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
-Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
-).
-However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance.
+Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
 In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
 
-<<AUC for single fisher methods, echo=FALSE, results=tex>>=
+<<auroc for single fisher methods, echo=FALSE, results=tex>>=
 sel <- grepl(Method, pattern = '^(Fisher test)')
 row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+tabl <- data.frame(Method = row_table, auroc = auroc[sel])
 print(xtable(tabl,
-             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
-             label = "auc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
@@
 
-<<AUC for combined fisher methods, echo=FALSE, results=tex>>=
+<<auroc for combined fisher methods, echo=FALSE, results=tex>>=
 sel <- grepl(Method, pattern = 'Combined Fisher test')
 row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+tabl <- data.frame(Method = row_table, auroc = auroc[sel])
 print(xtable(tabl,
-             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
-             label = "auc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
@@
 
+% Discuss alpha choice based on sample has large error (small sample).
+% Only provides a first indication
+
+% Comparison between methods not tested, large error given small sample.
+% This provides just initial work
+
 \bibliography{../bibliography/library}

### 2016-09-05 submission/manuscript.tex
Update manuscript generated files

@@
 
-The collected data included 36 genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and 39 fabricated datasets(\url{osf.io/e6zys}).
-3 participants did not participate for a bonus.
+The collected data included 36 genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and 39 fabricated datasets(\url{osf.io/e6zys}; 3 participants did not participate for a bonus).
+
 Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
-Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
+These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
 
@@
 
-The distributions in Figure \ref{densities} indicate little difference between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large differences when subjects were required to fabricate significant data (i.e., condition hypothesis).
-From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have raised initial suspicions previously.
-These data confirm that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, nonetheless).
-Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
-
 \subsubsection*{Performance of using SDs to detect data fabrication}
 
+We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
+The $SD_z$ method \citep{simonsohn2013} inspects whether there the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs.
+Table \ref{auroc_variances} indicates that both methods have similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC).
+
+The AUROC value indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
+In other words, if $AUROC=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+Considering this, we will regard any AUROC$<.6$ as plainly insufficient for detecting data fabrication, $.6\leq AUROC<.7$ as failed, $.7\leq AUROC<.8$ as sufficient, $.8\leq AUROC<.9$ as good, and $.9\leq AUROC\leq 1$ as excellent.
+
 % latex table generated in R 3.3.1 by xtable 1.8-2 package
-% Thu Sep  1 17:46:56 2016
+% Mon Sep  5 09:04:38 2016
 \begin{table}[ht]
@@
   \hline
-Method & $SD_z$ & $maxmin_z$ \\ 
+Method & auroc $SD_z$ & auroc $maxmin_z$ \\ 
   \hline
-Homogeneous combined & 0.423 & 0.303 \\ 
-  Homogeneous study 1 & 0.368 & 0.374 \\ 
-  Homogeneous study 2 & 0.421 & 0.446 \\ 
-  Homogeneous study 3 & 0.510 & 0.521 \\ 
-  Homogeneous study 4 & 0.540 & 0.542 \\ 
-  Heterogeneous combined & 0.770 & 0.756 \\ 
-  Study 1 low condition & 0.643 & 0.643 \\ 
-  Study 1 high condition & 0.438 & 0.438 \\ 
-  Study 2 low condition & 0.751 & 0.751 \\ 
-  Study 2 high condition & 0.612 & 0.612 \\ 
-  Study 3 low condition & 0.668 & 0.668 \\ 
-  Study 3 high condition & 0.651 & 0.651 \\ 
-  Study 4 low condition & 0.796 & 0.796 \\ 
-  Study 4 high condition & 0.555 & 0.555 \\ 
+Homogeneous, combined & 0.423 & 0.303 \\ 
+  Homogeneous, study 1 & 0.368 & 0.374 \\ 
+  Homogeneous, study 2 & 0.421 & 0.446 \\ 
+  Homogeneous, study 3 & 0.510 & 0.521 \\ 
+  Homogeneous, study 4 & 0.540 & 0.542 \\ 
+  Heterogeneous, combined & 0.770 & 0.756 \\ 
+  Heterogeneous study 1, low anchor condition & 0.643 & 0.643 \\ 
+  Heterogeneous study 1, high anchor condition & 0.438 & 0.438 \\ 
+  Heterogeneous study 2, low anchor condition & 0.751 & 0.751 \\ 
+  Heterogeneous study 2, high anchor condition & 0.612 & 0.612 \\ 
+  Heterogeneous study 3, low anchor condition & 0.668 & 0.668 \\ 
+  Heterogeneous study 3, high anchor condition & 0.651 & 0.651 \\ 
+  Heterogeneous study 4, low anchor condition & 0.796 & 0.796 \\ 
+  Heterogeneous study 4, high anchor condition & 0.555 & 0.555 \\ 
    \hline
 \end{tabular}
-\caption{Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances.
+\caption{Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
 Homogeneous: assumes one population variance underlying all groups.
 Heterogeneous: assumes separate population variance per anchoring condition.}
-\label{auc_variances}
+\label{auroc_variances}
 \end{table}
@@
 We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
-Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
-).
-However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance.
+Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
 In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
@@
 % latex table generated in R 3.3.1 by xtable 1.8-2 package
-% Thu Sep  1 17:46:56 2016
+% Mon Sep  5 09:04:38 2016
 \begin{table}[ht]
@@
   \hline
-Method & AUC \\ 
+Method & auroc \\ 
   \hline
@@
 \end{tabular}
-\caption{Area Under the Curve (AUC) for PLACEHOLDER} 
-\label{auc_fisher}
+\caption{Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER} 
+\label{auroc_fisher}
 \end{table}
@@
 \end{tabular}
-\caption{Area Under the Curve (AUC) for PLACEHOLDER} 
-\label{auc_combined}
+\caption{Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER} 
+\label{auroc_combined}
 \end{table}
@@
 % How we don't know the prevalence, in fact.
+
+% Discuss alpha choice based on sample has large error (small sample).
+% Only provides a first indication
+
+% Comparison between methods not tested, large error given small sample.
+% This provides just initial work
 

### 2016-09-22 archive/response_ori_rev.md
Add first run at reviewer comments ORI grant

# Response to reviewers ORIIR160019-01-00

We thank the reviewer for the time taken to look at and think about our proposal. Below, we respond point-by-point to the different weaknesses mentioned by the reviewer.

# Reviewer remark 1
The application does not provide clear evidence that the type of misconduct to which scientists admit is aligned with the kind of misconduct that the proposed methods would be able to address.

## Response

We never aimed to support such claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed.

# Reviewer remark 2

The application did not explain why it only focuses on social and medical sciences.

## Response

We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures and our familiarity with the measures applied here. We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields.

# Reviewer remark 3

The Principal Investigator does not have experience overseeing a large project given that he is still emerging as a scientist in a Ph.D. program.

## Response

The PI will be supervised during this process by the PhD supervisors, who cumulatively have managed projects amounting to approximately 4 million euro's.

# Reviewer remark 4

There is no investigator with qualitative analysis experience.

## Response

The research team is embedded in a methods and statistics department, with experts on qualitative analysis who will be queried, if necessary, during the project.

# Reviewer remark 5

Many literatures have suggested the possibility of using automatic tools to screen for data anomalies, so the
idea proposed is not innovative.

## Response

We did not intend to propose this to be our innovation --- we only wanted to implement the idea after repeated suggestions.

# Reviewer remark 6

There are some weaknesses in Project 1, which include: 1) The application does not consider the situation where researchers do not fabricate the entire data but only modify some numbers in real data, 2) Researchers can improve the way they fabricate data if they know what kinds of statistical methods are used for fabrication detection, 3) Twenty participants might not cover all or most of fabrication behaviors, and 4) There is a possibility that none of the methods can distinguish genuine data from fabricated data. Therefore, it is unclear how the applicant will continue to Project 2 and 3.

## Response

Project 1 is indeed limited by focusing on only fabrication and not falsification. We hope to expand on this in Phase II. With respect to the prob

Weakness 1: The reviewer correctly identifies that the projects only look at fabrication, and not falsification. This is a limitation and we look to improve upon this in the Phase II grant proposal.

Weakness 2: Detecting data fabrication will become a cat-and-mouse game indeed, as the reviewer points out. However, there is always the higher-dimensional aspect. If a researcher fabricates data that cannot be detected as such at the univariate level, detecting data fabrication can be done at all the higher levels still (bivariate, then trivariate, etc.). At some point the fabrication process will become so complicated in order to not be detected, that it is more effortful to fabricate data than to actually conduct a study.

Weakness 3: Twenty participants is most likely not as variable as we would want to have our results. Note that this number is the result of a feasibility analysis based on the contents of the project, the strain on the participants, and the resources available.

Weakness 4: Project 2 and 3 can continue regardless of the success of methods used in Project 1, given that if the methods fail Project 2 is more important (how did they fabricate and is it reasonable that the results did not pick this up + what new methods would have picked it up?). Project 3 is infrastructure development and will not actually apply the methods from project 1 because it does not extract the raw data, so it is independent of the results of project 1 (the infrastructure is used to extract information for analysis, the analysis method is not fixed). Moreover, we have inspected similar methods based on summary results that proved to be effective. Hence, we are confident that Project 1 will be successful.

# Reviewer remark 7

The application does not make a convincing case that the limited timeframe available to study participants to construct fabricated data is relevant to contexts where actual fabrication takes place.

## Response

Given the remark by the reviewer, we discussed this issue and adjusted our protocol to allow the time spent fabricating the data to be at the discretion of the participant. They will be invited to participate and, if they accept, they will be prompted to finish fabricating data before the on site interview. This timeframe will be several weeks instead of 45 minutes.

# Reviewer remark 8

This application does not clearly demonstrate an inductive methodology.

## Response

With the ROC analyses we apply an inductive methodology to assess the weight of the premise "the statistical test for data fabrication is significant" in support of the conclusion that the data were in fact fabricated. For project 2 and 3, we indeed do not demonstrate an inductive methodology because Project 2 applies abductive reasoning and project 3 uses statistical testing as an inductive methodology, which was validated in project 1 (and other work).

# Reviewer remark 9

The application does not provide a convincing basis for drawing sharp inferences regarding the types of fabrication that present the greatest risk given the modest number of available participants.

## Response

We are unsure of what the reviewer means with this comment, given that part of the proposal is to discover more about how data is fabricated. It is difficult to state which type of data fabrication poses the greatest risk if we do not know what types there are.

# Reviewer remark 10

In Project 3, the investigators plan to use existing software for publication screening before applying their proposed detection method. This screening step might be risky since this software may fail to identify certain types of data anomalies.

## Response

The reviewer correctly remarks that certain types of data anomalies might be missed. If missed, it does not get "cleared" so to speak: the flagging system only aims to identify potential problems, not to say that those that aren't flagged do not contain problems.

# Reviewer remark 11

It is not clear in the application why material flagged by ContentMine would necessarily be thought of as presenting fabrication risk, which suggests a substantial proportion of false positives.

## Response

No material will be flagged in relation to the subproject with ContentMine, we will only develop software and validate its performance in extracting information (not analyzing or qualifying those data).

# Reviewer remark 12

There are no details on the specific resources available to study staff in completion of the proposed research, such as computer capability, storage, security, and software programs. Similarly, there should be separate information about Content Mine, as they are a central resource for the development of proposed Phase 3 tools.

## Response

Tilburg University provides the research team with sufficient office space, computer facilities and support. Software programs used will all be free and open-source, and ContentMine has already provided the PI computing power on their servers. All sensitive files will be encrypted and stored on the PI's local copy with several encrypted backups.

### 2016-09-22 archive/response_ori_rev.md
Minor update reviewer comments

@@
 
-We never aimed to support such claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed.
+We never aimed to support such a claim; we only aimed to sketch the problem with the way estimates of data fabrication are now constructed.
+We fully agree with the reviewer that there is no way of knowing whether the data fabrication admitted to is the same as the data fabrication these methods could detect.
 
@@
 
-We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures and our familiarity with the measures applied here.
+We focus only on the social- and medical sciences given the widespread use of randomized experimental procedures in these fields and our familiarity with the misconduct cases in these fields.
 We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields.
@@
 ## Response
-
-Project 1 is indeed limited by focusing on only fabrication and not falsification. We hope to expand on this in Phase II. With respect to the prob
 

### 2016-09-26 archive/response_ori_rev.md
Update response according to Jan his comments

@@
 We fully agree with the reviewer that there is no way of knowing whether the data fabrication admitted to is the same as the data fabrication these methods could detect.
+Project 1 and 2 were also designed to shed more light on the question how misconduct occurs so that they will help not only in identifying whether the proposed method are sufficient but also provide helpful data for developing new methods if the proposed ones fail.
 
@@
 We could expand to other fields with sufficient resources, but given the constraints of the current grant scheme we focused on these fields.
+Regardless, the methods investigated can be applied to other fields as well.
 

### 2016-10-25 submission/manuscript.Rnw
Residual commit

--- 2016-09-05 submission/manuscript.Rnw
@@
 suppressPackageStartupMessages(library(httr))
+suppressPackageStartupMessages(if (!require(car)) install.packages('car'))
+suppressPackageStartupMessages(library(car))
+suppressPackageStartupMessages(if (!require(effects)) install.packages('effects'))
+suppressPackageStartupMessages(library(effects))
+suppressPackageStartupMessages(if (!require(lsr)) install.packages('lsr'))
+suppressPackageStartupMessages(library(lsr))
+suppressPackageStartupMessages(if (!require(data.table)) install.packages('data.table'))
+suppressPackageStartupMessages(library(data.table))
+suppressPackageStartupMessages(if (!require(dplyr)) install.packages('dplyr'))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(if (!require(reshape2)) install.packages('reshape2'))
+suppressPackageStartupMessages(library(reshape2))
 
@@
 x12 <- '../'
-# x12 <- ''
+x12 <- ''
 @
@@
 summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/ML3StroopRaw.csv', x12)
+ml3_clean_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/StroopCleanSet.csv', x12)
 pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
@@
 
+# Study 1
 # Compute the summary statistics for Many Labs
@@
 }
+
+# Study 2
+# Compute the processed raw data for Many Labs 3 stroop
+source(sprintf('%sfunctions/compute_raw_stroop_ml3.R', x12))
 @
@@
 For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
-All materials, data, and analyses scripts are freely available on the OSF (\url{osf.io/b24pq}) and were preregistered (\url{osf.io/ejf5x}; deviations are explicated in this report).
+All materials, data, and analyses scripts are freely available on the OSF (\url{https://osf.io/b24pq}) and were preregistered (\url{https:// .io/ejf5x}; deviations are explicated in this report).
 
@@
 
-We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{osf.io/pqf9r};][]{klein2014}.
+We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{https://osf.io/pqf9r};][]{klein2014}.
 The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
@@
 
-A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}).
+A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{https://osf.io/s4w8r}).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
-The full text of the Qualtrics survey is available at \url{osf.io/w984b}.
+The full text of the Qualtrics survey is available at \url{https://osf.io/w984b}.
 
@@
 We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data.
-Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{osf.io/w6v4u}).
+Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{https://osf.io/w6v4u}).
 We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
@@
 For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combined methods) we carried out sensitivity and specificity analyses using ROC-curves.
-ROC-curves indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
+ROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
 With these ROC-curves, informed decisions about optimal alpha levels can be made based on various criteria.
@@
 For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.
+% Maybe include bootstrapped errors here.
 
@@
 
-The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{osf.io/e6zys}).
-\Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus.
+The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{https://osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{https://osf.io/e6zys}; \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus).
+
 Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
-Such group-level comparisons provide a general idea of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
+These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
 
@@
 
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
+df <- data.frame(Method = temp,
+                     AUROC = NA,
+                     CI.lb = NA,
+                     CI.ub = NA)
+Method <- c("$SD_z$ homogeneous all",
+            "$SD_z$ study 1",
+            "$SD_z$ study 2",
+            "$SD_z$ study 3",
+            "$SD_z$ study 4",
+            "$maxmin_z$ homogeneous all",
+            "$maxmin_z$ study 1",
+            "$maxmin_z$ study 2",
+            "$maxmin_z$ study 3",
+            "$maxmin_z$ study 4",
+            "$SD_z$ heterogeneous all",
+            "$SD_z$ study 1 low condition",
+            "$SD_z$ study 1 high condition",
+            "$SD_z$ study 2 low condition",
+            "$SD_z$ study 2 high condition",
+            "$SD_z$ study 3 low condition",
+            "$SD_z$ study 3 high condition",
+            "$SD_z$ study 4 low condition",
+            "$SD_z$ study 4 high condition",
+            "$maxmin_z$ heterogeneous all",
+            "$maxmin_z$ study 1 low condition",
+            "$maxmin_z$ study 1 high condition",
+            "$maxmin_z$ study 2 low condition",
+            "$maxmin_z$ study 2 high condition",
+            "$maxmin_z$ study 3 low condition",
+            "$maxmin_z$ study 3 high condition",
+            "$maxmin_z$ study 4 low condition",
+            "$maxmin_z$ study 4 high condition",
+            "Fisher test gender hypothesis",
+            "Fisher test interaction hypothesis",
+            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
+            "Effect sizes (1-r)")
+
 @
@@
 
-<<AUC for variance methods, echo=FALSE, results=tex>>=
+We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
+The $SD_z$ method \citep{simonsohn2013} inspects whether the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs varies sufficiently.
+These two methods operate similarly, except for the final computation.
+Other operationalizations are possible and we invite others to reuse the data from this study (\url{https://osf.io/b24pq}).
+
+Table \ref{auroc_variances} indicates that both methods show similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC), but with a preference for $SD_z$.
+This preference is due to the variance of variances outperforming the range of variances when all studies are combined in one test and its past application \citep{simonsohn2013}.
+Throughout the rest of this section, we will only discuss the results of $SD_z$ further.
+
+<<auroc for variance methods, echo=FALSE, results=tex>>=
 selmaxmin <- grepl(Method, pattern = '^.maxmin_')
 selsd <- grepl(x = Method, pattern = '^.SD_z')
-row_table <- c("Homogeneous combined",
-                    "Homogeneous study 1",
-                    "Homogeneous study 2",
-                    "Homogeneous study 3",
-                    "Homogeneous study 4",
-                    "Heterogeneous combined",
-                    "Study 1 low condition",
-                    "Study 1 high condition",
-                    "Study 2 low condition",
-                    "Study 2 high condition",
-                    "Study 3 low condition",
-                    "Study 3 high condition",
-                    "Study 4 low condition",
-                    "Study 4 high condition")
+row_table <- c("Homogeneous, all studies combined",
+               "Homogeneous, study 1",
+               "Homogeneous, study 2",
+               "Homogeneous, study 3",
+               "Homogeneous, study 4",
+               "Heterogeneous, all studies combined",
+               "Heterogeneous study 1, low anchor condition",
+               "Heterogeneous study 1, high anchor condition",
+               "Heterogeneous study 2, low anchor condition",
+               "Heterogeneous study 2, high anchor condition",
+               "Heterogeneous study 3, low anchor condition",
+               "Heterogeneous study 3, high anchor condition",
+               "Heterogeneous study 4, low anchor condition",
+               "Heterogeneous study 4, high anchor condition")
 variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
-names(variances_table) <- c("Method", "$SD_z$", "$maxmin_z$")
+names(variances_table) <- c("Method", "AUROC $SD_z$", "AUROC $maxmin_z$")
 print(xtable(variances_table,
-             caption = "Area Under the Curve (AUC) for the two statistical methods used to detect data fabrication based on variances.
+             caption = "Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
 Homogeneous: assumes one population variance underlying all groups.
 Heterogeneous: assumes separate population variance per anchoring condition.",
-             label = "auc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             label = "auroc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
 
-<<generate variance ROC, echo=FALSE, results=hide>>=
-if(!file.exists(sprintf('%sfigures/varianceplot.pdf', x12)))
-{
-  pdf(sprintf('%sfigures/varianceplot.pdf', x12), width = 8, height = 6)
-  plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
-       type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance analysis',
-       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)
-  abline(a = 0, b = 1)
-  lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
-        type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
-        xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 1)
-  legend(x = 0, y = 1, bty = 'n', lty = c(2, 1), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
-  dev.off()
-}
-@
+The AUROC indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
+In other words, if AUROC $=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
 
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/varianceplot.pdf}
-\caption{PLACEHOLDER}
-\label{varianceplot}
-\end{center}
-\end{figure}
+The AUROC for the variance of variance analyses is insufficient or sufficient depending on the assumption regarding population variances.
+Table \ref{auroc_variances} indicates that AUROC $=.423$ when homogeneous population variances are assumed, whereas AUROC $=.770$ when heterogeneous population variances are assumed.
+For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method.
+The method that incorporates heterogeneous population variances (i.e., one per anchoring condition) greatly improves the performance of the variance of variances analysis.
+
+Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=\Sexpr{seq(0, 1, .01)[max(which(tnr$variance_sd_p_overall_hetero == 1))]}$.
 
@@
 We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
-Consequently, our hypothesis was that researchers who fabricate data would be unlikely to fabricate a uniform $p$-value distribution, given many researchers misinterpret the $p$-value (e.g., as the probability of an effect %REF
-).
-However, as Table \ref{auc_fisher} indicates, the AUC for these methods are hardly better than chance.
+Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
 In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
 
-<<AUC for single fisher methods, echo=FALSE, results=tex>>=
+<<auroc for single fisher methods, echo=FALSE, results=tex>>=
 sel <- grepl(Method, pattern = '^(Fisher test)')
 row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
 print(xtable(tabl,
-             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
-             label = "auc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
@@
 
-<<AUC for combined fisher methods, echo=FALSE, results=tex>>=
+<<auroc for combined fisher methods, echo=FALSE, results=tex>>=
 sel <- grepl(Method, pattern = 'Combined Fisher test')
 row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUC = AUC[sel])
+tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
 print(xtable(tabl,
-             caption = "Area Under the Curve (AUC) for PLACEHOLDER",
-             label = "auc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
 @
@@
   url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
-  # If link is broken, more persistent version availabl at
+  # If link is broken, more persistent version available at
   # http://dx.doi.org/10.17026/dans-2cm-v9j9
@@
 
+% Discuss alpha choice based on sample has large error (small sample).
+% Only provides a first indication
+
+% Comparison between methods not tested, large error given small sample.
+% This provides just initial work
+
+<<study 2 stuff, echo = FALSE, eval = FALSE>>=
+# Computing the Stroop effect in ML3
+mean(Stroop$StroopEffect,na.rm=TRUE)
+t.test(Stroop$StroopEffect,y=NULL,alternative="two.sided",mu=0,paired=FALSE,var.equal=FALSE,conf.level=.95)
+#Cohen's d for one sample
+d<-mean(Stroop$StroopEffect,na.rm=TRUE)/sd(Stroop$StroopEffect,na.rm=TRUE)
+d
+@
+
 \bibliography{../bibliography/library}

### 2016-10-25 submission/manuscript.tex
Residual commit

--- 2016-08-02 submission/manuscript.tex
@@
 \section*{Study 1}
-
-We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies \citep{tversky1974,jacowitz1995}.
-The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
-For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'.
-These questions yield mean responses of 25\% and 45\%, respectively \citep{tversky1974}, despite essentially posing the same factual question.
-A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
-
-\subsection*{Methods}
-
-The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States.
-Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
-Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
-Respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
-All materials, data, and analyses scripts are freely available on the OSF (\url{osf.io/b24pq}) and were preregistered (\url{osf.io/ejf5x}; deviations are explicated in this report).
-
-\subsubsection*{Data collection}
-
-We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{osf.io/pqf9r};][]{klein2014}.
-The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
-Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed, for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
-We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
-
-Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
-The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
-We sampled psychology researchers to improve familiarity with the anchoring effect \citep{jacowitz1995,tversky1974}, for which summary results were fabricated.
-We filtered for U.S.
-researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
-researchers were included because this filter also retained papers with co-authors from the U.S.).
-WoS was searched on October 13, 2015.
-In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).
-
-A random sample of 1,000 researchers were digitally approached to participate in this study on April 25, 2016 (invitation: \url{osf.io/s4w8r}).
-The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
-We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication.
-We also clarified to the  respondents that they could stop at any time without providing a reason.
-If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation for which they had to provide their email address, after which they could win an additional \$50 Amazon gift card if they were one of three top fabricators.
-The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
-The full text of the Qualtrics survey is available at \url{osf.io/w984b}.
-
-Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
-We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
-Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
-The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
-
-We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they choose to fabricate data.
-Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{osf.io/w6v4u}).
-We requested the respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
-Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
-When these results confirm the hypotheses, a checkmark appears as depicted in the green cells.
-We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet.png}
-\caption{Example of a filled in template spreadsheet used in the fabrication process.
-Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
-If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell.}
-\label{fig1}
-\end{center}
-\end{figure}
-
-Upon completing the fabrication of the data, respondents were debriefed.
-Several questions were asked about their statistical knowledge and approach to data fabrication.
-They were also reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
-
-We rewarded participation with a \$30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus \$50 Amazon gift card.
-If the participant wanted to receive a compensation and contend for the bonus \$50, he/she had to enter an email to receive the reward.
-These email addresses were unlinked from individual responses upon sending the gift cards.
-Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
-
-\subsubsection*{Data analysis}
-
-To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies.
-Such methods test whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
-For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
-To compute this test, we first standardized the SDs for each of the four studies by computing
-\begin{equation}
-z_j=\sqrt{\frac{s^2_j}{MS_w}}=\sqrt{\frac{s^2_j}{\left(\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}\right)}}
-\label{s2_j}
-\end{equation}
-where $z_j$ denotes the standardized SD in group $j$ ($MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells, which is the case for the fabricated datasets).
-We tested different measures to detect data fabrication that utilize these standardized SDs (i.e., $z_j$).
-We included the variance of the standardized SDs \citep[i.e.,  $SD_{z}$;][]{simonsohn2013} and tried out the max-min distance of the standardized SDs (denoted $max-min_{z}$) as an alternative measure.
-We compared the observed value for each measure with the expected distribution when the summary results are used to generate random samples.
-To this end, we simulated the expected distribution of standardized SDs and computed the expected distribution of each measure.
-This expected distribution was used to determine the $p$-value of the observed $SD_z$ and $max-min_z$.
-We simulated the standardized variance for each of the $j$ groups as
-\begin{equation}
-z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
-\label{simvar}
-\end{equation}
-These simulated values are used to compute the expected distribution of the $SD_z$ and $max-min_z$  measures.
-
-Second, we applied the reversed Fisher method to the nonsignificant $p$-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
-The Fisher method \citep{fisher1925} tests for evidence of an effect in a set of $p$-values by testing for a right-skew $p$-value distribution, but we adjusted it here to test for results that are overly consistent with the null hypothesis and result in a left-skew distribution (see Figure \ref{leftskew}).
-The original Fisher method is computed as
-\begin{equation}
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
-\label{fisher}
-\end{equation}
-and tests for right-skew in a set of $p$-values, but we adjust it to the following
-\begin{equation}
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
-\label{fisheradjusted}
-\end{equation}
-where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
-We set this threshold to .05 in order to include only nonsignificant test results.
-
-% add plot of left and right skew
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/fisherfig.pdf}
-\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and our adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B).
-Both panels test whether there is sufficient evidence that the solid line deviates from the dashed line, except that the type of deviation that the test is sensitive to is the exact opposite.}
-\label{leftskew}
-\end{center}
-\end{figure}
-
-% Finally, we combined the results of these three individual tests for data fabrication using the Fisher method.
-We expect this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests.
-Based on the results of the combined test results, the three 'best' data fabricators are selected.
-The three respondents with the highest *p*-values contain the least evidential value for deviating from genuine data and receive an additional $50 Amazon gift card.
-% 
-% For each of these three tests to detect data fabrication we carry out sensitivity and specificity analyses using ROC-curves in order to determine optimal alpha levels.
-This analysis helps determine the classification performance of these three tests.
-In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1 and assessed the classification performance of these methods to detect data fabrication.
-The optimal alpha level is determined by finding that alpha level for which both the true positive classification rate and the true negative classification rate are highest.
-For example,
-
-\subsection*{Results}
-
-\bibliography{../bibliography/library}
-\end{document}

### 2017-02-06 functions/compute_raw_stroop_ml3.R
Residual commit

@@ -74,7 +74,7 @@ myTbl$SUBEXCL<-0
 myTblNoLong<-filter(myTbl,TRIAL_LATENCY<10000,TRIAL_LATENCY>=0)
 
 myFastTbl<-filter(myTbl) %>%
-  summarise(FASTM=sum(TRIAL_LATENCY<300)/length(TRIAL_LATENCY))
+  dplyr::summarise(FASTM=sum(TRIAL_LATENCY<300)/length(TRIAL_LATENCY))
 
 isTooFast<-filter(myFastTbl,FASTM>.10)%>%
   select(SESSION_ID)
@@ -88,7 +88,7 @@ myTblNotFast<-group_by(myTblNoLong,SESSION_ID,CONGRUENT)
 #NOTE: in TRIAL_ERROR, 0=error, 1=correct
 
 meanReplace<-filter(myTblNotFast,TRIAL_ERROR==1) %>%
-  summarise(blockMean=mean(TRIAL_LATENCY)+600)
+  dplyr::summarise(blockMean=mean(TRIAL_LATENCY)+600)
 # meanReplace
 # head(meanReplace)
 # str(meanReplace)
@@ -112,10 +112,10 @@ Incongruent<-subset(Corrected,Corrected$CONGRUENT=="Incongruent")
 # head(Congruent)
 # head(Incongruent)
 
-blockMeans1<-summarise(group_by(Congruent,SESSION_ID),MC=mean(TRIAL_LATENCY),SDC=sd(TRIAL_LATENCY),NC=length(TRIAL_LATENCY))
+blockMeans1<-dplyr::summarise(group_by(Congruent,SESSION_ID),MC=mean(TRIAL_LATENCY),SDC=sd(TRIAL_LATENCY),NC=length(TRIAL_LATENCY))
 tblM1<-blockMeans1
 
-blockMeans2<-summarise(group_by(Incongruent,SESSION_ID),MI=mean(TRIAL_LATENCY),SDI=sd(TRIAL_LATENCY),NI=length(TRIAL_LATENCY))
+blockMeans2<-dplyr::summarise(group_by(Incongruent,SESSION_ID),MI=mean(TRIAL_LATENCY),SDI=sd(TRIAL_LATENCY),NI=length(TRIAL_LATENCY))
 tblM2<-blockMeans2
 
 Means<-merge(tblM1,tblM2,by="SESSION_ID")

### 2017-02-06 submission/manuscript.Rnw
Draft intro and parts of study 1+2

@@
 
+Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP).
+Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
+These are just a few examples of cases in the last decade.
+Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once \citep{fanelli2009} and this is likely to be an underestimate due to socially desirable responses.
+The detection rate is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
+At best, this amounts to a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
+
+In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts.
+Although deterrence theory dates back to the middle of the 17th century \citep{leviathan}, its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
+This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago  \citep[e.g.,][]{Parker89computeralgorithms}.
+However, increased deterrence of fabrication and falsification by improved detection mechanisms has not been as widely implemented.
+
+In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct other than plagiarism.
+The Journal of Cell Biology scans each submitted image for potential manipulation \citep{The_Journal_of_Cell_Biology2015-vh}, which greatly increases the risk of detecting (blatant) image manipulation.
+More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations \citep{Koppers2016}.
+These developments in detecting image manipulation have increased detection risk during the pre-publication and post-publication phase by improving detection mechanisms and increasing the understanding of how images might be manipulated.
+Moreover, their application also helps researchers systematically evaluate research articles to estimate the extent of the problem of image manipulation \citep[4\% of all papers are estimated to contain manipulated images;][]{Bik06072016}.
+
+Statistical methods can provide one way to improve detection of data fabrication in empirical research.
+Humans are notoriously bad at understanding and estimating probabilities \citep[e.g.,][]{tversky1974, Tversky1971}, which could manifest itself in the fundamentally probabilistic data they try to fabricate.
+That researchers do not understand probabilistic processes also presents itself in the interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
+When data are fabricated, probabilistic principles are easily violated if these principles are forgotten at the univariate level, bivariate level, trivatiate level, or beyond \citep{Haldane1948-nm}.
+Based on such a theoretical framework, statistical methods that investigate whether the reported data are actually plausible under theoretically probabilistic processes can be used to detect potential data fabrication.
+
+The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis.
+For example, problems with papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
+In this case, baseline measures across randomized groups were examined for too little variation.
+Random assignment should introduce a certain degree of random error that is might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
+Another two cases are those of Sanna and Smeesters, where fabricated data were also detected with statistics \citep{simonsohn2013}.
+These cases inspected the variance of variances (i.e., the second level, or meta, variance).
+Once again, too little variation was what revealed problems in these data.
+These methods, although developed in a case-setting, need not be limited to cases.
+The application of such methods can be (semi-)automated if data are available in a machine-readable format that one of the statistical methods can be applied to.
+An example of such a potential case for mass application of using statistics to detect (potential) data fabrication is in the ClinicalTrials.gov database, where baseline measures across randomized groups are readily available for download and subsequent analysis \citep{Hartgerink2015-bm}.
+
+Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
+We hardly know how researchers might go about fabricating data.
+Cases such as Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
+Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place \citep[e.g., late at night when no one is around;][]{stapel_book}.
+Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown  prevalence of data fabrication and the power to actually to detect data fabrication.
+Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be simulated.
+
+The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated by the increased usage of public online discussion platforms such as PubPeer (\url{https://pubpeer.com}).
+PubPeer serves as an "online journal club" where anyone can discuss articles.
+Authors are notified when someone leaves a response, providing them with the possibility to respond.
+Such a platform allows for public discussion of the paper, including discussion of reanalyses, methodology, availability of materials, etc.
+When detection mechanisms are freely available to use, they can lead to (a surge of) comments when applied by users.
+Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments \citep{Baker_2016}.
+The impact of such new possibilities is not to be underestimated, although its potential to contribute to the scientific discussion should also not be.
+Nonetheless, the `statcheck` software was well validated prior to this application \citep{Nuijten_2015} and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
+
+Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data.
+Even though the data available look different depending on the structure of the study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
+Raw data frequently contain at least some variables measured at a interval- or ratio scale \citep{Stevens_1946}.
+
+We present a set of studies that directly test the validity of statistical methods to detect data fabrication.
+To this end, Study 1 inspected the performance of statistical methods to detect data fabrication when using only summary results (e.g., means and standard deviations) as typically reported in empirical research articles.
+Study 2 inspected the performance of statistical methods aimed at detecting data fabrication in raw data (i.e., the data underlying summary results).
+These two studies provide a first indication of how applicable and effective statistical methods are to detect data fabrication in practice, with actual researchers fabricating actual data.
+
 <<prepwork, echo=FALSE,results=hide>>=
-suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
+suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(pROC))
-suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
+suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(foreign))
-suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp')})
+suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(latex2exp))
-suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2')})
+suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(ggplot2))
-suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra')})
+suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(gridExtra))
-suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable')})
+suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(xtable))
-suppressPackageStartupMessages(if(!require(httr)){install.packages('httr')})
+suppressPackageStartupMessages(if(!require(httr)){install.packages('httr', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(httr))
-suppressPackageStartupMessages(if (!require(car)) install.packages('car'))
+suppressPackageStartupMessages(if (!require(car)){install.packages('car', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(car))
-suppressPackageStartupMessages(if (!require(effects)) install.packages('effects'))
+suppressPackageStartupMessages(if (!require(effects)){install.packages('effects', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(effects))
-suppressPackageStartupMessages(if (!require(lsr)) install.packages('lsr'))
+suppressPackageStartupMessages(if (!require(lsr)){install.packages('lsr', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(lsr))
-suppressPackageStartupMessages(if (!require(data.table)) install.packages('data.table'))
+suppressPackageStartupMessages(if (!require(data.table)){install.packages('data.table', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(data.table))
-suppressPackageStartupMessages(if (!require(dplyr)) install.packages('dplyr'))
+suppressPackageStartupMessages(if (!require(dplyr)){install.packages('dplyr', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(if (!require(reshape2)) install.packages('reshape2'))
+suppressPackageStartupMessages(if (!require(reshape2)){install.packages('reshape2', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(reshape2))
@@
 x12 <- '../'
-x12 <- ''
+# x12 <- ''
 @
@@
 
+\section*{Study 2}
+
+Above, we described results of detecting data fabrication with summary results; in Study 2 we present results of detecting data fabrication with raw data.
+
+To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment (Stroop 1935).
+
+Raw data are defined as
+
+\section*{Methods}
+
+Twenty genuine datasets were collected from the Many Labs 3 project (Ebersole et al. ).
+
+Twenty faked datasets were collected experimentally.
+We sampled 20 of 84 Dutch or Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015, which was indexed in Thomson Reuters’ Web of Science database.
+Dutch and Flemish researchers were selected to allow for potential follow-up on the way data was fabricated in a face-to-face interview.
+The period 2005-2015 was chosen to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
+Researchers who published on the Stroop task were selected to ensure their familiarity with the type of task for which data had to be fabricated.
+The database was searched on October 13, 2015 and 84 unique e-mails were extracted from 86 articles.
+
+\section*{Results}
+
+\section*{Discussion}
+
+\section*{General discussion}
+
+% Talk about deterrence theory and how marginal utility might make it more attractive to go towards more extreme forms of misconduct if zero-tolerance policy is applied.
+% Plagiarism scanners can be gamed (i.e., rogeting), so can statistics?
+
 \bibliography{../bibliography/library}

### 2017-02-06 submission/manuscript.tex
Draft intro and parts of study 1+2

@@
 
-\section*{Study 1}
+Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP).
+Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
+These are just a few examples of cases in the last decade.
+Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once \citep{fanelli2009} and this is likely to be an underestimate due to socially desirable responses.
+The detection rate is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
+At best, this amounts to a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
+
+In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts.
+Although deterrence theory dates back to the middle of the 17th century \citep{leviathan}, its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
+This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago  \citep[e.g.,][]{Parker89computeralgorithms}.
+However, increased deterrence of fabrication and falsification by improved detection mechanisms has not been as widely implemented.
+
+In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct other than plagiarism.
+The Journal of Cell Biology scans each submitted image for potential manipulation \citep{The_Journal_of_Cell_Biology2015-vh}, which greatly increases the risk of detecting (blatant) image manipulation.
+More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations \citep{Koppers2016}.
+These developments in detecting image manipulation have increased detection risk during the pre-publication and post-publication phase by improving detection mechanisms and increasing the understanding of how images might be manipulated.
+Moreover, their application also helps researchers systematically evaluate research articles to estimate the extent of the problem of image manipulation \citep[4\% of all papers are estimated to contain manipulated images;][]{Bik06072016}.
+
+Statistical methods can provide one way to improve detection of data fabrication in empirical research.
+Humans are notoriously bad at understanding and estimating probabilities \citep[e.g.,][]{tversky1974, Tversky1971}, which could manifest itself in the fundamentally probabilistic data they try to fabricate.
+That researchers do not understand probabilistic processes also presents itself in the interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
+When data are fabricated, probabilistic principles are easily violated if these principles are forgotten at the univariate level, bivariate level, trivatiate level, or beyond \citep{Haldane1948-nm}.
+Based on such a theoretical framework, statistical methods that investigate whether the reported data are actually plausible under theoretically probabilistic processes can be used to detect potential data fabrication.
+
+The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis.
+For example, problems with papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
+In this case, baseline measures across randomized groups were examined for too little variation.
+Random assignment should introduce a certain degree of random error that is might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
+Another two cases are those of Sanna and Smeesters, where fabricated data were also detected with statistics \citep{simonsohn2013}.
+These cases inspected the variance of variances (i.e., the second level, or meta, variance).
+Once again, too little variation was what revealed problems in these data.
+These methods, although developed in a case-setting, need not be limited to cases.
+The application of such methods can be (semi-)automated if data are available in a machine-readable format that one of the statistical methods can be applied to.
+An example of such a potential case for mass application of using statistics to detect (potential) data fabrication is in the ClinicalTrials.gov database, where baseline measures across randomized groups are readily available for download and subsequent analysis \citep{Hartgerink2015-bm}.
+
+Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
+We hardly know how researchers might go about fabricating data.
+Cases such as Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
+Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place \citep[e.g., late at night when no one is around;][]{stapel_book}.
+Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown  prevalence of data fabrication and the power to actually to detect data fabrication.
+Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be simulated.
+
+The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated by the increased usage of public online discussion platforms such as PubPeer (\url{https://pubpeer.com}).
+PubPeer serves as an "online journal club" where anyone can discuss articles.
+Authors are notified when someone leaves a response, providing them with the possibility to respond.
+Such a platform allows for public discussion of the paper, including discussion of reanalyses, methodology, availability of materials, etc.
+When detection mechanisms are freely available to use, they can lead to (a surge of) comments when applied by users.
+Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments \citep{Baker_2016}.
+The impact of such new possibilities is not to be underestimated, although its potential to contribute to the scientific discussion should also not be.
+Nonetheless, the `statcheck` software was well validated prior to this application \citep{Nuijten_2015} and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
+
+Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data.
+Even though the data available look different depending on the structure of the study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
+Raw data frequently contain at least some variables measured at a interval- or ratio scale \citep{Stevens_1946}.
+
+We present a set of studies that directly test the validity of statistical methods to detect data fabrication.
+To this end, Study 1 inspected the performance of statistical methods to detect data fabrication when using only summary results (e.g., means and standard deviations) as typically reported in empirical research articles.
+Study 2 inspected the performance of statistical methods aimed at detecting data fabrication in raw data (i.e., the data underlying summary results).
+These two studies provide a first indication of how applicable and effective statistical methods are to detect data fabrication in practice, with actual researchers fabricating actual data.
+
+% Talk about deterrence theory and how marginal utility might make it more attractive to go towards more extreme forms of misconduct if zero-tolerance policy is applied.
+% Plagiarism scanners can be gamed (i.e., rogeting), so can statistics?
+
+\bibliography{../bibliography/library}
+\newpage
+%------------------------------------
+%handy to include this at the end
+%------------------------------------
+\section*{SessionInfo}
+%-------------------------------------
+
+\begin{Schunk}
+\begin{Sinput}
+> sessionInfo()
+\end{Sinput}
+\begin{Soutput}
+R version 3.3.2 (2016-10-31)
+Platform: x86_64-redhat-linux-gnu (64-bit)
+Running under: Fedora 25 (Workstation Edition)
+
+locale:
+ [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
+ [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
+ [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
+ [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
+ [9] LC_ADDRESS=C               LC_TELEPHONE=C            
+[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C
+
+attached base packages:
+[1] stats     graphics  grDevices utils     datasets  methods   base
+
+loaded via a namespace (and not attached):
+[1] tools_3.3.2
+\end{Soutput}
+\begin{Sinput}
+> 
+\end{Sinput}
+\end{Schunk}
+
+\end{document}

### 2017-03-01 functions/concatenate_analyze_01.R
Add std_var function for analysis

@@ -82,330 +82,330 @@ for (pp in unique(dat$referrer))
       (((ms_interaction / ms_error) * 1) / (sum(dat$anch_n[indexor]) - 4)) / 
       ((((ms_interaction / ms_error) * 1) / (sum(dat$anch_n[indexor]) - 4)) + 1)
   }
-
-sel <- dat$referrer == pp
-
-# Variance analysis
-
-# ---
-# Assuming homogeneity of variances for all ANCHORING condition
-# ---
-# Standardizing the sds
-# Study 1
-sel1 <- dat$referrer == pp & dat$study == 1
-ms_w_1 <- sum((dat$anch_n[sel1] - 1) * dat$anch_sd[sel1]^2) / sum((dat$anch_n[sel1] - 1))
-tilde_s2_1 <- dat$anch_sd[sel1]^2 / ms_w_1
-# Study 2
-sel2 <- dat$referrer == pp & dat$study == 2
-ms_w_2 <- sum((dat$anch_n[sel2] - 1) * dat$anch_sd[sel2]^2) / sum((dat$anch_n[sel2] - 1))
-tilde_s2_2 <- dat$anch_sd[sel2]^2 / ms_w_2
-# Study 3
-sel3 <- dat$referrer == pp & dat$study == 3
-ms_w_3 <- sum((dat$anch_n[sel3] - 1) * dat$anch_sd[sel3]^2) / sum((dat$anch_n[sel3] - 1))
-tilde_s2_3 <- dat$anch_sd[sel3]^2 / ms_w_3
-# Study 4
-sel4 <- dat$referrer == pp & dat$study == 4
-ms_w_4 <- sum((dat$anch_n[sel4] - 1) * dat$anch_sd[sel4]^2) / sum((dat$anch_n[sel4] - 1))
-tilde_s2_4 <- dat$anch_sd[sel4]^2 / ms_w_4
-
-obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
-obs_maxmin <- c(max(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4)) -
-                  min(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4)))
-
-obs_sigma_sd_study1 <- sd(tilde_s2_1)
-obs_sigma_sd_study2 <- sd(tilde_s2_2)
[…]

### 2017-03-01 functions/std_var.R

@@ -1,0 +1,47 @@
+std_var <- function(n, sds, iter = 1000, ...)
+{
+  msw_obs <- msw(n, sds)
+  z2_sd_obs <- z2_sd(sds = sds, msw = msw_obs)
+  
+  obs_sd_z2 <- sd(z2_sd_obs)
+  
+  # Create a column of simulated variances per cell
+  tmp <- apply(t(n - 1), 2, function(x)
+  {
+    step1 <- rchisq(n = iter, df = x)
+    step2 <- step1 / x
+  })
+  
+  # Compute msw for simulated variances (per row)
+  msw_sim <- apply(tmp, 1, function(x) msw(n, x))
+  
+  # Normalize simulated variances
+  sim_z2 <- z2_sd(sds = tmp, msw = msw_sim)
+  # Calculate SD for each iteration
+  sim_sd_z2 <- apply(sim_z2, 1, sd)
+  
+  res <- sum(sim_sd_z2 < obs_sd_z2) / iter
+  
+  return(res)
+}
+
+msw <- function(
+  n,
+  sds
+)
+{
+  if (is.null(n)) stop("Please specify n")
+  if (is.null(sds)) stop("Please specify sd")
+  
+  res <- sum((n - 1) * sds^2) / sum((n - 1))
+  
+  return(res)
+}
+
+z2_sd <- function(sds, var, msw)
+{
+  # Implement check that not both sd and var are given
+  res <- sds^2 / msw
+  
+  return(res)
+}

### 2017-03-03 submission/manuscript.Rnw
Preregister study 2

@@
 \usepackage{adjustbox}
+\usepackage{eurosym}
 \bibliographystyle{apalike}
@@
 \title{Ecological performance of detecting data fabrication with summary statistics}
-\author{Chris HJ Hartgerink, Jelte M Wicherts, Marcel ALM van Assen}
+\author{Chris HJ Hartgerink, Jan G Voelkel, Jelte M Wicherts, Marcel ALM van Assen\\
+Preregistration conducted by first author}
 
@@
 # Compute the processed raw data for Many Labs 3 stroop
+if(!file.exists(sprintf('%sdata/study_02/ml3_stroop.csv', x12)))
+{
   source(sprintf('%sfunctions/compute_raw_stroop_ml3.R', x12))
+}
 @
@@
 For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
-All materials, data, and analyses scripts are freely available on the OSF (\url{https://osf.io/b24pq}) and were preregistered (\url{https:// .io/ejf5x}; deviations are explicated in this report).
+All materials, data, and analyses scripts are freely available on the OSF (\url{https://osf.io/b24pq}) and a preregistration is available at \url{https://osf.io/ejf5x} (deviations are explicated in this report).
 
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet.png}
-\caption{Example of a filled in template spreadsheet used in the fabrication process.
+\caption{Example of a filled in template spreadsheet used in the fabrication process of Study 1.
 Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
-If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell.}
+If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell (one of four template spreadsheets available at \url{https://osf.io/w6v4u/}).}
 \label{fig1}
@@
 
-<<read in data, echo = FALSE, results = hide>>=
-# Read in datafile, just in case the computations were not re-run.
-dat_summary <- read.csv(dat_summary_file)
-# Select only those from qualtrics who did for bonus
-# removed <- sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))
-# dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
-
-type_index <- which(names(dat_summary) == 'type')
-temp <- dat_summary[, c(type_index, 18:length(names(dat_summary)))]  
-dat_summary$es_gender <- sqrt(dat_summary$es2_gender)
-dat_summary$es_condition <- sqrt(dat_summary$es2_condition)
-dat_summary$es_interaction <- sqrt(dat_summary$es2_interaction)
-
-# naming just for ease of use later
-dat_summary$es_p <- 1 - dat_summary$es_condition
-
-if(!file.exists(sprintf('%sfigures/ddfab_density.pdf', x12)))
-{
-  pdf(sprintf('%sfigures/ddfab_density.pdf', x12), width = 10, height = 7)
-  # Gender
-  plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
-    geom_density(alpha = .3) + 
-    xlab(TeX("$P$-value")) + 
-    ylab("Density") + 
-    ylim(0, 1.5) + 
-    scale_fill_discrete(guide=FALSE) + 
-    ggtitle('Gender')
-
-  plot_es_gender <- ggplot(dat_summary, aes(x = es_gender, fill = type)) + 
-    geom_density(alpha = .3) + 
-    xlab(TeX("Effect size ($r$)")) + 
-    ylab("Density") + 
-    scale_fill_discrete(guide=FALSE)
-
-  # Condition
-  plot_p_condition <- ggplot(dat_summary, aes(x = p_condition, fill = type)) +
-    geom_density(alpha = .3) +
-    xlim(0, 1) +
-    xlab(TeX("$P$-value")) +
-    ylab("Density") +
-    scale_fill_discrete(labels = c("Genuine","Fabricated")) + 
-    theme(legend.position="top") + 
-    ggtitle('Condition')
-
-  plot_p_condition$labels$fill <- ""
-
-  plot_es_condition <- ggplot(dat_summary, aes(x = es_condition, fill = type)) + 
-    geom_density(alpha = .3) + 
-    xlim(0, 1) + 
-    xlab(TeX("Effect size ($r$)")) + 
-    ylab("Density") + 
-    scale_fill_discrete(guide=FALSE)
-
-  # Interaction
-  plot_p_interaction <- ggplot(dat_summary, aes(x = p_interaction, fill = type)) + 
-    geom_density(alpha = .3) + 
-    xlab(TeX("$P$-value")) + 
-    ylab("Density") + 
-    scale_fill_discrete(guide=FALSE) +
-    ylim(0, 1.5) +
-    ggtitle('Interaction')
-
-  plot_es_interaction <- ggplot(dat_summary, aes(x = es_interaction, fill = type)) + 
-    geom_density(alpha = .3) + 
-    xlab(TeX("Effect size ($r$)")) + 
-    ylab("Density") + 
-    scale_fill_discrete(guide=FALSE)
-
-  # Plot
-  grid.arrange(plot_p_gender,
-               plot_p_condition,
-               plot_p_interaction,
-               plot_es_gender,
-               plot_es_condition,
-               plot_es_interaction,
-               ncol = 3)
-  dev.off()
-}
-@
-
-The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{https://osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{https://osf.io/e6zys}; \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus).
-
-Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
-Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
-These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
-From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
-These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
-Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
-In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
-
-% add plot of left and right skew
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/ddfab_density.pdf}
-\caption{Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
-We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.}
-\label{densities}
-\end{center}
-\end{figure}
-
-<<generate results p/method, echo = FALSE, results = hide>>=
-tp <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-fp <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-fn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-tn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-
-temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
-
-j <- 1
-
-for (variables in which(grepl(names(dat_summary), pattern = "_p")))
-{
-  i <- 1
-
-  for (threshold in seq(0, 1, .01))
-  {
-    tp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
-    fp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'ml', na.rm = TRUE)
-    fn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
-    tn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'ml', na.rm = TRUE)
-
-    i <- i + 1
-  }
-
-  j <- j + 1
-}
-
-# loop through matrix for proper comps
-
-tpr <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-fpr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-fnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-tnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-
-ppv <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-fdr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-npv <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-false_or <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
-
-for (i in 1:sum(grepl(names(dat_summary), pattern = "_p")))
-{
-  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
-  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
-  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
-  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])
-
-  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
-  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
-  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
-  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
-}
-fpr <- as.data.frame(fpr)
-tpr <- as.data.frame(tpr)
-fnr <- as.data.frame(fnr)
-tnr <- as.data.frame(tnr)
-
-ppv <- as.data.frame(ppv)
-fdr <- as.data.frame(fdr)
-npv <- as.data.frame(npv)
-false_or <- as.data.frame(false_or)
-
-names(fpr) <- temp
-names(tpr) <- temp
-names(fnr) <- temp
-names(tnr) <- temp
-
-names(ppv) <- temp
-names(fdr) <- temp
-names(npv) <- temp
-names(false_or) <- temp
-
-height = (tpr[-1, ] + tpr[-dim(tpr)[1], ])/2
-width = apply(fpr, 2, diff) # = diff(rev(omspec))
-AUC_res <- apply(height * width, 2, sum)
-
-Method <- c("$SD_z$ homogeneous all",
-                    "$SD_z$ study 1",
-                    "$SD_z$ study 2",
-                    "$SD_z$ study 3",
-                    "$SD_z$ study 4",
-                    "$maxmin_z$ homogeneous all",
-                    "$maxmin_z$ study 1",
-                    "$maxmin_z$ study 2",
-                    "$maxmin_z$ study 3",
-                    "$maxmin_z$ study 4",
-                    "$SD_z$ heterogeneous all",
-                    "$SD_z$ study 1 low condition",
-                    "$SD_z$ study 1 high condition",
-                    "$SD_z$ study 2 low condition",
-                    "$SD_z$ study 2 high condition",
-                    "$SD_z$ study 3 low condition",
-                    "$SD_z$ study 3 high condition",
-                    "$SD_z$ study 4 low condition",
-                    "$SD_z$ study 4 high condition",
-                    "$maxmin_z$ heterogeneous all",
-                    "$maxmin_z$ study 1 low condition",
-                    "$maxmin_z$ study 1 high condition",
-                    "$maxmin_z$ study 2 low condition",
-                    "$maxmin_z$ study 2 high condition",
-                    "$maxmin_z$ study 3 low condition",
-                    "$maxmin_z$ study 3 high condition",
-                    "$maxmin_z$ study 4 low condition",
-                    "$maxmin_z$ study 4 high condition",
-                    "Fisher test gender hypothesis",
-                    "Fisher test interaction hypothesis",
-                    "Combined Fisher test (3 results, $SD_z$ homogeneous)",
-                    "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
-                    "Combined Fisher test (6 results, $SD_z$ homogeneous)",
-                    "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
-                    "Effect sizes (1-r)")
-AUC <- as.numeric(AUC_res)
-# print(xtable(data.frame(Method, AUC),
-#              caption = "Area Under the Curve (AUC) for the various statistical methods used to detect data fabrication.
-Homogeneous: assumes one population variance underlying all groups.
-Heterogeneous: assumes separate population variance per anchoring condition.",
-#              label = "auc", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
-
-temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
-df <- data.frame(Method = temp,
-                     AUROC = NA,
-                     CI.lb = NA,
-                     CI.ub = NA)
-Method <- c("$SD_z$ homogeneous all",
-            "$SD_z$ study 1",
-            "$SD_z$ study 2",
-            "$SD_z$ study 3",
-            "$SD_z$ study 4",
-            "$maxmin_z$ homogeneous all",
-            "$maxmin_z$ study 1",
-            "$maxmin_z$ study 2",
-            "$maxmin_z$ study 3",
-            "$maxmin_z$ study 4",
-            "$SD_z$ heterogeneous all",
-            "$SD_z$ study 1 low condition",
-            "$SD_z$ study 1 high condition",
-            "$SD_z$ study 2 low condition",
-            "$SD_z$ study 2 high condition",
-            "$SD_z$ study 3 low condition",
-            "$SD_z$ study 3 high condition",
-            "$SD_z$ study 4 low condition",
-            "$SD_z$ study 4 high condition",
-            "$maxmin_z$ heterogeneous all",
-            "$maxmin_z$ study 1 low condition",
-            "$maxmin_z$ study 1 high condition",
-            "$maxmin_z$ study 2 low condition",
-            "$maxmin_z$ study 2 high condition",
-            "$maxmin_z$ study 3 low condition",
-            "$maxmin_z$ study 3 high condition",
-            "$maxmin_z$ study 4 low condition",
-            "$maxmin_z$ study 4 high condition",
-            "Fisher test gender hypothesis",
-            "Fisher test interaction hypothesis",
-            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
-            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
-            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
-            "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
-            "Effect sizes (1-r)")
-
-@
-
-\subsubsection*{Performance of using SDs to detect data fabrication}
-
-We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
-The $SD_z$ method \citep{simonsohn2013} inspects whether the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs varies sufficiently.
-These two methods operate similarly, except for the final computation.
-Other operationalizations are possible and we invite others to reuse the data from this study (\url{https://osf.io/b24pq}).
-
-Table \ref{auroc_variances} indicates that both methods show similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC), but with a preference for $SD_z$.
-This preference is due to the variance of variances outperforming the range of variances when all studies are combined in one test and its past application \citep{simonsohn2013}.
-Throughout the rest of this section, we will only discuss the results of $SD_z$ further.
-
-<<auroc for variance methods, echo=FALSE, results=tex>>=
-selmaxmin <- grepl(Method, pattern = '^.maxmin_')
-selsd <- grepl(x = Method, pattern = '^.SD_z')
-row_table <- c("Homogeneous, all studies combined",
-               "Homogeneous, study 1",
-               "Homogeneous, study 2",
-               "Homogeneous, study 3",
-               "Homogeneous, study 4",
-               "Heterogeneous, all studies combined",
-               "Heterogeneous study 1, low anchor condition",
-               "Heterogeneous study 1, high anchor condition",
-               "Heterogeneous study 2, low anchor condition",
-               "Heterogeneous study 2, high anchor condition",
-               "Heterogeneous study 3, low anchor condition",
-               "Heterogeneous study 3, high anchor condition",
-               "Heterogeneous study 4, low anchor condition",
-               "Heterogeneous study 4, high anchor condition")
-variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
-names(variances_table) <- c("Method", "AUROC $SD_z$", "AUROC $maxmin_z$")
-print(xtable(variances_table,
-             caption = "Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
-Homogeneous: assumes one population variance underlying all groups.
-Heterogeneous: assumes separate population variance per anchoring condition.",
-             label = "auroc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
-@
-
-The AUROC indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
-In other words, if AUROC $=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
-For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
-
-The AUROC for the variance of variance analyses is insufficient or sufficient depending on the assumption regarding population variances.
-Table \ref{auroc_variances} indicates that AUROC $=.423$ when homogeneous population variances are assumed, whereas AUROC $=.770$ when heterogeneous population variances are assumed.
-For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method.
-The method that incorporates heterogeneous population variances (i.e., one per anchoring condition) greatly improves the performance of the variance of variances analysis.
-
-Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=\Sexpr{seq(0, 1, .01)[max(which(tnr$variance_sd_p_overall_hetero == 1))]}$.
-
-\subsubsection*{Performance of using $p$-values to detect data fabrication}
-
-We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
-Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
-In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
-
-<<auroc for single fisher methods, echo=FALSE, results=tex>>=
-sel <- grepl(Method, pattern = '^(Fisher test)')
-row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
-print(xtable(tabl,
-             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
-             label = "auroc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
-@
-
-\subsubsection*{Performance of combining SDs and $p$-value methods to detect data fabrication}
-
-<<auroc for combined fisher methods, echo=FALSE, results=tex>>=
-sel <- grepl(Method, pattern = 'Combined Fisher test')
-row_table <- Method[sel]
-tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
-print(xtable(tabl,
-             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
-             label = "auroc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
-@
-
-\subsubsection*{Performance of large effect sizes to detect data fabrication}
-
-<<get massive statcheck data for checks, echo=FALSE, results=hide>>=
-if(!file.exists(sprintf('%sdata/statcheck_dataset.csv', x12)))
-{
-  url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
-  # If link is broken, more persistent version available at
-  # http://dx.doi.org/10.17026/dans-2cm-v9j9
-
-  GET(url,
-      write_disk(sprintf('%sdata/statcheck_dataset.csv', x12),
-                 overwrite = TRUE))
-}
-
-statcheck_data <- read.csv(sprintf('%sdata/statcheck_dataset.csv', x12))
-# Compute the effect sizes
-sel <- statcheck_data$Statistic == 'F'
-statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel] *
-                                  (statcheck_data$df1[sel] /
-                                     statcheck_data$df2[sel])) /
-                                 (((statcheck_data$Value[sel] *
-                                      statcheck_data$df1[sel]) /
-                                     statcheck_data$df2[sel]) + 1))
-
-sel <- statcheck_data$Statistic == 't'
-statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel]^2 *
-                                  (1 / statcheck_data$df2[sel])) /
-                                 (((statcheck_data$Value[sel]^2 * 1) /
-                                     statcheck_data$df2[sel]) + 1))
-
-sel <- statcheck_data$Statistic == 'r' &
-  statcheck_data$Value <= 1 &
-  statcheck_data$Value > 0
-statcheck_data$es[sel] <- statcheck_data$Value[sel]
-@
-
-%The \Sexpr{sum(dat_summary$es_condition > max(dat_summary$es_condition[dat_summary$type == 'ml']))} largest significant effects were fabricated, with \Sexpr{sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9)} (\Sexpr{round(sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9) / sum(dat_summary$type == 'qualtrics'), 3)}\%) larger than $r=.9$.
-Based on descriptive data throughout psychology \citep{Hartgerink2016-lg}, effect sizes $\geq.9$ belong to the \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .9) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile of effects throughout the psychology literature and effect sizes $\geq.95$ \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .95) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile.
-
 \subsection*{Discussion}
@@
 
-Above, we described results of detecting data fabrication with summary results; in Study 2 we present results of detecting data fabrication with raw data.
+In Study 2 we investigated detecting data fabrication in raw data as an extension of Study 1, which presented results of detecting data fabrication in summary results.
+In essence, the procedure is similar: we asked actual researchers to fabricate data that they thought would go undetected.
+For Study 2 we included a face-to-face interview to qualitatively assess how data fabrication occurs.
+A preregistration of this study occurred during the seeking of funding \citep{10.3897/rio.2.e8860} and during data collection (\url{https://osf.io/XXXX}).
 
-To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment (Stroop 1935).
-
-Raw data are defined as
+To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment \citep{Stroop_1935}.
+In the Stroop task, participants are asked to determine the color a word is presented in (i.e., word colors), but the word also reads a color (i.e., color words).
+The presented word color (i.e., 'red', 'blue', or 'green') can be either presented in the congruent color (e.g., 'red' presented in red) or an incongruent color (i.e., 'red' presented in green).
+The dependent variable in the Stroop task is the response latency (in this study milliseconds are used).
+Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serves as the raw data.
+The Stroop effect typically is computed as the difference in mean response latencies between the congruent and incongruent conditions.
 
@@
 
-Twenty genuine datasets were collected from the Many Labs 3 project (Ebersole et al. ).
+<<echo = FALSE>>=
+ml3_dat <- read.csv(sprintf('%sdata/study_02/ml3_stroop.csv', x12))
+@
 
-Twenty faked datasets were collected experimentally.
-We sampled 20 of 84 Dutch or Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015, which was indexed in Thomson Reuters’ Web of Science database.
-Dutch and Flemish researchers were selected to allow for potential follow-up on the way data was fabricated in a face-to-face interview.
-The period 2005-2015 was chosen to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
-Researchers who published on the Stroop task were selected to ensure their familiarity with the type of task for which data had to be fabricated.
-The database was searched on October 13, 2015 and 84 unique e-mails were extracted from 86 articles.
+Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project \citep[\url{https://osf.io/n8xa7/};][]{Ebersole201668}.
+Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample \citep[the original preregistration mentioned 20 datasets, accidentally overlooking the online sample;][]{10.3897/rio.2.e8860}.
+Using the original raw data and analysis script from ML3 (\url{https://osf.io/qs8tp/}), we computed the mean (M) and standard deviation (SD) for the participant's response latencies in both the within-subjects conditions of congruent trials and incongruent trials.
+These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure \ref{spreadsheet2}).
+The Stroop effect was calculated as a $t$-test of the difference ($H_0:\mu=0$).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet2.png}
+\caption{Example of a filled in template spreadsheet used in the fabrication process for Study 2.
+Respondents fabricated data in the yellow cells and green cells, which were used to compute the results of the hypothesis test of the condition effect.
+If the fabricated data confirm the hypotheses, a checkmark appeared.
+This template is available at \url{https://osf.io/2qrbs/}.}
+\label{spreadsheet2}
+\end{center}
+\end{figure}
+
+We collected twenty-eight faked datasets on the Stroop task experimentally in a two-stage sampling procedure.
+First, we invited 80 Dutch and Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015 as available in the Thomson Reuters’ Web of Science database.
+We selected Dutch and Flemish researchers to allow for a face-to-face interview on how the data were fabricated.
+We chose the period 2005-2015 to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
+The database was searched on October 10, 2016 and 80 unique e-mails were retrieved from 90 publications.
+Only two of these 80 participated in the study; we subsequently implemented a second sampling stage where we collected e-mails from all PhD-candidates, teachers, and professors of psychology related departments at Dutch universities.
+This resulted in 1659 additional unique e-mails that we subsequently invited to participate in this study.
+Due to a malfunction in Qualtrics' quotum sampling, we oversampled, resulting in 28 participants instead of the originally intended 20 participants.
+
+Each participant received instructions on the data fabrication task via Qualtrics but was allowed to fabricate data until the face-to-face interview took place.
+In other words, each participant could take the time they wanted/needed to fabricate the data as extensively as they liked.
+Each participant received downloadable instructions (\url{https://osf.io/7qhy8/}) and the template spreadsheet via Qualtrics (see Figure \ref{spreadsheet2}).
+The interview was scheduled via Qualtrics with JGV, who blinded the rest of the research team from the identifying information of each participant and the date of the interview.
+All interviews took place between January 31 and March 3, 2017.
+To incentivize researchers to participate, they received \euro 100 for participation; to incentivize them to fabricate (supposedly) hard to detect data they could win an additional \euro 100 if they belonged to one out of three top fabricators.
+The contents of the interview will be transcribed for further research on qualitatively assessing how researchers might fabricate experimental data.
+
+The procedure to evaluate the genuine- and fabricated data included digit analyses, variance analyses, comparison of true- and fabricated multivariate associations, and combining results of several of the aforementioned methods with the Fisher method.
+Figure \ref{study2proc} shows how the various methods are combined.
+In short, the digit analyses include Benford's law \citep{Benford1938-fl} and terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj}; analyzing the variance of the standardized SDs \citep[similar to Study 1;][]{simonsohn2013}; the multivariate associations compare the observed correlations between the variables in the fabricated data with the observed correlations between the same variables in the genuine data (the multivariate comparison is only done for fabricated data).
+The Fisher method (Equation \ref{fishertest}) is used to combine the results of the terminal digit analyses, the analyses of the standardized SD variance, and the multivariate associations to determine the hardest to detect fabricated datasets.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/study2proc.pdf}
+\caption{The applied statistical methods to test for data fabrication in Study 2, depicting those that are combined into an overall test for data fabrication with the Fisher method.
+Benford’s law is excluded from the overall tests because of an expected lack of utility.
+Original from \citet{10.3897/rio.2.e8860} under CC-BY.}
+\label{study2proc}
+\end{center}
+\end{figure}
+
+The digit analyses are based on a simple enough premise: test whether the first (i.e., leading) or final (i.e., terminal) digits follow an a priori specified distribution.
+Benford's law \citep{Benford1938-fl} stipulates that the leading digit follows the distribution of
+\begin{equation}
+P(d)=log_{10}(\frac{d+1}{d})
+\label{benford}
+\end{equation}
+where $d$ is the leading digit and $P(d)$ denotes the probability of $d$ (e.g., $P(1)=\Sexpr{round(log(base = 10, (1+1)/1), 3)}$).
+This expected distribution can be tested with a $\chi^2$-test ($df=8$) of the tabular count of leading digits.
+Similarly, terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj} expects that the final digit contains the most measurement error, hence, is uniformly distributed if sufficient digits are available.
+As a rule of thumb, three digits is sufficient to apply terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj}.
+The observed terminal digit count can be tested against the expected uniform distribution with a $\chi^2$-test as well, although with $df=9$ instead of $df=8$ because a leading digit can never be zero.
+
+We analyzed the variance of the standardized SDs for each condition in each dataset (i.e., two tests per dataset).
+Whereas in Study 1 the test was conducted on means and standard deviations across cells per study, in Study 2 we conducted the test on means and standard deviations across respondents per condition.
+The technical aspects of this test remain equivalent to the application in Study 1 (see equations \ref{s2_j} and \ref{simvar}).
+As such, the only difference is that $N_j$ is no longer the sample size, but the number of Stroop trials presented to the participant.
+
+We analyzed the multivariate associations between the means and standard deviations of the participant-level data in four ways.
+We computed the observed multivariate associations between the means across conditions (i.e., $r$($M_{congruent}$,$M_{incongruent}$)), the standard deviations across conditions (i.e., $r$($SD_{congruent}$,$SD_{incongruent}$)), and across means and standard deviations within conditions (i.e., $r$($M_{congruent}$,$SD_{congruent}$) and $r$($M_{incongruent}$,$SD_{incongruent}$)).
+We subsequently compared the observed multivariate correlations from a fabricated dataset with their respective observed multivariate correlations from the genuine data.
+We computed the probability that the genuine data yielded similar, or more extreme, multivariate correlations (i.e., a $p$-value).
+Given 21 genuine datasets are available, only 21 $p$-values are possible (i.e., lowest $p$-values possible are \Sexpr{round(seq(0, 1, 1/21)[1], 3)}, \Sexpr{round(seq(0, 1, 1/21)[2], 3)}, and \Sexpr{round(seq(0, 1, 1/21)[3], 3)}).
+
+We combined the results from the four terminal digit analyses, the two variance analyses, and the four multivariate analyses with the Fisher method.
+This result was used to determine the top three fabricators, by rank-ordering the $p$-values for each fabricator (higher $p$-value equating to less evidence for fabrication).
+This omnibus method aggregates evidence from the various methods, making it potentially more sensitive for various fabrication behaviors.
+We evaluated each of the methods to detect data fabrication using AUROC-curves, using the same procedures as in Study 1.
 
@@
 
+<<echo = FALSE>>=
+tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[1], ]
+
+@
+
 \section*{Discussion}
+
+% Be sure to discuss why Benford's law wasn't included in the combination
+% Reflect on whether it worked to detect fabrication
 

### 2017-03-03 submission/manuscript.tex
Preregister study 2

@@
 
+\section*{Study 1}
+
+We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies \citep{tversky1974,jacowitz1995}.
+The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
+For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'.
+These questions yield mean responses of 25\% and 45\%, respectively \citep{tversky1974}, despite essentially posing the same factual question.
+A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
+
+\subsection*{Methods}
+
+The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States.
+Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
+Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
+For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
+All materials, data, and analyses scripts are freely available on the OSF (\url{https://osf.io/b24pq}) and a preregistration is available at \url{https://osf.io/ejf5x} (deviations are explicated in this report).
+
+\subsubsection*{Data collection}
+
+We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project \citep[\url{https://osf.io/pqf9r};][]{klein2014}.
+The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
+Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
+For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
+We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
+
+Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
+Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
+The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
+We sampled psychology researchers to improve familiarity with the anchoring effect \citep{jacowitz1995,tversky1974}, for which summary results were fabricated.
+We filtered for U.S.
+researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
+researchers were included because this filter also retained papers with co-authors from the U.S.).
+WoS was searched on October 13, 2015.
+In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).
+
+A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{https://osf.io/s4w8r}).
+The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
+We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication.
+We also clarified to the  respondents that they could stop at any time without providing a reason.
+If they wanted, respondents received a \$30 Amazon gift card as compensation for their participation if they were willing to enter their email address.
+They could win an additional \$50 Amazon gift card if they were one of three top fabricators.
+The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
+The full text of the Qualtrics survey is available at \url{https://osf.io/w984b}.
+
+Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
+We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
+Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
+The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
+
+We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data.
+Figure \ref{fig1} depicts an example of this spreadsheet (original:  \url{https://osf.io/w6v4u}).
+We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
+Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
+If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure \ref{fig1}.
+We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet.png}
+\caption{Example of a filled in template spreadsheet used in the fabrication process of Study 1.
+Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
+If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell (one of four template spreadsheets available at \url{https://osf.io/w6v4u/}).}
+\label{fig1}
+\end{center}
+\end{figure}
+
+Upon completing the fabrication of the data, respondents were debriefed.
+Respondents answered several questions about their statistical knowledge and approach to data fabrication and finally we reminded them that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
+We rewarded participation with a \$30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus \$50 Amazon gift card.
+
+\subsubsection*{Data analysis}
+
+To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies.
+This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
+For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
+To compute this probability, we first standardized the SDs for each of the four studies with
+\begin{equation}
+z_j=\sqrt{\frac{s^2_j}{MS_w}}=\sqrt{\frac{s^2_j}{\left(\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}\right)}}
+\label{s2_j}
+\end{equation}
+where $z_j$ denotes the standardized SD in group $j$ ($MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells, which is the case for the fabricated datasets).
+We tested different measures to detect data fabrication that utilize these standardized SDs (i.e., $z_j$).
+We included the variance of the standardized SDs \citep[i.e.,  $SD_{z}$;][]{simonsohn2013} and tried out the max-min distance of the standardized SDs (denoted $max-min_{z}$) as an alternative measure.
+We compared the observed value for each measure with the expected distribution when the summary results are used to generate random samples.
+To this end, we simulated the expected distribution of standardized SDs and computed the expected distribution of each measure.
+This expected distribution was used to determine the $p$-value of the observed $SD_z$ and $max-min_z$.
+We simulated the standardized variance for each of the $j$ groups as
+\begin{equation}
+z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
+\label{simvar}
+\end{equation}
+These simulated values are used to compute the expected distribution of the $SD_z$ and $max-min_z$  measures.
+
+Testing the standardized SDs for potential data fabrication can be done either for each study separately or all studies combined; the test can also be done under different assumptions of population variances across conditions.
+The assumptions of population variance can either by that all SDs originate from the same distribution \citep[as in][]{simonsohn2013}, the SDs within a factor are from the same distribution, or each group comes from its own distribution.
+We preregistered the method that assumes the SDs are drawn from the same distribution for the various conditions (i.e., homogeneous SDs) and are tested across all studies.
+However, upon conducting the analyses, we decided homogenous SDs are not unequivocal and included computations where the SDs for the low anchor and high anchor are from different distributions (i.e., heterogeneous SDs).
+Additionally, the signal for data fabrication across the four anchoring studies might result in different studies cancelling each other out, so we also included analyses where each study was analyzed separately.
+
+Second, we applied the reversed Fisher method to detect data fabrication to the nonsignificant $p$-values twice: once for the results of gender effects hypothesis in each study and once for the results of the interaction effect hypothesis for each study.
+The Fisher method \citep{fisher1925} tests for evidence of an effect in a set of $p$-values by testing for a right-skew $p$-value distribution, but we adjusted it here to test for results that are overly consistent with the null hypothesis and result in a left-skew distribution (see Figure \ref{leftskew}).
+The original Fisher method is computed as
+\begin{equation}
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
+\label{fishertest}
+\end{equation}
+and tests for right-skew in a set of $p$-values, but we adjust it to the following
+\begin{equation}
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
+\label{fisheradjusted}
+\end{equation}
+where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
+We set this threshold to .05 in order to include only nonsignificant test results.
+The theoretical idea behind this method is that researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution, given the frequent misinterpretation of $p$-values \citep[e.g., as the probability of an effect,][]{Goodman2008135,Altman_1995}.
+% I can add more refs but it is just a rabbit hole to start with more.
+
+% add plot of left and right skew
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/fisherfig.pdf}
+\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and what the adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B).
+Both panels test whether there is sufficient evidence that the solid line deviates from the dashed line, except that the type of deviation that the test is sensitive to is the exact opposite.}
+\label{leftskew}
+\end{center}
+\end{figure}
+
+Finally, we combined the aforementioned methods to detect data fabrication with the Fisher method.
+This included the $SD_z$ measure across all studies and the Fisher test (Equation \ref{fisheradjusted}) of the gender hypothesis test and the interaction test.
+We expected this combination test of the three individual tests for data fabrication to be more powerful than the individual tests, given that these tests inspect different manifestations of data fabrications.
+Based on the results of the combined test results, the three least detectable data fabricators were selected.
+The three respondents with the highest $p$-values on this combined method to detect data fabrication contained the least evidential value for deviating from genuine data and received an additional \$50 Amazon gift card.
+
+For each of these four tests to detect data fabrication ($SD_z$, Fisher test for the gender and interaction hypotheses, combined methods) we carried out sensitivity and specificity analyses using ROC-curves.
+ROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
+With these ROC-curves, informed decisions about optimal alpha levels can be made based on various criteria.
+In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest.
+For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.
+% Maybe include bootstrapped errors here.
+
+\subsection*{Results}
+
+\subsection*{Discussion}
+
+% variance analysis and effect size best ways to inspect
+% but severely correlated: smaller variances = larger effects
+% easiest way is too look for massive effects in the effects
+
+% Simonsohn method not invalid under homogeneous, just somethign to take into account
+% easily adjusted
+
+% Discuss how the PPV is likely to be overestimated because prevalence is 50% in this study
+% How we don't know the prevalence, in fact.
+
+% Discuss alpha choice based on sample has large error (small sample).
+% Only provides a first indication
+
+% Comparison between methods not tested, large error given small sample.
+% This provides just initial work
+
+\section*{Study 2}
+
+In Study 2 we investigated detecting data fabrication in raw data as an extension of Study 1, which presented results of detecting data fabrication in summary results.
+In essence, the procedure is similar: we asked actual researchers to fabricate data that they thought would go undetected.
+For Study 2 we included a face-to-face interview to qualitatively assess how data fabrication occurs.
+A preregistration of this study occurred during the seeking of funding \citep{10.3897/rio.2.e8860} and during data collection (\url{https://osf.io/XXXX}).
+
+To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment \citep{Stroop_1935}.
+In the Stroop task, participants are asked to determine the color a word is presented in (i.e., word colors), but the word also reads a color (i.e., color words).
+The presented word color (i.e., 'red', 'blue', or 'green') can be either presented in the congruent color (e.g., 'red' presented in red) or an incongruent color (i.e., 'red' presented in green).
+The dependent variable in the Stroop task is the response latency (in this study milliseconds are used).
+Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serves as the raw data.
+The Stroop effect typically is computed as the difference in mean response latencies between the congruent and incongruent conditions.
+
+\section*{Methods}
+
+Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project \citep[\url{https://osf.io/n8xa7/};][]{Ebersole201668}.
+Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample \citep[the original preregistration mentioned 20 datasets, accidentally overlooking the online sample;][]{10.3897/rio.2.e8860}.
+Using the original raw data and analysis script from ML3 (\url{https://osf.io/qs8tp/}), we computed the mean (M) and standard deviation (SD) for the participant's response latencies in both the within-subjects conditions of congruent trials and incongruent trials.
+These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure \ref{spreadsheet2}).
+The Stroop effect was calculated as a $t$-test of the difference ($H_0:\mu=0$).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/spreadsheet2.png}
+\caption{Example of a filled in template spreadsheet used in the fabrication process for Study 2.
+Respondents fabricated data in the yellow cells and green cells, which were used to compute the results of the hypothesis test of the condition effect.
+If the fabricated data confirm the hypotheses, a checkmark appeared.
+This template is available at \url{https://osf.io/2qrbs/}.}
+\label{spreadsheet2}
+\end{center}
+\end{figure}
+
+We collected twenty-eight faked datasets on the Stroop task experimentally in a two-stage sampling procedure.
+First, we invited 80 Dutch and Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015 as available in the Thomson Reuters’ Web of Science database.
+We selected Dutch and Flemish researchers to allow for a face-to-face interview on how the data were fabricated.
+We chose the period 2005-2015 to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
+The database was searched on October 10, 2016 and 80 unique e-mails were retrieved from 90 publications.
+Only two of these 80 participated in the study; we subsequently implemented a second sampling stage where we collected e-mails from all PhD-candidates, teachers, and professors of psychology related departments at Dutch universities.
+This resulted in 1659 additional unique e-mails that we subsequently invited to participate in this study.
+Due to a malfunction in Qualtrics' quotum sampling, we oversampled, resulting in 28 participants instead of the originally intended 20 participants.
+
+Each participant received instructions on the data fabrication task via Qualtrics but was allowed to fabricate data until the face-to-face interview took place.
+In other words, each participant could take the time they wanted/needed to fabricate the data as extensively as they liked.
+Each participant received downloadable instructions (\url{https://osf.io/7qhy8/}) and the template spreadsheet via Qualtrics (see Figure \ref{spreadsheet2}).
+The interview was scheduled via Qualtrics with JGV, who blinded the rest of the research team from the identifying information of each participant and the date of the interview.
+All interviews took place between January 31 and March 3, 2017.
+To incentivize researchers to participate, they received \euro 100 for participation; to incentivize them to fabricate (supposedly) hard to detect data they could win an additional \euro 100 if they belonged to one out of three top fabricators.
+The contents of the interview will be transcribed for further research on qualitatively assessing how researchers might fabricate experimental data.
+
+The procedure to evaluate the genuine- and fabricated data included digit analyses, variance analyses, comparison of true- and fabricated multivariate associations, and combining results of several of the aforementioned methods with the Fisher method.
+Figure \ref{study2proc} shows how the various methods are combined.
+In short, the digit analyses include Benford's law \citep{Benford1938-fl} and terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj}; analyzing the variance of the standardized SDs \citep[similar to Study 1;][]{simonsohn2013}; the multivariate associations compare the observed correlations between the variables in the fabricated data with the observed correlations between the same variables in the genuine data (the multivariate comparison is only done for fabricated data).
+The Fisher method (Equation \ref{fishertest}) is used to combine the results of the terminal digit analyses, the analyses of the standardized SD variance, and the multivariate associations to determine the hardest to detect fabricated datasets.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/study2proc.pdf}
+\caption{The applied statistical methods to test for data fabrication in Study 2, depicting those that are combined into an overall test for data fabrication with the Fisher method.
+Benford’s law is excluded from the overall tests because of an expected lack of utility.
+Original from \citet{10.3897/rio.2.e8860} under CC-BY.}
+\label{study2proc}
+\end{center}
+\end{figure}
+
+The digit analyses are based on a simple enough premise: test whether the first (i.e., leading) or final (i.e., terminal) digits follow an a priori specified distribution.
+Benford's law \citep{Benford1938-fl} stipulates that the leading digit follows the distribution of
+\begin{equation}
+P(d)=log_{10}(\frac{d+1}{d})
+\label{benford}
+\end{equation}
+where $d$ is the leading digit and $P(d)$ denotes the probability of $d$ (e.g., $P(1)=0.301$).
+This expected distribution can be tested with a $\chi^2$-test ($df=8$) of the tabular count of leading digits.
+Similarly, terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj} expects that the final digit contains the most measurement error, hence, is uniformly distributed if sufficient digits are available.
+As a rule of thumb, three digits is sufficient to apply terminal digit analysis \citep{Mosimann1995-av,Mosimann2002-oj}.
+The observed terminal digit count can be tested against the expected uniform distribution with a $\chi^2$-test as well, although with $df=9$ instead of $df=8$ because a leading digit can never be zero.
+
+We analyzed the variance of the standardized SDs for each condition in each dataset (i.e., two tests per dataset).
+Whereas in Study 1 the test was conducted on means and standard deviations across cells per study, in Study 2 we conducted the test on means and standard deviations across respondents per condition.
+The technical aspects of this test remain equivalent to the application in Study 1 (see equations \ref{s2_j} and \ref{simvar}).
+As such, the only difference is that $N_j$ is no longer the sample size, but the number of Stroop trials presented to the participant.
+
+We analyzed the multivariate associations between the means and standard deviations of the participant-level data in four ways.
+We computed the observed multivariate associations between the means across conditions (i.e., $r$($M_{congruent}$,$M_{incongruent}$)), the standard deviations across conditions (i.e., $r$($SD_{congruent}$,$SD_{incongruent}$)), and across means and standard deviations within conditions (i.e., $r$($M_{congruent}$,$SD_{congruent}$) and $r$($M_{incongruent}$,$SD_{incongruent}$)).
+We subsequently compared the observed multivariate correlations from a fabricated dataset with their respective observed multivariate correlations from the genuine data.
+We computed the probability that the genuine data yielded similar, or more extreme, multivariate correlations (i.e., a $p$-value).
+Given 21 genuine datasets are available, only 21 $p$-values are possible (i.e., lowest $p$-values possible are 0, 0.048, and 0.095).
+
+We combined the results from the four terminal digit analyses, the two variance analyses, and the four multivariate analyses with the Fisher method.
+This result was used to determine the top three fabricators, by rank-ordering the $p$-values for each fabricator (higher $p$-value equating to less evidence for fabrication).
+This omnibus method aggregates evidence from the various methods, making it potentially more sensitive for various fabrication behaviors.
+We evaluated each of the methods to detect data fabrication using AUROC-curves, using the same procedures as in Study 1.
+
+\section*{Results}
+
+\section*{Discussion}
+
+% Be sure to discuss why Benford's law wasn't included in the combination
+% Reflect on whether it worked to detect fabrication
+
+\section*{General discussion}
+
 % Talk about deterrence theory and how marginal utility might make it more attractive to go towards more extreme forms of misconduct if zero-tolerance policy is applied.
@@
 
+other attached packages:
+ [1] stringr_1.1.0     plyr_1.8.4        reshape2_1.4.2    dplyr_0.5.0      
+ [5] data.table_1.10.0 lsr_0.5           effects_3.1-2     car_2.0-19       
+ [9] httr_1.2.1        xtable_1.7-1      gridExtra_2.2.1   ggplot2_2.2.1    
+[13] latex2exp_0.4.0   foreign_0.8-67    pROC_1.8
+
 loaded via a namespace (and not attached):
-[1] tools_3.3.2
+ [1] Rcpp_0.12.9      magrittr_1.5     splines_3.3.2    MASS_7.3-45     
+ [5] munsell_0.4.3    colorspace_1.3-2 lattice_0.20-34  R6_2.2.0        
+ [9] minqa_1.2.4      tools_3.3.2      nnet_7.3-12      grid_3.3.2      
+[13] nlme_3.1-128     gtable_0.2.0     DBI_0.5-1        lme4_1.1-12     
+[17] lazyeval_0.2.0   assertthat_0.1   tibble_1.2       Matrix_1.2-7.1  
+[21] nloptr_1.0.4     stringi_1.1.2    scales_0.4.1    
 \end{Soutput}

### 2017-03-06 functions/std_var.R
AH forgot a sqrt()

@@ -1,6 +1,6 @@
 std_var <- function(n, sds, iter = 1000, ...)
 {
-  msw_obs <- msw(n, sds)
+  msw_obs <- msw(n = n, sds = sds)
   z2_sd_obs <- z2_sd(sds = sds, msw = msw_obs)
   
   obs_sd_z2 <- sd(z2_sd_obs)
@@ -13,10 +13,10 @@ std_var <- function(n, sds, iter = 1000, ...)
   })
   
   # Compute msw for simulated variances (per row)
-  msw_sim <- apply(tmp, 1, function(x) msw(n, x))
+  msw_sim <- apply(sqrt(tmp), 1, function(x) msw(n = n, sds = x))
   
   # Normalize simulated variances
-  sim_z2 <- z2_sd(sds = tmp, msw = msw_sim)
+  sim_z2 <- z2_sd(sds = sqrt(tmp), msw = msw_sim)
   # Calculate SD for each iteration
   sim_sd_z2 <- apply(sim_z2, 1, sd)
   

### 2017-03-06 submission/manuscript.Rnw
Add analysis code for study 2 (initial run; pre-data availability; JGV still has data and rest is blind)

@@
 <<echo = FALSE>>=
-tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[1], ]
+
+df_ml3 <- NULL
+# Compute the results for the ML3 data
+for(i in 1:length(unique(ml3_dat$study_name)))
+{
+  tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[i], ]
+
+  binder <- data.frame(id = unique(ml3_dat$study_name)[i],
+                       benford_congr_m_p = digit_analysis(tmp$MC, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(tmp$SDC, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(tmp$MI, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(tmp$SDI, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(tmp$MC, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(tmp$SDC, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(tmp$MI, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(tmp$SDI, type = 'terminal')$pval,
+                       std_congr_p = std_var(tmp$SDC, tmp$NC, iter = 100000),
+                       std_incongr_p = std_var(tmp$SDI, tmp$NI, iter = 100000),
+                       mult_m_sd_congr = cor(tmp$MC, tmp$SDC),
+                       mult_m_sd_incongr = cor(tmp$MI, tmp$SDI),
+                       mult_m_m_across = cor(tmp$MC, tmp$MI),
+                       mult_sd_sd_across = cor(tmp$SDC, tmp$SDI))
+
+  df_ml3 <- rbind(df_ml3, binder)
+}
+
+# The responses from the study
+responses <- list.files(sprintf('%sdata/study_02/responses', x12))
+df_fab <- NULL
+
+for (response in responses)
+{
+  fab_dat <- read.table(sprintf('%sdata/study_02/responses/%s', x12, response),
+                        sep = '\t', header = TRUE)
+  # For clarity sake
+  names(fab_dat) <- c('id',
+                      'mean_congruent',
+                      'sd_congruent',
+                      'congruent_trials',
+                      'mean_incongruent',
+                      'sd_incongruent',
+                      'incongruent_trials')
+
+  mult_m_sd_congr <- cor(fab_dat$mean_congruent, fab_dat$sd_congruent)
+  mult_m_sd_incongr <- cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent)
+  mult_m_m_across <- cor(fab_dat$mean_congruent, fab_dat$mean_incongruent)
+  mult_sd_sd_across <- cor(fab_dat$sd_congruent, fab_dat$sd_incongruent)
+
+  p_mult_m_sd_congr <- ifelse(mean(df_ml3$mult_m_sd_congr) > mult_m_sd_congr,
+                              sum(df_ml3$mult_m_sd_congr < mult_m_sd_congr) / length(df_ml3$mult_m_sd_congr),
+                              sum(df_ml3$mult_m_sd_congr > mult_m_sd_congr) / length(df_ml3$mult_m_sd_congr))
+  p_mult_m_sd_incongr <- ifelse(mean(df_ml3$mult_m_sd_incongr) > mult_m_sd_incongr,
+                                sum(df_ml3$mult_m_sd_incongr < mult_m_sd_incongr) / length(df_ml3$mult_m_sd_incongr),
+                                sum(df_ml3$mult_m_sd_incongr > mult_m_sd_incongr) / length(df_ml3$mult_m_sd_incongr))
+  p_mult_m_m_across <- ifelse(mean(df_ml3$mult_m_m_across) > mult_m_m_across,
+                              sum(df_ml3$mult_m_m_across < mult_m_m_across) / length(df_ml3$mult_m_m_across),
+                              sum(df_ml3$mult_m_m_across > mult_m_m_across) / length(df_ml3$mult_m_m_across))
+  p_mult_sd_sd_across <- ifelse(mean(df_ml3$mult_sd_sd_across) > mult_sd_sd_across,
+                                sum(df_ml3$mult_sd_sd_across < mult_sd_sd_across) / length(df_ml3$mult_sd_sd_across),
+                                sum(df_ml3$mult_sd_sd_across > mult_sd_sd_across) / length(df_ml3$mult_sd_sd_across))
+
+  binder <- data.frame(id = response,
+                       benford_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'terminal')$pval,
+                       std_congr_p = std_var(fab_dat$sd_congruent, fab_dat$congruent_trials, iter = 10000),
+                       std_incongr_p = std_var(fab_dat$sd_incongruent, fab_dat$incongruent_trials, iter = 10000),
+                       p_mult_m_sd_congr,
+                       p_mult_m_sd_incongr,
+                       p_mult_m_m_across,
+                       p_mult_sd_sd_across)
+
+  p_for_fish <- unlist(ifelse(binder[,6:15] == 0, .0000001, binder[,6:15]))
+
+  fish <- -2*sum(log(p_for_fish))
+  df_fish <- length(p_for_fish) * 2
+  p_fish <- pchisq(q = fish, df = df_fish, lower.tail = FALSE)
+  binder <- cbind(binder, p_fish)
+
+  df_fab <- rbind(df_fab, binder)
+}
 

### 2017-03-08 submission/manuscript.Rnw
Sourcing for previous commit
Update study 2 analyses before analyzing for bonus.

--- 2017-03-03 submission/manuscript.Rnw
@@
 # x12 <- ''
+
+source(sprintf('%sfunctions/digit_analysis.R', x12))
+source(sprintf('%sfunctions/std_var.R', x12))
 @
@@
 <<echo = FALSE>>=
-tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[1], ]
+
+df_ml3 <- NULL
+# Compute the results for the ML3 data
+for(i in 1:length(unique(ml3_dat$study_name)))
+{
+  tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[i], ]
+
+  binder <- data.frame(id = unique(ml3_dat$study_name)[i],
+                       benford_congr_m_p = digit_analysis(tmp$MC, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(tmp$SDC, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(tmp$MI, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(tmp$SDI, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(tmp$MC, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(tmp$SDC, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(tmp$MI, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(tmp$SDI, type = 'terminal')$pval,
+                       std_congr_p = std_var(tmp$SDC, tmp$NC, iter = iter),
+                       std_incongr_p = std_var(tmp$SDI, tmp$NI, iter = iter),
+                       mult_m_sd_congr = cor(tmp$MC, tmp$SDC),
+                       mult_m_sd_incongr = cor(tmp$MI, tmp$SDI),
+                       mult_m_m_across = cor(tmp$MC, tmp$MI),
+                       mult_sd_sd_across = cor(tmp$SDC, tmp$SDI))
+
+  df_ml3 <- rbind(df_ml3, binder)
+}
+
+# The responses from the study
+responses <- list.files(sprintf('%sdata/study_02/responses', x12))
+df_fab <- NULL
+
+for (response in responses)
+{
+  fab_dat <- read.table(sprintf('%sdata/study_02/responses/%s', x12, response),
+                        sep = '\t', header = TRUE)
+  # For clarity sake
+  names(fab_dat) <- c('id',
+                      'mean_congruent',
+                      'sd_congruent',
+                      'congruent_trials',
+                      'mean_incongruent',
+                      'sd_incongruent',
+                      'incongruent_trials')
+
+  mult_m_sd_congr <- cor(fab_dat$mean_congruent, fab_dat$sd_congruent)
+  mult_m_sd_incongr <- cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent)
+  mult_m_m_across <- cor(fab_dat$mean_congruent, fab_dat$mean_incongruent)
+  mult_sd_sd_across <- cor(fab_dat$sd_congruent, fab_dat$sd_incongruent)
+
+  p_mult_m_sd_congr <- ifelse(mean(df_ml3$mult_m_sd_congr) > mult_m_sd_congr,
+                              sum(df_ml3$mult_m_sd_congr < mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr),
+                              sum(df_ml3$mult_m_sd_congr > mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr))
+  p_mult_m_sd_incongr <- ifelse(mean(df_ml3$mult_m_sd_incongr) > mult_m_sd_incongr,
+                                sum(df_ml3$mult_m_sd_incongr < mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr),
+                                sum(df_ml3$mult_m_sd_incongr > mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr))
+  p_mult_m_m_across <- ifelse(mean(df_ml3$mult_m_m_across) > mult_m_m_across,
+                              sum(df_ml3$mult_m_m_across < mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across),
+                              sum(df_ml3$mult_m_m_across > mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across))
+  p_mult_sd_sd_across <- ifelse(mean(df_ml3$mult_sd_sd_across) > mult_sd_sd_across,
+                                sum(df_ml3$mult_sd_sd_across < mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across),
+                                sum(df_ml3$mult_sd_sd_across > mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across))
+
+  binder <- data.frame(id = response,
+                       benford_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'terminal')$pval,
+                       std_congr_p = std_var(fab_dat$sd_congruent, fab_dat$congruent_trials, iter = iter),
+                       std_incongr_p = std_var(fab_dat$sd_incongruent, fab_dat$incongruent_trials, iter = iter),
+                       p_mult_m_sd_congr,
+                       p_mult_m_sd_incongr,
+                       p_mult_m_m_across,
+                       p_mult_sd_sd_across)
+
+  # Add 1 ten millionth to any zero
+  # so the log doesn't go to infinite and messes with the Fisher method
+  p_for_fish <- unlist(ifelse(binder[,6:15] == 0, .0000001, binder[,6:15]))
+
+  fish <- -2 * sum(log(p_for_fish))
+  df_fish <- length(p_for_fish) * 2
+  p_fish <- pchisq(q = fish, df = df_fish, lower.tail = FALSE)
+  binder <- cbind(binder, p_fish)
+
+  df_fab <- rbind(df_fab, binder)
+}
 

### 2017-03-08 submission/manuscript.Rnw
Update the ML3 data file, based on Charlie's emails from October 2016.

@@
 summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
-ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/ML3StroopRaw.csv', x12)
-ml3_clean_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/ML3 Stroop Data/StroopCleanSet.csv', x12)
+ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/StroopCleanSet.csv', x12)
 pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)

### 2017-03-08 functions/compute_raw_stroop_ml3.R
Rerun the ML3 data cleaning

@@ -32,12 +32,13 @@ JustTest[JustTest$trial_word=="blue",]$trial_word=2
 JustTest[JustTest$trial_word=="green",]$trial_word=3
 # list(JustTest$trial_word)
 
-JustTest[JustTest$block_pairing_definition=="red",]$block_pairing_definition=1
+# JustTest[JustTest$block_pairing_definition=="red",]$block_pairing_definition=1
 # list(JustTest$block_pairing_definition)
-JustTest[JustTest$block_pairing_definition=="blue",]$block_pairing_definition=2
-JustTest[JustTest$block_pairing_definition=="green",]$block_pairing_definition=3
+# JustTest[JustTest$block_pairing_definition=="blue",]$block_pairing_definition=2
+# JustTest[JustTest$block_pairing_definition=="green",]$block_pairing_definition=3
 # list(JustTest$block_pairing_definition)
 ###Now the color and meaning of each word are coded as numbers
+# CHJH: were already coded as numbers in the clean set.
 
 ###making variable for congruent vs. incongruent trials
 JustTest$congruent<-JustTest$block_pairing_definition==JustTest$trial_word

### 2017-03-09 submission/manuscript.Rnw
Add write-out of fabricated datasets testing.
Interim commit

@@
 Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data.
-Even though the data available look different depending on the structure of the study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+Even though the data available can look different depending on the structure of a study, there are certain common characteristics of results and the underlying raw data that can be inspected.
 For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
@@
 
-We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies \citep{tversky1974,jacowitz1995}.
+We tested the performance of statistical methods to detect data fabrication in summary results with genuine- and fabricated summary results from four anchoring studies \citep{tversky1974,jacowitz1995}.
 The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
@@
 A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
+All described methods were approved by the Tilburg Ethical Review Board (EC-2015.50).
 
@@
 
-The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States.
-Each of the four studies provided summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
+We collected summary results for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States \citep{jacowitz1995}.
+Each of the four studies provided us with summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
 Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
@@
 The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
-Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
+Considering the size of the ML project, the transparency of research results, and minimal individual gain for fabricating data, we assumed these data to be genuine.
+For each of the thirty-six locations we computed sample sizes, means, and standard deviations for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations.
 We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
 
-Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
-Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
-The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
+Using quotum sampling, we collected thirty-six fabricated datasets of summary results for the same four anchoring studies.
+Quotum sampling was used to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
+The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in Web of Science (WoS) with the filter set to the U.S.
 We sampled psychology researchers to improve familiarity with the anchoring effect \citep{jacowitz1995,tversky1974}, for which summary results were fabricated.
@@
 researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
-researchers were included because this filter also retained papers with co-authors from the U.S.).
+researchers were included because the WoS filter also retained papers with co-authors from the U.S.).
 WoS was searched on October 13, 2015.
@@
 
-A random sample of 1,000 researchers were approached via e-mail to participate in this study on April 25, 2016 (invitation: \url{https://osf.io/s4w8r}).
+We invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: \url{https://osf.io/s4w8r}).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 They could win an additional \$50 Amazon gift card if they were one of three top fabricators.
-The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
+The provided e-mail addresses were unlinked from individual responses upon sending the bonus gift cards.
 The full text of the Qualtrics survey is available at \url{https://osf.io/w984b}.
@@
 Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
-We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
-Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
-The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
+We instructed respondents to fabricate results for the following hypotheses: there is (i) a main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
+We fixed the sample sizes to 25 per cell; respondents did not need to fabricate sample sizes.
+The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of statistical tools to detect data fabrication.
 
@@
 \subsection*{Results}
+
+<<read in data, echo = FALSE, results = hide>>=
+# Read in datafile, just in case the computations were not re-run.
+dat_summary <- read.csv(dat_summary_file)
+# Select only those from qualtrics who did for bonus
+# removed <- sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))
+# dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
+
+type_index <- which(names(dat_summary) == 'type')
+temp <- dat_summary[, c(type_index, 18:length(names(dat_summary)))]  
+dat_summary$es_gender <- sqrt(dat_summary$es2_gender)
+dat_summary$es_condition <- sqrt(dat_summary$es2_condition)
+dat_summary$es_interaction <- sqrt(dat_summary$es2_interaction)
+
+# naming just for ease of use later
+dat_summary$es_p <- 1 - dat_summary$es_condition
+
+if(!file.exists(sprintf('%sfigures/ddfab_density.pdf', x12)))
+{
+  pdf(sprintf('%sfigures/ddfab_density.pdf', x12), width = 10, height = 7)
+  # Gender
+  plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    ylim(0, 1.5) + 
+    scale_fill_discrete(guide=FALSE) + 
+    ggtitle('Gender')
+
+  plot_es_gender <- ggplot(dat_summary, aes(x = es_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Condition
+  plot_p_condition <- ggplot(dat_summary, aes(x = p_condition, fill = type)) +
+    geom_density(alpha = .3) +
+    xlim(0, 1) +
+    xlab(TeX("$P$-value")) +
+    ylab("Density") +
+    scale_fill_discrete(labels = c("Genuine","Fabricated")) + 
+    theme(legend.position="top") + 
+    ggtitle('Condition')
+
+  plot_p_condition$labels$fill <- ""
+
+  plot_es_condition <- ggplot(dat_summary, aes(x = es_condition, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlim(0, 1) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Interaction
+  plot_p_interaction <- ggplot(dat_summary, aes(x = p_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE) +
+    ylim(0, 1.5) +
+    ggtitle('Interaction')
+
+  plot_es_interaction <- ggplot(dat_summary, aes(x = es_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Plot
+  grid.arrange(plot_p_gender,
+               plot_p_condition,
+               plot_p_interaction,
+               plot_es_gender,
+               plot_es_condition,
+               plot_es_interaction,
+               ncol = 3)
+  dev.off()
+}
+@
+
+The collected data included \Sexpr{table(dat_summary$type)[1]} genuine data from Many Labs 1 \citep[\url{https://osf.io/pqf9r};][]{klein2014} and \Sexpr{table(dat_summary$type)[2]} fabricated datasets(\url{https://osf.io/e6zys}; \Sexpr{sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))} participants did not participate for a bonus).
+
+Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
+Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
+These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
+
+% add plot of left and right skew
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/ddfab_density.pdf}
+\caption{Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.}
+\label{densities}
+\end{center}
+\end{figure}
+
+<<generate results p/method, echo = FALSE, results = hide>>=
+tp <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fp <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
+
+j <- 1
+
+for (variables in which(grepl(names(dat_summary), pattern = "_p")))
+{
+  i <- 1
+
+  for (threshold in seq(0, 1, .01))
+  {
+    tp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    fp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'ml', na.rm = TRUE)
+    fn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
+    tn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'ml', na.rm = TRUE)
+
+    i <- i + 1
+  }
+
+  j <- j + 1
+}
+
+# loop through matrix for proper comps
+
+tpr <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fpr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+ppv <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fdr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+npv <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+false_or <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+for (i in 1:sum(grepl(names(dat_summary), pattern = "_p")))
+{
+  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
+  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
+  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
+  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])
+
+  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
+  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
+  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
+  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
+}
+fpr <- as.data.frame(fpr)
+tpr <- as.data.frame(tpr)
+fnr <- as.data.frame(fnr)
+tnr <- as.data.frame(tnr)
+
+ppv <- as.data.frame(ppv)
+fdr <- as.data.frame(fdr)
+npv <- as.data.frame(npv)
+false_or <- as.data.frame(false_or)
+
+names(fpr) <- temp
+names(tpr) <- temp
+names(fnr) <- temp
+names(tnr) <- temp
+
+names(ppv) <- temp
+names(fdr) <- temp
+names(npv) <- temp
+names(false_or) <- temp
+
+height = (tpr[-1, ] + tpr[-dim(tpr)[1], ])/2
+width = apply(fpr, 2, diff) # = diff(rev(omspec))
+AUC_res <- apply(height * width, 2, sum)
+
+Method <- c("$SD_z$ homogeneous all",
+            "$SD_z$ study 1",
+            "$SD_z$ study 2",
+            "$SD_z$ study 3",
+            "$SD_z$ study 4",
+            "$maxmin_z$ homogeneous all",
+            "$maxmin_z$ study 1",
+            "$maxmin_z$ study 2",
+            "$maxmin_z$ study 3",
+            "$maxmin_z$ study 4",
+            "$SD_z$ heterogeneous all",
+            "$SD_z$ study 1 low condition",
+            "$SD_z$ study 1 high condition",
+            "$SD_z$ study 2 low condition",
+            "$SD_z$ study 2 high condition",
+            "$SD_z$ study 3 low condition",
+            "$SD_z$ study 3 high condition",
+            "$SD_z$ study 4 low condition",
+            "$SD_z$ study 4 high condition",
+            "$maxmin_z$ heterogeneous all",
+            "$maxmin_z$ study 1 low condition",
+            "$maxmin_z$ study 1 high condition",
+            "$maxmin_z$ study 2 low condition",
+            "$maxmin_z$ study 2 high condition",
+            "$maxmin_z$ study 3 low condition",
+            "$maxmin_z$ study 3 high condition",
+            "$maxmin_z$ study 4 low condition",
+            "$maxmin_z$ study 4 high condition",
+            "Fisher test gender hypothesis",
+            "Fisher test interaction hypothesis",
+            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
+            "Effect sizes (1-r)")
+AUC <- as.numeric(AUC_res)
+# print(xtable(data.frame(Method, AUC),
+#              caption = "Area Under the Curve (AUC) for the various statistical methods used to detect data fabrication.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.",
+#              label = "auc", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
+df <- data.frame(Method = temp,
+                 AUROC = NA,
+                 CI.lb = NA,
+                 CI.ub = NA)
+Method <- c("$SD_z$ homogeneous all",
+            "$SD_z$ study 1",
+            "$SD_z$ study 2",
+            "$SD_z$ study 3",
+            "$SD_z$ study 4",
+            "$maxmin_z$ homogeneous all",
+            "$maxmin_z$ study 1",
+            "$maxmin_z$ study 2",
+            "$maxmin_z$ study 3",
+            "$maxmin_z$ study 4",
+            "$SD_z$ heterogeneous all",
+            "$SD_z$ study 1 low condition",
+            "$SD_z$ study 1 high condition",
+            "$SD_z$ study 2 low condition",
+            "$SD_z$ study 2 high condition",
+            "$SD_z$ study 3 low condition",
+            "$SD_z$ study 3 high condition",
+            "$SD_z$ study 4 low condition",
+            "$SD_z$ study 4 high condition",
+            "$maxmin_z$ heterogeneous all",
+            "$maxmin_z$ study 1 low condition",
+            "$maxmin_z$ study 1 high condition",
+            "$maxmin_z$ study 2 low condition",
+            "$maxmin_z$ study 2 high condition",
+            "$maxmin_z$ study 3 low condition",
+            "$maxmin_z$ study 3 high condition",
+            "$maxmin_z$ study 4 low condition",
+            "$maxmin_z$ study 4 high condition",
+            "Fisher test gender hypothesis",
+            "Fisher test interaction hypothesis",
+            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ heterogeneous)",
+            "Effect sizes (1-r)")
+
+@
+
+\subsubsection*{Performance of using SDs to detect data fabrication}
+
+We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
+The $SD_z$ method \citep{simonsohn2013} inspects whether the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs varies sufficiently.
+These two methods operate similarly, except for the final computation.
+Other operationalizations are possible and we invite others to reuse the data from this study (\url{https://osf.io/b24pq}).
+
+Table \ref{auroc_variances} indicates that both methods show similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC), but with a preference for $SD_z$.
+This preference is due to the variance of variances outperforming the range of variances when all studies are combined in one test and its past application \citep{simonsohn2013}.
+Throughout the rest of this section, we will only discuss the results of $SD_z$ further.
+
+<<auroc for variance methods, echo=FALSE, results=tex>>=
+selmaxmin <- grepl(Method, pattern = '^.maxmin_')
+selsd <- grepl(x = Method, pattern = '^.SD_z')
+row_table <- c("Homogeneous, all studies combined",
+               "Homogeneous, study 1",
+               "Homogeneous, study 2",
+               "Homogeneous, study 3",
+               "Homogeneous, study 4",
+               "Heterogeneous, all studies combined",
+               "Heterogeneous study 1, low anchor condition",
+               "Heterogeneous study 1, high anchor condition",
+               "Heterogeneous study 2, low anchor condition",
+               "Heterogeneous study 2, high anchor condition",
+               "Heterogeneous study 3, low anchor condition",
+               "Heterogeneous study 3, high anchor condition",
+               "Heterogeneous study 4, low anchor condition",
+               "Heterogeneous study 4, high anchor condition")
+variances_table <- data.frame(Method = row_table, SDz = AUC[selsd], maxminz = AUC[selmaxmin])
+names(variances_table) <- c("Method", "AUROC $SD_z$", "AUROC $maxmin_z$")
+print(xtable(variances_table,
+             caption = "Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.",
+             label = "auroc_variances", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+The AUROC indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
+In other words, if AUROC $=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
+
+The AUROC for the variance of variance analyses is insufficient or sufficient depending on the assumption regarding population variances.
+Table \ref{auroc_variances} indicates that AUROC $=.423$ when homogeneous population variances are assumed, whereas AUROC $=.770$ when heterogeneous population variances are assumed.
+For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method.
+The method that incorporates heterogeneous population variances (i.e., one per anchoring condition) greatly improves the performance of the variance of variances analysis.
+
+Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=\Sexpr{seq(0, 1, .01)[max(which(tnr$variance_sd_p_overall_hetero == 1))]}$.
+
+\subsubsection*{Performance of using $p$-values to detect data fabrication}
+
+We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
+Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
+In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
+
+<<auroc for single fisher methods, echo=FALSE, results=tex>>=
+sel <- grepl(Method, pattern = '^(Fisher test)')
+row_table <- Method[sel]
+tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
+print(xtable(tabl,
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_fisher", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+\subsubsection*{Performance of combining SDs and $p$-value methods to detect data fabrication}
+
+<<auroc for combined fisher methods, echo=FALSE, results=tex>>=
+sel <- grepl(Method, pattern = 'Combined Fisher test')
+row_table <- Method[sel]
+tabl <- data.frame(Method = row_table, AUROC = AUC[sel])
+print(xtable(tabl,
+             caption = "Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER",
+             label = "auroc_combined", digits = 3), include.rownames = FALSE, sanitize.text.function=identity)
+@
+
+\subsubsection*{Performance of large effect sizes to detect data fabrication}
+
+<<get massive statcheck data for checks, echo=FALSE, results=hide>>=
+if(!file.exists(sprintf('%sdata/statcheck_dataset.csv', x12)))
+{
+  url <- 'https://github.com/chartgerink/2016statcheck_data/raw/master/statcheck_dataset.csv'
+  # If link is broken, more persistent version available at
+  # http://dx.doi.org/10.17026/dans-2cm-v9j9
+
+  GET(url,
+      write_disk(sprintf('%sdata/statcheck_dataset.csv', x12),
+                 overwrite = TRUE))
+}
+
+statcheck_data <- read.csv(sprintf('%sdata/statcheck_dataset.csv', x12))
+# Compute the effect sizes
+sel <- statcheck_data$Statistic == 'F'
+statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel] *
+                                  (statcheck_data$df1[sel] /
+                                     statcheck_data$df2[sel])) /
+                                 (((statcheck_data$Value[sel] *
+                                      statcheck_data$df1[sel]) /
+                                     statcheck_data$df2[sel]) + 1))
+
+sel <- statcheck_data$Statistic == 't'
+statcheck_data$es[sel] <- sqrt((statcheck_data$Value[sel]^2 *
+                                  (1 / statcheck_data$df2[sel])) /
+                                 (((statcheck_data$Value[sel]^2 * 1) /
+                                     statcheck_data$df2[sel]) + 1))
+
+sel <- statcheck_data$Statistic == 'r' &
+  statcheck_data$Value <= 1 &
+  statcheck_data$Value > 0
+statcheck_data$es[sel] <- statcheck_data$Value[sel]
+@
+
+%The \Sexpr{sum(dat_summary$es_condition > max(dat_summary$es_condition[dat_summary$type == 'ml']))} largest significant effects were fabricated, with \Sexpr{sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9)} (\Sexpr{round(sum(dat_summary$es_condition[dat_summary$type == 'qualtrics'] > .9) / sum(dat_summary$type == 'qualtrics'), 3)}\%) larger than $r=.9$.
+Based on descriptive data throughout psychology \citep{Hartgerink2016-lg}, effect sizes $\geq.9$ belong to the \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .9) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile of effects throughout the psychology literature and effect sizes $\geq.95$ \Sexpr{round(sum(statcheck_data$es[!is.na(statcheck_data$es)] < .95) / length(statcheck_data$es[!is.na(statcheck_data$es)])*100, 0)}th percentile.
 
@@
 
+write.csv(sprintf('%sdata/df_fab.csv', x12), row.names = FALSE)
+
 @
@@
 @
-
-\end{document}

### 2017-05-11 submission/manuscript.Rnw
Interim commit

@@
 Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP). 
-Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
+% Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
 These are just a few examples of cases in the last decade.
@@
 In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts. 
-Although deterrence theory dates back to the middle of the 17th century \citep{leviathan}, its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+% Although deterrence theory dates back to the middle of the 17th century \citep{leviathan}, its implementation has not occurred across the different forms of scientific misconduct equilaterally.
 Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
@@
 In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct other than plagiarism.
-The Journal of Cell Biology scans each submitted image for potential manipulation \citep{The_Journal_of_Cell_Biology2015-vh}, which greatly increases the risk of detecting (blatant) image manipulation.
+% The Journal of Cell Biology scans each submitted image for potential manipulation \citep{The_Journal_of_Cell_Biology2015-vh}, which greatly increases the risk of detecting (blatant) image manipulation.
 More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations \citep{Koppers2016}.
@@
 Humans are notoriously bad at understanding and estimating probabilities \citep[e.g.,][]{tversky1974, Tversky1971}, which could manifest itself in the fundamentally probabilistic data they try to fabricate.
-That researchers do not understand probabilistic processes also presents itself in the interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
+% That researchers do not understand probabilistic processes also presents itself in the interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
 When data are fabricated, probabilistic principles are easily violated if these principles are forgotten at the univariate level, bivariate level, trivatiate level, or beyond \citep{Haldane1948-nm}.
@@
 The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis. 
-For example, problems with papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
+% For example, problems with papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
 In this case, baseline measures across randomized groups were examined for too little variation.
@@
 Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
-We hardly know how researchers might go about fabricating data.
+% We hardly know how researchers might go about fabricating data.
 Cases such as Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
@@
 The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated by the increased usage of public online discussion platforms such as PubPeer (\url{https://pubpeer.com}).
-PubPeer serves as an "online journal club" where anyone can discuss articles.
+% PubPeer serves as an "online journal club" where anyone can discuss articles.
 Authors are notified when someone leaves a response, providing them with the possibility to respond.
@@
 Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
-Even though the data available can look different depending on the structure of a study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+% Even though the data available can look different depending on the structure of a study, there are certain common characteristics of results and the underlying raw data that can be inspected.
 For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
@@
 We present a set of studies that directly test the validity of statistical methods to detect data fabrication. 
-To this end, Study 1 inspected the performance of statistical methods to detect data fabrication when using only summary results (e.g., means and standard deviations) as typically reported in empirical research articles.
+% To this end, Study 1 inspected the performance of statistical methods to detect data fabrication when using only summary results (e.g., means and standard deviations) as typically reported in empirical research articles.
 Study 2 inspected the performance of statistical methods aimed at detecting data fabrication in raw data (i.e., the data underlying summary results).
@@
 
-write.csv(sprintf('%sdata/df_fab.csv', x12), row.names = FALSE)
+write.csv(df_fab, sprintf('%sdata/study_02/df_fab.csv', x12), row.names = FALSE)
 

### 2017-05-11 submission/manuscript.tex
Interim commit

@@
 Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
-Even though the data available look different depending on the structure of the study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+% Even though the data available can look different depending on the structure of a study, there are certain common characteristics of results and the underlying raw data that can be inspected.
 For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
@@
 \subsection*{Results}
+
+The collected data included 36 genuine data from Many Labs 1 \citep[\url{https://osf.io/pqf9r};][]{klein2014} and 39 fabricated datasets(\url{https://osf.io/e6zys}; 3 participants did not participate for a bonus).
+
+Figure \ref{densities} shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
+Such group-level comparisons provide an overview of the differences between the genuine- and fabricated data \citep[see also][]{Akhtar-Danesh2003}.
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses) whereas there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+From our own experience, and anecdotal evidence elsewhere \citep{BAILEY1991741}, large effects have previously raised initial suspicions.
+These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
+
+% add plot of left and right skew
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/ddfab_density.pdf}
+\caption{Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.}
+\label{densities}
+\end{center}
+\end{figure}
+
+\subsubsection*{Performance of using SDs to detect data fabrication}
+
+We applied two different operationalizations to inspect for data fabrication in the genuine- and fabricated datasets based on variance in the SDs.
+The $SD_z$ method \citep{simonsohn2013} inspects whether the variance of the SDs themselves varies sufficiently, and we tested another method that inspects the range of the SDs varies sufficiently.
+These two methods operate similarly, except for the final computation.
+Other operationalizations are possible and we invite others to reuse the data from this study (\url{https://osf.io/b24pq}).
+
+Table \ref{auroc_variances} indicates that both methods show similar performance when inspected with the Area Under the Receiver Operating Curve (AUROC), but with a preference for $SD_z$.
+This preference is due to the variance of variances outperforming the range of variances when all studies are combined in one test and its past application \citep{simonsohn2013}.
+Throughout the rest of this section, we will only discuss the results of $SD_z$ further.
+
+% latex table generated in R 3.3.3 by xtable 1.7-1 package
+% Tue Apr 18 19:23:42 2017
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrr}
+  \hline
+Method & AUROC $SD_z$ & AUROC $maxmin_z$ \\ 
+  \hline
+Homogeneous, all studies combined & 0.423 & 0.303 \\ 
+  Homogeneous, study 1 & 0.368 & 0.374 \\ 
+  Homogeneous, study 2 & 0.421 & 0.446 \\ 
+  Homogeneous, study 3 & 0.510 & 0.521 \\ 
+  Homogeneous, study 4 & 0.540 & 0.542 \\ 
+  Heterogeneous, all studies combined & 0.770 & 0.756 \\ 
+  Heterogeneous study 1, low anchor condition & 0.643 & 0.643 \\ 
+  Heterogeneous study 1, high anchor condition & 0.438 & 0.438 \\ 
+  Heterogeneous study 2, low anchor condition & 0.751 & 0.751 \\ 
+  Heterogeneous study 2, high anchor condition & 0.612 & 0.612 \\ 
+  Heterogeneous study 3, low anchor condition & 0.668 & 0.668 \\ 
+  Heterogeneous study 3, high anchor condition & 0.651 & 0.651 \\ 
+  Heterogeneous study 4, low anchor condition & 0.796 & 0.796 \\ 
+  Heterogeneous study 4, high anchor condition & 0.555 & 0.555 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Receiver Operating Curve (AUROC) for the two statistical methods used to detect data fabrication based on variances.
+Homogeneous: assumes one population variance underlying all groups.
+Heterogeneous: assumes separate population variance per anchoring condition.}
+\label{auroc_variances}
+\end{table}
+The AUROC indicates the probability that a randomly drawn fabricated dataset is classified as fabricated before a randomly drawn genuine dataset is classified as fabricated \citep{doi:10.1148/radiology.143.1.7063747}.
+In other words, if AUROC $=.5$ this indicates that correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
+
+The AUROC for the variance of variance analyses is insufficient or sufficient depending on the assumption regarding population variances.
+Table \ref{auroc_variances} indicates that AUROC $=.423$ when homogeneous population variances are assumed, whereas AUROC $=.770$ when heterogeneous population variances are assumed.
+For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method.
+The method that incorporates heterogeneous population variances (i.e., one per anchoring condition) greatly improves the performance of the variance of variances analysis.
+
+Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=0.13$.
+
+\subsubsection*{Performance of using $p$-values to detect data fabrication}
+
+We asked researchers to fabricate data for nonsignificant effect sizes after inspecting whether the genuine data resembled a uniform distribution.
+Consequently,  However, as Table \ref{auroc_fisher} indicates, the auroc for these methods are hardly better than chance.
+In other words, for effects that are specifically fabricated to be nonsignificant, researchers might not fabricate such large $p$-values to be suspicious.
+
+% latex table generated in R 3.3.3 by xtable 1.7-1 package
+% Tue Apr 18 19:23:42 2017
+\begin{table}[ht]
+\centering
+\begin{tabular}{lr}
+  \hline
+Method & AUROC \\ 
+  \hline
+Fisher test gender hypothesis & 0.521 \\ 
+  Fisher test interaction hypothesis & 0.535 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER} 
+\label{auroc_fisher}
+\end{table}
+\subsubsection*{Performance of combining SDs and $p$-value methods to detect data fabrication}
+
+% latex table generated in R 3.3.3 by xtable 1.7-1 package
+% Tue Apr 18 19:23:42 2017
+\begin{table}[ht]
+\centering
+\begin{tabular}{lr}
+  \hline
+Method & AUROC \\ 
+  \hline
+Combined Fisher test (3 results, $SD_z$ homogeneous) & 0.602 \\ 
+  Combined Fisher test (3 results, $SD_z$ heterogeneous) & 0.736 \\ 
+  Combined Fisher test (6 results, $SD_z$ homogeneous) & 0.643 \\ 
+  Combined Fisher test (6 results, $SD_z$ heterogeneous) & 0.643 \\ 
+   \hline
+\end{tabular}
+\caption{Area Under the Receiver Operating Curve (AUROC) for PLACEHOLDER} 
+\label{auroc_combined}
+\end{table}
+
+\subsubsection*{Performance of large effect sizes to detect data fabrication}
+
+%The 23 largest significant effects were fabricated, with 13 (0.333\%) larger than $r=.9$.
+Based on descriptive data throughout psychology \citep{Hartgerink2016-lg}, effect sizes $\geq.9$ belong to the 96th percentile of effects throughout the psychology literature and effect sizes $\geq.95$ 98th percentile.
 
@@
 \section*{Results}
-
-\section*{Discussion}
-
-% Be sure to discuss why Benford's law wasn't included in the combination
-% Reflect on whether it worked to detect fabrication
-
-\section*{General discussion}
-
-% Talk about deterrence theory and how marginal utility might make it more attractive to go towards more extreme forms of misconduct if zero-tolerance policy is applied.
-% Plagiarism scanners can be gamed (i.e., rogeting), so can statistics?
-
-\bibliography{../bibliography/library}
-\newpage
-%------------------------------------
-%handy to include this at the end
-%------------------------------------
-\section*{SessionInfo}
-%-------------------------------------
-
-\begin{Schunk}
-\begin{Sinput}
-> sessionInfo()
-\end{Sinput}
-\begin{Soutput}
-R version 3.3.2 (2016-10-31)
-Platform: x86_64-redhat-linux-gnu (64-bit)
-Running under: Fedora 25 (Workstation Edition)
-
-locale:
- [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
- [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
- [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
- [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
- [9] LC_ADDRESS=C               LC_TELEPHONE=C            
-[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C
-
-attached base packages:
-[1] stats     graphics  grDevices utils     datasets  methods   base
-
-other attached packages:
- [1] stringr_1.1.0     plyr_1.8.4        reshape2_1.4.2    dplyr_0.5.0      
- [5] data.table_1.10.0 lsr_0.5           effects_3.1-2     car_2.0-19       
- [9] httr_1.2.1        xtable_1.7-1      gridExtra_2.2.1   ggplot2_2.2.1    
-[13] latex2exp_0.4.0   foreign_0.8-67    pROC_1.8
-
-loaded via a namespace (and not attached):
- [1] Rcpp_0.12.9      magrittr_1.5     splines_3.3.2    MASS_7.3-45     
- [5] munsell_0.4.3    colorspace_1.3-2 lattice_0.20-34  R6_2.2.0        
- [9] minqa_1.2.4      tools_3.3.2      nnet_7.3-12      grid_3.3.2      
-[13] nlme_3.1-128     gtable_0.2.0     DBI_0.5-1        lme4_1.1-12     
-[17] lazyeval_0.2.0   assertthat_0.1   tibble_1.2       Matrix_1.2-7.1  
-[21] nloptr_1.0.4     stringi_1.1.2    scales_0.4.1    
-\end{Soutput}
-\begin{Sinput}
-> 
-\end{Sinput}
-\end{Schunk}
-
-\end{document}

### 2017-05-17 submission/manuscript.Rmd
Update study 1, add rmarkdown

@@
 ---
-title: "Ecological validity of detecting data fabrication in experimental studies."
-author: "Chris HJ Hartgerink, Jelte M Wicherts, Marcel ALM van Assen"
+title: "Ecological performance of detecting data fabrication"
+author: "Chris HJ Hartgerink, Jan G Voelkel, Jelte M Wicherts, Marcel ALM van Assen"
 date: '`r format(Sys.time(), "%d %B, %Y")`'
-output: pdf_document
+output:
+  word_document: default
+  html_document:
+    toc: yes
 csl: ../bibliography/apa.csl
-bibliography: ../bibliography/library.bib
+bibliography: ../bibliography/library2.bib
 ---
 
-```{r prepwork, echo = FALSE}
-suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
+```{r preparation, echo = FALSE}
+suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(pROC))
-suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
+suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign', repos = 'http://cran.us.r-project.org')})
 suppressPackageStartupMessages(library(foreign))
+suppressPackageStartupMessages(if(!require(latex2exp)){install.packages('latex2exp', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(latex2exp))
+suppressPackageStartupMessages(if(!require(ggplot2)){install.packages('ggplot2', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(if(!require(gridExtra)){install.packages('gridExtra', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(gridExtra))
+suppressPackageStartupMessages(if(!require(xtable)){install.packages('xtable', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(xtable))
+suppressPackageStartupMessages(if(!require(httr)){install.packages('httr', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(httr))
+suppressPackageStartupMessages(if (!require(car)){install.packages('car', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(car))
+suppressPackageStartupMessages(if (!require(effects)){install.packages('effects', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(effects))
+suppressPackageStartupMessages(if (!require(lsr)){install.packages('lsr', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(lsr))
+suppressPackageStartupMessages(if (!require(data.table)){install.packages('data.table', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(data.table))
+suppressPackageStartupMessages(if (!require(dplyr)){install.packages('dplyr', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(if (!require(reshape2)){install.packages('reshape2', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(reshape2))
 
@@
 # x12 <- ''
-```
 
-<!---
+source(sprintf('%sfunctions/digit_analysis.R', x12))
+source(sprintf('%sfunctions/std_var.R', x12))
 
-# Abstract
---placeholder--
-
-# Introduction
-
-Data fabrication is malicious to scientific knowledge, hence it is imperative to be able to detect it.
-An estimated 2% of all researchers admit to having fabricated data at least once, and 14% have said to have witnessed someone fabricate data [@fanelli2009].
-In stark contrast to plagiarism, which has a similar admittance rate but double the witness rate [@pupovac2015], hardly any systems are implemented during the editorial process to detect problematic data.
-Recently, one journal has explicitly stated they are considering such a system (Miller 2015), another is looking BMC SCIENCEMATTERS.
-Editors and reviewers hardly pay attention to potential problems with the data during the editor process either (Bornmann et al.
-2008), which highlights the potential of automated detection systems.
-
-Similar to how plagiarism scanners are implemented to detect plagiarism, statistical methods can be applied to detect potentially fabricated data.
-By extracting information from research papers, called content mining (Smith-Unna and Murray-Rust 2014), statistical analyses of the presented research results can be facilitated.
-Previous statistical content mining methods, extracting for example reported test results across 30,000 papers (Nuijten et al.
-2015), indicate the feasibility of extracting statistical information from research papers in large quantities.
-
-However helpful these technological advances are, the statistical methods applied to extracted data in order to detect potential data fabrication require thorough validation.
-More specifically, the statistical methods need to have a well-balanced trade-off between the false positive rate and the false negative rate.
-Considering the, presumably, low prevalence rate of data fabrication, false positive rates can have tremendous effects when applied at a large scale.
-For example, if we assume that 2% of the research papers is fabricated and we can detect it perfectly if it occurs, we would detect approximately 2.5 times more false positives than true positives.
-And this is if we assume the false positive rate is 5% and no higher.
-
-How data is fabricated by researchers is not well-known and simulating the properties of statistical methods to detect data fabrication is therefore invalid.
-When the process is unknown, it is hardly feasible to properly approximate reality and draw valid conclusions.
-Moreover, it seems reasonable to state that there are many different ways to fabricate data and that these different data fabrication ‘styles’ can be combined.
-Even if certain fabrication processes were known, simulating ecologically valid processes would still be quite difficult.
-
-Nonetheless, statistical methods to detect data fabrication have been developed based on theoretical principles, which help detect data fabrication in experiments.
-These methods are based on the tenet that humans are bad at fabricating results that originate from probabilistic processes.
-Outcome variables that are inspected in experiments are based on a sample which results in observations that are the result of a random variable, hence subject to probabilistic (i.e., stochastic) processes.
-The inadequacy of humans in generating such sequences is the consequence of mental heuristics.
-For example, most humans succumb to the gambler’s fallacy, estimating the probability of heads as more likely when we have thrown tails several times (Tversky and Kahneman 1974).
-Other fallacious heuristics include the local-representativeness heuristic (), .
-
-Statistical methods to detect data fabrication have been successfully applied in ad hoc investigations, but their value in screening processes remains opaque.
-For example, Simonsohn’s variance of variances method (Simonsohn 2013) has been applied to the Smeesters and Sanna cases, but only after suspicions had already arisen.
-The value of applying such a method as a screening measure is hard to assess regardless of its previous successes in ad hoc investigations.
-
-In this paper, we experimentally test the validity of a set of statistical methods to detect data fabrication, based on summary results (Study 1) or raw data (Study 2), and assess the optimal balance between decision criterion and detection accuracy.
-We apply the statistical methods to detect data fabrication to both (assumed) genuine data from the Many Labs experiments and fabricated datasets, which we collected in an experimental setting where researchers were invited to fabricate data according to a controlled set of hypotheses.
-Both experiments were approved by the Tilburg Ethics committee (EC-2015.50).
---->
-# Study 1
-
-```{r, echo = FALSE}
-# Dynamically generate path names
 ml_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
@@
 summary_stat_file <- sprintf('%sdata/study_01/ml_summary_stats.csv', x12)
+ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/StroopCleanSet.csv', x12)
 pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
@@
 
-# Compute the summary statistics for Many Labs
-source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
-# Process the collected, fabricated data
-source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
-# Concatenate, analyze, and write out all ML and qualtrics data
-# Uncomment this line to rerun
-# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))
+tabnr <- 1
+fignr <- 1
 ```
 
-We tested the performance of statistical methods to detect data fabrication based on summary results with genuine and fabricated summary results of four anchoring studies [@tversky1974;@jacowitz1995].
+Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP).
+Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
+These are just a few examples of misconduct cases in the last decade.
+Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once [@10.1371/journal.pone.0005738] and this is likely to be an underestimate due to socially desirable responses.
+The detection rate is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
+At best, this amounts to a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
+
+In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts. 
+Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
+This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
+However, increased deterrence of fabrication and falsification by improved detection mechanisms has not been as widely implemented.
+
+In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct (alongside plagiarism).
+The Journal of Cell Biology scans each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh], which greatly increases the risk of detecting (blatant) image manipulation.
+More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations [@10.1007/s11948-016-9841-7].
+These developments in detecting image manipulation have increased detection risk during the pre-publication and post-publication phase by improving detection mechanisms and increasing the understanding of how images might be manipulated.
+Moreover, their application also helps researchers systematically evaluate research articles to estimate the extent of the problem of image manipulation [4\% of all papers are estimated to contain manipulated images, @10.1128/mBio.00809-16].
+
+Statistical methods can provide one way to improve detection of data fabrication in empirical research.
+Humans are notoriously bad at understanding and estimating probabilities [e.g., @10.1126/science.185.4157.1124;@10.1037/h0031322], which could manifest itself in the fundamentally probabilistic data they try to fabricate.
+That researchers do not understand probabilistic processes also presents itself in false interpretation of genuine research data [@10.3758/BF03213921;@10.1007/s11336-015-9446-0;@10.7326/0003-4819-130-12-199906150-00008].
+When data are fabricated, probabilistic principles are easily violated if forgotten at the univariate level, bivariate level, trivatiate level, or beyond [@Haldane1948-nm].
+Based on this idea, statistical methods that investigate whether the reported data are feasible under the theoretically probabilistic processes can be used to detect potential data fabrication.
+
+The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis. 
+For example, problems in papers by Fuji were highlighted with statistical methods [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], resulting in 183 retractions [@oransky2015].
+In this case, baseline measures across randomized groups were examined for too little variation.
+Random assignment should introduce a certain degree of random error that might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
+Another two cases are those of Sanna and Smeesters, where fabricated data were also detected with statistics [@10.1177/0956797613480366].
+These cases inspected the variance of variances (i.e., the second, or meta level variance).
+Once again, too little variation was what revealed problems in these data [other examples include @lacour-complaint;@foerster-complaint].
+These methods, although developed in a case-setting, need not be limited to cases.
+The application of such methods can be (semi-)automated if data are available in a machine-readable format that one of the statistical methods can be applied to.
+An example of such a potential case for mass application of using statistics to detect (potential) data fabrication is in the ClinicalTrials.gov database, where baseline measures across randomized groups are readily available for download and subsequent analysis [@10.3897/rio.1.e7462].
+
+Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
+We hardly know how researchers might go about fabricating data.
+Cases such as Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
+Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place [e.g., late at night when no one is around; @stapel_book].
+However, trustworthiness of these accounts can be called into question.
+Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually to detect data fabrication.
+Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be simulated.
+
+The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated in the digital age by the increased usage of public online discussion platforms such as [PubPeer (https://pubpeer.com)](https://pubpeer.com).
+PubPeer serves as an "online journal club" where anyone can discuss articles.
+Authors are notified when someone leaves a response, providing them with the possibility to respond.
+Such a platform allows for public discussion of the paper, including discussion of reanalyses, methodology, availability of materials, etc.
+When detection mechanisms are freely available to use, they can lead to (a surge of) comments when applied by users.
+Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments [@10.1038/540151a].
+The impact of such new possibilities is not to be underestimated, although its potential to constructively contribute to the scientific discussion should also not be [@10.1038/540007b].
+Nonetheless, the `statcheck` software was well validated prior to this application [@10.3758/s13428-015-0664-2] and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
+
+# Theoretical framework
+
+Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
+Even though structure and contents of data can look different depending on the structure of a study and the measures, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
+For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
+Raw data frequently contain at least some variables measured at a interval- or ratio scale [@10.1126/science.103.2684.677].
+Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results.
+We review the theoretical framework of the specific methods we apply throughout this paper, but these are not exhaustive of all methods available to test for potential problems in empirical data [see also @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
+
+## Detecting data fabrication in summary results
+
+### P-value analysis
+
+The distribution of one $p$-value depends on various parameters, but there are specific theoretical boundary conditions to this distribution [@fisher1925].
+Based on the population effect size, the precision of the estimate, and the observed effect size, the $p$-value distribution can be uniform (when then null hypothesis is true) or right-skewed (when the alternative hypothesis is true).
+By extension, any other distribution, after taking into account sampling error, is theoretically suspect.
+For example, a distribution might show a bump when authors $p$-hack [e.g., Figure 1 in @10.7717/peerj.1935], but fabricators might create other non-uniform or non-right-skewed distributions, failing to take into account the theoretical boundary conditions.
+
+In order to test whether observed $p$-values transgress the boundary condition, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
+This adaptation is a simple reversal of the Fisher method [@fisher1925], which was originally introduced as a simple meta-analytic test to indicate presence of an effect; this test is computed as
+$$
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
+$$
+where it tests for right-skew (i.e., more smaller $p$-values than larger $p$-values) across the $k$ number of $p$-values. Reversing the Fisher method results in 
+$$
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
+$$
+where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
+This threshold is added and can be set to anything.
+Given the frequent misinterpretation of $p$-values [e.g., as the probability of an effect, @10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
+In that case, it makes  sense to set $t=.05$ or $t=.10$, in order to include only nonsignificant test results.
+
+Despite this test being useful for detecting data anomalies in nonsignificant $p$-values, two clear exceptions should be taken into account: (1) model-fit tests and (2) wrongly specified one-tailed tests.
+When model-fit tests are used, these can quickly result in high $p$-values because of model saturation (i.e., where the null hypothesis is good fit and the alternative is bad fit).
+For properly specified one-tailed tests, the $p$-value distribution is right-skewed.
+When wrongly specified, this distribution is reversed and becomes left-skew.
+These two exceptional cases should not be forgotten during the application of this test, but are irrelevant for the rest of this paper due to our study design (see methods of both studies).
+
+### Variance analysis
+
+Variance- or standard deviation estimates are typically reported to indicate spread, but just like the mean there should be sampling error in this estimate (i.e., the variance of the variances) proportionate to the sample size.
+A variance estimate follows a $\chi^2$-distribution, which is dependent on the sample size [p.
+445; @hogg-tanis]; that is
+$$
+z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
+$$
+where $N_j$ is the sample size of the $j$th group and $MS_w$ is the normalizing constant resulting in a standardized variance $z^2_j$. The normalizing constant $MS_w$ is computed as 
+$$
+MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
+$$
+where $s^2_j$ is the variance in the $j$th group. If simulating (see next paragraph), the simulated variances are used to compute $MS_w$.
+
+Assuming that the observed variances are from the same population distribution, the expected spread of reported standardized variances can be simulated.
+By repeatedly drawing (standardized) variance estimates for $j$ groups and then computing their spread allows for approximation of the sampling distribution.
+Spread can be operationalized in various ways, such as the standard deviation of the variances (denoted in this paper as $SD_z$) or as the range of the variances (denoted as $max-min_z$).
+If there is reason to believe that the observed variances come from heterogeneous populations, subgrouping (i.e., one variance analysis per subgroup) is necessary to prevent false results.
+
+Subsequently, the observed sampling variance (or range) can be compared to the expected sampling distribution.
+Too consistent results would indicate potential anomalies in the reported data [@10.1177/0956797613480366].
+For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
+
+### Effect size analysis
+
+A fabricator might present unrealistically large effects, forgetting the exponential relation between the effect size measure and the implied correlation.
+From our own experience, and anecdotal evidence elsewhere [@10.1016/0197-24569190037-M], large effects have previously raised initial suspicions.
+The size of a large effect can quickly become unrealistic; $d=1.2$ already implies a correlation of `r round(sqrt((1.2^2/(1.2^2+4))), 2)` between the dependent- and independent measures.
+More generally, the relation between the implied correlation and the effect size tends to be exponential, as Figure `r fignr` depicts.
+
+```{r d2, fig.cap="_Figure XX._ The relation between Cohen's d effect size and its direct transformation, the correlation r (or vice versa).
+If effects d>2 are fabricated, the implied correlation between the dependent- and independent measure(s) is approximately .6.", out.width='100%', echo=FALSE}
+d2 <- seq(0, 10, .01)
+
+plot(sqrt(d2^2/(d2^2+4)), x = d2,
+     type='l', xlab = "Cohen's d", ylab = "Correlation r")
+
+fignr <- fignr + 1
+```
+
+Taking the observed effect size and transforming it into a correlation, allows for an easy way to assess how extreme the presented result is.
+One minus the observed correlation can be used as a measure for extreme effects (i.e., $1-r$); as a heuristic, it can be regarded as a $p$-value.
+That is, this measure too ranges from zero to one and the more extreme the effect size, the smaller the value.
+This method specifically looks at situations where fabricators would want to fabricate the existence of an effect (not the absence of one).
+
+## Detecting data fabrication in raw data
+
+### Digit analysis
+
+### Variance analysis
+
+### Multivariate associations
+
+# Study 1
+
+We tested the performance of statistical methods to detect data fabrication in summary results with genuine- and fabricated summary results from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058].
 The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
 For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'.
-These questions yield mean responses of 25\% and 45\%, respectively [@tversky1974], despite essentially posing the same factual question.
+These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question.
 A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
+This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
 
@@
 
-The four anchoring studies for which results were collected were (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States.
-Each of the four studies provided summary results for a 2 (low/high anchoring) × 2 (male/female) factorial design.
+```{r prep study 1, echo=FALSE}
+# Study 1
+# Compute the summary statistics for Many Labs
+suppressWarnings(suppressMessages(source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))))
+# Process the collected, fabricated data
+suppressMessages(source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12)))
+# Concatenate, analyze, and write out all ML and qualtrics data
+# Uncomment this line to rerun, but take care: might take a while
+if(!file.exists(sprintf('%sdata/study_01/study1_res.csv', x12)))
+{
+  set.seed(123);suppressMessages(source(sprintf('%sfunctions/concatenate_analyze_01.R', x12)))  
+}
+```
+
+We collected summary results for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
+Each of the four studies provided us with summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
 Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
-Respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
-All materials, data, and analyses scripts are freely available on the OSF ([osf.io/b24pq](osf.io/b24pq)) and were preregistered ([osf.io/ejf5x](osf.io/ejf5x); deviations are explicated in this report).
+For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
+All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/ejf5x](https://osf.io/ejf5x) (deviations are explicated in this report).
 
-### Data collection.
+### Data collection
 
-We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project [@klein2014, [osf.io/pqf9r](osf.io/pqf9r)].
+We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178].
 The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
-Considering the size of the ML project, the transparency of research results, and minimal individual gain for fraud, we assumed these data to be genuine.
-For each of the thirty-six locations, sample sizes, means, and standard deviations (four each) were computed, for each of the four conditions in the four anchoring studies across the thirty-six locations (i.e., $3\times4\times4\times36$).
+Considering the size of the ML project, the transparency of research results, and minimal individual gain for fabricating data, we assumed these data to be genuine.
+For each of the thirty-six locations we computed sample sizes, means, and standard deviations for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations.
 We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
 
-Using quotum sampling, we collected thirty-six fabricated datasets of summary results for all four anchoring studies.
-The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS) with the filter set to the U.S.
-We sampled psychology researchers to improve familiarity with the anchoring effect [@jacowitz1995;@tversky1974], for which summary results were fabricated.
+Using quotum sampling, we collected thirty-six fabricated datasets of summary results for the same four anchoring studies.
+Quotum sampling was used to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
+The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in Web of Science (WoS) with the filter set to the U.S.
+We sampled psychology researchers to improve familiarity with the anchoring effect [@10.1126/science.185.4157.1124;@10.1037/e722982011-058], for which summary results were fabricated.
 We filtered for U.S.
 researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
-researchers were included because this filter also retained papers with co-authors from the U.S.).
+researchers were included because the WoS filter also retained papers with co-authors from the U.S.).
 WoS was searched on October 13, 2015.
@@
 
-A random sample of 1,000 researchers were digitally approached to participate in this study on April 25, 2016 (invitation: [osf.io/s4w8r](osf.io/s4w8r)).
+We invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: [https://osf.io/s4w8r](https://osf.io/s4w8r)).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 We also clarified to the  respondents that they could stop at any time without providing a reason.
-If they wanted, respondents received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address, after which they could win an additional $50 Amazon gift card if they were one of three top fabricators.
-The provided email addresses were unlinked from individual responses upon sending the bonus gift cards.
-The text of the Qualtrics survey is available at [osf.io/w984b](osf.io/w984b).
+If they wanted, respondents received a $30 Amazon gift card as compensation for their participation if they were willing to enter their email address.
+They could win an additional $50 Amazon gift card if they were one of three top fabricators.
+The provided e-mail addresses were unlinked from individual responses upon sending the bonus gift cards.
+The full text of the Qualtrics survey is available at [https://osf.io/w984b](https://osf.io/w984b).
 
 Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
-We instructed respondents to fabricate results for the hypotheses (i) main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
-Respondents did not need to fabricate sample sizes, which were set to 25 per cell a priori.
-The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of tools to detect data fabrication.
+We instructed respondents to fabricate results for the following hypotheses: there is (i) a main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
+We fixed the sample sizes to 25 per cell; respondents did not need to fabricate sample sizes.
+The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of statistical tools to detect data fabrication.
 
-We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they choose to fabricate data.
-Figure `r fig <- 1; fig` depicts an example of this spreadsheet (original:  [osf.io/w6v4u](osf.io/w6v4u)).
-We requested the respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
+We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data.
+Figure `r fignr` depicts an example of this spreadsheet (original:  [https://osf.io/w6v4u](https://osf.io/w6v4u)).
+We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions.
 Using these values, statistical tests are computed and shown in the "Current result" column instantaneously.
-When these results confirm the hypotheses, a checkmark appears as depicted in the green cells.
+If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure `r fignr`.
 We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
 
-![spreadsheet](../figures/spreadsheet.png)
+```{r spreadsheet-study1, fig.cap="_Figure XX._ Example of a filled in template spreadsheet used in the fabrication process of Study 1.
+Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
+If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell (one of four template spreadsheets available at [https://osf.io/w6v4u/](https://osf.io/w6v4u/)).", out.width='100%', echo=FALSE}
+knitr::include_graphics('../figures/spreadsheet.png')
 
-**Figure `r fig`.** Example of a filled in template spreadsheet used in the fabrication process.
-Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
-If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell.
+fignr <- fignr + 1
+```
 
 Upon completing the fabrication of the data, respondents were debriefed.
-Several questions were asked about their statistical knowledge and approach to data fabrication.
-They were also reminded that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
+Respondents answered several questions about their statistical knowledge and approach to data fabrication and finally we reminded them that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
+We rewarded participation with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card.
 
-We rewarded participation with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card.
-If the participant wanted to receive a compensation and contend for the bonus $50, he/she had to enter an email to receive the reward.
-These email addresses were unlinked from individual responses upon sending the gift cards.
-Quotum sampling was applied to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
+### Data analysis
 
-### Data analysis.
-
-To detect data fabrication in a set of summary results, we first test the variance of fabricated standard deviations [SDs; @simonsohn2013] across the four anchoring studies.
-This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on stochastic sampling processes.
-For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000 (this is simply an example).
-To compute this test, we first standardize the SDs for each of the four studies by computing
-
-$\tilde{s}^2_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
-<!--- \limits^k_{j=1} --->
-
-where $\tilde{s}_j$ denotes the standardized SD in group *j*.
-Note that $MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells.
-We test several different measures to detect data fabrication that utilize these standardized SDs (i.e., $\tilde{s}_j$), including the max-min distance (denoted $\tilde{\sigma}_{max-min}$) and the variance of the standardized SDs [i.e.,  $\tilde{\sigma}_{sd}$; @simonsohn2013].
-We compare the observed value for each $\tilde{\sigma}$ measure with the expected distribution of outcomes when the data would be the result of random sampling processes.
-To this end, we simulate the expected distribution of standardized SDs and compute the expected distribution of each $\tilde{\sigma}$.
-This expected distribution is used to determine the *p*-value of the observed $\tilde{\sigma}$ value.
-We simulate the standardized SD for each of the *j* groups as
-
-$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}}{N_j-1}\Bigg]/MS_w$
-
-These simulated values are used to compute the expected distribution of all $\tilde{\sigma}$ measures.
-
-Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication.
-The Fisher method [@fisher1925] tests for evidence of an effect in a set of *p*-values and has previously been used as a meta-analytic method [@hong2008], but we adjust it here to test for results that are overly consistent with the null hypothesis.
-The original Fisher method is computed as
-
-$\chi^2_{2k}=-2\sum\ln(p_i)$
-<!--- \limits^k_{i=1} --->
-
-and tests for right-skew in a set of *p*-values, but we adjust it to the following
-
-$\chi^2_{2k}=-2\sum\ln(1-\frac{p_i-t}{1-t})$
-
-where it now tests for left-skew (i.e., more larger *p*-values than smaller *p*-values) across the *k* number of *p*-values that falls above the threshold *t*.
-We set this threshold to .05 in order to include only nonsignificant test results.
-
-Finally, we combined the results of these three individual tests for data fabrication using the Fisher method.
-We expect this combination test of the three individual tests for data fabrication to be a more powerful than the individual tests.
-Based on the results of the combined test results, the three 'best' data fabricators are selected.
-The three respondents with the highest *p*-values contain the least evidential value for deviating from genuine data and receive an additional $50 Amazon gift card.
-
-For each of these three tests to detect data fabrication we carry out sensitivity and specificity analyses using ROC-curves in order to determine optimal alpha levels.
-This analysis helps determine the classification performance of these three tests.
-In order to determine the optimal alpha level, we varied the alpha level from .000001 through .1 and assessed the classification performance of these methods to detect data fabrication.
-The optimal alpha level is determined by finding that alpha level for which both the true positive classification rate and the true negative classification rate are highest.
-For example,
-
-<!---
-Something about reporting tendencies?
---->
-
-### Results.
-```{r inspect results to detect data fabrication, echo = FALSE}
+```{r analysis study 1, echo=FALSE}
 # Read in datafile, just in case the computations were not re-run.
 dat_summary <- read.csv(dat_summary_file)
-dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
 # Select only those from qualtrics who did for bonus
+# removed <- sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))
+# dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
 
 type_index <- which(names(dat_summary) == 'type')
+temp <- dat_summary[, c(type_index, 18:length(names(dat_summary)))]  
+dat_summary$es_gender <- sqrt(dat_summary$es2_gender)
+dat_summary$es_condition <- sqrt(dat_summary$es2_condition)
+dat_summary$es_interaction <- sqrt(dat_summary$es2_interaction)
 
-temp <- dat_summary[, c(type_index, 18:45)]
+# naming just for ease of use later
+dat_summary$es_p <- 1 - dat_summary$es_condition
+```
 
-# ggplot(temp) +
-#   facet_grid ()
-# geom_density(aes(Result, group = type, col = type)) + 
-#   xlab(title_name)
-# 
-# p <- ggplot(temp)
-# for (i in 18:45)
-# {
-#   temp <- dat_summary[, c(type_index, i)]  
-#   title_name <- names(temp)[2]
-#   names(temp)[2] <- 'Result'
-#   
-#   ggplot(temp) +
-#     geom_density(aes(Result, group = type, col = type)) + 
-#     xlab(title_name)
-# }
-# dev.off()
+We analyzed the genuine- and fabricated datasets for the four anchoring studies in four ways.
+First, we applied variance analyses to the reported variances of each of the four groups per study separately.
+Second, we applied the reversed Fisher method to the results of the gender and interaction hypotheses (i.e., nonsignificant results) across the four studies.
+Third, we combined the results from the variance analyses and the reversed Fisher method, using the original Fisher method [@fisher1925].
+Fourth, and not preregistered, we used effect size analysis (i.e., $1-r$) that is a proxy of how extreme an effect is.
 
-tp <- matrix(NA, ncol = 20, nrow = 101)
-fp <- matrix(NA,ncol = 20, nrow = 101)
-fn <- matrix(NA,ncol = 20, nrow = 101)
-tn <- matrix(NA,ncol = 20, nrow = 101)
+Specifically for the variance analyses, we deviated from the preregistration.
+Initially, we simultaneously analyzed the reported variances per study across the anchoring conditions.
+However, upon analyzing these values, we realized that the variance analyses assume that the reported variances are from the same population distribution, which is not necessarily the case for the anchoring conditions.
+Hence, we included two variance analyses per anchoring study (i.e., one for the high anchoring condition and one for the low anchoring condition).
+In the results we differentiate between these by using 'homogeneous' (across conditions) and 'heterogeneous' (separated for low- and high anchoring conditions).
 
-temp <- names(dat_summary)[c(18:31, 34, 37, 39, 41, 43, 45)]
+For each of these statistical tests to detect data fabrication we carried out sensitivity and specificity analyses using Area Under Receiving Operator Characteristic (AUROC) curves.
+AUROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
+With these AUROC-curves, informed decisions about optimal alpha levels can be made based on various criteria.
+In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest.
+For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.
+
+AUROC values indicates the probability that a randomly drawn fabricated- and genuine dataset can be correctly classified as fabricated and genuine [@10.1148/radiology.143.1.7063747].
+In other words, if $AUROC=.5$, correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
+
+## Results
+
+```{r echo=FALSE}
+tp <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fp <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tn <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
 
@@
 
-for (variables in c(18:31, 34, 37, 39, 41, 43, 45))
+for (variables in which(grepl(names(dat_summary), pattern = "_p")))
 {
@@
 
-tpr <- matrix(NA, ncol = 20, nrow = 101)
-fpr <- matrix(NA,ncol = 20, nrow = 101)
-fnr <- matrix(NA,ncol = 20, nrow = 101)
-tnr <- matrix(NA,ncol = 20, nrow = 101)
+tpr <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fpr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+tnr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
 
-ppv <- matrix(NA, ncol = 20, nrow = 101)
-fdr <- matrix(NA,ncol = 20, nrow = 101)
-npv <- matrix(NA,ncol = 20, nrow = 101)
-false_or <- matrix(NA,ncol = 20, nrow = 101)
+ppv <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+fdr <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+npv <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
+false_or <- matrix(NA,ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
 
-for (i in 1:20)
+for (i in 1:sum(grepl(names(dat_summary), pattern = "_p")))
 {
@@
 
-for(i in 1:20)
-{
-  plot(fpr[, i], tpr[, i],
-       type = 's', xlim = c(0,1), ylim = c(0,1), main = names(fpr)[i],
-       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
-  abline(a = 0, b = 1)
-}
+height = (tpr[-1, ] + tpr[-dim(tpr)[1], ])/2
+width = apply(fpr, 2, diff) # = diff(rev(omspec))
+AUC_res <- apply(height * width, 2, sum)
 
-tp[6,which(temp == 'fish_combine_3_hetero_p')]
-fp[6,which(temp == 'fish_combine_3_hetero_p')]
-fn[6,which(temp == 'fish_combine_3_hetero_p')]
-tn[6,which(temp == 'fish_combine_3_hetero_p')]
+AUC <- as.numeric(AUC_res)
 
-plot(fpr$fish_combine_3_hetero_p, tpr$fish_combine_3_hetero_p,
-     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Fisher combined',
-     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
-abline(a = 0, b = 1)
-roc(response = dat_summary$type, predictor = dat_summary$fish_combine_3_hetero_p)
+temp <- names(dat_summary)[grepl(names(dat_summary), pattern = "_p")]
+Method <- c("$SD_z$ homogeneous all",
+            "$SD_z$ study 1",
+            "$SD_z$ study 2",
+            "$SD_z$ study 3",
+            "$SD_z$ study 4",
+            "$maxmin_z$ homogeneous all",
+            "$maxmin_z$ study 1",
+            "$maxmin_z$ study 2",
+            "$maxmin_z$ study 3",
+            "$maxmin_z$ study 4",
+            "$SD_z$ heterogeneous all",
+            "$SD_z$ study 1 low condition",
+            "$SD_z$ study 1 high condition",
+            "$SD_z$ study 2 low condition",
+            "$SD_z$ study 2 high condition",
+            "$SD_z$ study 3 low condition",
+            "$SD_z$ study 3 high condition",
+            "$SD_z$ study 4 low condition",
+            "$SD_z$ study 4 high condition",
+            "$maxmin_z$ heterogeneous all",
+            "$maxmin_z$ study 1 low condition",
+            "$maxmin_z$ study 1 high condition",
+            "$maxmin_z$ study 2 low condition",
+            "$maxmin_z$ study 2 high condition",
+            "$maxmin_z$ study 3 low condition",
+            "$maxmin_z$ study 3 high condition",
+            "$maxmin_z$ study 4 low condition",
+            "$maxmin_z$ study 4 high condition",
+            "Reversed Fisher method gender hypothesis",
+            "Reversed Fisher method interaction hypothesis",
+            "Combined Fisher test (3 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (3 results, $SD_z$ heterogeneous)",
+            "Combined Fisher test (6 results, $SD_z$ homogeneous)",
+            "Combined Fisher test (10 results, $SD_z$ heterogeneous)",
+            "Effect sizes ($1-r$)")
 
-height = (tpr$fish_combine_3_hetero_p[-1]+tpr$fish_combine_3_hetero_p[-length(tpr$fish_combine_3_hetero_p)])/2
-width = diff(fpr$fish_combine_3_hetero_p) # = diff(rev(omspec))
-sum(height*width)
-
-plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
-     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
-     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
-abline(a = 0, b = 1)
-roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_homo)
-
-height = (tpr$variance_sd_p_overall_homo[-1]+tpr$variance_sd_p_overall_homo[-length(tpr$variance_sd_p_overall_homo)])/2
-width = diff(fpr$variance_sd_p_overall_homo) # = diff(rev(omspec))
-sum(height*width)
-
-plot(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
-     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
-     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
-abline(a = 0, b = 1)
-roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_hetero)
-
-height = (tpr$variance_sd_p_overall_hetero[-1]+tpr$variance_sd_p_overall_hetero[-length(tpr$variance_sd_p_overall_hetero)])/2
-width = diff(fpr$variance_sd_p_overall_hetero) # = diff(rev(omspec))
-sum(height*width)
-
-plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
-     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
-     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
-abline(a = 0, b = 1)
-lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
-     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
-     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)
-
-legend(x = 0, y = 1, bty = 'n', lty = c(1, 2), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))
+df <- data.frame(Method = Method,
+                 AUROC = AUC_res)
 ```
 
-<!---
+The collected data included `r table(dat_summary$type)[1]` genuine data from Many Labs 1 [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and `r table(dat_summary$type)[2]` fabricated datasets ([https://osf.io/e6zys](https://osf.io/e6zys); `r sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))` participants did not participate for a bonus).
 
-# Study 2
+Figure `r fignr` shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
+These group-level comparisons provide an overview of the differences between the genuine- and fabricated data [see also @10.1186/1471-2288-3-18].
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses).
+However, there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
 
-To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment (Stroop 1935).
+```{r ddfab_density, fig.cap="_Figure XX._ Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.", out.width='100%', echo=FALSE}
+plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    ylim(0, 1.5) + 
+    scale_fill_discrete(guide=FALSE) + 
+    ggtitle('Gender')
+
+  plot_es_gender <- ggplot(dat_summary, aes(x = es_gender, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Condition
+  dat_summary_tmp <- dat_summary
+  dat_summary_tmp$p_condition <- log10(dat_summary_tmp$p_condition)
+  plot_p_condition <- ggplot(dat_summary_tmp, aes(x = p_condition, fill = type)) +
+    geom_density(alpha = .3) +
+    xlab(TeX("log10 $P$-value")) +
+    ylab("Density") +
+    scale_fill_discrete(labels = c("Genuine","Fabricated")) + 
+    theme(legend.position="top") +
+    ggtitle('Condition')
+
+  plot_p_condition$labels$fill <- ""
+
+  plot_es_condition <- ggplot(dat_summary, aes(x = es_condition, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlim(0, 1) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Interaction
+  plot_p_interaction <- ggplot(dat_summary, aes(x = p_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE) +
+    ylim(0, 1.5) +
+    ggtitle('Interaction')
+
+  plot_es_interaction <- ggplot(dat_summary, aes(x = es_interaction, fill = type)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("Effect size ($r$)")) + 
+    ylab("Density") + 
+    scale_fill_discrete(guide=FALSE)
+
+  # Plot
+  grid.arrange(plot_p_gender,
+               plot_p_condition,
+               plot_p_interaction,
+               plot_es_gender,
+               plot_es_condition,
+               plot_es_interaction,
+               ncol = 3)
+
+fignr <- fignr + 1
+```
+
+### Performance of variance analysis to detect data fabrication
+
+Table `r tabnr` indicates that both operationalizations (i.e., $SD_z$ and $max-min_z$) show similar performance based on the AUROC.
+All in all, their performance ranges from `r round(min(df$AUROC[1:28]), 3)` through `r round(max(df$AUROC[1:28]), 3)`.
+As such, there is considerable variation for the various applications of the variance analyses.
+
+```{r table_var, echo=FALSE}
+dfvar <- data.frame(Method = c("Homogeneous, all studies combined",
+               "Homogeneous, study 1",
+               "Homogeneous, study 2",
+               "Homogeneous, study 3",
+               "Homogeneous, study 4",
+               "Heterogeneous, all studies combined",
+               "Heterogeneous study 1, low anchor condition",
+               "Heterogeneous study 1, high anchor condition",
+               "Heterogeneous study 2, low anchor condition",
+               "Heterogeneous study 2, high anchor condition",
+               "Heterogeneous study 3, low anchor condition",
+               "Heterogeneous study 3, high anchor condition",
+               "Heterogeneous study 4, low anchor condition",
+               "Heterogeneous study 4, high anchor condition"),
+               SD_z = df$AUROC[c(1:5, 11:19)],
+               max_min_z = df$AUROC[c(6:10, 20:28)])
+dfvar2 <- dfvar
+names(dfvar2) <- c('Method', 'AUROC $SD_z$', 'AUROC $max-min_z$')
+knitr::kable(dfvar2, row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using variance analyses to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+Combining the variance analyses across the different studies improves performance.
+This is as expected, considering that the sample size increases for the analyses (i.e., more reported variances are included) and that causes an increase in the statistical power to detect data fabrication.
+
+More notably, combining the studies and taking the heterogeneous approach (i.e., separating anchoring conditions) greatly increases the performance to detect data fabrication considerably.
+Where the AUROC under homogeneous variances for $SD_z=`r round(dfvar$SD_z[1], 3)`$ ($max-min_z=`r round(dfvar$max_min_z[1], 3)`$), under heterogeneous variances it increases to $SD_z=`r round(dfvar$SD_z[6], 3)`$ ($max-min_z=`r round(dfvar$max_min_z[6], 3)`$).
+Further inspecting the heterogeneous variance of variances analysis indicates that no false positives occur until $\alpha=`r seq(0, 1, .01)[max(which(tnr$variance_sd_p_overall_hetero == 1))]`$, making this the optimal alpha level based on this sample (but note the small sample).
+
+### Performance of $p$-values analysis to detect data fabrication
+
+Table `r tabnr` indicates that methods using nonsignificant $p$-values to detect data fabrication are hardly better than chance level in the current sample.
+We asked researchers to fabricate data for nonsignificant effect sizes, thinking they might be unable to produce uniformly distributed $p$-values.
+However, these results (and the density plot in Figure XX) indicate that widespread detection based on this is not promising.
+
+```{r table_p, echo=FALSE}
+knitr::kable(df[29:30,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using $p$-value analyses to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of combining variance- and $p$-value analyis to detect data fabrication
+
+Table `r tabnr` indicates that combining the variance- and $p$-value methods provides little beyond the methods separately.
+The overall performance of this combination is driven by the variance analyses, given that the $p$-value analysis yields little more than chance classification.
+When combining the results from variance analyses per anchoring condition (i.e., 10 results, $SD_z$ heterogeneous) and the $p$-value analyses, a minor improvement occurs over the heterogeneous variance analysis (all studies combined, $AUROC=`r round(dfvar$SD_z[6], 3)`$).
+However, this difference is negligible and potentially due to sampling error.
+
+```{r table_comb, echo=FALSE}
+knitr::kable(df[31:34,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of combining variance- and $p$-value analyses to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of extreme effects to detect data fabrication
+
+Table `r tabnr` indicates that using effect sizes (i.e., $1-r$) is a simple but effective way to detect data fabrication ($AUROC=`r round(df[35,2], 3)`$).
+Compared to the variance analyses several sections ago, its performance in this sample is a bit worse (i.e., `r round(df[35,2], 3)` compared to `r round(dfvar$SD_z[6], 3)`).
+However, it makes up for this by computational parsimony.
+Whereas the variance analyses require a considerable amount of effort to implement, computing the correlation and taking the inverse is a relatively simple task.
+Further inspecting the effect size approach to detecting data fabrication indicates that no false positives occur until  $\alpha=`r seq(0, 1, .01)[max(which(tnr$es_p == 1))]`$ (i.e., $r>`r seq(1, 0, -.01)[max(which(tnr$es_p == 1))]`$), making this the optimal alpha level based on this sample (but note the small sample).
+
+```{r table_es, echo=FALSE}
+knitr::kable(df[35,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using effect sizes to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+<!-- ## Discussion -->
+
+<!-- These data corroborate the idea that extremely large effect sizes (e.g., $r>.95$) might prove to be an easy-to-implement flag for potentially anomalous data (it is wise to seek for alternative explanations after flagging, however).
+-->
+
+<!-- For the anchoring studies, homogeneous population variances across conditions seem unreasonable and greatly affect the performance of the statistical method.
+These result highlight that the origin of the variances should be  -->
+
+<!-- % variance analysis and effect size best ways to inspect
+% but severely correlated: smaller variances = larger effects
+% easiest way is too look for massive effects in the effects
+
+% Simonsohn method not invalid under homogeneous, just somethign to take into account
+% easily adjusted
+
+% Discuss how the PPV is likely to be overestimated because prevalence is 50% in this study
+% How we don't know the prevalence, in fact.
+
+% Discuss alpha choice based on sample has large error (small sample).
+% Only provides a first indication
+
+% Comparison between methods not tested, large error given small sample.
+% This provides just initial work -->
+
+<!-- This could be done automatically at a large scale easily [data for this are available in @10.3758/s13428-015-0664-2;@10.3390/data1030014] or by a reader while going through a manuscript (e.g., during peer-review).
+wrt effect sizes -->
+
+<!-- # Study 2
+
+```{r prep study 2, echo=FALSE}
+ml3_dat_file <- sprintf('%sdata/study_02/study_02-ml3_stroop/StroopCleanSet.csv', x12)
+pdf_file <- sprintf('%sarchive/gender_interaction.pdf', x12)
+
+# Set the number of iterations to use in calculations
+iter <- 100000
+
+# Compute the processed raw data for Many Labs 3 stroop
+if(!file.exists(sprintf('%sdata/study_02/ml3_stroop.csv', x12)))
+{
+  source(sprintf('%sfunctions/compute_raw_stroop_ml3.R', x12))
+}
+```
+
+We investigated detecting data fabrication in raw data as an extension of Study 1.
+In essence, the procedure is similar: we asked actual researchers to fabricate data that they thought would go undetected.
+For Study 2 we included a face-to-face interview to qualitatively assess how data fabrication occurs.
+A preregistration of this study occurred during the seeking of funding [@10.3897/rio.2.e8860] and during data collection ([https://osf.io/fc35g](https://osf.io/fc35g)).
+
+To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment [@10.1037/h0054651].
+In the Stroop task, participants are asked to determine the color a word is presented in (i.e., word colors), but the word also reads a color (i.e., color words).
+The presented word color (i.e., 'red', 'blue', or 'green') can be either presented in the congruent color (e.g., 'red' presented in red) or an incongruent color (i.e., 'red' presented in green).
+The dependent variable in the Stroop task is the response latency (in this study milliseconds are used).
+Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serves as the raw data.
+The Stroop effect typically is computed as the difference in mean response latencies between the congruent and incongruent conditions.
 
@@
 
-### Data collection.
+### Data collection
 
-Twenty genuine datasets were collected from the Many Labs 3 project (Ebersole et al. ).
+Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012}.
+Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample [the original preregistration mentioned 20 datasets, accidentally overlooking the online sample; @10.3897/rio.2.e8860].
+Using the original raw data and analysis script from ML3 ([https://osf.io/qs8tp/](https://osf.io/qs8tp/)), we computed the mean (M) and standard deviation (SD) for the participant's response latencies in both the within-subjects conditions of congruent trials and incongruent trials.
+These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure X).
+The Stroop effect was calculated as a $t$-test of the difference ($H_0:\mu=0$).
 
-Twenty faked datasets were collected experimentally.
-We sampled 20 of 84 Dutch or Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015, which was indexed in Thomson Reuters’ Web of Science database.
-Dutch and Flemish researchers were selected to allow for potential follow-up on the way data was fabricated in a face-to-face interview.
-The period 2005-2015 was chosen to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
-Researchers who published on the Stroop task were selected to ensure their familiarity with the type of task for which data had to be fabricated.
-The database was searched on October 13, 2015 and 84 unique e-mails were extracted from 86 articles.
+```{r spreadsheet-study2, fig.cap="_Figure X._ Example of a filled in template spreadsheet used in the fabrication process for Study 2.
+Respondents fabricated data in the yellow cells and green cells, which were used to compute the results of the hypothesis test of the condition effect.
+If the fabricated data confirm the hypotheses, a checkmark appeared.
+This template is available at [https://osf.io/2qrbs/](https://osf.io/2qrbs/).", out.width='100%', echo=FALSE}
+knitr::include_graphics('../figures/spreadsheet2.png')
+```
+
+We collected twenty-eight faked datasets on the Stroop task experimentally in a two-stage sampling procedure.
+First, we invited 80 Dutch and Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015 as available in the Thomson Reuters’ Web of Science database.
+We selected Dutch and Flemish researchers to allow for a face-to-face interview on how the data were fabricated.
+We chose the period 2005-2015 to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
+The database was searched on October 10, 2016 and 80 unique e-mails were retrieved from 90 publications.
+Only two of these 80 participated in the study; we subsequently implemented a second sampling stage where we collected e-mails from all PhD-candidates, teachers, and professors of psychology related departments at Dutch universities.
+This resulted in 1659 additional unique e-mails that we subsequently invited to participate in this study.
+Due to a malfunction in Qualtrics' quotum sampling, we oversampled, resulting in 28 participants instead of the originally intended 20 participants.
+
+Each participant received instructions on the data fabrication task via Qualtrics but was allowed to fabricate data until the face-to-face interview took place.
+In other words, each participant could take the time they wanted/needed to fabricate the data as extensively as they liked.
+Each participant received downloadable instructions (original: [https://osf.io/7qhy8/](https://osf.io/7qhy8/)) and the template spreadsheet via Qualtrics (see Figure X; [https://osf.io/2qrbs/](https://osf.io/2qrbs/)).
+The interview was scheduled via Qualtrics with JGV, who blinded the rest of the research team from the identifying information of each participant and the date of the interview.
+All interviews took place between January 31 and March 3, 2017.
+To incentivize researchers to participate, they received 100 euros for participation; to incentivize them to fabricate (supposedly) hard to detect data they could win an additional 100 euros if they belonged to one out of three top fabricators.
+The contents of the interview were transcribed for further research on qualitatively assessing how researchers might fabricate experimental data.
+
+### Data analysis
 
@@
 
-# Discussion
+## Discussion
 
-- Open data for further testing (see osf.io/xxxx)
-- Ecological validity
---->
+# General discussion -->
+
+# Session info
+
+```{r}
+sessionInfo()
+```
 

### 2017-05-17 submission/manuscript.Rnw
Update study 1, add rmarkdown

--- 2017-03-09 submission/manuscript.Rnw
@@
 Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP). 
-Psychology was faced with Stapel; medical sciences were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
-These are just a few examples of cases in the last decade.
+Psychology was faced with Stapel; medical sciencoes were faced with Poldermans and Macchiarini; life sciences were faced with Voignet.
+These are just a few examples of misconduct cases in the last decade.
 Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once \citep{fanelli2009} and this is likely to be an underestimate due to socially desirable responses.
@@
 
-In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct other than plagiarism.
+In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct (alongside plagiarism).
 The Journal of Cell Biology scans each submitted image for potential manipulation \citep{The_Journal_of_Cell_Biology2015-vh}, which greatly increases the risk of detecting (blatant) image manipulation.
@@
 Humans are notoriously bad at understanding and estimating probabilities \citep[e.g.,][]{tversky1974, Tversky1971}, which could manifest itself in the fundamentally probabilistic data they try to fabricate.
-That researchers do not understand probabilistic processes also presents itself in the interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
-When data are fabricated, probabilistic principles are easily violated if these principles are forgotten at the univariate level, bivariate level, trivatiate level, or beyond \citep{Haldane1948-nm}.
-Based on such a theoretical framework, statistical methods that investigate whether the reported data are actually plausible under theoretically probabilistic processes can be used to detect potential data fabrication.
+That researchers do not understand probabilistic processes also presents itself in false interpretation of genuine research data \citep{Hoekstra2006, Sijtsma2015-ts, Goodman_1999}.
+When data are fabricated, probabilistic principles are easily violated if forgotten at the univariate level, bivariate level, trivatiate level, or beyond \citep{Haldane1948-nm}.
+Based on this idea, statistical methods that investigate whether the reported data are feasible under the theoretically probabilistic processes can be used to detect potential data fabrication.
 
 The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis. 
-For example, problems with papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
+For example, problems in papers by Fuji were highlighted with statistical methods \citep{Carlisle2012-yg,Carlisle2015-wm}, resulting in 183 retractions \citep{oransky2015}.
 In this case, baseline measures across randomized groups were examined for too little variation.
-Random assignment should introduce a certain degree of random error that is might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
+Random assignment should introduce a certain degree of random error that might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
 Another two cases are those of Sanna and Smeesters, where fabricated data were also detected with statistics \citep{simonsohn2013}.
-These cases inspected the variance of variances (i.e., the second level, or meta, variance).
-Once again, too little variation was what revealed problems in these data.
+These cases inspected the variance of variances (i.e., the second, or meta level variance).
+Once again, too little variation was what revealed problems in these data \citep[other examples include ][]{lacour-complaint,foerster-complaint}.
 These methods, although developed in a case-setting, need not be limited to cases.
@@
 Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place \citep[e.g., late at night when no one is around;][]{stapel_book}.
+Trustworthiness of these accounts can be called into question.
 Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually to detect data fabrication.
@@
 
-The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated by the increased usage of public online discussion platforms such as PubPeer (\url{https://pubpeer.com}).
+The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated in the digital age by the increased usage of public online discussion platforms such as PubPeer (\url{https://pubpeer.com}).
 PubPeer serves as an "online journal club" where anyone can discuss articles.
@@
 Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments \citep{Baker_2016}.
-The impact of such new possibilities is not to be underestimated, although its potential to contribute to the scientific discussion should also not be.
+The impact of such new possibilities is not to be underestimated, although its potential to constructively contribute to the scientific discussion should also not be \citep{10.1038/540007b}.
 Nonetheless, the `statcheck` software was well validated prior to this application \citep{Nuijten_2015} and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
@@
 Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
-Even though the data available can look different depending on the structure of a study, there are certain common characteristics of results and the underlying raw data that can be inspected.
+Even though the available data can look different depending on the structure of a study, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
 For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
 Raw data frequently contain at least some variables measured at a interval- or ratio scale \citep{Stevens_1946}.
+Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results.
 
-We present a set of studies that directly test the validity of statistical methods to detect data fabrication.
-To this end, Study 1 inspected the performance of statistical methods to detect data fabrication when using only summary results (e.g., means and standard deviations) as typically reported in empirical research articles.
-Study 2 inspected the performance of statistical methods aimed at detecting data fabrication in raw data (i.e., the data underlying summary results).
-These two studies provide a first indication of how applicable and effective statistical methods are to detect data fabrication in practice, with actual researchers fabricating actual data.
+\section{Theoretical framework}
+
+\subsection{Detecting data fabrication in summary results}
+
+\subsubsection{\textit{P}-values}
+
+The distribution of one $p$-value depends on various factors, but there are specific theoretical boundary conditions \citep{fisher1925}.
+Based on the population effect size, the precision of the estimate, and the observed effect size, the $p$-value distribution can be uniform (when then null hypothesis is true) or right-skewed (when the alternative hypothesis is true).
+By extension, any other distribution, after taking into account sampling error, is theoretically not possible.
+For example, a distribution might show a bump when authors $p$-hack \citep[e.g., Figure 1 in ][]{10.7717/peerj.1935}, but fabricators might create other non-uniform or non-right-skewed distributions, failing to take into account the theoretical boundary conditions.
+
+In order to test whether observed $p$-values transgress this boundary condition, we proposed an adaptation of Fisher's method \citep{10.1186/s41073-016-0012-9}.
+This adaptation is a simple reversal of the Fisher method \citep{fisher1925}, which was originally introduced as a simple meta-analytic test to indicate presence of an effect; this test is computed as
+\begin{equation}
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
+\label{fishertest}
+\end{equation}
+where it tests for right-skew (i.e., more smaller $p$-values than larger $p$-values) across the $k$ number of $p$-values. Reversing the Fisher method results in 
+\begin{equation}
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
+\label{fisheradjusted}
+\end{equation}
+where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
+This threshold is added and can be set to anything.
+Given the frequent misinterpretation of $p$-values [e.g., as the probability of an effect,  @Goodman2008135;@Altman_1995], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
+In that case, it makes  sense to set $t=.05$ or $t=.10$, in order to include only nonsignificant test results.
+
+Two clear exceptions should be taken into account when using this test: (1) model-fit tests and (2) wrongly specified one-tailed tests.
+When model-fit tests are used, these can quickly result in high $p$-values because of model saturation.
+For properly specified one-tailed tests, the $p$-value distribution is right-skewed.
+When wrongly specified, it flips around and becomes left-skew.
+These two exceptional cases should not be forgotten during the application of this test, but are irrelevant for the rest of this paper due to our study design (see methods of both studies).
+
+\subsubsection{Variances}
+
+Variance or standard deviation estimates are typically reported to indicate spread, but just like the mean there should be sampling error in this estimate (i.e., the variance of the variances) proportionate to the sample size.
+TheA variance estimate follows a $\chi^2$-distribution, which is dependent on the sample size, that is
+\begin{equation}
+z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
+\label{simvar}
+\end{equation}
+where $N_j$ is the sample size of the $j$th group and $MS_w$ is the normalizing constant resulting in a standardized variance $z_j$. The normalizing constant $MS_w$ is computed as 
+\begin{equation}
+MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
+\label{msw}
+\end{equation}
+where $s^2_j$ is the observed variance in the $j$th group.
+
+By extension, the expected spread of reported standardized variances creates the benchmark to.
+This spread can be computed in various ways, such as the standard deviation of the standardized variances (denoted $SD_z$) or as the range of the standardized variances (denoted $max-min_z$).
+
+To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies.
+This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
+For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
+To compute this probability, we first standardized the SDs for each of the four studies with
+\begin{equation}
+z_j=\sqrt{\frac{s^2_j}{MS_w}}=\sqrt{\frac{s^2_j}{\left(\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}\right)}}
+\label{s2_j}
+\end{equation}
+where $z_j$ denotes the standardized SD in group $j$ ($MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells, which is the case for the fabricated datasets).
+We tested different measures to detect data fabrication that utilize these standardized SDs (i.e., $z_j$).
+We included the variance of the standardized SDs \citep[i.e.,  $SD_{z}$;][]{simonsohn2013} and tried out the max-min distance of the standardized SDs (denoted $max-min_{z}$) as an alternative measure.
+We compared the observed value for each measure with the expected distribution when the summary results are used to generate random samples.
+To this end, we simulated the expected distribution of standardized SDs and computed the expected distribution of each measure.
+This expected distribution was used to determine the $p$-value of the observed $SD_z$ and $max-min_z$.
+We simulated the standardized variance for each of the $j$ groups as
+\begin{equation}
+z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
+\label{simvar}
+\end{equation}
+These simulated values are used to compute the expected distribution of the $SD_z$ and $max-min_z$  measures.
+
+Testing the standardized SDs for potential data fabrication can be done either for each study separately or all studies combined; the test can also be done under different assumptions of population variances across conditions.
+The assumptions of population variance can either by that all SDs originate from the same distribution \citep[as in][]{simonsohn2013}, the SDs within a factor are from the same distribution, or each group comes from its own distribution.
+We preregistered the method that assumes the SDs are drawn from the same distribution for the various conditions (i.e., homogeneous SDs) and are tested across all studies.
+However, upon conducting the analyses, we decided homogenous SDs are not unequivocal and included computations where the SDs for the low anchor and high anchor are from different distributions (i.e., heterogeneous SDs).
+Additionally, the signal for data fabrication across the four anchoring studies might result in different studies cancelling each other out, so we also included analyses where each study was analyzed separately.
+
+\subsection{Detecting data fabrication in raw data}
 
@@
 
-To detect data fabrication in a set of summary results, we first tested the standardized standard deviations (SDs) for data fabrication \citep{simonsohn2013} across the four anchoring studies.
-This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on random sampling processes.
-For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
-To compute this probability, we first standardized the SDs for each of the four studies with
-\begin{equation}
-z_j=\sqrt{\frac{s^2_j}{MS_w}}=\sqrt{\frac{s^2_j}{\left(\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}\right)}}
-\label{s2_j}
-\end{equation}
-where $z_j$ denotes the standardized SD in group $j$ ($MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells, which is the case for the fabricated datasets).
-We tested different measures to detect data fabrication that utilize these standardized SDs (i.e., $z_j$).
-We included the variance of the standardized SDs \citep[i.e.,  $SD_{z}$;][]{simonsohn2013} and tried out the max-min distance of the standardized SDs (denoted $max-min_{z}$) as an alternative measure.
-We compared the observed value for each measure with the expected distribution when the summary results are used to generate random samples.
-To this end, we simulated the expected distribution of standardized SDs and computed the expected distribution of each measure.
-This expected distribution was used to determine the $p$-value of the observed $SD_z$ and $max-min_z$.
-We simulated the standardized variance for each of the $j$ groups as
-\begin{equation}
-z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
-\label{simvar}
-\end{equation}
-These simulated values are used to compute the expected distribution of the $SD_z$ and $max-min_z$  measures.
-
-Testing the standardized SDs for potential data fabrication can be done either for each study separately or all studies combined; the test can also be done under different assumptions of population variances across conditions.
-The assumptions of population variance can either by that all SDs originate from the same distribution \citep[as in][]{simonsohn2013}, the SDs within a factor are from the same distribution, or each group comes from its own distribution.
-We preregistered the method that assumes the SDs are drawn from the same distribution for the various conditions (i.e., homogeneous SDs) and are tested across all studies.
-However, upon conducting the analyses, we decided homogenous SDs are not unequivocal and included computations where the SDs for the low anchor and high anchor are from different distributions (i.e., heterogeneous SDs).
-Additionally, the signal for data fabrication across the four anchoring studies might result in different studies cancelling each other out, so we also included analyses where each study was analyzed separately.
-
 Second, we applied the reversed Fisher method to detect data fabrication to the nonsignificant $p$-values twice: once for the results of gender effects hypothesis in each study and once for the results of the interaction effect hypothesis for each study.
-The Fisher method \citep{fisher1925} tests for evidence of an effect in a set of $p$-values by testing for a right-skew $p$-value distribution, but we adjusted it here to test for results that are overly consistent with the null hypothesis and result in a left-skew distribution (see Figure \ref{leftskew}).
-The original Fisher method is computed as
-\begin{equation}
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
-\label{fishertest}
-\end{equation}
-and tests for right-skew in a set of $p$-values, but we adjust it to the following
-\begin{equation}
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
-\label{fisheradjusted}
-\end{equation}
-where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
-We set this threshold to .05 in order to include only nonsignificant test results.
-The theoretical idea behind this method is that researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution, given the frequent misinterpretation of $p$-values \citep[e.g., as the probability of an effect,][]{Goodman2008135,Altman_1995}.
-% I can add more refs but it is just a rabbit hole to start with more.
-
-<<figure, echo = FALSE, results = hide>>=
-if(!file.exists(sprintf('%sfigures/fisherfig.pdf', x12)))
-{
-  pdf(sprintf('%sfigures/fisherfig.pdf', x12), width = 14, height = 7)
-  par(mar = c(5, 5, 3, 1), mfrow = c(1, 2))
-
-  plot(dbeta(seq(0, 1, .001), .05, 1),
-       x = seq(0, 1, .001), type = 'l',
-       bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(A) Right-skew (normal)')
-  lines(dunif(seq(0, 1, .001)),
-        x = seq(0, 1, .001), lty = 2)
-  plot(dbeta(seq(0, 1, .001), 1, .05),
-       x = seq(0, 1, .001), type = 'l',
-       bty = 'n', xlab = 'P-value', ylab = 'Density',
-       main = '(B) Left-skew (potentially anomalous)')
-  lines(dunif(seq(0, 1, .001)),
-        x = seq(0, 1, .001), lty = 2)
-  abline(v = .05, lty = 3)
-  text(x = .15, y = 33, labels = "<- Threshold")
-  dev.off()
-}
-@
-
-% add plot of left and right skew
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../figures/fisherfig.pdf}
-\caption{Conceptual representation of what the Fisher test inspects (Equation \ref{fishertest}; panel A) and what the adjusted Fisher test inspects (Equation \ref{fisheradjusted}; panel B).
-Both panels test whether there is sufficient evidence that the solid line deviates from the dashed line, except that the type of deviation that the test is sensitive to is the exact opposite.}
-\label{leftskew}
-\end{center}
-\end{figure}
 

### 2017-05-17 functions/concatenate_analyze_01.R

@@ -444,14 +444,18 @@ dat_summary$fish_combine_6_homo <- -2 * (log(dat_summary$variance_sd_p_study1) +
                                            log(dat_summary$interaction_fish_p))
 dat_summary$fish_combine_6_homo_p <- pchisq(q = dat_summary$fish_combine_6_homo,
                                             df = 2 * 6, lower.tail = FALSE)
-dat_summary$fish_combine_6_hetero <- -2 * (log(dat_summary$variance_sd_p_study1) +
-                                             log(dat_summary$variance_sd_p_study2) + 
-                                             log(dat_summary$variance_sd_p_study3) + 
-                                             log(dat_summary$variance_sd_p_study4) +
+dat_summary$fish_combine_10_hetero <- -2 * (log(dat_summary$variance_sd_p_study1_low) +
+                                           log(dat_summary$variance_sd_p_study2_low) + 
+                                           log(dat_summary$variance_sd_p_study3_low) + 
+                                           log(dat_summary$variance_sd_p_study4_low) +
+                                           log(dat_summary$variance_sd_p_study1_high) +
+                                           log(dat_summary$variance_sd_p_study2_high) + 
+                                           log(dat_summary$variance_sd_p_study3_high) + 
+                                           log(dat_summary$variance_sd_p_study4_high) +
                                              log(dat_summary$gender_fish_p) + 
                                              log(dat_summary$interaction_fish_p))
-dat_summary$fish_combine_6_hetero_p <- pchisq(q = dat_summary$fish_combine_6_hetero,
-                                              df = 2 * 6, lower.tail = FALSE)
+dat_summary$fish_combine_10_hetero_p <- pchisq(q = dat_summary$fish_combine_10_hetero,
+                                              df = 2 * 10, lower.tail = FALSE)
 
 write.csv(dat_summary,
           dat_summary_file, row.names = FALSE)

### 2017-06-24 submission/manuscript.Rmd
Update theoretical framework

@@
 output:
-  word_document: default
+  pdf_document:
+    toc: yes
   html_document:
     toc: yes
+  word_document: default
 csl: ../bibliography/apa.csl
@@
 
-Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
+Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods function well enough to make it responsible to apply them.
 We hardly know how researchers might go about fabricating data.
@@
 
-Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
+Throughout this paper, we inspect statistical methods to detect potential data fabrication that can be applied to (1) summary results or (2) raw data. 
 Even though structure and contents of data can look different depending on the structure of a study and the measures, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
@@
 Raw data frequently contain at least some variables measured at a interval- or ratio scale [@10.1126/science.103.2684.677].
-Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results.
+Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results to screen for problematic data.
 We review the theoretical framework of the specific methods we apply throughout this paper, but these are not exhaustive of all methods available to test for potential problems in empirical data [see also @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
@@
 
-In order to test whether observed $p$-values transgress the boundary condition, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
+In order to test whether observed $p$-values transgress the boundary condition, we previously proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
 This adaptation is a simple reversal of the Fisher method [@fisher1925], which was originally introduced as a simple meta-analytic test to indicate presence of an effect; this test is computed as
@@
 In that case, it makes  sense to set $t=.05$ or $t=.10$, in order to include only nonsignificant test results.
+Upon writing this paper, it became clear to us that this is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in Randomized Clinical Trials [RCTs; @10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
 
@@
 
-Variance- or standard deviation estimates are typically reported to indicate spread, but just like the mean there should be sampling error in this estimate (i.e., the variance of the variances) proportionate to the sample size.
+Variance- or standard deviation estimates are typically reported to indicate spread, but just like the mean there should be sampling error in this estimate proportionate to the sample size (i.e., the variance of the variances).
 A variance estimate follows a $\chi^2$-distribution, which is dependent on the sample size [p.
@@
 The size of a large effect can quickly become unrealistic; $d=1.2$ already implies a correlation of `r round(sqrt((1.2^2/(1.2^2+4))), 2)` between the dependent- and independent measures.
-More generally, the relation between the implied correlation and the effect size tends to be exponential, as Figure `r fignr` depicts.
+More generally, the relation between the implied correlation and the effect size tends to be exponential (see Figure `r fignr`) depicts.
 
-```{r d2, fig.cap="_Figure XX._ The relation between Cohen's d effect size and its direct transformation, the correlation r (or vice versa).
+```{r d2, fig.cap="The relation between Cohen's d effect size and its direct transformation, the correlation r (or vice versa).
 If effects d>2 are fabricated, the implied correlation between the dependent- and independent measure(s) is approximately .6.", out.width='100%', echo=FALSE}
@@
 
-### Variance analysis
+Raw data can contain ratio- or interval scale measures that, under specific conditions, are subject to mathematical properties.
+These properties pertain either to the leading (first) digit (e.g., the 1 in 123.45) or the terminal (last) digit (e.g., the 5 in 123.45).
+By analyzing these leading- and terminal digits for deviations from such mathematical properties, it might be possible to screen for problematic data.
+These properties can be extended to sequences of digits, but in this article we focus on leading digit analysis (i.e., Benford's law) and terminal digit analysis to detect potentially problematic data.
+
+#### Newcomb-Benford law
+
+The Newcomb-Benford law [NBL; @10.2307/2369148;@10.2307/984802] states that leading digits do not have an equal probability of occuring in various cases.
+A leading digit is the left-most digit of a numeric value, where a digit is any of the nine natural numbers ($1,2,3,...,9$).
+The distribution of the leading digit, according to the NBL is
+$$
+P(d)=log_{10}\frac{1+d}{d}
+$$
+where $d$ is the natural number of the leading digit and $P(d)$ is the probability of $d$ occurring.
+This law has been empirically observed in a variety of cases, ranging from population data to the number of rivers in an area [@10.2307/984802].
+Models that delineate what kinds of measures do- and do not adhere to NBL are non-trivial to compose.
+
+For ratio scale measures that are scale and base invariant, the NBL often applies empirically but for measures other than those it is non-evident whether they follow the NBL [@10.2307/2246134;@
+10.1214/11-PS175].
+Scale- and base invariance indicate that the results of the measure do not change if the measure is multiplied by constant $c$ or transformed into a log scale of variable base.
+However, by extension, deviations from a ratio scale that is base- and scale invariant are likely to cause the  NBL to not be applicable.
+For example, if a ratio scale is truncated (either with a minimum or maximum) it is already sufficient to cause a violation of the NBL [@10.1515/9781400866595-011].
+Moreover, a base- and scale invariant ratio measure implies adherence to the NBL [@10.1090/S0002-9939-1995-1233974-8], but does not necessitate that the leading digits follow the NBL.
+As such, empirical support that the numbers under investigation, in fact, follow the NBL is of importance before using the NBL to detect potential problems.
+
+Despite the limitations of the NBL, this property has been applied to detect financial fraud [e.g., @10.2307/27643897] or voting fraud [e.g., @durtschi2004effective] and also to detect problems in scientific data.
+Previously, the NBL has been tested on 20 falsified anesthesia papers, detecting 18 as problematic [@10.1007/s00101-012-2029-x], or to test coefficients reported in economics journals [@10.1111/j.1468-0475.2009.00475.x].
+The NBL is typically used to compute the expected values, which are then compared to the observed values using a $\chi^2$-test.
+However, the outcomes have not been validated to test the performance of the method.
+
+The performance of the NBL to detect problematic data is not evidential.
+Based on the NBL, Obama's 2008 election was rigged [@Deckert].
+Financial data is likely to be ridden with digit preferences, for example due to price setting, causing false flags.
+Additionally, scientific data do not necessarily follow the NBL, especially in the social sciences, because data are relatively sparse and often the result of human thought, which has previously been addressed as a reason why digits do not follow the NBL [@durtschi2004effective].
+Moreover, people might even be sensitive to fabricating data that are in line with the NBL [@10.1080/02664760601004940], potentially depending on whether fabricators generate or select values [@Burns2009].
+
+#### Terminal digit analysis
+
+Terminal digit analysis is based on the principle that the rightmost digit contains most of the measurement error in the number [@10.1080/08989629508573866;@10.1080/03610919608813325].
+For example, when someone's height is measured in micrometers, measurement one might be 1.848 metres, and a second measurement 1.841, etc.
+If the true height is 1.845 metres, it is a logical consequent that the terminal digit is more likely to be adjusted by measurement error (i.e., someone is unlikely to be two or zero metres tall due to measurement error).
+This is in essence a consequent of classical test theory, where each measurement is thought of as measuring a true score and random error [@10.1016/0022-2496(66)90002-2].
+
+As such, the rightmost digit can be expected to be uniformly distributed if sufficient precision is provided [@10.1080/08989629508573866].
+For our purposes, sufficient precision is determined as the terminal digit being at least the third leading digit.
+As such, if height measurements are reported in 1.8 metres, there are only three leading digits and there is insufficient precision.
+However, "1.84" contains three leading digits and is regarded as sufficient.
+Note also that this implies that Likert scales are wholly inappropriate for terminal digit analysis.
+
+Terminal digit analysis is conducted with a $\chi^2$-test on the digit occurrence counts.
+As such, it compares the observed frequencies with the expected uniform frequencies.
+Before applying this method is important to consider the applicability of the principle that the last digit contains the most measurement error [@10.14293/S2199-1006.1.SOR-STAT.AFHTWC.v1] because it is central to the analysis.
+For example, if it is reasonable to expect there are digit preferences in genuine data, this method is unlikely to differentiate between potentially problematic and genuine data.
 
 ### Multivariate associations
+
+True data occur within a web of relations, which can be observed in genuine data and easily forgotten in fabricated data.
+The multivariate relations between different variables arise from stochastic processes and are not readily known and therefore difficult to take into account when someone wants to fabricate data.
+As such, using these multivariate associations to detect anomalies from genuine data might prove valuable.
+
+The multivariate associations between various variables can be estimated from control data that are (assumably) genuine.
+For example, the multivariate relation between the means (Ms) and standard deviations (SDs) can be collected from comparable studies and measures in the literature.
+It is important to collect information from homogeneous studies and measures, to limit the influence of confounders that either suppress or exacerbate the relation.
+If the study under investigation for example uses a Hot Sauce measure for aggression [@10.1002/SICI1098-2337199925:5<331::AID-AB2>3.0.CO;2-1], it is important to collect data on that Hot Sauce measure's properties in other studies that use it, not in studies that use various measures for aggression.
+
+Subsequently, the (non-)parametric estimates of the multivariate relations can be used to determine how extreme the observed multivariate relations are.
+Consider the following example, with parametric estimates of the multivariate association between Ms and SDs.
+For example, imagine a set of studies that use the Hot Sauce aggression measure.
+When meta-analyzed, the Fisher transformed correlation [@10.2307/2331838] between the Ms and SDs across studies is estimated to be $0.123$, with a standard deviation of $0.1$.
+When an investigated paper presents results from a Hot Sauce aggression measure that correlate highly (Fisher transformed: $.5$), this indicates there might be an anomaly, considering only $`r pnorm(.5, .123, .1, lower.tail = FALSE)`$ of studies are expected to show such a strong relation (or more extreme) between Ms and SDs if the control data are representative of the population effect.
+
+Contrary to the aforementioned methods, this method is less generic because it requires the investigator to collect control data.
+However, because of this, it also has the potential to be more sensitive then the generic methods.
+Additionally, multivariate associations are always present in data and therefore the applicability of this method would be greater than the generic analyses that have a specific set of conditions that need to be fulfilled before the methods are applicable.
 
@@
 
-```{r spreadsheet-study1, fig.cap="_Figure XX._ Example of a filled in template spreadsheet used in the fabrication process of Study 1.
+```{r spreadsheet-study1, fig.cap="Example of a filled in template spreadsheet used in the fabrication process of Study 1.
 Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
@@
 
-```{r ddfab_density, fig.cap="_Figure XX._ Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+```{r ddfab_density, fig.cap="Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
 We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.", out.width='100%', echo=FALSE}
@@
 
-<!-- # Study 2
+# Study 2
 
@@
 
-Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012}.
+Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012].
 Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample [the original preregistration mentioned 20 datasets, accidentally overlooking the online sample; @10.3897/rio.2.e8860].
@@
 
-```{r spreadsheet-study2, fig.cap="_Figure X._ Example of a filled in template spreadsheet used in the fabrication process for Study 2.
+```{r spreadsheet-study2, fig.cap="Example of a filled in template spreadsheet used in the fabrication process for Study 2.
 Respondents fabricated data in the yellow cells and green cells, which were used to compute the results of the hypothesis test of the condition effect.
@@
 
-# General discussion -->
+# General discussion
+
+## `ddfab` package
+
+All the methods used in this paper are also implemented in the open source R package `ddfab`.
+
+However, these results indicate that application of these methods should be informed and as a screening method.
+
+## Study fallout
+
+While conducting Study 2 reported in this paper, there was considerable criticism from several parties.
+
+We
 

### 2017-06-28 submission/manuscript.Rmd
Update code
Transfer study 2 analysis from .Rnw to .Rmd, some minor revisions.

@@
 Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once [@10.1371/journal.pone.0005738] and this is likely to be an underestimate due to socially desirable responses.
-The detection rate is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
+The detection rate of data fabrication is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
 At best, this amounts to a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
@@
 In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts. 
-Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred equally across fabrication, falsification, and plagiarism.
 Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
 This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
-However, increased deterrence of fabrication and falsification by improved detection mechanisms has not been as widely implemented.
-
-In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct (alongside plagiarism).
+In the last decade, detecting image manipulation has become one of the few forms of detecting data fabrication.
 The Journal of Cell Biology scans each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh], which greatly increases the risk of detecting (blatant) image manipulation.
@@
 
+```{r ml3}
+ml3_dat <- read.csv(sprintf('%sdata/study_02/ml3_stroop.csv', x12))
+
+df_ml3 <- NULL
+# Compute the results for the ML3 data
+for(i in 1:length(unique(ml3_dat$study_name)))
+{
+  tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[i], ]
+  # This is an object to simplify concatenation
+  binder <- data.frame(id = unique(ml3_dat$study_name)[i],
+                       benford_congr_m_p = digit_analysis(tmp$MC, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(tmp$SDC, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(tmp$MI, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(tmp$SDI, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(tmp$MC, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(tmp$SDC, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(tmp$MI, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(tmp$SDI, type = 'terminal')$pval,
+                       std_congr_p = std_var(tmp$SDC, tmp$NC, iter = iter),
+                       std_incongr_p = std_var(tmp$SDI, tmp$NI, iter = iter),
+                       mult_m_sd_congr = cor(tmp$MC, tmp$SDC),
+                       mult_m_sd_incongr = cor(tmp$MI, tmp$SDI),
+                       mult_m_m_across = cor(tmp$MC, tmp$MI),
+                       mult_sd_sd_across = cor(tmp$SDC, tmp$SDI))
+
+  df_ml3 <- rbind(df_ml3, binder)
+}
+
+# The responses from the study
+responses <- list.files(sprintf('%sdata/study_02/responses', x12))
+df_fab <- NULL
+
+for (response in responses)
+{
+  fab_dat <- read.table(sprintf('%sdata/study_02/responses/%s', x12, response),
+                        sep = '\t', header = TRUE)
+  # For clarity sake
+  names(fab_dat) <- c('id',
+                      'mean_congruent',
+                      'sd_congruent',
+                      'congruent_trials',
+                      'mean_incongruent',
+                      'sd_incongruent',
+                      'incongruent_trials')
+
+  mult_m_sd_congr <- cor(fab_dat$mean_congruent, fab_dat$sd_congruent)
+  mult_m_sd_incongr <- cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent)
+  mult_m_m_across <- cor(fab_dat$mean_congruent, fab_dat$mean_incongruent)
+  mult_sd_sd_across <- cor(fab_dat$sd_congruent, fab_dat$sd_incongruent)
+
+  # Slotted for removal and replacement by parametric approach 20170628
+  p_mult_m_sd_congr <- ifelse(mean(df_ml3$mult_m_sd_congr) > mult_m_sd_congr,
+                              sum(df_ml3$mult_m_sd_congr < mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr),
+                              sum(df_ml3$mult_m_sd_congr > mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr))
+  p_mult_m_sd_incongr <- ifelse(mean(df_ml3$mult_m_sd_incongr) > mult_m_sd_incongr,
+                                sum(df_ml3$mult_m_sd_incongr < mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr),
+                                sum(df_ml3$mult_m_sd_incongr > mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr))
+  p_mult_m_m_across <- ifelse(mean(df_ml3$mult_m_m_across) > mult_m_m_across,
+                              sum(df_ml3$mult_m_m_across < mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across),
+                              sum(df_ml3$mult_m_m_across > mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across))
+  p_mult_sd_sd_across <- ifelse(mean(df_ml3$mult_sd_sd_across) > mult_sd_sd_across,
+                                sum(df_ml3$mult_sd_sd_across < mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across),
+                                sum(df_ml3$mult_sd_sd_across > mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across))
+
+  binder <- data.frame(id = response,
+                       benford_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'benford')$pval,
+                       benford_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'benford')$pval,
+                       benford_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'benford')$pval,
+                       benford_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'benford')$pval,
+                       terminal_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'terminal')$pval,
+                       terminal_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'terminal')$pval,
+                       terminal_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'terminal')$pval,
+                       terminal_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'terminal')$pval,
+                       std_congr_p = std_var(fab_dat$sd_congruent, fab_dat$congruent_trials, iter = iter),
+                       std_incongr_p = std_var(fab_dat$sd_incongruent, fab_dat$incongruent_trials, iter = iter),
+                       p_mult_m_sd_congr,
+                       p_mult_m_sd_incongr,
+                       p_mult_m_m_across,
+                       p_mult_sd_sd_across)
+
+  # Add 1 ten millionth to any zero
+  # so the log doesn't go to infinite and messes with the Fisher method
+  p_for_fish <- unlist(ifelse(binder[,6:15] == 0, .0000001, binder[,6:15]))
+
+  fish <- -2 * sum(log(p_for_fish))
+  df_fish <- length(p_for_fish) * 2
+  p_fish <- pchisq(q = fish, df = df_fish, lower.tail = FALSE)
+  binder <- cbind(binder, p_fish)
+
+  df_fab <- rbind(df_fab, binder)
+}
+
+write.csv(df_fab, sprintf('%sdata/study_02/df_fab.csv', x12), row.names = FALSE)
+```
+
 ## Results

### 2017-07-03 submission/manuscript.Rmd
Revisions intro, add results study 2

--- 2017-05-17 submission/manuscript.Rmd
@@
 output:
-  word_document: default
+  pdf_document:
+    toc: yes
   html_document:
     toc: yes
+    toc_depth: 2
 csl: ../bibliography/apa.csl
@@
 suppressPackageStartupMessages(library(pROC))
+suppressPackageStartupMessages(if(!require(knitr)){install.packages('knitr', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(knitr))
 suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign', repos = 'http://cran.us.r-project.org')})
@@
 suppressPackageStartupMessages(library(reshape2))
+suppressPackageStartupMessages(if (!require(metafor)){install.packages('metafor', repos = 'http://cran.us.r-project.org')})
+suppressPackageStartupMessages(library(metafor))
 
@@
 source(sprintf('%sfunctions/std_var.R', x12))
+source(sprintf('%sfunctions/fisher_method.R', x12))
 
@@
 In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts. 
-Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred across the different forms of scientific misconduct equilaterally.
+Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred equally across fabrication, falsification, and plagiarism.
 Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
 This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
-However, increased deterrence of fabrication and falsification by improved detection mechanisms has not been as widely implemented.
-
-In the last decade, detecting image manipulation has become one of the few forms of detecting scientific misconduct (alongside plagiarism).
-The Journal of Cell Biology scans each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh], which greatly increases the risk of detecting (blatant) image manipulation.
+In the last decade, detecting image manipulation has become one of the few forms of detecting data fabrication .
+The Journal of Cell Biology and EMBO scan each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh;@10.1038/546575a], which greatly increases the risk of detecting (blatant) image manipulation.
 More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations [@10.1007/s11948-016-9841-7].
@@
 
-Statistical methods can provide one way to improve detection of data fabrication in empirical research.
+Statistical methods provide one way to improve detection of data fabrication in empirical research.
 Humans are notoriously bad at understanding and estimating probabilities [e.g., @10.1126/science.185.4157.1124;@10.1037/h0031322], which could manifest itself in the fundamentally probabilistic data they try to fabricate.
-That researchers do not understand probabilistic processes also presents itself in false interpretation of genuine research data [@10.3758/BF03213921;@10.1007/s11336-015-9446-0;@10.7326/0003-4819-130-12-199906150-00008].
 When data are fabricated, probabilistic principles are easily violated if forgotten at the univariate level, bivariate level, trivatiate level, or beyond [@Haldane1948-nm].
@@
 
-The application of such statistical methods to detect data fabrication has occurred in several cases in recent years and has potential for future application beyond a case-basis. 
+```{r echo=FALSE}
+set.seed(1234)
+ex1 <- t(replicate(n = 10, expr = table(sample(x = c("M", "F"), size = 100, replace = TRUE))))
+ex1p <- pchisq(apply(ex1, 1, function(x) sum((x-50)^2/50)), df = 1, lower.tail = FALSE)
+set.seed(1234)
+ex2_1 <- 50 + sample(x = -1:1, size = 10, replace = TRUE)
+ex2_2 <- 100 - ex2_1
+ex2 <- cbind(ex2_1, ex2_2)
+ex2p <- pchisq(apply(ex2, 1, function(x) sum((x-50)^2/50)), df = 1, lower.tail = FALSE)
+
+df <- data.frame(study = sprintf("Study %s", 1:10),
+                 ex1,
+                 ex1p,
+                 ex2,
+                 ex2p)
+names(df) <- c("Study",
+               "Experimental [S1]",
+               "Control [S1]",
+               "P-value [S1]",
+               "Experimental [S2]",
+               "Control [S2]",
+               "P-value [S2]")
+```
+
+The application of such statistical methods to detect data fabrication has occurred in several cases of scientific misconduct in recent years and has potential for future application beyond these specific cases.
 For example, problems in papers by Fuji were highlighted with statistical methods [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], resulting in 183 retractions [@oransky2015].
-In this case, baseline measures across randomized groups were examined for too little variation.
-Random assignment should introduce a certain degree of random error that might be missed by a human fabricator, misestimating the probabilistic process that generates such error.
-Another two cases are those of Sanna and Smeesters, where fabricated data were also detected with statistics [@10.1177/0956797613480366].
-These cases inspected the variance of variances (i.e., the second, or meta level variance).
-Once again, too little variation was what revealed problems in these data [other examples include @lacour-complaint;@foerster-complaint].
-These methods, although developed in a case-setting, need not be limited to cases.
+This method works as follows: in true randomized clinical trials (RCTs), baseline measurements should be statistically equal across groups.
+As such, the $p$-values for group comparisons would be expected to be uniformly distributed because the null hypothesis of equal groups is true by definition of the design.
+In the Fuji papers, group comparisons showed excessive consistency, resulting primarily in high $p$-values (e.g., .99, .95) and a high mean $p$-value across the comparisons, where a mean $p$-value of .5 is expected.
+As an illustration, see Table `r tabnr`, which depicts the assignment of participants to the experimental or control condition for a true randomized design (Set 1) or for a fabricated design (Set 2).
+The mean $p$-value for the true randomized design Set 1 is `r round(mean(ex1p), 3)`, whereas the fabricated Set 2 has mean $p$-value `r round(mean(ex2p), 3)`.
+Other statistical methods to detect data fabrication are addressed in the theoretical framework.
+.
+
+```{r table_excess, echo = FALSE}
+knitr::kable(df, digits = 3, caption = "Examples of participant counts for genuine- and fabricated randomized clinical trials.
+Set 1 (S1) is randomly generated data under the null hypothesis of random assignment (assumed to be the genuine process), whereas Set 2 (S2) is generated under excessive consistency with equal groups.
+Each trial contains 100 participants.
+The $p$-values ")
+
+tabnr <- tabnr + 1
+```
+
+Such statistical methods to detect data anomalies, although developed to quantify suspicions in a specific paper, could be applied to screen multiple papers.
 The application of such methods can be (semi-)automated if data are available in a machine-readable format that one of the statistical methods can be applied to.
@@
 
-Nonetheless, considering the potential harm of applying statistical methods to flag potentially problematic results, it needs to be sorted out whether such methods have diagnosticity that actually makes it responsible to apply them.
+Nonetheless, prior to applying statistical methods to flag potentially problematic results, investigating whether such methods function well enough in detecting problems is required for responsible application.
 We hardly know how researchers might go about fabricating data.
-Cases such as Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
+Cases such as Stapel, Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
 Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place [e.g., late at night when no one is around; @stapel_book].
@@
 Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually to detect data fabrication.
-Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be simulated.
+Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be assessed.
 
-The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated in the digital age by the increased usage of public online discussion platforms such as [PubPeer (https://pubpeer.com)](https://pubpeer.com).
-PubPeer serves as an "online journal club" where anyone can discuss articles.
-Authors are notified when someone leaves a response, providing them with the possibility to respond.
-Such a platform allows for public discussion of the paper, including discussion of reanalyses, methodology, availability of materials, etc.
-When detection mechanisms are freely available to use, they can lead to (a surge of) comments when applied by users.
-Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments [@10.1038/540151a].
-The impact of such new possibilities is not to be underestimated, although its potential to constructively contribute to the scientific discussion should also not be [@10.1038/540007b].
-Nonetheless, the `statcheck` software was well validated prior to this application [@10.3758/s13428-015-0664-2] and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
+Throughout this paper, we inspect statistical methods to detect potential data fabrication that can be applied to (1) summary results or (2) raw data. 
+Even though structure and contents of data can look different depending on the structure of a study and the measures, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
+For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
+Raw data frequently contain at least some variables measured at a interval- or ratio scale [@10.1126/science.103.2684.677].
+Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results to screen for problematic data.
+We review the theoretical framework of the specific methods we apply throughout this paper, but these are not exhaustive of all methods available to test for potential problems in empirical data [see also @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
 
@@
 
-Throughout this paper, we inspect statistical methods to detect data fabrication that can be applied to (1) summary results or (2) raw data. 
-Even though structure and contents of data can look different depending on the structure of a study and the measures, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
-For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
-Raw data frequently contain at least some variables measured at a interval- or ratio scale [@10.1126/science.103.2684.677].
-Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results.
-We review the theoretical framework of the specific methods we apply throughout this paper, but these are not exhaustive of all methods available to test for potential problems in empirical data [see also @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
+In the current paper, we differentiate between statistical methods to detect potential data fabrication based on reported data (i.e., summary results) or raw data.
+For summary results, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data anomalies.
+$P$-value analysis can be applied whenever sufficient nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size can be computed [e.g., an APA reported $t$- or $F$-statistic;@10.1525/collabra.71].
+For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis), and multivariate associations as potential ways to detect data anomalies.
+Digit analyses can be applied when ratio scale measures are present in the raw data; multivariate associations can be applied whenever there is a multivariate relation in the raw data that can be computed and control data is available from the literature.
 
@@
 
-The distribution of one $p$-value depends on various parameters, but there are specific theoretical boundary conditions to this distribution [@fisher1925].
-Based on the population effect size, the precision of the estimate, and the observed effect size, the $p$-value distribution can be uniform (when then null hypothesis is true) or right-skewed (when the alternative hypothesis is true).
-By extension, any other distribution, after taking into account sampling error, is theoretically suspect.
-For example, a distribution might show a bump when authors $p$-hack [e.g., Figure 1 in @10.7717/peerj.1935], but fabricators might create other non-uniform or non-right-skewed distributions, failing to take into account the theoretical boundary conditions.
+The distribution of a $p$-value is uniform if the null hypothesis is true and right-skewed if the alternative hypothesis is true [@fisher1925].
+One $p$-value is the result of the population effect size, the precision of the estimate, and the observed effect size, whose properties carry over to a set of $p$-values if those $p$-values are independent.
+As such, the $p$-value distribution of a set of $p$-values is uniform when the null hypothesis is true, or right-skewed when the alternative hypothesis is true.
 
-In order to test whether observed $p$-values transgress the boundary condition, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
-This adaptation is a simple reversal of the Fisher method [@fisher1925], which was originally introduced as a simple meta-analytic test to indicate presence of an effect; this test is computed as
+When the $p$-value distribution is not uniform nor right-skewed, it can indicate potential data anomalies.
+For example, a distribution might show a bump when excessive $p$-hacking occurs that seeks barely significant results [e.g., Figure 1 in @10.7717/peerj.1935].
+However, data fabricators might create other non-uniform or non-right-skewed distributions, failing to take into account the theoretical boundary conditions.
+For example, given the frequent misinterpretation of $p$-values [@10.3758/BF03213921;@10.1007/s11336-015-9446-0;@10.7326/0003-4819-130-12-199906150-00008], it is possible that the same underlying misinterpration will manifest itself in fabricated data.
+More specifically, given the frequent misinterpretation of $p$-valuesas the probability of an effect [@10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
+
+In order to test whether observed $p$-values are anomalous, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
+This adaptation is a simple reversal of the original Fisher method [@fisher1925], which was introduced as a meta-analytic test for the presence of an effect.
+This test is computed as
 $$
@@
 where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
-This threshold is added and can be set to anything.
-Given the frequent misinterpretation of $p$-values [e.g., as the probability of an effect, @10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
-In that case, it makes  sense to set $t=.05$ or $t=.10$, in order to include only nonsignificant test results.
+This threshold is added and can be set to any value between zero and one.
+Upon writing this paper, it became clear to us that this is reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
 
-Despite this test being useful for detecting data anomalies in nonsignificant $p$-values, two clear exceptions should be taken into account: (1) model-fit tests and (2) wrongly specified one-tailed tests.
-When model-fit tests are used, these can quickly result in high $p$-values because of model saturation (i.e., where the null hypothesis is good fit and the alternative is bad fit).
+Despite this test being useful for detecting data anomalies in nonsignificant $p$-values, one exception should be taken into account: wrongly specified one-tailed tests.
 For properly specified one-tailed tests, the $p$-value distribution is right-skewed.
 When wrongly specified, this distribution is reversed and becomes left-skew.
-These two exceptional cases should not be forgotten during the application of this test, but are irrelevant for the rest of this paper due to our study design (see methods of both studies).
+As such, any data anomalies detected with this method would need to be inspected for misspecified one-tailed hypotheses to preclude false conclusions.
 
@@
 
-Variance- or standard deviation estimates are typically reported to indicate spread, but just like the mean there should be sampling error in this estimate (i.e., the variance of the variances) proportionate to the sample size.
+Variance- or standard deviation estimates are typically reported to indicate dispersion, but just like the mean there should be sampling error in this estimate proportional to the sample size [i.e., $\sigma/\sqrt{2n}$ under the assumption of normality, p.
+351;@yule1922].
 A variance estimate follows a $\chi^2$-distribution, which is dependent on the sample size [p.
@@
 $$
-where $s^2_j$ is the variance in the $j$th group. If simulating (see next paragraph), the simulated variances are used to compute $MS_w$.
+where $s^2_j$ is the variance in the $j$th group.
 
-Assuming that the observed variances are from the same population distribution, the expected spread of reported standardized variances can be simulated.
-By repeatedly drawing (standardized) variance estimates for $j$ groups and then computing their spread allows for approximation of the sampling distribution.
-Spread can be operationalized in various ways, such as the standard deviation of the variances (denoted in this paper as $SD_z$) or as the range of the variances (denoted as $max-min_z$).
-If there is reason to believe that the observed variances come from heterogeneous populations, subgrouping (i.e., one variance analysis per subgroup) is necessary to prevent false results.
-
-Subsequently, the observed sampling variance (or range) can be compared to the expected sampling distribution.
-Too consistent results would indicate potential anomalies in the reported data [@10.1177/0956797613480366].
-For example, if four independent samples all yield the variance $2.22$, this could be considered excessively consistent when the probability that this amount of consistency (or more) is less than 1 out of 1000 in truly random samples.
+The observed dispersion of the variances can be compared to various measures of expected dispersion in the variances.
+Dispersion can be operationalized in various ways, such as the standard deviation of the variances [denoted in this paper as $SD_z$;@10.1177/0956797613480366] or as the range of the variances (denoted as $max-min_z$).
+Too consistent results would indicate potential anomalies in the reported data.
+For example, in the Smeesters case three independent conditions from the same study ($n_k=15$) were reported to have standard deviations 25.09, 24.58, and 25.65.
+The standard deviation of the standard deviations here is `r round(sd(c(25.09, 24.58, 25.65)), 2)` (i.e., $SD_z$).
+Such consistency (or more consistency) would only be observed in `r round(std_var(n = rep(15, 3), sds = c(25.09, 24.58, 25.65), iter = 100000)*100, 2)`% of 100,000 simulated replications [@10.1177/0956797613480366].
 
@@
 
-A fabricator might present unrealistically large effects, forgetting the exponential relation between the effect size measure and the implied correlation.
 From our own experience, and anecdotal evidence elsewhere [@10.1016/0197-24569190037-M], large effects have previously raised initial suspicions.
-The size of a large effect can quickly become unrealistic; $d=1.2$ already implies a correlation of `r round(sqrt((1.2^2/(1.2^2+4))), 2)` between the dependent- and independent measures.
-More generally, the relation between the implied correlation and the effect size tends to be exponential, as Figure `r fignr` depicts.
-
-```{r d2, fig.cap="_Figure XX._ The relation between Cohen's d effect size and its direct transformation, the correlation r (or vice versa).
-If effects d>2 are fabricated, the implied correlation between the dependent- and independent measure(s) is approximately .6.", out.width='100%', echo=FALSE}
-d2 <- seq(0, 10, .01)
-
-plot(sqrt(d2^2/(d2^2+4)), x = d2,
-     type='l', xlab = "Cohen's d", ylab = "Correlation r")
-
-fignr <- fignr + 1
-```
-
 Taking the observed effect size and transforming it into a correlation, allows for an easy way to assess how extreme the presented result is.
@@
 
-### Variance analysis
+Raw data with ratio- or interval measures can be subjected to digit analysis under specific conditions.
+More specifically, the properties of the leading (first) digit (e.g., the 1 in 123.45) or the terminal (last) digit (e.g., the 5 in 123.45) can be examined.
+By analyzing these leading- and terminal digits for deviations from specific digit distributions, it might be possible to screen for problematic data.
+In this article we focus on leading digit analysis (i.e., Newcomb-Benford Law) and terminal digit analysis to detect potentially problematic data.
+
+#### Newcomb-Benford law
+
+The Newcomb-Benford law [NBL; @10.2307/2369148;@10.2307/984802] states that leading digits do not have an equal probability of occuring under certain conditions.
+A leading digit is the left-most digit of a numeric value, where a digit is any of the nine natural numbers ($1,2,3,...,9$).
+The distribution of the leading digit, according to the NBL is
+$$
+P(d)=log_{10}\frac{1+d}{d}
+$$
+where $d$ is the natural number of the leading digit and $P(d)$ is the probability of $d$ occurring.
+Table `r tabnr` indicates the expected leading digit distribution based on the NBL.
+This expected distribution is typically compared to the observed distribution with a $\chi^2$-test ($df=9-1$), which requires a minimum of 45 observations based on the rule of thumb outlined by @agresti2003categorical ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
+The NBL has been applied to detect financial fraud [e.g., @10.2307/27643897], voting fraud [e.g., @durtschi2004effective], and also to detect problems in scientific data [e.g., @10.1007/s00101-017-0333-1].
+
+<!-- In science, for example, the NBL has been tested on 20 falsified anesthesia papers, detecting 18 as problematic [@10.1007/s00101-012-2029-x], or to test coefficients reported in economics journals [@10.1111/j.1468-0475.2009.00475.x].
+-->
+```{r, echo=FALSE}
+tab <- data.frame(digit = 1:9, prop = log10((1+1:9)/1:9))
+names(tab) <- c('Digit', 'Proportion')
+knitr::kable(tab, digits = 3, caption = 'The expected first digit distribution, based on the Newcomb-Benford Law.')
+tabnr <- tabnr + 1
+```
+
+However, given that the NBL only applies under specific conditions that are rarely fulfilled in the social sciences, its applicability for detecting data anomalies in science can be questioned.
+First, the NBL only applies for true ratio scale measures [@10.2307/2246134;@10.1214/11-PS175].
+Second, sufficient range on the measure is required for the NBL to apply [i.e., range from $1-1000000$ ;@10.1198/tast.2009.0005].
+Third, these measures should not be subject to digit preferences, for example due to psychological preferences for rounded numbers.
+Fourth, any form of truncation undermines the NBL [@10.1515/9781400866595-011].
+Moreover, some research has even indicated humans might be sensitive to fabricating data that are in line with the NBL [@10.1080/02664760601004940;@Burns2009], immediately undermining the applicability of the NBL.
+Nonetheless, considering the four conditions for the NBL to apply, we preregistered that this method would not prove fruitful [@10.3897/rio.2.e8860].
+
+#### Terminal digit analysis
+
+Terminal digit analysis is based on the principle that the rightmost digit is the most random digit of a number, hence, is expected to be uniformly distributed under specific conditions [@10.1080/08989629508573866;@10.1080/03610919608813325].
+Terminal digit analysis is conducted with a $\chi^2$-test ($df=10-1$) on the digit occurrence counts (including zero), where the observed frequencies are compared with the expected uniform frequencies.
+Tthe rule of thumb outlined by @agresti2003categorical indicates at least 50 observations are required to provide a meaningful test of the terminal digit distribution ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
+Terminal digit analysis was developed during the Imanishi-Kari case by @10.1080/03610919608813325 [for a history of this decade long case, see @kevles2000baltimore].
+
+As an example, Figure `r fignr` depicts the digit counts for the first- through fifth digit of a random, normally distributed variable.
+The first- and second digit distributions are clearly non-uniform, whereas the third-, fourth-, and fifth digit distributions are uniformly distributed.
+
+```{r, echo=FALSE, fig.align="center", fig.asp=.5, out.width='100%', fig.cap="Illustration of how digit distributions evolve from first- through later digits.
+We sampled 100,000 values from a normal distribution, N~(0, 1.5), to create these digit distributions."}
+set.seed(1234)
+tmp1 <- 0
+tmp2 <- 1.5
+y <- data.frame(value = rnorm(100000, tmp1, tmp2))
+x <- abs(y$value)
+splitted <- strsplit(as.character(x), "")
+df1 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[1])))))
+df1 <- data.frame(digit = df1[!df1$digit == 0,])
+df2 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[3])))))
+df3 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[4])))))
+df4 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[5])))))
+df5 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[6])))))
+
+overall <- ggplot(y, aes(x = value)) +
+  geom_density(alpha = .3, fill = 'red') + 
+  xlab(sprintf("Value from N~(%s,%s)", tmp1, tmp2)) +
+  ylab("Density") +
+  theme(axis.title=element_text(size=10))
+
+p1 <- ggplot(df1, aes(x = digit)) +
+  geom_bar(alpha = .3, fill = 'blue') +
+  xlab("First digit") + 
+  ylab("Frequency") + 
+  theme(axis.title=element_text(size=10)) + 
+  scale_x_discrete(breaks = 0:10, limits = 0:9)
+
+p2 <- ggplot(df2, aes(x = digit)) +
+  geom_bar(alpha = .3, fill = 'blue') +
+  xlab("Second digit") + 
+  ylab("") +
+  theme(axis.title=element_text(size=10)) + 
+  scale_x_discrete(breaks = 0:10, limits = 0:9)
+
+p3 <- ggplot(df3, aes(x = digit)) +
+  geom_bar(alpha = .3, fill = 'blue') +
+  xlab("Third digit") + 
+  ylab("") +
+  theme(axis.title=element_text(size=10)) + 
+  scale_x_discrete(breaks = 0:10, limits = 0:9)
+
+p4 <- ggplot(df4, aes(x = digit)) +
+  geom_bar(alpha = .3, fill = 'blue') +
+  xlab("Fourth digit") + 
+  ylab("") +
+  theme(axis.title=element_text(size=10)) + 
+  scale_x_discrete(breaks = 0:10, limits = 0:9)
+
+p5 <- ggplot(df5, aes(x = digit)) +
+  geom_bar(alpha = .3, fill = 'blue') +
+  xlab("Fifth digit") + 
+  ylab("") +
+  theme(axis.title=element_text(size=10)) + 
+  scale_x_discrete(breaks = 0:10, limits = 0:9)
+
+# Plot
+empty <- ggplot() + theme(panel.background = element_rect(fill = 'white'))
+grid.arrange(p1, p2, p3, p4, p5, empty, empty, overall, empty, empty,
+             ncol = 5)
+
+fignr <- fignr + 1
+```
+
+As such, the rightmost digit can be expected to be uniformly distributed if sufficient precision is provided [@10.1080/08989629508573866].
+For our purposes, sufficient precision is determined as the terminal digit being at least the third leading digit [i.e., minimally 1.23 or 12.3 or 123].
 
@@
 
-# Study 1
+True data occur within a web of relations, which can be observed in genuine data and easily forgotten while fabricating data.
+The multivariate relations between different variables arise from stochastic processes and are not readily known, hence difficult to take into account when someone wants to fabricate data.
+As such, using these multivariate associations to detect anomalies from genuine data might prove valuable.
+
+The multivariate associations between different variables can be estimated from control data that are (assumably) genuine.
+For example, if the multivariate association between means (Ms) and standard deviations (SDs) is of interest, control data for that same measure can be collected from the literature, assuming the measure has been used in other studies.
+With these control data, a meta-analysis provides an overall estimate of the multivariate relation.
+
+```{r, echo=FALSE}
+cortmp <- NULL
+set.seed(1234)
+for(i in 1:100)
+{
+n     <- 100                    # length of vector
+rho   <- rnorm(1, .123, .1)                   # desired correlation = cos(angle)
+theta <- acos(rho)             # corresponding angle
+x1    <- rnorm(n, 75, 10)        # fixed given data
+x2    <- rnorm(n, 25, 4)      # new random data
+X     <- cbind(x1, x2)         # matrix
+Xctr  <- scale(X, center=TRUE, scale=FALSE)   # centered columns (mean 0)
+
+Id   <- diag(n)                               # identity matrix
+Q    <- qr.Q(qr(Xctr[ , 1, drop=FALSE]))      # QR-decomposition, just matrix Q
+P    <- tcrossprod(Q)          # = Q Q'       # projection onto space defined by x1
+x2o  <- (Id-P) %*% Xctr[ , 2]                 # x2ctr made orthogonal to x1ctr
+Xc2  <- cbind(Xctr[ , 1], x2o)                # bind to matrix
+Y    <- Xc2 %*% diag(1/sqrt(colSums(Xc2^2)))  # scale columns to length 1
+
+x <- Y[ , 2] + (1 / tan(theta)) * Y[ , 1]     # final new vector
+x <- x+25
+cortmp[i] <- cor(x1, x)                                    #
+}
+cortmp <- data.frame(cortmp)
+corfabno <- data.frame(cor = .2)
+corfab <- data.frame(cor = .5)
+```
+
+The multivariate relation from the genuine data is subsequently used to estimate how extreme the observed multivariate relation is.
+Consider the following fictitious example, regarding the multivariate association between Ms and SDs for a response latency task.
+Figure `r fignr` depicts a simulated distribution of the association between Ms and SDs from the literature.
+The observed relation between Ms and SDs from two papers we want to (fictitiously) screen are `r corfab$cor` and `r corfabno$cor`.
+As such, we immediately see in Figure `r fignr` that the former is flagged as being potentially anomalous (i.e., the red dot; two-tailed $p$-value $`r pnorm(corfab$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$ of the time), whereas the latter (blue dot) is not flagged ($p$-value: $`r pnorm(corfab$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$).
+
+```{r, echo=FALSE, out.width='100%', fig.cap="A fictitious distribution of observed association between Ms and SDs across 100 studies.
+The blue dot indicates the observed relation that is subject to screening for data anomalies."}
+ggplot(cortmp, aes(x = cortmp)) +
+  geom_density() +
+  xlim(-1, 1) + 
+  xlab("Association between M and SD") + 
+  ylab("Density") +
+  geom_point(data = corfabno, aes(x = cor, y = 0, col="Not flagged", size = 2)) +
+  geom_point(data = corfab, aes(x = cor, y = 0, col="Flagged", size = 2)) + 
+  scale_size(guide = 'none')
+```
+
+# Study 1 - detecting fabricated anchoring effects
 
@@
 
-<!-- # Study 2
+# Study 2 - detecting fabricated Stroop data
 
@@
 
-Twenty-one genuine datasets on the Stroop task were collected from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012}.
+We collected twenty-one genuine datasets on the Stroop task from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012].
 Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample [the original preregistration mentioned 20 datasets, accidentally overlooking the online sample; @10.3897/rio.2.e8860].
+Similar to Study 1, we assumed these data to be genuine due to the minimal individual gains for fabricating data and the transparency of the project.
 Using the original raw data and analysis script from ML3 ([https://osf.io/qs8tp/](https://osf.io/qs8tp/)), we computed the mean (M) and standard deviation (SD) for the participant's response latencies in both the within-subjects conditions of congruent trials and incongruent trials.
 These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure X).
-The Stroop effect was calculated as a $t$-test of the difference ($H_0:\mu=0$).
+The Stroop effect was calculated as a $t$-test of the difference between the congruent and incongruent conditions ($H_0:\mu=0$).
 
-```{r spreadsheet-study2, fig.cap="_Figure X._ Example of a filled in template spreadsheet used in the fabrication process for Study 2.
+```{r spreadsheet-study2, fig.cap="Example of a filled in template spreadsheet used in the fabrication process for Study 2.
 Respondents fabricated data in the yellow cells and green cells, which were used to compute the results of the hypothesis test of the condition effect.
@@
 
+To detect data
+
+```{r analyze data, echo = FALSE}
+if(!file.exists(sprintf('%sdata/study_02/ml3_fabricated_processed_collated.csv', x12)))
+{
+  ml3_dat <- read.csv(sprintf('%sdata/study_02/ml3_stroop.csv', x12))
+
+  df_ml3 <- NULL
+  # Compute the results for the ML3 data
+  for(i in 1:length(unique(ml3_dat$study_name)))
+  {
+    tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[i], ]
+
+    x <- t.test(tmp$StroopEffect, mu = 0, var.equal = TRUE)
+    es_r <- sqrt((x$statistic / x$parameter) / ((x$statistic / x$parameter) + 1))
+    # This is an object to simplify concatenation
+    binder <- data.frame(id = unique(ml3_dat$study_name)[i],
+                         type = 'ml3',
+                         benford_congr_m_p = digit_analysis(tmp$MC, type = 'benford')$pval,
+                         benford_congr_sd_p = digit_analysis(tmp$SDC, type = 'benford')$pval,
+                         benford_incongr_m_p = digit_analysis(tmp$MI, type = 'benford')$pval,
+                         benford_incongr_sd_p = digit_analysis(tmp$SDI, type = 'benford')$pval,
+                         terminal_congr_m_p = digit_analysis(tmp$MC, type = 'terminal')$pval,
+                         terminal_congr_sd_p = digit_analysis(tmp$SDC, type = 'terminal')$pval,
+                         terminal_incongr_m_p = digit_analysis(tmp$MI, type = 'terminal')$pval,
+                         terminal_incongr_sd_p = digit_analysis(tmp$SDI, type = 'terminal')$pval,
+                         std_congr_p = std_var(tmp$SDC, tmp$NC, iter = iter),
+                         std_incongr_p = std_var(tmp$SDI, tmp$NI, iter = iter),
+                         mult_m_sd_congr = cor(tmp$MC, tmp$SDC),
+                         mult_m_sd_incongr = cor(tmp$MI, tmp$SDI),
+                         mult_m_m_across = cor(tmp$MC, tmp$MI),
+                         mult_sd_sd_across = cor(tmp$SDC, tmp$SDI),
+                         p_f_mult_m_sd_congr = NA,
+                         p_f_mult_m_sd_incongr = NA,
+                         p_f_mult_m_m_across = NA,
+                         p_f_mult_sd_sd_across = NA,
+                         fisher_combination = NA,
+                         one_min_es_r = 1 - es_r,
+                         es_r = es_r)
+
+    df_ml3 <- rbind(df_ml3, binder)
+  }
+
+  # Meta-analyze the multivariate associations to acquire the parametric estimate
+  df_ml3$f_mult_m_sd_congr = atanh(df_ml3$mult_m_sd_congr)
+  df_ml3$f_mult_m_sd_incongr = atanh(df_ml3$mult_m_sd_incongr)
+  df_ml3$f_mult_m_m_across = atanh(df_ml3$mult_m_m_across)
+  df_ml3$f_mult_sd_sd_across = atanh(df_ml3$mult_sd_sd_across)
+
+  x <- metafor::rma(f_mult_m_sd_congr, sei = 1/sqrt(25-3), method = 'FE', data = df_ml3)
+  f_mult_m_sd_congr_mean <- x$b[1]
+  f_mult_m_sd_congr_std <- x$se[1]
+
+  x <- metafor::rma(f_mult_m_sd_incongr, sei = 1/sqrt(25-3), method = 'FE', data = df_ml3)
+  f_mult_m_sd_incongr_mean <- x$b[1]
+  f_mult_m_sd_incongr_std <- x$se[1]
+
+  x <- metafor::rma(f_mult_m_m_across, sei = 1/sqrt(25-3), method = 'FE', data = df_ml3)
+  f_mult_m_m_across_mean <- x$b[1]
+  f_mult_m_m_across_std <- x$se[1]
+
+  x <- metafor::rma(f_mult_sd_sd_across, sei = 1/sqrt(25-3), method = 'FE', data = df_ml3)
+  f_mult_sd_sd_across_mean <- x$b[1]
+  f_mult_sd_sd_across_std <- x$se[1]
+
+  # Compute the multivariate p-values for the ML data
+  z_val <- (df_ml3$f_mult_m_sd_congr - f_mult_m_sd_congr_mean) / f_mult_m_sd_congr_std
+  df_ml3$p_f_mult_m_sd_congr <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+  z_val <- (df_ml3$f_mult_m_sd_incongr - f_mult_m_sd_incongr_mean) / f_mult_m_sd_incongr_std
+  df_ml3$p_f_mult_m_sd_incongr <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+  z_val <- (df_ml3$f_mult_m_m_across - f_mult_m_m_across_mean) / f_mult_m_m_across_std
+  df_ml3$p_f_mult_m_m_across <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+  z_val <- (df_ml3$f_mult_sd_sd_across - f_mult_sd_sd_across_mean) / f_mult_sd_sd_across_std
+  df_ml3$p_f_mult_sd_sd_across <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+  # Combining the terminal digit analysis, variance analysis and the multivariate associations
+  # Note that this function adds .0000001 to zero values to prevent -Inf values (log(0) = -Inf)
+  # df_ml3$fisher_combination <- apply(df_ml3[,c(6:11, 16:19)], 1, function(x) fisher_method(x)[,3])
+
+  df_ml3$fisher_combination <- apply(cbind(df_ml3$terminal_congr_m_p,
+      df_ml3$terminal_congr_sd_p,
+      df_ml3$terminal_incongr_m_p,
+      df_ml3$terminal_incongr_sd_p,
+      df_ml3$std_congr_p,
+      df_ml3$std_incongr_p,
+      df_ml3$p_f_mult_m_sd_congr,
+      df_ml3$p_f_mult_m_sd_incongr,
+      df_ml3$p_f_mult_m_m_across,
+      df_ml3$p_f_mult_sd_sd_across), 1, function(x) fisher_method(x)[,3])
+
+  # Dropping the redundant variables
+  # If code above changes this will break
+  df_ml3 <- df_ml3[,1:23]
+
+  # The responses from the fabrication study
+  responses <- list.files(sprintf('%sdata/study_02/responses', x12))
+  df_fab <- NULL
+
+  for (response in responses)
+  {
+    fab_dat <- read.table(sprintf('%sdata/study_02/responses/%s', x12, response),
+                          sep = '\t', header = TRUE)
+    # For clarity sake
+    names(fab_dat) <- c('id',
+                        'mean_congruent',
+                        'sd_congruent',
+                        'congruent_trials',
+                        'mean_incongruent',
+                        'sd_incongruent',
+                        'incongruent_trials')
+    # Eliminate overprecision in reporting
+    # Instructed participants to fabricate milliseconds and 123.45 is result of copy-paste
+    # Spreadsheet automatically removed this, but by copy-pasting this was undone by PP
+    fab_dat <- as.data.frame(apply(fab_dat, 2, function(x) round(x, 0)))
+
+    # Stroop effect size calculation
+    sdpooled <- sqrt(((fab_dat$congruent_trials - 1) * fab_dat$sd_congruent^2 + (fab_dat$incongruent_trials - 1) * fab_dat$sd_incongruent^2) / ((fab_dat$congruent_trials + fab_dat$incongruent_trials - 2)))
+    stroopeffect <- (fab_dat$mean_incongruent - fab_dat$mean_congruent) / sdpooled
+    x <- t.test(stroopeffect, mu = 0, var.equal = TRUE)
+    es_r <- sqrt((x$statistic / x$parameter) / ((x$statistic / x$parameter) + 1))
+
+    # Compute the multivariate correlation p-values for the fab data
+    f_mult_m_sd_congr <- atanh(cor(fab_dat$mean_congruent, fab_dat$sd_congruent))
+    f_mult_m_sd_incongr <- atanh(cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent))
+    f_mult_m_m_across <- atanh(cor(fab_dat$mean_congruent, fab_dat$mean_incongruent))
+    f_mult_sd_sd_across <- atanh(cor(fab_dat$sd_congruent, fab_dat$sd_incongruent))
+
+    z_val <- (f_mult_m_sd_congr - f_mult_m_sd_congr_mean) / f_mult_m_sd_congr_std
+    p_f_mult_m_sd_congr <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+    z_val <- (f_mult_m_sd_incongr - f_mult_m_sd_incongr_mean) / f_mult_m_sd_incongr_std
+    p_f_mult_m_sd_incongr <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+    z_val <- (f_mult_m_m_across - f_mult_m_m_across_mean) / f_mult_m_m_across_std
+    p_f_mult_m_m_across <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+    z_val <- (f_mult_sd_sd_across - f_mult_sd_sd_across_mean) / f_mult_sd_sd_across_std
+    p_f_mult_sd_sd_across <- 2 * pnorm(q = abs(z_val), mean = 0, sd = 1, lower = FALSE)
+
+    binder <- data.frame(id = response,
+                         type = 'fabricated',
+                         benford_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'benford')$pval,
+                         benford_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'benford')$pval,
+                         benford_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'benford')$pval,
+                         benford_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'benford')$pval,
+                         terminal_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'terminal')$pval,
+                         terminal_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'terminal')$pval,
+                         terminal_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'terminal')$pval,
+                         terminal_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'terminal')$pval,
+                         std_congr_p = std_var(fab_dat$sd_congruent, fab_dat$congruent_trials, iter = iter),
+                         std_incongr_p = std_var(fab_dat$sd_incongruent, fab_dat$incongruent_trials, iter = iter),
+                         mult_m_sd_congr = cor(fab_dat$mean_congruent, fab_dat$sd_congruent),
+                         mult_m_sd_incongr = cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent),
+                         mult_m_m_across = cor(fab_dat$mean_congruent, fab_dat$mean_incongruent),
+                         mult_sd_sd_across = cor(fab_dat$sd_congruent, fab_dat$sd_incongruent),
+                         p_f_mult_m_sd_congr = p_f_mult_m_sd_congr,
+                         p_f_mult_m_sd_incongr = p_f_mult_m_sd_incongr,
+                         p_f_mult_m_m_across = p_f_mult_m_m_across,
+                         p_f_mult_sd_sd_across = p_f_mult_sd_sd_across,
+                         fisher_combination = NA,
+                         one_min_es_r = 1 - es_r,
+                         es_r = es_r)
+
+    binder$fisher_combination <- fisher_method(c(binder$terminal_congr_m_p,
+                                                 binder$terminal_congr_sd_p,
+                                                 binder$terminal_incongr_m_p,
+                                                 binder$terminal_incongr_sd_p,
+                                                 binder$std_congr_p,
+                                                 binder$std_incongr_p,
+                                                 binder$p_f_mult_m_sd_congr,
+                                                 binder$p_f_mult_m_sd_incongr,
+                                                 binder$p_f_mult_m_m_across,
+                                                 binder$p_f_mult_sd_sd_across))[,3]
+
+    df_fab <- rbind(df_fab, binder)
+    # print(response)
+  }
+
+  write.csv(rbind(df_ml3, df_fab), sprintf('%sdata/study_02/ml3_fabricated_processed_collated.csv', x12), row.names = FALSE)
+}
+```
+
 ## Results
+
+```{r, echo = FALSE}
+dat <- read.csv(sprintf('%sdata/study_02/ml3_fabricated_processed_collated.csv', x12))
+
+tp <- matrix(NA, ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+fp <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+fn <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+tn <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+
+temp <- names(dat)[grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")]
+
+j <- 1
+
+for (variables in which(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")))
+{
+  i <- 1
+
+  for (threshold in seq(0, 1, .01))
+  {
+    tp[i,j] <- sum(dat[, variables] <= threshold & dat$type == 'fabricated', na.rm = TRUE)
+    fp[i,j] <- sum(dat[, variables] <= threshold & dat$type == 'ml3', na.rm = TRUE)
+    fn[i,j] <- sum(dat[, variables] > threshold & dat$type == 'fabricated', na.rm = TRUE)
+    tn[i,j] <- sum(dat[, variables] > threshold & dat$type == 'ml3', na.rm = TRUE)
+
+    i <- i + 1
+  }
+
+  j <- j + 1
+}
+
+# loop through matrix for proper comps
+
+tpr <- matrix(NA, ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+fpr <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+fnr <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+tnr <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+
+ppv <- matrix(NA, ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+fdr <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+npv <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+false_or <- matrix(NA,ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
+
+for (i in 1:sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")))
+{
+  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
+  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
+  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
+  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])
+
+  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
+  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
+  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
+  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
+}
+fpr <- as.data.frame(fpr)
+tpr <- as.data.frame(tpr)
+fnr <- as.data.frame(fnr)
+tnr <- as.data.frame(tnr)
+
+ppv <- as.data.frame(ppv)
+fdr <- as.data.frame(fdr)
+npv <- as.data.frame(npv)
+false_or <- as.data.frame(false_or)
+
+names(fpr) <- temp
+names(tpr) <- temp
+names(fnr) <- temp
+names(tnr) <- temp
+
+names(ppv) <- temp
+names(fdr) <- temp
+names(npv) <- temp
+names(false_or) <- temp
+
+height = (tpr[-1, ] + tpr[-dim(tpr)[1], ])/2
+width = apply(fpr, 2, diff) # = diff(rev(omspec))
+AUC_res <- apply(height * width, 2, sum)
+
+temp <- names(dat)[grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")]
+Method <- c("NBL, congruent means",
+            "NBL, congruent SDs",
+            "NBL, incongruent means",
+            "NBL, incongruent SDs",
+            "Terminal digit analysis, congruent means",
+            "Terminal digit analysis, congruent SDs",
+            "Terminal digit analysis, incongruent means",
+            "Terminal digit analysis, incongruent SDs",
+            "Variance analysis, congruent condition",
+            "Variance analysis, incongruent condition",
+            "Multivariate association means and SDs, congruent condition",
+            "Multivariate association means and SDs, incongruent condition",
+            "Multivariate association means, across conditions",
+            "Multivariate association SDs, across conditions",
+            "Fisher combination of terminal, variance, and multivariate",
+            "Effect size ($1-r$)")
+
+df <- data.frame(Method = Method,
+                 AUROC = AUC_res)
+```
+
+### Performance of NBL to detect data fabrication
+
+```{r table_nbl, echo=FALSE}
+knitr::kable(df[1:4,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using the Newcomb-Benford law (NBL) to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+```{r}
+ggplot(dat, aes(x = benford_congr_m_p)) + geom_density(aes(fill = type)) + xlim(0, .00001)
+```
+
+### Performance of terminal digit analysis to detect data fabrication
+
+```{r table_terminal, echo=FALSE}
+knitr::kable(df[5:8,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using terminal digit analysis to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of variance analysis to detect data fabrication
+
+```{r table_variance_raw, echo=FALSE}
+knitr::kable(df[9:10,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using variance analysis to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of multivariate associations to detect data fabrication
+
+```{r table_multi, echo=FALSE}
+knitr::kable(df[11:14,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using multivariate associations to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of combining
+
+```{r table_fisher_raw, echo=FALSE}
+knitr::kable(df[15,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using variance analysis to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+### Performance of effect sizes
+
+```{r table_es_raw, echo=FALSE}
+knitr::kable(df[16,], row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using variance analysis to detect data fabrication, depicted with the AUROC-value.")
+tabnr <- tabnr + 1
+```
+
+```{r, echo=FALSE, out.width='100%', fig.cap="The effect size distributions from Many Labs 3 and those fabricated by the participants"}
+ggplot(dat, aes(x = es_r)) + geom_density(aes(fill = type), alpha = .3)
+# > min(dat$es_r[dat$type == 'fabricated'])
+# [1] 0.294654
+# > max(dat$es_r[dat$type == 'ml3'])
+# [1] 0.3164714
+```
 
@@
 
-# General discussion -->
+<!-- # General discussion -->
+
+<!-- The effectiveness of detection mechanisms and their consequences, hence their expected deterrence, is exacerbated in the digital age by the availability of public discussion platforms such as [PubPeer (https://pubpeer.com)](https://pubpeer.com).
+-->
+<!-- PubPeer serves as an "online journal club" where anyone can discuss articles.
+Authors are notified when someone leaves a response, providing them with the possibility to respond.
+Such a platform allows for public discussion of the paper, including discussion of reanalyses, methodology, availability of materials, etc.
+When detection mechanisms are freely available to use, they can lead to (a surge of) comments when applied by users.
+Recently, in 2016, one user (the main author of this paper) used `statcheck` software to report potential statistical reporting inconsistencies for 50,000 psychology articles, which led to a large discussion about (automated) online comments [@10.1038/540151a].
+The impact of such new possibilities is not to be underestimated, although its potential to constructively contribute to the scientific discussion should also not be [@10.1038/540007b].
+Nonetheless, the `statcheck` software was well validated prior to this application [@10.3758/s13428-015-0664-2] and the same principle applies to the application of statistical methods to detect (potential) data fabrication.
+-->
+
+<!-- ## `ddfab` package -->
+
+<!-- All the methods used in this paper are also implemented in the open source R package `ddfab`. -->
+
+<!-- However, these results indicate that application of these methods should be informed and as a screening method. -->
+
+<!-- ## Study fallout -->
+
+<!-- While conducting Study 2 reported in this paper, there was considerable criticism from several parties. -->
+
+<!-- We  -->
 

### 2017-07-03 functions/digit_analysis.R

@@ -27,6 +27,8 @@ digit_analysis <- function(
   {
     df <- 10 - 1 
     
+    # x <- decimator(x)
+    
     matrix_of_digits <- apply(
       t(x),
       1,
@@ -128,3 +130,10 @@ expected_digit_counter <- function(
   
   return(counts)
 }
+
+# decimator <- function(x)
+# {
+#   
+#   
+#   return(decimated)
+# }

### 2017-07-03 functions/fisher_method.R

@@ -1,0 +1,14 @@
+fisher_method <- function(pval,
+                          adjustment = .0000001)
+{
+  if (adjustment > 0)
+  {
+    pval <- ifelse(pval == 0, pval + adjustment, pval)
+  }
+  
+  fish <- -2 * sum(log(pval))
+  df_fish <- length(pval) * 2
+  p_fish <- pchisq(q = fish, df = df_fish, lower.tail = FALSE)
+  
+  return(cbind(fish, df_fish, p_fish))
+}

### 2017-07-24 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts.
-Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred equally across fabrication, falsification, and plagiarism.
-Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
+Deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
 This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
-In the last decade, detecting image manipulation has become one of the few forms of detecting data fabrication .
+In the last decade, detecting image manipulation has become one of the few forms of detecting data fabrication.
 The Journal of Cell Biology and EMBO scan each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh;@10.1038/546575a], which greatly increases the risk of detecting (blatant) image manipulation.
@@
 
-Statistical methods provide one way to improve detection of data fabrication in empirical research.
+Statistical methods provide another way to improve detection of data fabrication in empirical research.
 Humans are notoriously bad at understanding and estimating probabilities [e.g., @10.1126/science.185.4157.1124;@10.1037/h0031322], which could manifest itself in the fundamentally probabilistic data they try to fabricate.
@@
 Cases such as Stapel, Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
-Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place [e.g., late at night when no one is around; @stapel_book].
-However, trustworthiness of these accounts can be called into question.
+Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process.
 Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually to detect data fabrication.

### 2017-07-25 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 Other statistical methods to detect data fabrication are addressed in the theoretical framework.
-.
 
@@
 For example, given the frequent misinterpretation of $p$-values [@10.3758/BF03213921;@10.1007/s11336-015-9446-0;@10.7326/0003-4819-130-12-199906150-00008], it is possible that the same underlying misinterpration will manifest itself in fabricated data.
-More specifically, given the frequent misinterpretation of $p$-valuesas the probability of an effect [@10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
+More specifically, given the frequent misinterpretation of $p$-values as the probability of an effect [@10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
 
@@
 This threshold is added and can be set to any value between zero and one.
-Upon writing this paper, it became clear to us that this is reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
+Upon writing this paper, it became clear to us that this reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
 
@@
 Terminal digit analysis is conducted with a $\chi^2$-test ($df=10-1$) on the digit occurrence counts (including zero), where the observed frequencies are compared with the expected uniform frequencies.
-Tthe rule of thumb outlined by @agresti2003categorical indicates at least 50 observations are required to provide a meaningful test of the terminal digit distribution ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
+The rule of thumb outlined by @agresti2003categorical indicates at least 50 observations are required to provide a meaningful test of the terminal digit distribution ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
 Terminal digit analysis was developed during the Imanishi-Kari case by @10.1080/03610919608813325 [for a history of this decade long case, see @kevles2000baltimore].
@@
 The dependent variable in the Stroop task is the response latency (in this study milliseconds are used).
-Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serves as the raw data.
+Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serve as the raw data.
 The Stroop effect typically is computed as the difference in mean response latencies between the congruent and incongruent conditions.

### 2017-07-27 submission/manuscript.Rmd
Revisions in progress

--- 2017-07-03 submission/manuscript.Rmd
@@
 ---
-title: "Ecological performance of detecting data fabrication"
+title: "Automated detection of data fabrication using statistical tools"
 author: "Chris HJ Hartgerink, Jan G Voelkel, Jelte M Wicherts, Marcel ALM van Assen"
@@
 ---
+
+# Abstract
+
+PLACEHOLDER
+
+## Keywords
+
+PLACEHOLDER
 
@@
 suppressPackageStartupMessages(library(car))
-suppressPackageStartupMessages(if (!require(effects)){install.packages('effects', repos = 'http://cran.us.r-project.org')})
-suppressPackageStartupMessages(library(effects))
 suppressPackageStartupMessages(if (!require(lsr)){install.packages('lsr', repos = 'http://cran.us.r-project.org')})
@@
 
+# Introduction
+
 Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP).
@@
 These are just a few examples of misconduct cases in the last decade.
-Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once [@10.1371/journal.pone.0005738] and this is likely to be an underestimate due to socially desirable responses.
-The detection rate of data fabrication is likely to be even lower; for example, only around a dozen cases are discovered in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
-At best, this amounts to a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
+Overall, an estimated 2\% of all scholars have admitted to falsifying or fabricating research results at least once [@10.1371/journal.pone.0005738], which is likely to be an underestimate due to socially desirable responses.
+The detection rate of data fabrication is likely to be even lower; for example, only around a dozen cases become public in the United States and the Netherlands, despite covering several hundreds of thousands of researchers.
+At best, this suggests a detection rate far below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.
 
 In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such harmful attempts. 
-Although deterrence theory dates back to the middle of the 17th century [@leviathan], its implementation has not occurred equally across fabrication, falsification, and plagiarism.
-Basically, deterrence theory stipulates that with increased risk of detection, the utility of scientific misconduct (for this context) will decrease and therefore fewer people will engage in such behaviors.
-This principle of deterrence has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
-In the last decade, detecting image manipulation has become one of the few forms of detecting data fabrication .
-The Journal of Cell Biology and EMBO scan each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh;@10.1038/546575a], which greatly increases the risk of detecting (blatant) image manipulation.
+This idea is based on deterrence theory [@leviathan], which stipulates that with increased risk of detection, the utility of scientific misconduct will decrease and therefore fewer people will engage in such behaviors.
+Implementation of deterrence has not occurred equally across fabrication, falsification, and plagiarism.
+For plagiarism, it has been implemented with plagiarism scanners, a development that already started a long time ago [e.g., @10.1109/13.28038].
+For data fabrication, detecting image manipulation has increasingly become possible and implemented.
+The Journal of Cell Biology and the EMBO journal scan each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh;@10.1038/546575a], which greatly increases the risk of detecting (blatant) image manipulation.
 More recently, algorithms have been developed to automate the scanning of images for (subtle) manipulations [@10.1007/s11948-016-9841-7].
-These developments in detecting image manipulation have increased detection risk during the pre-publication and post-publication phase by improving detection mechanisms and increasing the understanding of how images might be manipulated.
+These developments in detecting image manipulation have increased detection risk during the pre-publication and post-publication phase and increase the understanding of how images might be manipulated.
 Moreover, their application also helps researchers systematically evaluate research articles to estimate the extent of the problem of image manipulation [4\% of all papers are estimated to contain manipulated images, @10.1128/mBio.00809-16].
@@
 Statistical methods provide one way to improve detection of data fabrication in empirical research.
-Humans are notoriously bad at understanding and estimating probabilities [e.g., @10.1126/science.185.4157.1124;@10.1037/h0031322], which could manifest itself in the fundamentally probabilistic data they try to fabricate.
-When data are fabricated, probabilistic principles are easily violated if forgotten at the univariate level, bivariate level, trivatiate level, or beyond [@Haldane1948-nm].
+Humans are notoriously bad at understanding and estimating randomness [@10.1126/science.185.4157.1124;@10.1037/h0031322;@10.1037/1082-989X.5.2.241], which could manifest itself in the fundamentally probabilistic data they try to fabricate.
+When data are fabricated, principles of statistics and randomness are easily violated at the univariate level, bivariate level, trivatiate level, or beyond [@Haldane1948-nm].
 Based on this idea, statistical methods that investigate whether the reported data are feasible under the theoretically probabilistic processes can be used to detect potential data fabrication.
@@
 ```{r echo=FALSE}
+m <- 50
+sd <- 10
+n <- 100
+
 set.seed(1234)
-ex1 <- t(replicate(n = 10, expr = table(sample(x = c("M", "F"), size = 100, replace = TRUE))))
-ex1p <- pchisq(apply(ex1, 1, function(x) sum((x-50)^2/50)), df = 1, lower.tail = FALSE)
+x1_1 <- replicate(n = 10, expr = rnorm(n, m, sd))
+x1_2 <- replicate(n = 10, expr = rnorm(n, m, sd))
+
+ex1_1em <- apply(x1_1, 2, mean)
+ex1_1esd <- apply(x1_1, 2, sd)
+ex1_1cm <- apply(x1_2, 2, mean)
+ex1_1csd <- apply(x1_2, 2, sd)
+ex1_1tp <- NULL
+for (i in 1:dim(x1_1)[2]) ex1_1tp[i] <- t.test(x = x1_1[,i], y = x1_2[,i], var.equal=TRUE)$p.value
+ex1_1tp <- unlist(ex1_1tp)
+
 set.seed(1234)
-ex2_1 <- 50 + sample(x = -1:1, size = 10, replace = TRUE)
-ex2_2 <- 100 - ex2_1
-ex2 <- cbind(ex2_1, ex2_2)
-ex2p <- pchisq(apply(ex2, 1, function(x) sum((x-50)^2/50)), df = 1, lower.tail = FALSE)
+x2_1em <- replicate(n = 10, expr = m + runif(1, 0, 20))
+x2_2cm <- replicate(n = 10, expr = m + runif(1, 0, 20))
+x2_1esd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))
+x2_2csd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))
+
+sdpooled <- ((n - 1) * x2_1esd^2 + (n - 1) * x2_2csd^2)/(n * 2 - 2)
+tval <- (x2_1em - x2_2cm) / sdpooled
+ex2_1tp <- pt(abs(tval), n * 2 - 2, lower.tail = FALSE) * 2
+
+# Just saving for later use in theory section
+# set.seed(1234)
+# std_var(n = rep(100, length(x2_1esd) * 2), sds = c(x2_1esd, x2_2csd), iter = 10000)
 
 df <- data.frame(study = sprintf("Study %s", 1:10),
-                 ex1,
-                 ex1p,
-                 ex2,
-                 ex2p)
+         sprintf("%s (%s)", round(ex1_1em, 3), round(ex1_1esd, 3)),
+         sprintf("%s (%s)", round(ex1_1cm, 3), round(ex1_1csd, 3)),
+         ex1_1tp,
+         sprintf("%s (%s)", round(x2_1em, 3), round(x2_1esd, 3)),
+         sprintf("%s (%s)", round(x2_2cm, 3), round(x2_2csd, 3)),
+         ex2_1tp)
 names(df) <- c("Study",
-               "Experimental [S1]",
-               "Control [S1]",
+        "$M_E$ ($SD_E$) [S1]",
+        "$M_C$ ($SD_C$) [S1]",
         "P-value [S1]",
-               "Experimental [S2]",
-               "Control [S2]",
+        "$M_E$ ($SD_E$) [S2]",
+        "$M_C$ ($SD_C$) [S2]",
         "P-value [S2]")
@@
 
-The application of such statistical methods to detect data fabrication has occurred in several cases of scientific misconduct in recent years and has potential for future application beyond these specific cases.
-For example, problems in papers by Fuji were highlighted with statistical methods [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], resulting in 183 retractions [@oransky2015].
-This method works as follows: in true randomized clinical trials (RCTs), baseline measurements should be statistically equal across groups.
-As such, the $p$-values for group comparisons would be expected to be uniformly distributed because the null hypothesis of equal groups is true by definition of the design.
+Statistical methods to detect data fabrication have been applied in several cases of scientific misconduct in recent years and has potential for future application beyond these specific cases. 
+For example, excessive consistency in papers by Fuji were highlighted with statistical methods [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], resulting in 183 retractions [@oransky2015].
+Carlisle's method works as follows: in true randomized clinical trials (RCTs) baseline measurements should be identically distributed across groups.
+As such, the $p$-values for group comparisons would be expected to be uniformly distributed because the null hypothesis of identical distributions across groups is true by definition of the randomized design.
 In the Fuji papers, group comparisons showed excessive consistency, resulting primarily in high $p$-values (e.g., .99, .95) and a high mean $p$-value across the comparisons, where a mean $p$-value of .5 is expected.
-As an illustration, see Table `r tabnr`, which depicts the assignment of participants to the experimental or control condition for a true randomized design (Set 1) or for a fabricated design (Set 2).
-The mean $p$-value for the true randomized design Set 1 is `r round(mean(ex1p), 3)`, whereas the fabricated Set 2 has mean $p$-value `r round(mean(ex2p), 3)`.
-Other statistical methods to detect data fabrication are addressed in the theoretical framework.
+As an illustration, see Table `r tabnr`, which depicts 10 hypothetical studies containing 100 participants per condition, for true randomized designs (Set 1) or for fabricated designs (Set 2).
+The mean $p$-value for the true randomized design Set 1 is `r round(mean(ex1_1tp), 3)`, whereas the fabricated Set 2 has mean $p$-value `r round(mean(ex2_1tp), 3)`.
+Other statistical methods to detect data fabrication are addressed in the theoretical sections.
 .
@@
 ```{r table_excess, echo = FALSE}
-knitr::kable(df, digits = 3, caption = "Examples of participant counts for genuine- and fabricated randomized clinical trials.
+knitr::kable(df, digits = 3, caption = "Examples of means and standard deviations for a continuous outcome in genuine- and fabricated randomized clinical trials.
 Set 1 (S1) is randomly generated data under the null hypothesis of random assignment (assumed to be the genuine process), whereas Set 2 (S2) is generated under excessive consistency with equal groups.
-Each trial contains 100 participants.
-The $p$-values ")
-
-tabnr <- tabnr + 1
-```
-
-Such statistical methods to detect data anomalies, although developed to quantify suspicions in a specific paper, could be applied to screen multiple papers.
+Each trial condition contains 100 participants.
+The $p$-values are the result of independent $t$-tests comparing the experimental and control conditions within each respective set.")
+```
+
+Statistical methods to detect data fabrication, although developed to quantify suspicions in a specific paper, could be applied to screen multiple papers.
 The application of such methods can be (semi-)automated if data are available in a machine-readable format that one of the statistical methods can be applied to.
@@
 
-Nonetheless, prior to applying statistical methods to flag potentially problematic results, investigating whether such methods function well enough in detecting problems is required for responsible application.
+Nonetheless, prior to applying statistical methods to flag potentially fabricated results, investigating whether such methods perform well enough in detecting data fabrication is required for responsible application.
 We hardly know how researchers might go about fabricating data.
-Cases such as Stapel, Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, systematically biased.
+Cases such as Stapel, Fuji, Smeesters, and Sanna provide some insights, but are highly pre-selected (i.e., those who got caught/confessed) and as such, may be systematically biased.
 Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place [e.g., late at night when no one is around; @stapel_book].
-However, trustworthiness of these accounts can be called into question.
-Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually to detect data fabrication.
+Additionally, the performance of methods to detect data fabrication is highly dependent on the unknown prevalence of data fabrication and the power to actually detect data fabrication.
 Given that we do not know how researchers might fabricate data, the diagnosticity of these methods cannot realistically be assessed.
 
-Throughout this paper, we inspect statistical methods to detect potential data fabrication that can be applied to (1) summary results or (2) raw data. 
+Throughout this paper, we inspect statistical methods to detect potential data fabrication that can be applied to summary statistics (Study 1) or raw data (Study 2). 
 Even though structure and contents of data can look different depending on the structure of a study and the measures, there are certain common characteristics of empirical results and the underlying raw data that can be inspected.
-For example, summary results frequently include means, standard deviations, test-statistics, and $p$-values.
+For example, summary statistics frequently include means, standard deviations, test-statistics, and $p$-values.
 Raw data frequently contain at least some variables measured at a interval- or ratio scale [@10.1126/science.103.2684.677].
-Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results to screen for problematic data.
-We review the theoretical framework of the specific methods we apply throughout this paper, but these are not exhaustive of all methods available to test for potential problems in empirical data [see also @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
+Such common characteristics allow for the development of generic statistical methods that can be applied across a varied set of results to screen for fabricated data.
+For each study, we review the theory of the specific methods we apply.
+However, the reviewed methods are not exhaustive of all methods available to test for potential data fabrication in empirical data [see also, @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers].
 
@@
 
-In the current paper, we differentiate between statistical methods to detect potential data fabrication based on reported data (i.e., summary results) or raw data.
-For summary results, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data anomalies.
-$P$-value analysis can be applied whenever sufficient nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size can be computed [e.g., an APA reported $t$- or $F$-statistic;@10.1525/collabra.71].
-For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis), and multivariate associations as potential ways to detect data anomalies.
-Digit analyses can be applied when ratio scale measures are present in the raw data; multivariate associations can be applied whenever there is a multivariate relation in the raw data that can be computed and control data is available from the literature.
-
-## Detecting data fabrication in summary results
+In the current paper, we differentiate between statistical methods to detect potential data fabrication based on reported summary statistics or raw data.
+For summary statistics, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data fabrication.
+$P$-value analysis can be applied whenever sufficient nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size is reported or can be computed [e.g., an APA reported t- or F-statistic;@10.1525/collabra.71].
+For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis) and multivariate associations as potential ways to detect data fabrication.
+Both types of digit analyses can be applied when ratio scale measures are present in the raw data and only terminal digit analysis can be applied when there are continuous measures.
+Multivariate associations can be investigated whenever there are two or more variables and data on that same relation is available from (assumably) genuine data sources.
+
+## Detecting data fabrication in summary statistics
 
@@
 The distribution of a $p$-value is uniform if the null hypothesis is true and right-skewed if the alternative hypothesis is true [@fisher1925].
-One $p$-value is the result of the population effect size, the precision of the estimate, and the observed effect size, whose properties carry over to a set of $p$-values if those $p$-values are independent.
+The distribution of one $p$-value is the result of the population effect size, the precision of the estimate, and the observed effect size, whose properties carry over to a set of independent $p$-values if those $p$-values are independent.
 As such, the $p$-value distribution of a set of $p$-values is uniform when the null hypothesis is true, or right-skewed when the alternative hypothesis is true.
 
-When the $p$-value distribution is not uniform nor right-skewed, it can indicate potential data anomalies.
-For example, a distribution might show a bump when excessive $p$-hacking occurs that seeks barely significant results [e.g., Figure 1 in @10.7717/peerj.1935].
-However, data fabricators might create other non-uniform or non-right-skewed distributions, failing to take into account the theoretical boundary conditions.
-For example, given the frequent misinterpretation of $p$-values [@10.3758/BF03213921;@10.1007/s11336-015-9446-0;@10.7326/0003-4819-130-12-199906150-00008], it is possible that the same underlying misinterpration will manifest itself in fabricated data.
-More specifically, given the frequent misinterpretation of $p$-valuesas the probability of an effect [@10.1053/j.seminhematol.2008.04.003;@10.1136/bmj.311.7003.485], researchers who fabricate nonsignificant data might forget to fabricate a uniform $p$-value distribution and generate only large $p$-values when fabricating nonsignificant results.
-
-In order to test whether observed $p$-values are anomalous, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
-This adaptation is a simple reversal of the original Fisher method [@fisher1925], which was introduced as a meta-analytic test for the presence of an effect.
+When a $p$-value distribution of independent $p$-values is not uniform or right-skewed, as would be theoretically expected, it can indicate potential data fabrication.
+For example, in the Fuji case, supposedly identically distributed groups were fabricated.
+However, this resulted in excessively large $p$-values and ultimately the identification of potential data fabrication by @10.1111/j.1365-2044.2012.07128.x.
+Our illustration in Table `r tabnr` also shows the difference between expected data under the null distribution (Set 1) and what might result from excessively consistent and fabricated data (Set 2).
+More specifically, the expected value of a uniform $p$-value distribution is .5, but the fabricated data from our illustration result in a mean $p$-value of `r round(mean(ex2_1tp), 3)`.
+
+In order to test whether the distribution of nonsignificant and independent $p$-values might be fabricated, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
+This adaptation is a reversal of the original Fisher method [@fisher1925], which was introduced as a meta-analytic test for the presence of an effect.
 This test is computed as
-$$
+$$F
 \chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
 $$
-where it tests for right-skew (i.e., more smaller $p$-values than larger $p$-values) across the $k$ number of $p$-values. Reversing the Fisher method results in 
+where it tests for more smaller $p$-values than larger $p$-values across the $k$ number of $p$-values.
+Reversing the original Fisher method, which tests for right-skew, into a Fisher method that tests for left-skew results in
 $$
@@
 $$
-where it now tests for left-skew (i.e., more larger $p$-values than smaller $p$-values) across the $k$ number of $p$-values that falls above the threshold $t$.
-This threshold is added and can be set to any value between zero and one.
-Upon writing this paper, it became clear to us that this is reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
-
-Despite this test being useful for detecting data anomalies in nonsignificant $p$-values, one exception should be taken into account: wrongly specified one-tailed tests.
+where it now tests for more larger $p$-values than smaller $p$-values across the $k$ number of $p$-values that fall above the threshold $t$.
+When the threshold is set to zero, it selects all $p$-values, but when this $t>0$ the remaining $p$-values are rescaled to fit the original 0-1 range (i.e., by dividing by $1-t$).
+Upon writing this paper, it became clear to us that this reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], which we had not realized before.
+
+```{r, echo = FALSE}
+threshold <- .05
+genuine_p <- ex1_1tp[ex1_1tp > threshold]
+fab_p <- ex2_1tp[ex2_1tp > threshold]
+genuine_chi <- -2 * sum(log(1 - ((genuine_p - threshold) / (1 - threshold))))
+fab_chi <- -2 * sum(log(1 - ((fab_p - threshold) / (1 - threshold))))
+genuine_chi_p <- pchisq(q = genuine_chi, df = 2 * length(genuine_p), lower.tail = FALSE)
+fab_chi_p <- pchisq(q = fab_chi, df = 2 * length(fab_p), lower.tail = FALSE)
+x <- c(.21, -.08, -.37, -.08, .32)
+pval <- pnorm(abs(x), 0, 1, lower.tail = FALSE) * 2
+pval <- pval[pval > threshold]
+chi <- -2 * sum(log(1 - ((pval - threshold) / (1 - threshold))))
+p_chi <- pchisq(q = chi, df = 2 * length(pval), lower.tail = FALSE)
+```
+
+As an example, we apply the reversed Fisher method to both the genuine- and fabricated results from our illustration in Table `r tabnr` and data from the Fuji case.
+Using the threshold $t=`r threshold`$ to only select the nonsignificant results, we retain $k=`r length(genuine_p)`$ genuine $p$-values and $k=`r length(fab_p)`$ fabricated $p$-values.
+Calculating the $\chi^2$ value for sets of $k$ nonsigificant $p$-values results in a $\chi^2=`r round(genuine_chi, 3)`$ for the $p$-values resulting from the genuine data and $\chi^2=`r round(fab_chi, 3)`$ for the $p$-values resulting from the fabricated data, with $p$-values `r round(genuine_chi_p, 3)` and `r round(fab_chi_p, 3)` respectively, using $2k$ as the degrees of freedom of the $\chi^2$-test.
+Another example, directly from the Fuji case [@10.1111/j.1365-2044.2012.07128.x], anecdotally illustrates that fabricated data can result in significant findings with the reversed Fisher method.
+$p$-values from five independent comparisons for one dependent measure [fentanyl dose, as extracted from Table 3 in @10.1111/j.1365-2044.2012.07128.x] show excessively high $p$-values, $\chi^2_{`r length(pval) * 2`}=`r round(chi, 3)`, p=`r round(p_chi, 3)`$.
+
+Despite this test being useful for detecting data fabrication in nonsignificant $p$-values, one exception should be taken into account: wrongly specified one-tailed tests.
 For properly specified one-tailed tests, the $p$-value distribution is right-skewed.
 When wrongly specified, this distribution is reversed and becomes left-skew.
-As such, any data anomalies detected with this method would need to be inspected for misspecified one-tailed hypotheses to preclude false conclusions.
+As such, any data fabrication detected with this method would need to be inspected for misspecified one-tailed hypotheses to preclude false conclusions.
 
@@
 Variance- or standard deviation estimates are typically reported to indicate dispersion, but just like the mean there should be sampling error in this estimate proportional to the sample size [i.e., $\sigma/\sqrt{2n}$ under the assumption of normality, p.
-351;@yule1922].
-A variance estimate follows a $\chi^2$-distribution, which is dependent on the sample size [p.
+351,@yule1922].
+If an observed random variable $x$ is normally distributed, the variance of $x$ is $\chi^2$-distributed [p.
 445; @hogg-tanis]; that is
+$$
+var(x)\sim\frac{\chi^2_{N_j-1}}{N_j-1}
+$$
+where $N$ is the sample size of the $j$th group. Using the reported summary statistics, we can compute the Mean Squares within ($MS_w$) each condition as
+$$
+MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
+$$
+where $s^2_j$ is the variance in the $j$th group. The reported variances can be standardized by dividing the observed variances by the $MS_w$; we denote standardized variances with z^2$.
+
+Standardizing the reported variances allows for several measures of observed dispersion to be calculated.
+Observed dispersion of the standardized variances can be operationalized as the standard deviation of the variances [denoted in this paper as $SD_z$, @10.1177/0956797613480366] or as the range of the variances (denoted as $max-min_z$).
+Note that such comparisons are only meaningful if the reported variances originate from a homogeneous population distribution of variances (otherwise, subgroups need to be made).
+
+In order to compute the expected dispersion, we use the distribution of the standardized variances to compute how extreme the observed dispersion of the variances is.
+Assuming normality, the distribution of the standardized variances follows a $\chi^2$-distribution in the form of
 $$
@@
 $$
-where $N_j$ is the sample size of the $j$th group and $MS_w$ is the normalizing constant resulting in a standardized variance $z^2_j$. The normalizing constant $MS_w$ is computed as 
-$$
-MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
-$$
-where $s^2_j$ is the variance in the $j$th group.
-
-The observed dispersion of the variances can be compared to various measures of expected dispersion in the variances.
-Dispersion can be operationalized in various ways, such as the standard deviation of the variances [denoted in this paper as $SD_z$;@10.1177/0956797613480366] or as the range of the variances (denoted as $max-min_z$).
-Too consistent results would indicate potential anomalies in the reported data.
-For example, in the Smeesters case three independent conditions from the same study ($n_k=15$) were reported to have standard deviations 25.09, 24.58, and 25.65.
+which is the result of the distribution of $var(x)$ as denoted earlier, divided by the $MS_w$.
+From this distribution, fictitious variances can be generated for each group under investigation that are subsequently used to compute one of the measures for dispersion proposed in the previous paragraph (e.g., standard deviation of the variances).
+Repeating this across $i$ iterations provides an estimate of the density function for the expection dispersion of the variances, to which the observed dispersion of the variances can be compared.
+For our purposes, too little dispersion in the variances indicates potential fabrication in the reported data [@10.1177/0956797613480366].
+
+```{r, echo = FALSE}
+sd1 <- c(ex1_1esd, ex1_1csd)
+sd2 <- c(x2_1esd, x2_2csd)
+
+iterate <- 10000
+res1 <- std_var(n = rep(100, length(sd1)), sds = sd1, iter = iterate)
+res2 <- std_var(n = rep(100, length(sd2)), sds = sd2, iter = iterate)
+```
+
+As an example, we apply the variance analysis to the illustration from Table `r tabnr` and the Smeesters case.
+For the reported standard deviations in Table `r tabnr`, we apply the variance analysis across those in the genuine- and fabricated sets separately.
+For the genuine data (Set 1), we find that the reported mean standard deviation is `r mean(sd1)` with a standard deviation of `r sd(sd1)`; for the fabricated data (Set 2), we find that the reported mean standard deviation is `r mean(sd2)` with a standard deviation of `r sd(sd2)`.
+These summary statistics of the summary statistics already indicate there is a difference between the genuine- and fabricated data, which the variance analyses confirm: Set 1 has no excessive consistency (`r round(res1, 3)`), whereas Set 2 does show excessive consistency (`r round(res2, 3)`).
+In words, out of `r iterate` fictitious samples, `r res1 * iterate` showed more consistency for Set 1, whereas only `r res2 * iterate` showed more consistency for Set 2.
+In the Smeesters case three independent conditions from the same study ($n_k=15$) were reported to have standard deviations 25.09, 24.58, and 25.65.
 The standard deviation of the standard deviations here is `r round(sd(c(25.09, 24.58, 25.65)), 2)` (i.e., $SD_z$).
-Such consistency (or more consistency) would only be observed in `r round(std_var(n = rep(15, 3), sds = c(25.09, 24.58, 25.65), iter = 100000)*100, 2)`% of 100,000 simulated replications [@10.1177/0956797613480366].
+Such consistency (or more consistency) would only be observed in `r round(std_var(n = rep(15, 3), sds = c(25.09, 24.58, 25.65), iter = iterate) * 100, 2)`% of 100,000 simulated replications [@10.1177/0956797613480366].
+
+```{r, echo = FALSE}
+tabnr <- tabnr + 1
+```
 
@@
 
-From our own experience, and anecdotal evidence elsewhere [@10.1016/0197-24569190037-M], large effects have previously raised initial suspicions.
-Taking the observed effect size and transforming it into a correlation, allows for an easy way to assess how extreme the presented result is.
-One minus the observed correlation can be used as a measure for extreme effects (i.e., $1-r$); as a heuristic, it can be regarded as a $p$-value.
-That is, this measure too ranges from zero to one and the more extreme the effect size, the smaller the value.
+Large effects have previously been opted to arise from dubious origins [@10.1111/j.1745-6924.2009.01128.x], but there is sufficient evidence that large effects arise from data fabrication.
+For example, in the misconduct investigations in the Stapel case, effect sizes were one particular indicator of data fabrication in certain papers [@Levelt2012].
+Some papers showed explained variances of up to 95%, which
+Moreover, @10.1186/1471-2288-3-18 asked faculty members from three universities to fabricate data sets and found that the fabricated data showed much larger effect sizes than the genuine data.
+From our own experience, we have found that large effect sizes raised initial suspicions of data fabrication.
+In clinical trials, this is also used to identify potentially fabricated data in multi-site trials while the study is still being conducted [@10.1016/0197-24569190037-M].
+
+```{r, echo = FALSE}
+tval <- 3.55
+df <- 59
+```
+
+Effect sizes can be reported in research reports in various ways.
+For example, the most commons ways effect sizes are reported in papers are as a standardized mean difference (e.g., $d$), as an explained variance (e.g., $R^2$), or as a test statistic.
+A test statistic is also a measure of effect size, albeit in a not directly interpretable form.
+A test result such as $t(`r df`)=`r tval`$ corresponds to $d=`r round(2*tval / sqrt(df), 3)` and $r=`r round((tval^2 / df) / ((tval^2 / df) + 1), 3)` [@10.1525/collabra.71].
+These effect sizes can readily be recomputed based on data extracted with `statcheck` across thousands of results [@10.3758/s13428-015-0664-2;@10.3390/data1030014].
+
+Observed effect sizes can subsequently be compared with the effect distribution of other studies investigating the same effect.
+For example, if a study on the 'foot-in-the-door' technique yields an effect size of $r=.8$, we can collect other studies that investigate the 'foot-in-the-door' effect and compare how extreme that $r=.8$ is in comparison to the other studies.
+If the largest observed effect size in the literature is $r=.2$ and a number of studies on the 'foot-in-the-door' effect have been done, this can be considered extreme and a flag for potential data fabrication.
 This method specifically looks at situations where fabricators would want to fabricate the existence of an effect (not the absence of one).
 
+Collecting the effect distribution to compare with requires some attention, however.
+Considering published research is biased towards statistically significant results [@], resulting in inflated effect sizes [@], effect distributions collected from published literature will tend to be conservative in detecting potential data fabrication except in extreme cases.
+Unbiased effect size distributions for an effect can be collected from large-scale replication projects, such as Registered Replication Reports [RRR;@].
+
 ## Detecting data fabrication in raw data
-
+6
 ### Digit analysis
 
-Raw data with ratio- or interval measures can be subjected to digit analysis under specific conditions.
+Raw data can be subjected to digit analysis under specific conditions, which we explain below.
 More specifically, the properties of the leading (first) digit (e.g., the 1 in 123.45) or the terminal (last) digit (e.g., the 5 in 123.45) can be examined.
-By analyzing these leading- and terminal digits for deviations from specific digit distributions, it might be possible to screen for problematic data.
-In this article we focus on leading digit analysis (i.e., Newcomb-Benford Law) and terminal digit analysis to detect potentially problematic data.
+By analyzing these leading- and terminal digits for deviations from specific digit distributions, it might be possible to screen for fabricated data.
+In this article we focus on leading digit analysis (i.e., Newcomb-Benford Law) and terminal digit analysis to detect potentially fabricated data.
 
@@
 
-<!-- In science, for example, the NBL has been tested on 20 falsified anesthesia papers, detecting 18 as problematic [@10.1007/s00101-012-2029-x], or to test coefficients reported in economics journals [@10.1111/j.1468-0475.2009.00475.x].
+<!-- In science, for example, the NBL has been tested on 20 falsified anesthesia papers, detecting 18 as fabricated [@10.1007/s00101-012-2029-x], or to test coefficients reported in economics journals [@10.1111/j.1468-0475.2009.00475.x].
 -->
@@
 
-However, given that the NBL only applies under specific conditions that are rarely fulfilled in the social sciences, its applicability for detecting data anomalies in science can be questioned.
+However, given that the NBL only applies under specific conditions that are rarely fulfilled in the social sciences, its applicability for detecting data fabrication in science can be questioned.
 First, the NBL only applies for true ratio scale measures [@10.2307/2246134;@10.1214/11-PS175].
@@
 The multivariate relations between different variables arise from stochastic processes and are not readily known, hence difficult to take into account when someone wants to fabricate data.
-As such, using these multivariate associations to detect anomalies from genuine data might prove valuable.
+As such, using these multivariate associations to detect fabrication from genuine data might prove valuable.
 
@@
 ```{r, echo=FALSE, out.width='100%', fig.cap="A fictitious distribution of observed association between Ms and SDs across 100 studies.
-The blue dot indicates the observed relation that is subject to screening for data anomalies."}
+The blue dot indicates the observed relation that is subject to screening for data fabrication."}
 ggplot(cortmp, aes(x = cortmp)) +
@@
 
-We tested the performance of statistical methods to detect data fabrication in summary results with genuine- and fabricated summary results from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058].
+We tested the performance of statistical methods to detect data fabrication in summary statistics with genuine- and fabricated summary statistics from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058].
 The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
@@
 
-We collected summary results for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
-Each of the four studies provided us with summary results for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
+We collected summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
+Each of the four studies provided us with summary statistics for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design.
 Throughout this study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent.
@@
 
-Using quotum sampling, we collected thirty-six fabricated datasets of summary results for the same four anchoring studies.
+Using quotum sampling, we collected thirty-six fabricated datasets of summary statistics for the same four anchoring studies.
 Quotum sampling was used to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
 The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in Web of Science (WoS) with the filter set to the U.S.
-We sampled psychology researchers to improve familiarity with the anchoring effect [@10.1126/science.185.4157.1124;@10.1037/e722982011-058], for which summary results were fabricated.
+We sampled psychology researchers to improve familiarity with the anchoring effect [@10.1126/science.185.4157.1124;@10.1037/e722982011-058], for which summary statistics were fabricated.
 We filtered for U.S.
@@
 
-We invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: [https://osf.io/s4w8r](https://osf.io/s4w8r)).
+We invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: [osf.io/s4w8r](https://osf.io/s4w8r)).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 The provided e-mail addresses were unlinked from individual responses upon sending the bonus gift cards.
-The full text of the Qualtrics survey is available at [https://osf.io/w984b](https://osf.io/w984b).
+The full text of the Qualtrics survey is available at [osf.io/w984b](https://osf.io/w984b).
 
@@
 AUROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$).
-With these AUROC-curves, informed decisions about optimal alpha levels can be made based on various criteria.
-In this case, we determine the optimal alpha level by finding that alpha level for which the combination of TPR and TNR were highest.
-For example, if $\alpha=.04$ results in $TPR=.30$ and $TNR=.70$, but $\alpha=.05$ results in $TPR=.5$ and $TNR=.5$, .05 was chosen as an optimal decision criterion based on the sample.
-
-AUROC values indicates the probability that a randomly drawn fabricated- and genuine dataset can be correctly classified as fabricated and genuine [@10.1148/radiology.143.1.7063747].
+AUROC values indicate the probability that a randomly drawn fabricated- and genuine dataset can be correctly classified as fabricated and genuine [@10.1148/radiology.143.1.7063747].
 In other words, if $AUROC=.5$, correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
-For this setting, we will regard any AUROC $<.6$ as plainly insufficient for detecting data fabrication, $.6\leq$ AUROC $<.7$ as failed, $.7\leq$ AUROC $<.8$ as sufficient, $.8\leq$ AUROC $<.9$ as good, and $.9\leq$ AUROC $\leq 1$ as excellent.
+For this setting, we follow the guidelines of @10.1093/jpepsy/jst062 and regard any AUROC value $<.7$ as poor for detecting data fabrication, $.7\leq$ AUROC $<.8$ as fair, $.8\leq$ AUROC $<.9$ as good, and AUROC $\geq.9$ as excellent.
+
+PROC package 10.1186/1471-2105-12-77
 
@@
 ```{r echo=FALSE}
+apply(dat_summary[, grepl(names(dat_summary), pattern = "_p")],
+   2,
+   function(x)
+   {
+    y <- pROC::roc(response = dat_summary$type, x, direction = ">")
+    return(y$auc[1])
+   }
+)
+
 tp <- matrix(NA, ncol = sum(grepl(names(dat_summary), pattern = "_p")), nrow = 101)
@@
 
-We investigated detecting data fabrication in raw data as an extension of Study 1.
+We investigated automated detection of data fabrication in raw data using statistics as an extension of Study 1.
 In essence, the procedure is similar: we asked actual researchers to fabricate data that they thought would go undetected.
@@
 
-To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of a Stroop experiment [@10.1037/h0054651].
-In the Stroop task, participants are asked to determine the color a word is presented in (i.e., word colors), but the word also reads a color (i.e., color words).
+To test the validity of statistical methods to detect data fabrication in raw data, we investigated raw data of Stroop experiments [@10.1037/h0054651].
+In a Stroop experiment, participants are asked to determine the color a word is presented in (i.e., word colors), but the word also reads a color (i.e., color words).
 The presented word color (i.e., 'red', 'blue', or 'green') can be either presented in the congruent color (e.g., 'red' presented in red) or an incongruent color (i.e., 'red' presented in green).
-The dependent variable in the Stroop task is the response latency (in this study milliseconds are used).
-Participants in actual studies are typically presented with a set of these, where the mean and standard deviation per condition serves as the raw data.
+The dependent variable in a Stroop experiment is the response latency (in this study we used milliseconds).
+Participants in actual studies are typically presented with a set of these Stroop tasks, where the mean and standard deviation per condition serves as the raw data [@10.1016/j.jesp.2015.10.012].
 The Stroop effect typically is computed as the difference in mean response latencies between the congruent and incongruent conditions.
@@
 Using the original raw data and analysis script from ML3 ([https://osf.io/qs8tp/](https://osf.io/qs8tp/)), we computed the mean (M) and standard deviation (SD) for the participant's response latencies in both the within-subjects conditions of congruent trials and incongruent trials.
-These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure X).
+These also formed the basis for the template of the data that needed to be fabricated by the participants (see also Figure `r fignr`).
 The Stroop effect was calculated as a $t$-test of the difference between the congruent and incongruent conditions ($H_0:\mu=0$).
@@
 knitr::include_graphics('../figures/spreadsheet2.png')
+
+fignr <- fignr + 1
 ```
@@
 First, we invited 80 Dutch and Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015 as available in the Thomson Reuters’ Web of Science database.
-We selected Dutch and Flemish researchers to allow for a face-to-face interview on how the data were fabricated.
+We selected Dutch and Flemish researchers to allow for face-to-face interviews on how the data were fabricated.
 We chose the period 2005-2015 to prevent a drastic decrease in the probability that the corresponding author would still be addressable via the given email.
 The database was searched on October 10, 2016 and 80 unique e-mails were retrieved from 90 publications.
-Only two of these 80 participated in the study; we subsequently implemented a second sampling stage where we collected e-mails from all PhD-candidates, teachers, and professors of psychology related departments at Dutch universities.
+Only two of these 80 participated in the study.
+We subsequently implemented a second sampling stage where we collected e-mails from all PhD-candidates, teachers, and professors of psychology related departments at Dutch universities.
 This resulted in 1659 additional unique e-mails that we subsequently invited to participate in this study.
@@
 
-To detect data
+To automatically detect data fabrication using statistics, we performed sixteen analyses.
+These sixteen analyses consisted of four NBL digit analyses, four terminal digit analyses, two variance analyses, four multivariate association analyses, a combination test, and effect sizes (using effect sizes was not preregistered).
+
+For the digit analyses, we separated the Ms and SDs per condition and conducted $\chi^2$-tests for each per data set.
+As such, for one data set, we conducted NBL digit analyses on the first digits of (i) the mean response latencies in the congruent condition, (ii) the mean response latencies in the incongruent condition, (iii) the standard deviation of the response latencies in the congruent condition, and (iv) the standard deviation of the response latencies in the incongruent condition.
+For the terminal digit analyses, we took the same four sets, but tested on the final digits.
+
+For the variance analyses, we analyzed the standard deviations of the response latencies separated per condition per data set.
+That is, we analyzed the standard deviations of the response latencies in the congruent condition for excessive consistency separate from the standard deviations of the incongruent condition.
+
+For the multivariate association analyses, we estimated how extreme the observed correlations between the means and standard deviations within and across conditions were.
+More specifically, we did this for (i) the correlation between the means across conditions, (ii) the standard deviations across conditions, (iii) the means and standard deviations within the congruent condition, and (iv) the means and standard deviations within the incongruent condition.
+Based on a meta-analysis of the observed correlations from the Many Labs 3 data, we estimated the parametric distribution of the multivariate relations for each of those four under investigation.
+Using the estimated parametric distribution, we computed the two-tailed $p$-value under that distribution.
+
+We also conducted a combination of the terminal digit analyses, the variance analyses, and the analyses based on multivariate associations.
+To this end, we took the $p$-values of the 10 statistical tests (i.e., four terminal digit analyses, two variance analyses, four analyses of the multivariate associations) and combined them using the Fisher method [@fisher1925].
+
+Study 1 showed that effect sizes are a potentially valuable tool to detect data fabrication, which we replicate in Study 2.
+Based on the data sets, we computed effect sizes for the Stroop effect based on the Many Labs 3 scripts ([osf.io/XXXX](https://osf.io/XXXX)).
+Using a difference $t$-test ($H_0:\mu=0$) we computed the $t$-value and its constituent effect size as a correlation using
+$$
+r=\sqrt{\frac{\frac{t^2}{df_2}}{\frac{t^2}{df_2}+1}}
+$$
+
+Similar to Study 1, we computed the AUROC for each of these statistical methods to detect data fabrication.
+To recapitulate, if $AUROC=.5$, correctly classifying a randomly drawn dataset in this sample is equal to a coin flip.
+We follow regard any AUROC value $<.7$ as poor for detecting data fabrication, $.7\leq$ AUROC $<.8$ as fair, $.8\leq$ AUROC $<.9$ as good, and AUROC $\geq.9$ as excellent [@10.1093/jpepsy/jst062].
 
@@
 
+apply(dat[, grepl(names(dat), pattern = "(_p|one_min_es_r|p_)")],
+   2,
+   function(x)
+   {
+    y <- pROC::roc(response = dat$type, x, direction = "<")
+    return(y$auc[1])
+   }
+)
+
 tp <- matrix(NA, ncol = sum(grepl(names(dat), pattern = "(_p|p_|one_min_es_r|fisher_combination)")), nrow = 101)
@@
 
+<!-- Effect sizes good way to detect, but based on unbiased effect sizes! ML is unbiased, published lit isn't -->
+
 <!-- ## `ddfab` package -->
@@
 <!-- We -->
+
+<!-- do something with this
+https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-3-18
+also shows effects are important and exaggerated by fabricators -->
 

### 2018-03-15 submission/manuscript.Rmd
Initialize redrafting

@@
 
-Statistical methods to detect data fabrication have been applied in several cases of scientific misconduct in recent years and has potential for future application beyond these specific cases. 
-For example, excessive consistency in papers by Fuji were highlighted with statistical methods [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], resulting in 183 retractions [@oransky2015].
-Carlisle's method works as follows: in true randomized clinical trials (RCTs) baseline measurements should be identically distributed across groups.
-As such, the $p$-values for group comparisons would be expected to be uniformly distributed because the null hypothesis of identical distributions across groups is true by definition of the randomized design.
-In the Fuji papers, group comparisons showed excessive consistency, resulting primarily in high $p$-values (e.g., .99, .95) and a high mean $p$-value across the comparisons, where a mean $p$-value of .5 is expected.
-As an illustration, see Table `r tabnr`, which depicts 10 hypothetical studies containing 100 participants per condition, for true randomized designs (Set 1) or for fabricated designs (Set 2).
-The mean $p$-value for the true randomized design Set 1 is `r round(mean(ex1_1tp), 3)`, whereas the fabricated Set 2 has mean $p$-value `r round(mean(ex2_1tp), 3)`.
-Other statistical methods to detect data fabrication are addressed in the theoretical sections.
-.
+Statistical methods to detect data fabrication have been applied in several
 
@@
 First, the NBL only applies for true ratio scale measures [@10.2307/2246134;@10.1214/11-PS175].
-Second, sufficient range on the measure is required for the NBL to apply [i.e., range from $1-1000000$ ;@10.1198/tast.2009.0005].
+Second, sufficient range on the measure is required for the NBL to apply [i.e., range from at least $1-1000000$ or $1-10^6$;@10.1198/tast.2009.0005].
 Third, these measures should not be subject to digit preferences, for example due to psychological preferences for rounded numbers.
@@
 Moreover, some research has even indicated humans might be sensitive to fabricating data that are in line with the NBL [@10.1080/02664760601004940;@Burns2009], immediately undermining the applicability of the NBL.
-Nonetheless, considering the four conditions for the NBL to apply, we preregistered that this method would not prove fruitful [@10.3897/rio.2.e8860].
+As such, we think that this method would not prove fruitful in psychology research because rarely are measures true ratio scales with sufficient range to show the NBL properties in the first digit [@10.3897/rio.2.e8860].
 
@@
 Terminal digit analysis is conducted with a $\chi^2$-test ($df=10-1$) on the digit occurrence counts (including zero), where the observed frequencies are compared with the expected uniform frequencies.
-Tthe rule of thumb outlined by @agresti2003categorical indicates at least 50 observations are required to provide a meaningful test of the terminal digit distribution ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
+The rule of thumb outlined by @agresti2003categorical indicates at least 50 observations are required to provide a meaningful test of the terminal digit distribution ($n=I\times J \times 5$, with $I$ rows and $J$ columns).
 Terminal digit analysis was developed during the Imanishi-Kari case by @10.1080/03610919608813325 [for a history of this decade long case, see @kevles2000baltimore].
 
-As an example, Figure `r fignr` depicts the digit counts for the first- through fifth digit of a random, normally distributed variable.
-The first- and second digit distributions are clearly non-uniform, whereas the third-, fourth-, and fifth digit distributions are uniformly distributed.
+As an example, Figure `r fignr` depicts the digit counts for the first- through fifth digit of a random, normally distributed variable (i.e., $N\sim(0,1)$).
+The first- and second digit distributions are clearly non-uniform, whereas the third digit distribution is less obvious but still non-uniform, and the fourth-, and fifth digit distributions are uniformly distributed.
 
 ```{r, echo=FALSE, fig.align="center", fig.asp=.5, out.width='100%', fig.cap="Illustration of how digit distributions evolve from first- through later digits.
-We sampled 100,000 values from a normal distribution, N~(0, 1.5), to create these digit distributions."}
+We sampled 100,000 values from a normal distribution, N~(0, 1), to create these digit distributions."}
 set.seed(1234)
 tmp1 <- 0
-tmp2 <- 1.5
+tmp2 <- 1
 y <- data.frame(value = rnorm(100000, tmp1, tmp2))
@@
 
+```{r, echo = FALSE}
+if(!file.exists('../data/study_02/p5'))
+{
+p1 <- NULL
+p2 <- NULL
+p3 <- NULL
+p4 <- NULL
+p5 <- NULL
+
+for(i in 1:1000)
+{
+set.seed(1234 + i)
+tmp1 <- 0
+tmp2 <- 1
+n <- 500
+y <- data.frame(value = rnorm(n, tmp1, tmp2))
+x <- abs(y$value)
+splitted <- strsplit(as.character(x), "")
+df1 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[1])))))
+df1 <- data.frame(digit = df1[!df1$digit == 0,])
+df2 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[3])))))
+df3 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[4])))))
+df4 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[5])))))
+df5 <- data.frame(digit = as.numeric(unlist(lapply(splitted, function(x) return(x[6])))))
+
+p1[i] <- digit_analysis(df1[,1], type = "terminal")$pval
+p2[i] <- digit_analysis(df2[,1], type = "terminal")$pval
+p3[i] <- digit_analysis(df3[,1], type = "terminal")$pval
+p4[i] <- digit_analysis(df4[,1], type = "terminal")$pval
+p5[i] <- digit_analysis(df5[,1], type = "terminal")$pval
+}
+
+save('../data/study_02/p1')
+save('../data/study_02/p2')
+save('../data/study_02/p3')
+save('../data/study_02/p4')
+save('../data/study_02/p5')
+}
+
+load('../data/study_02/p1')
+load('../data/study_02/p2')
+load('../data/study_02/p3')
+load('../data/study_02/p4')
+load('../data/study_02/p5')
+```
+
 As such, the rightmost digit can be expected to be uniformly distributed if sufficient precision is provided [@10.1080/08989629508573866].
-For our purposes, sufficient precision is determined as the terminal digit being at least the third leading digit [i.e., minimally 1.23 or 12.3 or 123].
+What sufficient precision is, we investigated by running a small simulation study, drawing 500 random values from a normal distribution ($N\sim(0,1)$) thousand times and conducting a terminal digit test for each of the first five digits (similar to Figure `r fignr`).
+For the third-, fourth-, and fifth- digits, tests operated on nominal $\alpha$ levels (i.e., under $\alpha=.05$, false positives were $`r round(sum(p3 > .05) / 1000, 3)`$, $`r round(sum(p4 > .05) / 1000, 3)`$, $`r round(sum(p5 > .05) / 1000, 3)`$, respectively).
+Hence, sufficient precision for our purposes is determined as the terminal digit being conducted on at least the third leading digit (i.e., minimally 1.23 or 12.3 or 123).
 
@@
 
-True data occur within a web of relations, which can be observed in genuine data and easily forgotten while fabricating data.
-The multivariate relations between different variables arise from stochastic processes and are not readily known, hence difficult to take into account when someone wants to fabricate data.
+Often, different measurements show relations that are non-obvious to the researcher.
+Hence, such relations between measurements might be forgotten by people who fabricate data or the fabricators might simply be unable to fabricate data that also show these relations.
+For example, in response time latencies, there is a negative relation between mean response time and the variance of the response time, where lower mean response times are accompanied by a lower variance.
+Given that the multivariate relations between different variables arise from stochastic processes and are not readily known in either their form or size, it might be difficult to take into account when someone wants to fabricate data.
 As such, using these multivariate associations to detect fabrication from genuine data might prove valuable.
@@
 For example, if the multivariate association between means (Ms) and standard deviations (SDs) is of interest, control data for that same measure can be collected from the literature, assuming the measure has been used in other studies.
-With these control data, a meta-analysis provides an overall estimate of the multivariate relation.
+With these control data, a meta-analysis provides an overall estimate of the multivariate relation that can subsequently be used in a parametric $z$-test (assuming normality).
 
@@
 Consider the following fictitious example, regarding the multivariate association between Ms and SDs for a response latency task.
-Figure `r fignr` depicts a simulated distribution of the association between Ms and SDs from the literature.
+Figure `r fignr` depicts a simulated population distribution of the association between Ms and SDs from the literature ($N\sim(.123, .1)$).
 The observed relation between Ms and SDs from two papers we want to (fictitiously) screen are `r corfab$cor` and `r corfabno$cor`.
-As such, we immediately see in Figure `r fignr` that the former is flagged as being potentially anomalous (i.e., the red dot; two-tailed $p$-value $`r pnorm(corfab$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$ of the time), whereas the latter (blue dot) is not flagged ($p$-value: $`r pnorm(corfab$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$).
+As such, we immediately see in Figure `r fignr` that the former is flagged as being potentially anomalous (i.e., the red dot; two-tailed $p$-value $`r pnorm(corfab$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$ of the time), whereas the latter (blue dot) is not flagged ($p$-value: $`r pnorm(corfabno$cor, mean(cortmp$cortmp), sd(cortmp$cortmp), lower.tail = FALSE) * 2`$).
 
@@
 The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
-For example 'Is the percentage of African countries in the United Nations more or less than [10\% or 65\%]?'.
+For example 'Do you think the percentage of African countries in the UN is above or below  [10\% or 65\%]?
+What do you think is the percentage of African countries in the UN?'.
 These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question.
-A considerable amount of genuine datasets on this heuristic are freely available and we collected fabricated datasets within this study.
+A considerable amount of genuine data sets on this heuristic are freely available and we collected fabricated data sets within this study.
 This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
@@
 For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from.
-All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/ejf5x](https://osf.io/ejf5x) (deviations are explicated in this report).
+All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/tshx8/](https://osf.io/tshx8/).
+Throughout this report, we will indicate which facets were not preregistered or deviate from the preregistration by denoting "(not preregistered)" or "(deviation from preregistration)", respectively.
 
@@
 
-We downloaded thirty-six genuine datasets from the publicly available Many Labs (ML) project [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178].
+We downloaded thirty-six genuine data sets from the publicly available Many Labs (ML) project [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178].
 The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously.
 Considering the size of the ML project, the transparency of research results, and minimal individual gain for fabricating data, we assumed these data to be genuine.
-For each of the thirty-six locations we computed sample sizes, means, and standard deviations for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations.
+For each of the thirty-six locations we computed three summary statistics (i.e., sample sizes, means, and standard deviations) for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations.
 We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
 
-Using quotum sampling, we collected thirty-six fabricated datasets of summary statistics for the same four anchoring studies.
-Quotum sampling was used to sample as many responses as possible for the available 36 rewards (i.e., not all respondents might request the gift card and count towards the quotum; one participant did not request a reward).
 The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in Web of Science (WoS) with the filter set to the U.S.
@@
 We filtered for U.S.
-researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies (note: we found out several non-U.S.
-researchers were included because the WoS filter also retained papers with co-authors from the U.S.).
+researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies and in order to reduce heterogeneity across fabricators.
 WoS was searched on October 13, 2015.
@@
 
-We invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: [osf.io/s4w8r](https://osf.io/s4w8r)).
+From these 2,038 psychology researchers, we invited a random sample of 1,000 researchers via e-mail to participate in this study on April 25, 2016 (invitation: [osf.io/s4w8r](https://osf.io/s4w8r)).
 The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-addresses saved).
@@
 
-Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that fulfilled three hypotheses.
-We instructed respondents to fabricate results for the following hypotheses: there is (i) a main effect of condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
+Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that corresponded to three hypotheses.
+We instructed respondents to fabricate results for the following hypotheses: there is (i) a positive main effect of the anchoring condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
 We fixed the sample sizes to 25 per cell; respondents did not need to fabricate sample sizes.
-The fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of statistical tools to detect data fabrication.
+These fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of statistical tools to detect data fabrication.
 
@@
 We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses.
+Technically, participants could provide a response that did not correspond to the instructions.
 
@@
 
-Upon completing the fabrication of the data, respondents were debriefed.
+Upon completing the fabrication of the data, respondents were debriefed within the Qualtrics survey environment ([osf.io/rg3qc/](https://osf.io/rg3qc/)).
 Respondents answered several questions about their statistical knowledge and approach to data fabrication and finally we reminded them that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
+This reminder was intented to minimize potential carry-over affects of the unethical behavior performed by the participants [@10.1509/jmkr.45.6.633].
 We rewarded participation with a $30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus $50 Amazon gift card.
+We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.
+Using quotum sampling, we collected as many responses as possible for the available 36 rewards, resulting in 39 fabricated data sets ([https://osf.io/e6zys](https://osf.io/e6zys); `r sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))` participants did not participate for a bonus).
 
@@
 
-We analyzed the genuine- and fabricated datasets for the four anchoring studies in four ways.
-First, we applied variance analyses to the reported variances of each of the four groups per study separately.
-Second, we applied the reversed Fisher method to the results of the gender and interaction hypotheses (i.e., nonsignificant results) across the four studies.
-Third, we combined the results from the variance analyses and the reversed Fisher method, using the original Fisher method [@fisher1925].
-Fourth, and not preregistered, we used effect size analysis (i.e., $1-r$) that is a proxy of how extreme an effect is.
+<!-- 1. pvalue
+2. variance
+3. effect size -->
+
+INVOEGEN
+Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
+
+We analyzed the genuine- and fabricated data sets for the four anchoring studies in four ways.
+First, we applied the reversed Fisher method to the results of the gender and interaction hypotheses (i.e., nonsignificant results) across the four studies.
+Second, we applied variance analyses to the reported variances of each of the four groups per study separately.
+Third, and not preregistered, we used effect size analysis (i.e., $1-r$) that is a proxy of how extreme an effect is.
+Fourth, we combined the results from the reversed Fisher method and variance analyses, using the original Fisher method [@fisher1925].
 
@@
 
-The collected data included `r table(dat_summary$type)[1]` genuine data from Many Labs 1 [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and `r table(dat_summary$type)[2]` fabricated datasets ([https://osf.io/e6zys](https://osf.io/e6zys); `r sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))` participants did not participate for a bonus).
-
 Figure `r fignr` shows a group-level comparison of the genuine- and fabricated $p$-values and effect sizes ($r$).
@@
 These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses).
-However, there seem to be large group differences when we required subjects to fabricate significant data (i.e., condition hypothesis).
-Considering this, we also investigated how well effect sizes perform in detecting data fabrication (not preregistered).
-In the following sections, we investigate the performance of such statistical methods to detect data fabrication on an respondent-level basis.
+However, there seem to be large group differences when we required subjects to fabricate significant summary statistics (i.e., condition hypothesis).respondent-level basis.
 
 ```{r ddfab_density, fig.cap="Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
-We instructed respondents to fabricate nonsignificant data for the gender and interaction effects, and a significant effect for the condition effect.", out.width='100%', echo=FALSE}
+We instructed respondents to fabricate nonsignificant summary statistics for the gender and interaction effects, and a significant effect for the condition effect.", out.width='100%', echo=FALSE}
 plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
@@
 ```
+
+<!-- aanhouden oorspronkelijke volgorde
+
+1. p
+2. variance
+3. effect
+4. fisher combined (p+variance) -->
 
@@
 
+<!-- (note: we found out several non-U.S. researchers were included because the WoS filter also retained papers with co-authors from the U.S.). 
+ -->
+
 <!-- This could be done automatically at a large scale easily [data for this are available in @10.3758/s13428-015-0664-2;@10.3390/data1030014] or by a reader while going through a manuscript (e.g., during peer-review).
@@
 
-We collected twenty-one genuine datasets on the Stroop task from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012].
-Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample [the original preregistration mentioned 20 datasets, accidentally overlooking the online sample; @10.3897/rio.2.e8860].
+We collected twenty-one genuine data sets on the Stroop task from the Many Labs 3 project [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012].
+Many Labs 3 (ML3) includes 20 participant pools from universities and one online sample [the original preregistration mentioned 20 data sets, accidentally overlooking the online sample; @10.3897/rio.2.e8860].
 Similar to Study 1, we assumed these data to be genuine due to the minimal individual gains for fabricating data and the transparency of the project.
@@
 
-We collected twenty-eight faked datasets on the Stroop task experimentally in a two-stage sampling procedure.
+We collected twenty-eight faked data sets on the Stroop task experimentally in a two-stage sampling procedure.
 First, we invited 80 Dutch and Flemish psychology researchers who published a peer-reviewed paper on the Stroop task between 2005-2015 as available in the Thomson Reuters’ Web of Science database.

### 2018-03-15 submission/redraft.rmd
Initialize redrafting

# Introduction

<!-- consistency of data fabrication v data anomalies -->

Any field of empirical inquiry is faced with cases of scientific misconduct at some point, either in the form of fabrication, falsification or plagiarism (FFP). 
Psychology faced Stapel; medical sciences faced Poldermans and Macchiarini; life sciences faced Voignet; physical sciences faced Sch&ouml;n --- these are just a few examples of misconduct cases in the last decade. 
Overall, an estimated 2\% of all scholars admit to falsifying or fabricating research results at least once [@10.1371/journal.pone.0005738], which due to its self-report nature is likely to be an underestimate. 
The detection rate of data fabrication is likely to be even lower; for example, only around a dozen cases become public in the United States and the Netherlands, despite that there are several hundreds of thousands of researchers in these countries. 
At best, this suggests a detection rate below 1\% of those 2\% who admit to fabricating data --- the tip of a seemingly much larger iceberg.

In order to stifle attempts at data fabrication, improved detection of fabricated data is considered to deter such behavior. 
This idea is based on deterrence theory [@leviathan], which stipulates that increased risk of detection decreases the utility of scientific misconduct, hence, fewer people will engage in it. 
Detection techniques have developed to varying degrees for fabrication, falsification, and plagiarism.
Plagiarism scanners have been around the longest [e.g., @10.1109/13.28038] and are widely implemented not only at journals but also in student evaluation. 
For data fabrication, developments around detecting image manipulation are more recent and these methods are being implemented at journals. 
For example, the Journal of Cell Biology and the EMBO journal scan each submitted image for potential manipulation [@The_Journal_of_Cell_Biology2015-vh;@10.1038/546575a], which supposedly increases the risk of (blatant) image manipulation. 
More recently, algorithms are being developed to automate the scanning of images for such manipulations [@10.1007/s11948-016-9841-7]. 
Moreover, the application of such tools can also help researchers systematically evaluate research articles in order to estimate the extent to which image manipulation occurs [4\% of all papers are estimated to contain manipulated images, @10.1128/mBio.00809-16] or what factors are predictive of image manipulation [@10.1007/s11948-018-0023-7].

Detection methods for data fabrication in empirical research are often based on a mix of psychology theory and statistics theory. 
Because humans are notoriously bad at understanding and estimating randomness [@10.1126/science.185.4157.1124;@10.1037/h0031322;@10.1037/1082-989X.5.2.241], this could manifest itself in the fundamentally probabilistic data they try to fabricate. 
As such, when data are fabricated, principles of statistics and randomness could easily be violated at various dimension of the data [@Haldane1948-nm]. 
Based on this idea, statistical methods can be used to detect anomalies in investigations. Whether data are in line with the reported probabilistic processes and their theoretically expected outcomes (e.g., random assignment) can indicate deviations from the reported protocol, potentially even data fabrication. 
<!-- ref naar wagenaar 1972? in l21 -->

Statistical methods have proven to be of importance in initiating data fabrication investigations or in assessing scope of potential data fabrication. 
For example, Kranke, Apfel, and Roewer skeptically perceived Fuji's "incredibly nice" data [@10.1213/00000539-200004000-00053] and used statistical methods to contextualize their skepticism.
At the time, a reviewer perceived them to be on a "crusade  against Fujii and his colleagues" [@@10.1111/j.1365-2044.2012.07318.x] and further investigation was absent. 
Only when Carlisle extended the systematic investigation to 168 of Fuji's papers [@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13650;@10.1111/anae.13126] did events cumulate into an investigation- and ultimately retraction of 183 peer-reviewed papers [@oransky2015;@10.1016/j.ijoa.2012.10.00]. 
In another example, the Stapel case, statistical evaluation of his oeuvre  occurred after he had already confessed to fabricating data [@Levelt2012].
This resulted in 58 retractions [@oransky2015] and cleared all PhD students of wrongdoing [@Levelt2012].

In order to determine whether generic application of statistical methods to detect data anomalies is responsible, their diagnostic value requires further investigation. 
After all, accusations of data fabrication have grave consequences for the people involved [regretfully, the STAP case brings this to the fore very clearly; @10.1038/520600a]. 
Many of these statistical methods to detect data anomalies are quantifications of initial suspicions by researchers.
Hence, until validated, these should be considered proposed methods.
In some cases, convergent evidence is provided by testing the underlying psychological premises in the general population [@10.1080/08989629508573866;@10.1080/08989620212969] but the question remains whether this premise also applies for data fabricators.
Considering we hardly know how researchers might go about fabricating data, this seems especially problematic. 
Known cases provide relatively few and biased insights into the mind of the data fabricator. 
Relatively extensive descriptions in rare and partial autobiogrophical accounts provide little insight into the actual data fabrication process, except for the setting where it might take place [e.g., late at night when no one is around; @stapel_book].

<!-- Carlisle tested whether Fuji's Randomized Clinical Trials (RCTs) baseline measurements were identically distributed across groups. 
If random assignment occurred, this should be the case. 
As such, the $p$-values for group comparisons would be expected to be uniformly distributed because the null hypothesis of identical distributions across groups is true by definition of the randomized design. 
In the Fuji papers, group comparisons showed excessive consistency, resulting primarily in high $p$-values (e.g., .99, .95) and a high mean $p$-value across the comparisons (mean $p$-value of .5 is expected under uniform distribution).
As an illustration, see Table 1, which depicts 10 hypothetical studies containing 100 participants per condition. 
Set 1 depicts true randomized designs; Set 2 depicts fabricated designs. 
The mean $p$-value for the true randomized design Set 1 is `r round(mean(ex1_1tp), 3)`, whereas the fabricated Set 2 has mean $p$-value `r round(mean(ex2_1tp), 3)`.
 -->

<!-- insert code for the r bits in the next paragraph here -->

We present two studies investigating the diagnostic performance of statistical methods to detect data fabrication.
These studies investigate methods to detect data fabrication in summary statistics (Study 1) or in raw data (Study 2). 
In Study 1, we invited researchers to fabricate summary statistics for a set of four anchoring studies, for which we also had genuine data from the Many Labs initiative [@].
In Study 2, we invited researchers to fabricate raw data for a Stroop experiment, for which we also had genuine data from the Many Labs 2/3 initiative [@]. 
Before presenting these studies, we expand on the theoretical framework of the investigated statistical methods to detect data fabrication.
<!-- We note that the reviewed methods are not exhaustive of all methods available to test for potential data fabrication in empirical data [see also, @buyse1999;@10.7287/peerj.preprints.2400v1;@10.7287/peerj.preprints.2064v1;@sprite-heathers]. -->

# Theoretical framework

In the current paper, we differentiate between statistical methods to detect potential data fabrication based on reported summary statistics or raw data. 
Below, we expand on the theoretical underpininings of these methods and provide sample code to run these, where appropriate (implemented in the `ddfab` package for R).
For summary statistics, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data fabrication. 
$P$-value analyses can be applied whenever a set of nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size is reported or can be computed [e.g., an APA reported t- or F-statistic;@10.1525/collabra.71]. 
For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis) and multivariate associations as potential ways to detect data fabrication. 
The Newcomb-Benford law can be applied when untruncated ratio- or count scale measures are present [@10.1016/j.spa.2005.05.003]; terminal digit analysis can be applied whenever there are sufficient digits [see also @10.1080/08989629508573866]. 
Multivariate associations can be investigated whenever there are two or more variables available and data on that same relation is available from (assumably) genuine data sources.

## Detecting data fabrication in summary statistics

### P-value analysis

### 2018-03-20 submission/redraft.rmd
Start redraft

@@
+---
+title: "Automated detection of data fabrication using statistical tools"
+author: "Chris HJ Hartgerink, Jan G Voelkel, Jelte M Wicherts, Marcel ALM van Assen"
+date: '`r format(Sys.time(), "%d %B, %Y")`'
+output:
+ pdf_document:
+  toc: yes
+ html_document:
+  toc: yes
+  toc_depth: 2
+csl: ../bibliography/apa.csl
+bibliography: ../bibliography/library2.bib
+---
+
 # Introduction
@@
 These studies investigate methods to detect data fabrication in summary statistics (Study 1) or in raw data (Study 2). 
-In Study 1, we invited researchers to fabricate summary statistics for a set of four anchoring studies, for which we also had genuine data from the Many Labs initiative [@].
-In Study 2, we invited researchers to fabricate raw data for a Stroop experiment, for which we also had genuine data from the Many Labs 2/3 initiative [@]. 
+In Study 1, we invited researchers to fabricate summary statistics for a set of four anchoring studies, for which we also had genuine data from the Many Labs 1 initiative [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178].
+In Study 2, we invited researchers to fabricate raw data for a Stroop experiment, for which we also had genuine data from the Many Labs 3 initiative [[https://osf.io/n8xa7/](https://osf.io/n8xa7/); @10.1016/j.jesp.2015.10.012].
 Before presenting these studies, we expand on the theoretical framework of the investigated statistical methods to detect data fabrication.
@@
 Below, we expand on the theoretical underpininings of these methods and provide sample code to run these, where appropriate (implemented in the `ddfab` package for R). 
+<!-- worth thinking about whether this is ethical if methods prove irresponsible -->
 For summary statistics, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data fabrication. 
-$P$-value analyses can be applied whenever a set of nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size is reported or can be computed [e.g., an APA reported t- or F-statistic;@10.1525/collabra.71].
+$P$-value analyses can be applied whenever a set of nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances and accompanying sample sizes are reported for independent, randomly assigned groups; effect size analysis can be used whenever the effect size is reported or can be computed [e.g., an APA reported t- or F-statistic; @10.1525/collabra.71].
 For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis) and multivariate associations as potential ways to detect data fabrication. 
@@
 ### P-value analysis
+
+The distribution of a single- or a set of $p$-values is uniform if the null hypothesis is true; it is right-skewed if the alternative hypothesis is true [@fisher1925]. 
+The distribution of one $p$-value is the result of the population effect size, the precision of the estimate, and the observed effect size, whose properties carry over to a set of independent $p$-values if those $p$-values are independent.
+As such, the $p$-value distribution of a set of independent $p$-values is uniform when the null hypothesis is true, or right-skewed when the alternative hypothesis is true.
+
+When assumptions underlying the computation of a $p$-value are violated, $p$-value distributions can take on a variety of shapes. 
+For example, when optional stopping occurs and the null hypothesis is true, $p$-values just below .05 become more frequent [@10.1080/17470218.2014.982664;@10.7717/peerj.1935]. 
+However, when optional stopping occurs under the alternative hypothesis or when other researcher degrees of freedom are used, a right-skewed distribution for significant $p$-values can still occur [@10.1037/xge0000086;@10.7717/peerj.1935/fig-1].
+
+When independent $p$-values are not right-skewed or uniformly distributed (as would be theoretically expected), it can indicate potential data fabrication. 
+For example, in the Fuji case, supposedly randomly assigned groups were fabricated. 
+In truly randomly assigned groups, the measurements are statistically identical (prior to an intervention). 
+However, in the Fuji case Carlisle observed many large $p$-values, which ultimately led to the identification of potential data fabrication [@]. 
+In Table xxxx we illustrate the difference between expected data under the null distribution (Set 1) and excessively consistent and potentially fabricated data (Set 2). 
+More specifically, the expected value of a uniform $p$-value distribution is .5, but the fabricated data from our illustration have a mean $p$-value of `r round(mean(ex2_1tp), 3)`.

### 2018-03-20 submission/manuscript.Rmd
Add paragraph(s?)

@@
 
-In the current paper, we differentiate between statistical methods to detect potential data fabrication based on reported summary statistics or raw data.
-For summary statistics, we review $p$-value analysis, variance analysis, and effect size analysis as potential ways to detect data fabrication.
-$P$-value analysis can be applied whenever sufficient nonsignificant $p$-values are reported; variance analysis can be applied whenever a set of variances are reported for independent groups alongside the sample sizes per group; effect size analysis can be used whenever the effect size is reported or can be computed [e.g., an APA reported t- or F-statistic;@10.1525/collabra.71].
-For raw data, we review digit analyses (i.e., the Newcomb-Benford law and terminal digit analysis) and multivariate associations as potential ways to detect data fabrication.
-Both types of digit analyses can be applied when ratio scale measures are present in the raw data and only terminal digit analysis can be applied when there are continuous measures.
-Multivariate associations can be investigated whenever there are two or more variables and data on that same relation is available from (assumably) genuine data sources.
-
 ## Detecting data fabrication in summary statistics
@@
 ### P-value analysis
-
-The distribution of a $p$-value is uniform if the null hypothesis is true and right-skewed if the alternative hypothesis is true [@fisher1925].
-The distribution of one $p$-value is the result of the population effect size, the precision of the estimate, and the observed effect size, whose properties carry over to a set of independent $p$-values if those $p$-values are independent.
-As such, the $p$-value distribution of a set of $p$-values is uniform when the null hypothesis is true, or right-skewed when the alternative hypothesis is true.
-
-When a $p$-value distribution of independent $p$-values is not uniform or right-skewed, as would be theoretically expected, it can indicate potential data fabrication.
-For example, in the Fuji case, supposedly identically distributed groups were fabricated.
-However, this resulted in excessively large $p$-values and ultimately the identification of potential data fabrication by @10.1111/j.1365-2044.2012.07128.x.
-Our illustration in Table `r tabnr` also shows the difference between expected data under the null distribution (Set 1) and what might result from excessively consistent and fabricated data (Set 2).
-More specifically, the expected value of a uniform $p$-value distribution is .5, but the fabricated data from our illustration result in a mean $p$-value of `r round(mean(ex2_1tp), 3)`.
-
-In order to test whether the distribution of nonsignificant and independent $p$-values might be fabricated, we proposed an adaptation of Fisher's method [@10.1186/s41073-016-0012-9].
-This adaptation is a reversal of the original Fisher method [@fisher1925], which was introduced as a meta-analytic test for the presence of an effect.
-This test is computed as
-$$F
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
-$$
-where it tests for more smaller $p$-values than larger $p$-values across the $k$ number of $p$-values.
-Reversing the original Fisher method, which tests for right-skew, into a Fisher method that tests for left-skew results in
-$$
-\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
-$$
-where it now tests for more larger $p$-values than smaller $p$-values across the $k$ number of $p$-values that fall above the threshold $t$.
-When the threshold is set to zero, it selects all $p$-values, but when this $t>0$ the remaining $p$-values are rescaled to fit the original 0-1 range (i.e., by dividing by $1-t$).
-Upon writing this paper, it became clear to us that this reversed Fisher method is similar to the operating principle of Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126], which we had not realized before.
 

### 2018-03-20 submission/redraft.rmd
Add paragraph(s?)

@@
 More specifically, the expected value of a uniform $p$-value distribution is .5, but the fabricated data from our illustration have a mean $p$-value of `r round(mean(ex2_1tp), 3)`.
+
+In order to test whether a distribution of independent $p$-values might be fabricated, we previously proposed using the Fisher method [@fisher1925;@10.1186/s41073-016-0012-9]. 
+The Fisher method originally was intended as a meta-analytic tool, which tests whether there is sufficient evidence for an effect (i.e., right-skewed $p$-value distribution). 
+This test is computed as
+$$
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(p_i)
+$$
+where it tests for more smaller $p$-values than larger $p$-values across the $k$ number of $p$-values. 
+Reversing this results in
+$$
+\chi^2_{2k}=-2\sum\limits^k_{i=1}\ln(1-\frac{p_i-t}{1-t})
+$$
+where it now tests for more larger $p$-values than smaller $p$-values across the $k$ number of $p$-values that fall above the threshold $t$ (i.e., the Fisher method now tests for left-skew). 
+When $t=0$, all $p$-values are selected. 
+When $t>0$ the remaining $p$-values are rescaled to fit the original 0-1 range (i.e., dividing by $1-t$). 
+This test is similar (but not equivalent) to Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].

### 2018-03-26 submission/redraft.rmd
Update before auto-mail

@@
 # Introduction
+
+```{r echo = FALSE}
+m <- 50
+sd <- 10
+n <- 100
+
+set.seed(1234)
+x1_1 <- replicate(n = 10, expr = rnorm(n, m, sd))
+x1_2 <- replicate(n = 10, expr = rnorm(n, m, sd))
+
+ex1_1em <- apply(x1_1, 2, mean)
+ex1_1esd <- apply(x1_1, 2, sd)
+ex1_1cm <- apply(x1_2, 2, mean)
+ex1_1csd <- apply(x1_2, 2, sd)
+ex1_1tp <- NULL
+for (i in 1:dim(x1_1)[2]) ex1_1tp[i] <- t.test(x = x1_1[,i], y = x1_2[,i], var.equal=TRUE)$p.value
+ex1_1tp <- unlist(ex1_1tp)
+
+set.seed(1234)
+x2_1em <- replicate(n = 10, expr = m + runif(1, 0, 20))
+x2_2cm <- replicate(n = 10, expr = m + runif(1, 0, 20))
+x2_1esd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))
+x2_2csd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))
+
+sdpooled <- ((n - 1) * x2_1esd^2 + (n - 1) * x2_2csd^2)/(n * 2 - 2)
+tval <- (x2_1em - x2_2cm) / sdpooled
+ex2_1tp <- pt(abs(tval), n * 2 - 2, lower.tail = FALSE) * 2
+
+# Just saving for later use in theory section
+# set.seed(1234)
+# std_var(n = rep(100, length(x2_1esd) * 2), sds = c(x2_1esd, x2_2csd), iter = 10000)
+
+df <- data.frame(study = sprintf("Study %s", 1:10),
+         sprintf("%s (%s)", round(ex1_1em, 3), round(ex1_1esd, 3)),
+         sprintf("%s (%s)", round(ex1_1cm, 3), round(ex1_1csd, 3)),
+         ex1_1tp,
+         sprintf("%s (%s)", round(x2_1em, 3), round(x2_1esd, 3)),
+         sprintf("%s (%s)", round(x2_2cm, 3), round(x2_2csd, 3)),
+         ex2_1tp)
+names(df) <- c("Study",
+        "$M_E$ ($SD_E$) [S1]",
+        "$M_C$ ($SD_C$) [S1]",
+        "P-value [S1]",
+        "$M_E$ ($SD_E$) [S2]",
+        "$M_C$ ($SD_C$) [S2]",
+        "P-value [S2]")
+```
 

### 2018-03-27 submission/redraft.rmd
Add two paragraphs

@@
 
+```{r table_excess, echo = FALSE}
+knitr::kable(df, digits = 3, caption = "Examples of means and standard deviations for a continuous outcome in genuine- and fabricated randomized clinical trials.
+Set 1 (S1) is randomly generated data under the null hypothesis of random assignment (assumed to be the genuine process), whereas Set 2 (S2) is generated under excessive consistency with equal groups.
+Each trial condition contains 100 participants.
+The $p$-values are the result of independent $t$-tests comparing the experimental and control conditions within each respective set.")
+```
+
 In order to test whether a distribution of independent $p$-values might be fabricated, we previously proposed using the Fisher method [@fisher1925;@10.1186/s41073-016-0012-9]. 
@@
 This test is similar (but not equivalent) to Carlisle's method testing for excessive homogeneity across baseline measurements in RCTs [@10.1111/anae.13938;@10.1111/j.1365-2044.2012.07128.x;@10.1111/anae.13126].
+
+```{r, echo = FALSE}
+threshold <- .05
+genuine_p <- ex1_1tp[ex1_1tp > threshold]
+fab_p <- ex2_1tp[ex2_1tp > threshold]
+genuine_chi <- -2 * sum(log(1 - ((genuine_p - threshold) / (1 - threshold))))
+fab_chi <- -2 * sum(log(1 - ((fab_p - threshold) / (1 - threshold))))
+genuine_chi_p <- pchisq(q = genuine_chi, df = 2 * length(genuine_p), lower.tail = FALSE)
+fab_chi_p <- pchisq(q = fab_chi, df = 2 * length(fab_p), lower.tail = FALSE)
+x <- c(.21, -.08, -.37, -.08, .32)
+pval <- pnorm(abs(x), 0, 1, lower.tail = FALSE) * 2
+pval <- pval[pval > threshold]
+chi <- -2 * sum(log(1 - ((pval - threshold) / (1 - threshold))))
+p_chi <- pchisq(q = chi, df = 2 * length(pval), lower.tail = FALSE)
+```
+
+As an example, we apply the reversed Fisher method to both the genuine- and fabricated results. 
+Using the threshold $t=`r threshold`$ to only select the nonsignificant results from Table xxxx, we retain $k=`r length(genuine_p)`$ genuine $p$-values and $k=`r length(fab_p)`$ fabricated $p$-values.
+This results in $\chi^2_{2\times`r length(genuine_p)`}=`r round(genuine_chi, 3)`,p=`r round(genuine_chi_p, 3)`$ for the genuine data from Table xxxx; $\chi^2_{2\times`r length(fab_p)`}=`r round(fab_chi, 3)`,p=`r round(fab_chi_p, 3)`$ for the fabricated data from Table xxxx.
+Another more practical example directly from the Fuji case [@10.1111/j.1365-2044.2012.07128.x], anecdotally illustrates that actual fabricated data can result in significant findings with the reversed Fisher method.
+For example, $p$-values extracted from the original Table 3 [fentanyl dose; @10.1111/j.1365-2044.2012.07128.x] for five independent comparisons show excessively high $p$-values, $\chi^2_{2\times`r length(pval)`}=`r round(chi, 3)`, p=`r round(p_chi, 3)`$.
+
+We note that misspecified one-tailed tests can also result in excessive amounts of large $p$-values.
+For correctly specified one-tailed tests, the $p$-value distribution is right-skewed if the alternative hypothesis is true. 
+When the alternative hypothesis is true, but the effect is in the opposite direction of the hypothesized effect (e.g., a negative effect when a one-tailed test for a positive effect is conducted), this results in a left-skewed $p$-value distribution.
+As such, any data fabrication detected with this method would need to be inspected for misspecified one-tailed hypotheses to preclude false conclusions. 
+In the studies we present in this manuscript, misspecification of one-tailed hypothesis testing is not an issue because we prespecified the effect and its direction to the participants.

### 2018-03-28 submission/redraft.rmd
Add paragraph

@@
 In the studies we present in this manuscript, misspecification of one-tailed hypothesis testing is not an issue because we prespecified the effect and its direction to the participants.
+
+# Study 1 - detecting fabricated summary statistics
+
+We tested the performance of statistical methods to detect data fabrication in summary statistics with genuine- and fabricated summary statistics from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058].
+The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity.
+For example 'Do you think the percentage of African countries in the UN is above or below  [10\% or 65\%]?  What do you think is the percentage of African countries in the UN?'. 
+These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question. 
+A considerable amount of (assumably) genuine data sets on the anchoring  heuristic are freely available [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and we collected fabricated data sets within this study.
+This study was approved by the Tilburg Ethical Review Board (EC-2015.50).

### 2018-04-03 submission/redraft.rmd
Add paragraph

@@
 This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
+
+## Methods
+
+We collected summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
+Each of the four studies provided us with summary statistics for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. 
+Throughout our study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. 
+For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. 
+All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/tshx8/](https://osf.io/tshx8/).
+Throughout this report, we will indicate which facets were not preregistered or deviate from the preregistration by denoting "(not preregistered)" or "(deviation from preregistration)", respectively.

### 2018-04-03 submission/redraft.rmd
Add paragraph

@@
 
+### Variance analysis
+
+Sample variance- or standard deviation estimates are typically reported to indicate dispersion, but just like the mean there should be sampling error in this estimate proportional to the sample size [i.e., $\sigma/\sqrt{2n}$ under the assumption of normality, p.
+351,@yule1922].
+If an observed random variable $x$ is normally distributed, the variance of $x$ is $\chi^2$-distributed [p. 445; @hogg-tanis]; that is
+$$
+var(x)\sim\frac{\chi^2_{N_j-1}}{N_j-1}
+$$
+where $N$ is the sample size of the $j$th group. 
+Using the reported summary statistics, we can compute the Mean Squares within ($MS_w$) each condition as
+$$
+MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
+$$
+where $s^2_j$ is the variance in the $j$th group. 
+The reported variances can be standardized by dividing the observed variances by the $MS_w$; we denote standardized variances with z^2$.
+
 # Study 1 - detecting fabricated summary statistics

### 2018-04-10 submission/redraft.rmd
Add paragraph

@@
 ---
+
+```{r echo = FALSE}
+source('../functions/digit_analysis.R')
+source('../functions/std_var.R')
+source('../functions/fisher_method.R')
+```
 
@@
 where $s^2_j$ is the variance in the $j$th group. 
-The reported variances can be standardized by dividing the observed variances by the $MS_w$; we denote standardized variances with z^2$.
+The reported variances can be standardized by dividing the observed variances by the $MS_w$; we denote standardized variances with $z^2$.
+
+By standardizing the reported variances observed dispersion across measures can be calculated. 
+Observed dispersion of the standardized variances can be operationalized as the standard deviation of the variances [denoted in this paper as $SD_z$, @10.1177/0956797613480366] or as the range of the variances (denoted as $max-min_z$).
+Note that such comparisons are only meaningful if the reported variances originate from a homogeneous population distribution of variances (otherwise, subgroups need to be made).
+
+In order to compute the expected dispersion, we use the distribution of the standardized variances to compute how extreme the observed dispersion of the variances is. 
+Assuming normality, the distribution of the standardized variances follows a $\chi^2$-distribution in the form of
+$$
+z^2_j\sim\left(\frac{\chi^2_{N_j-1}}{N_j-1}\right)/MS_w
+$$
+which is the result of the distribution of $var(x)$ as denoted earlier, divided by the $MS_w$. 
+From this distribution, fictitious variances can be generated for each group under investigation.
+These are subsequently used to compute one of the measures for dispersion proposed in the previous paragraph (e.g., standard deviation of the variances).
+Repeating this across $i$ iterations provides an estimate of the density function for the expected dispersion of the variances.
+By comparing the observed dispersion of the variances with the expected variances, we can estimate how extreme our observations are.
+For our purposes, too little dispersion in the variances indicates potential fabrication in the reported data [@10.1177/0956797613480366].
+
+```{r, echo = FALSE}
+sd1 <- c(ex1_1esd, ex1_1csd)
+sd2 <- c(x2_1esd, x2_2csd)
+
+iterate <- 10000
+res1 <- std_var(n = rep(100, length(sd1)), sds = sd1, iter = iterate)
+res2 <- std_var(n = rep(100, length(sd2)), sds = sd2, iter = iterate)
+```
+
+As an example, we apply the variance analysis to the illustration from Table xxxx and the Smeesters case. 
+For the reported standard deviations in Table xxxx, we apply the variance analysis across those in the genuine- and fabricated sets separately. 
+For the genuine data (Set 1), we find that the reported mean standard deviation is `r mean(sd1)` with a standard deviation of `r sd(sd1)`; for the fabricated data (Set 2), we find that the reported mean standard deviation is `r mean(sd2)` with a standard deviation of `r sd(sd2)`.
+These summary statistics of the summary statistics already indicate there is a difference between the genuine- and fabricated data.
+Variance analysis helps us quantify this: Set 1 has no excessive consistency (`r round(res1, 3)`), whereas Set 2 does show excessive consistency (`r round(res2, 3)`). 
+In words, out of `r iterate` theoretically expected samples, `r res1 * iterate` showed more consistency for Set 1, whereas only `r res2 * iterate` showed more consistency for Set 2. 
+As a non-fictional example, three independent conditions from the same study ($n_k=15$) were reported to have standard deviations 25.09, 24.58, and 25.65 in the Smeesters case. 
+The standard deviation of these standard deviations is `r round(sd(c(25.09, 24.58, 25.65)), 2)` (i.e., $SD_z$). 
+Such consistency (or even more) would only be observed in `r round(std_var(n = rep(15, 3), sds = c(25.09, 24.58, 25.65), iter = iterate) * 100, 2)`% of 100,000 simulated replications [@10.1177/0956797613480366].
 
@@
 Throughout this report, we will indicate which facets were not preregistered or deviate from the preregistration by denoting "(not preregistered)" or "(deviation from preregistration)", respectively.
+
+# References

### 2018-04-11 submission/redraft.rmd
Add paragraph

@@
 
+### Data collection
+
+We downloaded thirty-six genuine data sets from the publicly available Many Labs (ML) project [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178]. 
+The ML project replicated several effects across thirty-six locations, including the anchoring effect in the four studies mentioned previously. 
+Considering the size of the ML project, the transparency of research results, and minimal individual gain for fabricating data, we assumed these data to be genuine. 
+For each of the thirty-six locations we computed three summary statistics (i.e., sample sizes, means, and standard deviations) for each of the four conditions in the four anchoring studies (i.e., $3\times4\times4$) for each of the thirty-six locations.
+We computed these summary statistics from the raw ML data, which were cleaned using the original analysis scripts from the ML project.
+
 # References

### 2018-04-12 submission/redraft.rmd
Add paragraph

@@
 
+The sampling frame consisted of 2,038 psychology researchers who published a peer-reviewed paper in 2015, as indexed in Web of Science (WoS) with the filter set to the U.S. 
+We sampled psychology researchers to improve familiarity with the anchoring effect [@10.1126/science.185.4157.1124;@10.1037/e722982011-058], for which summary statistics were fabricated. 
+We filtered for U.S.
+researchers to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies and in order to reduce heterogeneity across fabricators.
+We searched WoS on October 13, 2015. In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).
+
 # References

### 2018-04-25 submission/redraft.rmd
Add five paragraphs

@@
 source('../functions/fisher_method.R')
+
+tabnr <- 1
+fignr <- 1
 ```
@@
 
+### Effect sizes
+
+Large effects have previously been opted to arise from dubious origins [@10.1111/j.1745-6924.2009.01128.x], but there is sufficient evidence that large effects arise from data fabrication. 
+For example, in the misconduct investigations in the Stapel case, effect sizes were one particular indicator of data fabrication in certain papers [@Levelt2012]. 
+Some papers showed extreme explained variances of up to 95%. 
+Moreover, @10.1186/1471-2288-3-18 asked faculty members from three universities to fabricate data sets and found that the fabricated data showed much larger effect sizes than the genuine data. 
+From our own anecdotal experience, we have found that large effect sizes raised initial suspicions of data fabrication (e.g., $d>20$). 
+In clinical trials, extreme effect sizes are also used to identify potentially fabricated data in multi-site trials while the study is still being conducted [@10.1016/0197-24569190037-M].
+
+```{r, echo = FALSE}
+tval <- 3.55
+df <- 59
+```
+
+Effect sizes can be reported in research reports in various ways. 
+For example, the most commons ways effect sizes are reported in papers are as a standardized mean difference (e.g., $d$), as an explained variance (e.g., $R^2$), or as a test statistic. 
+A test statistic is also a measure of effect size, albeit in a not directly interpretable form. 
+A test result such as $t(
+`r df`)=`r tval`$ corresponds to $d=`r round(2*tval / sqrt(df), 3)` and $r=`r round((tval^2 / df) / ((tval^2 / df) + 1), 3)` [@10.1525/collabra.71]. 
+These effect sizes can readily be recomputed based on data extracted with `statcheck` across thousands of results [@10.3758/s13428-015-0664-2;@10.3390/data1030014].
+
+Observed effect sizes can subsequently be compared with the effect distribution of other studies investigating the same effect. 
+For example, if a study on the 'foot-in-the-door' technique yields an effect size of $r=.8$, we can collect other studies that investigate the 'foot-in-the-door' effect and compare how extreme that $r=.8$ is in comparison to the other studies.
+If the largest observed effect size in the literature is $r=.2$ and a reasonable number of studies on the 'foot-in-the-door' effect have been done, this can be considered extreme and a flag for potential data fabrication.
+This method specifically looks at situations where fabricators would want to fabricate the existence of an effect (not the absence of one).
+
+Collecting the effect distribution to compare with requires some attention, however. 
+Considering published research is biased towards statistically significant results [e.g., @10.1007/bf01173636] and results in inflated effect sizes [@10.1037/gpr0000034], effect distributions from published literature will tend to be conservative in detecting potential extreme effects due to data fabrication.
+Unbiased effect size distributions for an effect can be collected from large-scale replication projects, such as Registered Replication Reports [e.g., @10.1177/1745691616664694].
+
 # Study 1 - detecting fabricated summary statistics
@@
 
+From these 2,038 psychology researchers, we e-mailed a random sample of 1,000 researchers to participate in this study (April 25, 2016; [osf.io/s4w8r](https://osf.io/s4w8r)). 
+We used Qualtrics and removed identifying information not essential to the study (e.g., no IP-addresses saved). 
+We informed the participating researchers that the study would require them to fabricate data and explicitly mentioned that we would investigate these data with statistical methods to detect data fabrication.
+We also clarified to the respondents that they could stop at any time without providing a reason. 
+If they wanted, respondents received a $30 Amazon gift card as compensation for their participation if they were willing to enter their email address. 
+They could win an additional $50 Amazon gift card if they were one of three top fabricators (how we determined this is explained in the Data Analysis section). 
+The provided e-mail addresses were unlinked from individual responses upon sending the bonus gift cards. 
+The full text of the Qualtrics survey is available at [osf.io/w984b](https://osf.io/w984b).
+
+Each respondent was instructed to fabricate 32 summary statistics (4 studies $\times$ 2 conditions $\times$ 2 sexes $\times$ 2 statistics [mean and sd]) that corresponded to three hypotheses. 
+We instructed respondents to fabricate results for the following hypotheses: there is (i) a positive main effect of the anchoring condition, (ii) no effect of sex, and (iii) no interaction effect between condition and sex.
+We fixed the sample sizes to 25 per cell; respondents did not need to fabricate sample sizes. 
+These fabricated summary statistics and their accompanying test results for these three hypotheses serve as the data to examine the properties of statistical tools to detect data fabrication.
+
+We provided respondents with a template spreadsheet to fill out the fabricated data, in order to standardize the fabrication process without restraining the participant in how they chose to fabricate data.
+Figure `r fignr` depicts an example of this spreadsheet (original: [https://osf.io/w6v4u](https://osf.io/w6v4u)). 
+We requested respondents to fill in the yellow cells with fabricated data, which includes means and the standard deviations for four conditions. 
+Using these values, statistical tests are computed and shown in the "Current result" column instantaneously. 
+If these results confirmed the hypotheses, a checkmark appeared as depicted in Figure `r fignr`. 
+We required respondents to copy-paste the yellow cells into Qualtrics, to provide a standardized response format that could be automatically processed in the analyses. 
+Technically, participants could provide a response that did not correspond to the instructions.
+
+```{r spreadsheet-study1, fig.cap="Example of a filled in template spreadsheet used in the fabrication process of Study 1.
+Respondents fabricated data in the yellow cells, which were used to compute the results of the hypothesis tests.
+If the fabricated data confirm the hypotheses, a checkmark appeared in a green cell (one of four template spreadsheets available at [https://osf.io/w6v4u/](https://osf.io/w6v4u/)).", out.width='100%', echo=FALSE}
+knitr::include_graphics('../figures/spreadsheet.png')
+
+fignr <- fignr + 1
+```
+
+Upon completion of the data fabrication, we debriefed respondents within the Qualtrics environment ([osf.io/rg3qc/](https://osf.io/rg3qc/)). 
+Respondents answered several questions about their statistical knowledge and approach to data fabrication and finally we reminded them that data fabrication is widely condemned by professional organizations, institutions, and funding agencies alike.
+This reminder was intended to minimize potential carry-over effects of the unethical behavior into actual research practice [@10.1509/jmkr.45.6.633]. 
+We rewarded participation with a \$30 Amazon gift card and the fabricated results that were most difficult to detect received a bonus \$50 Amazon gift card. 
+Using quotum sampling, we collected as many responses as possible for the available 36 rewards, resulting in 39 fabricated data sets ([https://osf.io/e6zys](https://osf.io/e6zys); `r sum(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus))` participants did not participate for a bonus).
+
+% We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.
+
+### Data analysis
+
+We analyzed the genuine- and fabricated data sets for the four anchoring studies in four ways. 
+First, we applied the reversed Fisher method to the results of the gender and interaction hypotheses (i.e., nonsignificant results) across the four studies. 
+Second, we applied variance analysis to the reported variances of each of the four groups per study separately. 
+Third, and not preregistered, we used the effect size to detect fabricated data based on the premise that fabricated effects would be larger. 
+Fourth, we combined the results from the reversed Fisher method and variance analyses, using the original Fisher method [@fisher1925].
+
+Specifically for the variance analyses, we deviated from the preregistration. 
+Initially, we simultaneously analyzed the reported variances per study across the anchoring conditions. 
+However, upon analyzing these values, we realized that the variance analyses assume that the reported variances are from the same population distribution, which is not necessarily the case for the anchoring conditions.
+Hence, we included two variance analyses per anchoring study, splitting the conditions into more homogeneous subsets (i.e., one subset across genders for the high anchoring condition and one across the genders for the low anchoring condition).
+In the results we differentiate between these by using 'homogeneous' (across conditions) and 'heterogeneous' (separated for low- and high anchoring conditions).
+
+## Results
+
+## Discussion
+
+# Study 2 - detecting fabricated raw data
+
+## Methods
+
+## Results
+
+## Discussion
+
+# General discussion
+
 # References

### 2018-04-26 submission/redraft.rmd
Add paragraph

@@
 This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
+<!-- link to approval -->
 
@@
 
-We collected summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
+We collected genuine- and fabricated summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058].
 Each of the four studies provided us with summary statistics for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. 
@@
 
-% We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.
+<!-- % We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.  -->
 
@@
 In the results we differentiate between these by using 'homogeneous' (across conditions) and 'heterogeneous' (separated for low- and high anchoring conditions).
+
+For each of these statistical tests to detect data fabrication we carried out sensitivity and specificity analyses using Area Under Receiving Operator Characteristic (AUROC) curves. 
+AUROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$). 
+AUROC values indicate the probability that a randomly drawn fabricated- and genuine dataset can be correctly classified as fabricated and genuine [@10.1148/radiology.143.1.7063747]. 
+In other words, if $AUROC=.5$, correctly classifying a randomly drawn dataset as fabricated (or genuine) in this sample is equal to 50%. 
+For this setting, we follow the guidelines of @10.1093/jpepsy/jst062 and regard any AUROC value $<.7$ as poor for detecting data fabrication, $.7\leq$ AUROC $<.8$ as fair, $.8\leq$ AUROC $<.9$ as good, and AUROC $\geq.9$ as excellent.
+We conducted these analyses using the `PROC` package [@10.1186/1471-2105-12-77].
 

### 2018-05-03 submission/redraft.rmd
Add paragraphs

@@
 ```{r echo = FALSE}
+library(ggplot2)
+
 source('../functions/digit_analysis.R')
@@
 source('../functions/fisher_method.R')
+
+ml_file <- '../data/study_01/ml_summary_stats.csv'
+qualtrics_file <- '../data/study_01/qualtrics_processed.csv'
+dat_summary_file <- '../data/study_01/study1_res.csv'
+file <- '../data/study_01/raw_summary_results_fabrication_qualtrics.csv'
+res_file <- '../data/study_01/qualtrics_processed.csv'
+ml_dat_file <- '../data/study_01/anchoring_ml/chjh ml1_anchoring cleaned.sav'
+summary_stat_file <- '../data/study_01/ml_summary_stats.csv'
+ml3_dat_file <- '../data/study_02/study_02-ml3_stroop/StroopCleanSet.csv'
+pdf_file <- '../archive/gender_interaction.pdf'
+
+# Set the number of iterations to use in calculations
+iter <- 100000
 
@@
 A test result such as $t(
-`r df`)=`r tval`$ corresponds to $d=`r round(2*tval / sqrt(df), 3)` and $r=`r round((tval^2 / df) / ((tval^2 / df) + 1), 3)` [@10.1525/collabra.71]. 
+`r df`)=`r tval`$ corresponds to d=`r round(2*tval / sqrt(df), 3)` and r=`r round((tval^2 / df) / ((tval^2 / df) + 1), 3)` [@10.1525/collabra.71]. 
 These effect sizes can readily be recomputed based on data extracted with `statcheck` across thousands of results [@10.3758/s13428-015-0664-2;@10.3390/data1030014].
@@
 Unbiased effect size distributions for an effect can be collected from large-scale replication projects, such as Registered Replication Reports [e.g., @10.1177/1745691616664694].
+
+## Detecting data fabrication in raw data
 
@@
 ## Methods
+
+```{r prep study 1, echo=FALSE}
+# Compute the summary statistics for Many Labs
+suppressWarnings(suppressMessages(source('../functions/compute_summary_anch_ml.R')))
+# Process the collected, fabricated data
+suppressMessages(source('../functions/process_qualtrics_anch_01.R'))
+# Concatenate, analyze, and write out all ML and qualtrics data
+if(!file.exists('../data/study_01/study1_res.csv'))
+{
+ set.seed(123);suppressMessages(source('../functions/concatenate_analyze_01.R')) 
+}
+
+dat_summary <- read.csv(dat_summary_file)
+
+type_index <- which(names(dat_summary) == 'type')
+temp <- dat_summary[, c(type_index, 18:length(names(dat_summary)))] 
+dat_summary$es_gender <- sqrt(dat_summary$es2_gender)
+dat_summary$es_condition <- sqrt(dat_summary$es2_condition)
+dat_summary$es_interaction <- sqrt(dat_summary$es2_interaction)
+
+# naming just for ease of use later
+dat_summary$es_p <- 1 - dat_summary$es_condition
+
+# ROC
+AUC <- apply(dat_summary[, grepl(names(dat_summary), pattern = "_p")],
+   2,
+   function(x)
+   {
+    y <- pROC::roc(response = dat_summary$type, x, direction = ">")
+    return(y)
+   }
+)
+```
 
@@
 
+Figure `r fignr` shows a group-level comparison of the genuine- and fabricated $p$-values and relevant effect sizes ($r$). 
+These group-level comparisons provide an overview of the differences between the genuine- and fabricated data [see also @10.1186/1471-2288-3-18]. 
+These distributions indicate little group differences between genuine- and fabricated data when nonsignificant effects are inspected (i.e., gender and interaction hypotheses). 
+However, there seem to be large group differences when we required subjects to fabricate significant summary statistics (i.e., condition hypothesis).
+
+```{r ddfab_density, fig.cap="Overlay of density distributions for both genuine and fabricated data, per effect and type of result.
+We instructed respondents to fabricate nonsignificant summary statistics for the gender and interaction effects, and a significant effect for the condition effect.", out.width='100%', echo=FALSE}
+plot_p_gender <- ggplot(dat_summary, aes(x = p_gender, fill = type)) + 
+ geom_density(alpha = .3) + 
+ xlab(latex2exp::TeX("$P$-value")) + 
+ ylab("Density") + 
+ ylim(0, 1.5) + 
+ scale_fill_discrete(guide=FALSE) + 
+ ggtitle('Gender')
+
+plot_es_gender <- ggplot(dat_summary, aes(x = es_gender, fill = type)) + 
+ geom_density(alpha = .3) + 
+ xlab(latex2exp::TeX("Effect size ($r$)")) + 
+ ylab("Density") + 
+ scale_fill_discrete(guide=FALSE)
+
+# Condition
+dat_summary_tmp <- dat_summary
+dat_summary_tmp$p_condition <- log10(dat_summary_tmp$p_condition)
+plot_p_condition <- ggplot(dat_summary_tmp, aes(x = p_condition, fill = type)) +
+ geom_density(alpha = .3) +
+ xlab(latex2exp::TeX("log10 $P$-value")) +
+ ylab("Density") +
+ scale_fill_discrete(labels = c("Genuine","Fabricated")) + 
+ theme(legend.position="top") +
+ ggtitle('Condition')
+
+plot_p_condition$labels$fill <- ""
+
+plot_es_condition <- ggplot(dat_summary, aes(x = es_condition, fill = type)) + 
+ geom_density(alpha = .3) + 
+ xlim(0, 1) + 
+ xlab(latex2exp::TeX("Effect size ($r$)")) + 
+ ylab("Density") + 
+ scale_fill_discrete(guide=FALSE)
+
+# Interaction
+plot_p_interaction <- ggplot(dat_summary, aes(x = p_interaction, fill = type)) + 
+ geom_density(alpha = .3) + 
+ xlab(latex2exp::TeX("$P$-value")) + 
+ ylab("Density") + 
+ scale_fill_discrete(guide=FALSE) +
+ ylim(0, 1.5) +
+ ggtitle('Interaction')
+
+plot_es_interaction <- ggplot(dat_summary, aes(x = es_interaction, fill = type)) + 
+ geom_density(alpha = .3) + 
+ xlab(latex2exp::TeX("Effect size ($r$)")) + 
+ ylab("Density") + 
+ scale_fill_discrete(guide=FALSE)
+
+# Plot
+gridExtra::grid.arrange(plot_p_gender,
+       plot_p_condition,
+       plot_p_interaction,
+       plot_es_gender,
+       plot_es_condition,
+       plot_es_interaction,
+       ncol = 3)
+
+fignr <- fignr + 1
+```
+
+### P-value analysis
+
+Using nonsignificant $p$-values to detect data fabrication is hardly better than chance level in the current sample. 
+We asked researchers to fabricate data for nonsignificant effect sizes across four anchoring studies, thinking they might be unable to produce uniformly distributed $p$-values due to misunderstanding of what a $p$-value means [@;@].
+<!-- add p-value interpretation from ej, sijtsma p value paper -->
+Our results indicate that the $p$-values for the gender effect and interaction effect perform only slightly above chance level for detecting fabricated data, $AUROC=`r round(AUC$gender_fish_p$auc[1], 3)`$ and $AUROC=`r round(AUC$interaction_fish_p$auc[1], 3)`$, respectively.
+In other words, widespread detection based on nonsignificant $p$-values does not seem promising.
+
+### Variance analysis
+
+```{r echo = FALSE}
+selector <- grepl(names(AUC), pattern = '(variance_|maxmin_)')
+selector_sd <- grepl(names(AUC), pattern = '(variance_)')
+selector_maxmin <- grepl(names(AUC), pattern = '(maxmin_)')
+```
+
+We performed a total of `r sum(selector)` variance analyses across the fabricated standard deviations for the four anchoring studies, with `r sum(selector_sd)` using the $SD_z$ measure and `r sum(selector_maxmin)` using the $max-min_z$ measure.
+More specifically, we analyzed the standard deviations across all studies combined (assuming homogeneity across conditions), across all studies (assuming heterogeneity across anchoring conditions), within each study, and within each anchoring condition.
+We computed the AUROC value with the directional assumption that genuine data would show more variation than fabricated data.
+Results are presented in Table `r tabnr`.
+
+```{r table_variance, echo = FALSE}
+dfvar <- data.frame(Method = c("Homogeneous, all studies combined",
+                "Homogeneous, study 1",
+                "Homogeneous, study 2",
+                "Homogeneous, study 3",
+                "Homogeneous, study 4",
+                "Heterogeneous, all studies combined",
+                "Heterogeneous study 1, low anchor condition",
+                "Heterogeneous study 1, high anchor condition",
+                "Heterogeneous study 2, low anchor condition",
+                "Heterogeneous study 2, high anchor condition",
+                "Heterogeneous study 3, low anchor condition",
+                "Heterogeneous study 3, high anchor condition",
+                "Heterogeneous study 4, low anchor condition",
+                "Heterogeneous study 4, high anchor condition"),
+          SD_z = c(
+            AUC$variance_sd_p_overall_homo$auc,
+            AUC$variance_sd_p_study1$auc,
+            AUC$variance_sd_p_study2$auc,
+            AUC$variance_sd_p_study3$auc,
+            AUC$variance_sd_p_study4$auc,
+            AUC$variance_sd_p_overall_hetero$auc,
+            AUC$variance_sd_p_study1_low$auc,
+            AUC$variance_sd_p_study1_high$auc,
+            AUC$variance_sd_p_study2_low$auc,
+            AUC$variance_sd_p_study2_high$auc,
+            AUC$variance_sd_p_study3_low$auc,
+            AUC$variance_sd_p_study3_high$auc,
+            AUC$variance_sd_p_study4_low$auc,
+            AUC$variance_sd_p_study4_high$auc
+            ),
+          max_min_z = c(
+            AUC$maxmin_p_overall_homo$auc,
+            AUC$maxmin_p_study1$auc,
+            AUC$maxmin_p_study2$auc,
+            AUC$maxmin_p_study3$auc,
+            AUC$maxmin_p_study4$auc,
+            AUC$maxmin_p_overall_hetero$auc,
+            AUC$maxmin_p_study1_low$auc,
+            AUC$maxmin_p_study1_high$auc,
+            AUC$maxmin_p_study2_low$auc,
+            AUC$maxmin_p_study2_high$auc,
+            AUC$maxmin_p_study3_low$auc,
+            AUC$maxmin_p_study3_high$auc,
+            AUC$maxmin_p_study4_low$auc,
+            AUC$maxmin_p_study4_high$auc
+            ))
+
+names(dfvar) <- c('Method', 'AUROC $SD_z$', 'AUROC $max-min_z$')
+knitr::kable(dfvar, row.names = FALSE, digits = 3, caption = "_Table XX._ Diagnosticity of using variance analyses to detect data fabrication, depicted with the AUROC-value.
+We assumed fabricated results would show ")
+tabnr <- tabnr + 1
+```
+
+Results indicate that (1) heterogeneity of population variances directly affect the effectiveness of detecting data fabrication, (2) the different operationalizations of variance analyses show minimal differences, and (3) that the combined analysis of standard deviations across anchoring conditions in the four studies is a preferred method.
+When comparing the combined variance analyses, we see that the homogeneity assumption drastically decreases the performance ($SD_z$; homogeneity: $AUROC=`r round(AUC$variance_sd_p_overall_homo$auc, 3))`$, heterogeneity: AUROC=`r round(AUC$variance_sd_p_overall_hetero$auc, 3))`).
+This assumption has not previously been explicated [@] and we also did not preregister analyses that took into account this assumption. 
+Moreover, the maximum absolute difference between the $SD_z$ and $max-min_z$ operationalizations is `r round(max(abs(dfvar$SD_z - dfvar$max_min_z)), 3)` and there is no reason to deviate from the original $SD_z$ operationalization as proposed by @.
+Lastly, we see that variance analyses separated per study or anchoring condition within a study are quite variable, which suggests that the combined analysis is preferred because selecting a priori selection of a specific subset is unfeasible in practice.
+
+### Effect sizes
+
+By simply comparing effect sizes of the main anchoring effect, results indicate that this is a parsiminious and effective way of detecting data fabrication.
+More specifically, given a genuine- and fabricated anchoring effect size, there is approximately a 75% chance that the larger effect size is the fabricated one (i.e., $AUROC=`r round(AUC$es_p$auc, 3)`$).
+Comparing this to the best performing variance analysis (i.e., $AUROC=`r round(AUC$variance_sd_p_overall_hetero$auc, 3)`$), performance is similar but considerably easier in practice.
+
+### Combination of p-value and variance analysis
+
 ## Discussion
@@
 
+### Digit analysis
+
+#### Newcomb-Benford Law
+
+#### Terminal digit analysis
+
+#### Multivariate associations
+
 ## Discussion
